### 2019-02-20 Paper/paper.tex
paper src

\documentclass[format=acmlarge, review=true, authordraft=true]{acmart}

%% scheme-list :
\usepackage{listings}
\usepackage{color}
\usepackage{textcomp}

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true
}
%% scheme-list .

% metadata

\title{BFS search in miniKanren}
\author{Kuang-Chen Lu}
\affiliation{Indiana University}
\author{Weixi Ma}
\affiliation{Indiana University}
\author{Daniel P. Friedman}
\affiliation{Indiana University}

%%% NOTE %%%
%
% - how to write scheme code
%
%   scheme-listing on GitHub
%   * use escapte to go back to latex world
%
% - plan paper writing
%   
%   * Abstract
%   * send to Dan
%   * Core Content
%     * how stream is implemented in TRS2's miniKanren
%     * how to do BFS search
%
% - how long does it usually take from drafting to submission
%
% - when is the deadline
%
%   last year submission deadline July 23, 2018
%
%%%%%%%%%%%%

% body
\begin{document}

\begin{abstract}

% background
% Translating Scheme programs to miniKanren programs is mostly mechanical. However,
% translation of cond deserves some attention, because conde generally prioritizes its left 
% clauses. For example, in a four-clauses conde expression, the first clause is searched 8 
% times more frequently than the last one.

The syntax of a programming language should reflect its semantics.
When using a disjunction operator in relational programming, a programmer would
expect all clauses of this disjunction to share the same chance of being explored,
as these clauses are written in parallel. The existing disjunctive operators in miniKanren,
however, prioritize their clauses by the order of which these clauses are written down.
% solution
We have devised a new search strategy that searches evenly in all clauses.
% evaluation
Based on our statistics, miniKanren slows down by a constant factor after applying our search strategy. (tested with very-recursiveo, need more tests)

\end{abstract}

\maketitle

\section{introduction}

OUTLINE:

( About miniKanren )

( Why the left clauses are explored more frequently? )

( How to solve the problem? )

( Summary of later sections )

\section{cost of answers}

%TODO the meaning of resolution step in Silvija Seres's paper
%TODO REPLize comment

The \emph{cost} of an answer is the number of relation applications needed to find the answer. We use the miniKanren program, \texttt{repeato}, in Fig.~\ref{repeato-1} to demonstrate the cost of answers. We borrow this idea from Silvija Seres's work [*]. \texttt{repeato} relates \texttt{x} with a list whose elements are all \texttt{x}s. The run expression uses \texttt{repeato} to generate 4 lists whose elements are all \texttt{*}s. The order of the answers reflects the order miniKanren discovers them. The leftmost answer is discovered first. The order here is not suprising: to generate the answer \texttt{'()}, miniKanren needs to apply \texttt{repeato} only once. And it needs more applications of \texttt{repeato} to find the later answers that are more complicated.

\begin{figure}
  \lstinputlisting{Code/repeat.rkt}
  \caption{\texttt{repeato}}
  \label{repeato-1}
\end{figure}

%TODO relation *application*
%TODO split figure 2 into 2 figures
%TODO define iDFS = interleaving DFS in Introduction
%TODO (define "cost-repsecting" "in order of increasing cost")
In the  example above, the cost of each answer is the same as one more than the number of \texttt{*}s. No answer of zero cost exists. For this \texttt{run}, both search strategies produces answers in increasing order of costs. In more complicated cases, however, interleaving DFS does not always produces answers of lower costs first. For instance, the \texttt{run} in Fig.~\ref{repeato-2} uses the iDFS strategy to produce answers in a seemingly random order. The answers listed by iDFS are a blend of three kinds, i.e., lists of \texttt{a}s, lists of \texttt{b}s, and lists of \texttt{c}s. The answers of this \texttt{run} is not cost-respecting, although each kind of answer is cost-respecting.

%TODO lafalf

However, the blended answers tends to include more answers from the first conde line, i.e. from (repeato 'a q). In general, iDFS prioritizes the left conde clauses.

\begin{figure}
	\lstinputlisting{Code/repeat-abc.rkt}
	\caption{\texttt{repeato}}
	\label{repeato-2}
\end{figure}

\section{change search strategy}

Now we change the search strategy and optimize the system in three steps. The result of these steps are mk-1, mk-2, and mk-3 respectively. The initial miniKanren is named mk-0, which is the miniKanren in TRS2.

\subsection{representation of search space}

In mk-0, search space is represented by streams. Streams can be finite or infinite. Finite streams are just lists. And infinite streams are improper lists, whose last cdr is a procedure which takes no arguments and returns a stream when involked. Cars of streams are (possibly incomplete) answers. We call the cars the mature part, and the last cdr the immature part.

(connect stream with cost)

\subsection{initial version}

(explain mk-0's append-inf)

\lstinputlisting{Code/append-inf-trs2.rkt}

To make the search BFS, we just need to have append-inf combines mature parts in the fashion of append, and combine non-empty immature parts by contructing a new procedure.

\lstinputlisting{Code/append-inf-bfs-loop.rkt}

\subsection{stepstone of optimization}

Make irrelevant parts in mK representation-independent w.r.t. search space, and combine mature part and immature part with cons.

\subsection{optimization}

The goal is to express BFS explicitly with queue, so that we don’t have to generate all answers of the same cost at once.

Interesting changes: (1) put thunks in a list; (2) change force-inf (introduced in 4.B) so that it can make progress in all thunks (3) use a queue to manage thunks in take-inf.

\section{conclusion}

\section*{acknowledgments}

\section*{references}

\end{document}

### 2019-02-20 Paper/paper.tex
improve sec2

@@
 %
-% - how to write scheme code
-%
-%   scheme-listing on GitHub
-%   * use escapte to go back to latex world
-%
 % - plan paper writing
@@
 %     * how to do BFS search
-%
-% - how long does it usually take from drafting to submission
 %
@@
 
-% background
-% Translating Scheme programs to miniKanren programs is mostly mechanical. However,
-% translation of cond deserves some attention, because conde generally prioritizes its left 
-% clauses. For example, in a four-clauses conde expression, the first clause is searched 8 
-% times more frequently than the last one.
-
 The syntax of a programming language should reflect its semantics.
@@
 however, prioritize their clauses by the order of which these clauses are written down.
-% solution
 We have devised a new search strategy that searches evenly in all clauses.
-% evaluation
-Based on our statistics, miniKanren slows down by a constant factor after applying our search strategy. (tested with very-recursiveo, need more tests)
+Based on our statistics, miniKanren slows down by a constant factor after applying our search strategy.
+(tested with very-recursiveo, need more tests)
 
@@
 
+%TODO define iDFS = interleaving DFS in Introduction
+
 ( How to solve the problem? )
@@
 %TODO the meaning of resolution step in Silvija Seres's paper
-%TODO REPLize comment
 
 The \emph{cost} of an answer is the number of relation applications needed to find the answer.
-We use the miniKanren program, \texttt{repeato}, in Fig.~\ref{repeato-1} to demonstrate the cost of answers.
+We use the miniKanren relation \texttt{repeato} in Fig.~\ref{def-repeato} to demonstrate the cost of answers.
 We borrow this idea from Silvija Seres's work [*].
@@
 And it needs more applications of \texttt{repeato} to find the later answers that are more complicated.
+In this example, the cost of each answer is the same as one more than the number of \texttt{*}s.
+No answer of zero cost exists.
 
 \begin{figure}
-  \lstinputlisting{Code/repeat.rkt}
+  \lstinputlisting{Figures/defrel-repeato.rkt}
+  \lstinputlisting{Figures/run-repeato-1.rkt}
   \caption{\texttt{repeato}}
-  \label{repeato-1}
+  \label{def-repeato}
 \end{figure}
@@
 %TODO relation *application*
-%TODO split figure 2 into 2 figures
-%TODO define iDFS = interleaving DFS in Introduction
-%TODO (define "cost-repsecting" "in order of increasing cost")
-In the  example above, the cost of each answer is the same as one more than the number of \texttt{*}s.
-No answer of zero cost exists.
-For this \texttt{run}, both search strategies produces answers in increasing order of costs.
-In more complicated cases, however, interleaving DFS does not always produces answers of lower costs first.
-For instance, the \texttt{run} in Fig.~\ref{repeato-2} uses the iDFS strategy to produce answers in a seemingly random order.
-The answers listed by iDFS are a blend of three kinds, i.e., lists of \texttt{a}s, lists of \texttt{b}s, and lists of \texttt{c}s.
-The answers of this \texttt{run} is not cost-respecting, although each kind of answer is cost-respecting.
 
-%TODO lafalf
-
-However, the blended answers tends to include more answers from the first conde line, i.e. from (repeato 'a q). In general, iDFS prioritizes the left conde clauses.
+For the above \texttt{run}, both search strategies produces answers in increasing order of costs, i.e.
+both of them are \emph{cost-respecting}.
+In more complicated cases, however, interleaving DFS does not always produces answers in cost-repecting order.
+For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces answers in a seemingly random order.
+In contrast, the same run with BFS produces answers in an expected order (Fig.~\ref{conde-repeato-BFS}).
 
 \begin{figure}
-	\lstinputlisting{Code/repeat-abc.rkt}
-	\caption{\texttt{repeato}}
-	\label{repeato-2}
+	\lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
+	\caption{run a program with interleaving depth-first search}
+	\label{conde-repeato-iDFS}
 \end{figure}
+
+\begin{figure}
+	\lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+	\caption{run a program with breadth-first search}
+	\label{conde-repeato-BFS}
+\end{figure}
+
+Although all answers by iDFS is not in cost-respecting order, the answers from each case are in cost-respecting order.
+The problem is that iDFS strategy prioritizes the first \texttt{conde} case considerablely.
+In general, when every conde case are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case, which share the same portion as the second last.
 
@@
 
-\lstinputlisting{Code/append-inf-trs2.rkt}
+\lstinputlisting{Figures/append-inf-trs2.rkt}
 
@@
 
-\lstinputlisting{Code/append-inf-bfs-loop.rkt}
+\lstinputlisting{Figures/append-inf-bfs-loop.rkt}
 

### 2019-02-21 Paper/paper.tex
mk-0 -> mk-1

@@
 
-Now we change the search strategy and optimize the system in three steps.
-The result of these steps are mk-1, mk-2, and mk-3 respectively.
-The initial miniKanren is named mk-0, which is the miniKanren in TRS2.
+Now we change the search strategy and optimize the system.
+The whole process is completed in three steps, corresponding to 4 versions of miniKanren.
+The initial version, \texttt{mk-0} is exactly the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
 
-\subsection{representation of search space}
+\subsection{from \texttt{mk-0} to \texttt{mk-1}}
 
-In mk-0, search space is represented by streams.
+In mk-0, search spaces are represented by streams of answers.
 Streams can be finite or infinite.
 Finite streams are just lists.
-And infinite streams are improper lists, whose last cdr is a procedure which takes no arguments and returns a stream when involked.
-Cars of streams are (possibly incomplete) answers.
-We call the cars the mature part, and the last cdr the immature part.
+And infinite streams are improper lists, whose last \texttt{cdr} is a thunk returning another stream.
+We call the \texttt{car}s the \emph{mature} part, and the last \texttt{cdr} the \emph{immature} part.
 
-(connect stream with cost)
-
-\subsection{initial version}
+Streams are cost respective when they are initially constructed by \texttt{==}.
+However, \texttt{append-inf}, a composer of stream, breaks cost respectiveness.
+By changing its definition, we can make the whole search strategy cost respective.
 
@@
 
-\lstinputlisting{Figures/append-inf-trs2.rkt}
+\begin{figure}
+	 \lstinputlisting{Figures/append-inf-0.rkt}	
+	 \caption{\texttt{append-inf} in \texttt{mk-0}}
+	 \label{append-inf-0}
+\end{figure}
 
-To make the search BFS, we just need to have append-inf combines mature parts in the fashion of append, and combine non-empty immature parts by contructing a new procedure.
-
-\lstinputlisting{Figures/append-inf-bfs-loop.rkt}
+\begin{figure}
+	 \lstinputlisting{Figures/append-inf-1.rkt}	
+	 \caption{\texttt{append-inf} in \texttt{mk-1}}
+	 \label{append-inf-1}
+\end{figure}
 

### 2019-02-28 Paper/paper.tex
update

@@
 The \emph{cost} of an answer is the number of relation applications needed to find the answer.
-We use the miniKanren relation \texttt{repeato} in Fig.~\ref{def-repeato} to demonstrate the cost of answers.
+We use the miniKanren relation \texttt{repeato} in Fig.~\ref{def-repeato} to demonstrate the concept.
 We borrow this idea from Silvija Seres's work [*].
-\texttt{repeato} relates \texttt{x} with a list whose elements are all \texttt{x}s.
-The run expression uses \texttt{repeato} to generate 4 lists whose elements are all \texttt{*}s.
+\texttt{repeato} relates a term \texttt{x} with a list whose elements are all \texttt{x}s.
+The \texttt{run} expression uses \texttt{repeato} to generate 4 lists whose elements are all \texttt{*}s.
 The order of the answers reflects the order miniKanren discovers them.
@@
 The whole process is completed in three steps, corresponding to 4 versions of miniKanren.
-The initial version, \texttt{mk-0} is exactly the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
+The initial version, \texttt{mk-0}, is exactly the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
 
@@
 
-In mk-0, search spaces are represented by streams of answers.
+In \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by streams of answers.
 Streams can be finite or infinite.
@@
 Streams are cost respective when they are initially constructed by \texttt{==}.
-However, \texttt{append-inf}, a composer of stream, breaks cost respectiveness.
-By changing its definition, we can make the whole search strategy cost respective.
-
-(explain mk-0's append-inf)
+However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}), a composer of stream, can break cost respectiveness.
+when its first argument, \texttt{s-inf} is infinite.
+The resulting mature part contains only the mature part of \texttt{s-inf}.
+The whole \texttt{t-inf} goes to the resulting immature part -- the newly constructed thunk.
 
@@
 
+The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) restores cost-respectiveness by combining the mature parts in the fashion of \texttt{append}.
+\texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver.
+Two streams are swapped in the third \texttt{cond} clause, where \texttt{s?} is also changed accordingly.
+
 \begin{figure}
@@
 
+\texttt{mk-1} is not efficient in two aspects.
+\texttt{append-inf} need to copy all \texttt{cons} cells of two input stream when the first one is infinite.
+Besides, \texttt{mk-1} generates answers of the same cost at once, even when only a small portion is queried.
+We solves the two problems in the next two subsections.
+
 \subsection{stepstone of optimization}
+
+(eqv to Seres's BFS ?)
 

### 2019-03-02 Paper/paper.tex
tuning

@@
 
-The \emph{cost} of an answer is the number of relation applications needed to find the answer.
-We use the miniKanren relation \texttt{repeato} in Fig.~\ref{def-repeato} to demonstrate the concept.
-We borrow this idea from Silvija Seres's work [*].
-\texttt{repeato} relates a term \texttt{x} with a list whose elements are all \texttt{x}s.
-The \texttt{run} expression uses \texttt{repeato} to generate 4 lists whose elements are all \texttt{*}s.
-The order of the answers reflects the order miniKanren discovers them.
-The leftmost answer is discovered first.
-The order here is not suprising: to generate the answer \texttt{'()}, miniKanren needs to apply \texttt{repeato} only once.
-And it needs more applications of \texttt{repeato} to find the later answers that are more complicated.
-In this example, the cost of each answer is the same as one more than the number of \texttt{*}s.
-No answer of zero cost exists.
+The \emph{cost} of an answer is the number of relation applications needed to
+find the answer. This idea is borrowed from Silvija Seres's work [*].
+Now we illustrate the costs of answers by running a miniKanren relation.
+Fig.~\ref{def-repeato} defines the relation \texttt{repeato} that 
+relates a term \texttt{x} with a list whose elements are all \texttt{x}s.
 
@@
   \lstinputlisting{Figures/defrel-repeato.rkt}
-  \lstinputlisting{Figures/run-repeato-1.rkt}
   \caption{\texttt{repeato}}
@@
 \end{figure}
+
+Consider the following \texttt{run} of \texttt{repeato}.
+\begin{center}
+  \begin{tabular}{c}
+  \lstinputlisting{Figures/run-repeato-1.rkt}
+   \end{tabular}
+\end{center}
+
+The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
+The order of the answers reflects the order miniKanren discovers them:
+the leftmost answer is the first one. This result is not suprising:
+to generate the first answer, \texttt{'()}, miniKanren needs to apply
+\texttt{repeato} only once and the later answers need more recursive
+applications. In this example, the cost of each answer is the same as
+one more than the number of \texttt{*}s. The cost of \texttt{'()} is 1,
+the cost of \texttt{'(*)} is 2, etc.
+
+A list of answer is in the \emph{cost-respecting} order if no answer occurs
+before another answer of a lower cost. In the above example, the answers are
+cost-respecting. The iDFS search, however, does not generate cost-respecting
+answers in general. As an example, consider the following \texttt{run} of
+\texttt{repeato}.
+\begin{center}
+  \begin{tabular}{c}
+   \lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
+   \end{tabular}
+\end{center}
+
+The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
+\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
+The problem is that iDFS strategy prioritizes the first \texttt{conde} case
+considerablely. In general, when every conde case are equally productive, the iDFS
+strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
+which share the same portion as the second last.
 
@@
 
-\begin{figure}
-	\lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
-	\caption{run a program with interleaving depth-first search}
-	\label{conde-repeato-iDFS}
-\end{figure}
-
-\begin{figure}
 \lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
-	\caption{run a program with breadth-first search}
-	\label{conde-repeato-BFS}
-\end{figure}
-
-Although all answers by iDFS is not in cost-respecting order, the answers from each case are in cost-respecting order.
-The problem is that iDFS strategy prioritizes the first \texttt{conde} case considerablely.
-In general, when every conde case are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case, which share the same portion as the second last.
 

### 2019-03-06 Paper/paper.tex
update

@@
 %
-% - plan paper writing
+% - deadline?
 %
-%   * Abstract
-%   * send to Dan
-%   * Core Content
-%     * how stream is implemented in TRS2's miniKanren
-%     * how to do BFS search
-%
-% - when is the deadline
-%
-%   last year submission deadline July 23, 2018
+%   last year submission deadline May 15, 2018
 %
@@
 both of them are \emph{cost-respecting}.
-In more complicated cases, however, interleaving DFS does not always produces answers in cost-repecting order.
+In more complicated cases, however, interleaving DFS might not produce answers in cost-repecting order.
 For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces answers in a seemingly random order.
@@
 Streams are cost respective when they are initially constructed by \texttt{==}.
-However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}), a composer of stream, can break cost respectiveness.
-when its first argument, \texttt{s-inf} is infinite.
+However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness when its first argument, \texttt{s-inf}, is infinite.
 The resulting mature part contains only the mature part of \texttt{s-inf}.
-The whole \texttt{t-inf} goes to the resulting immature part -- the newly constructed thunk.
+The whole \texttt{t-inf} goes to the resulting immature part.
 
@@
 The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) restores cost-respectiveness by combining the mature parts in the fashion of \texttt{append}.
-\texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver.
+This \texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver.
 Two streams are swapped in the third \texttt{cond} clause, where \texttt{s?} is also changed accordingly.
@@
 
-The goal is to express BFS explicitly with queue, so that we don’t have to generate all answers of the same cost at once.
+The goal is to express BFS explicitly with queue, so that the system doesn't generate all answers of the same cost at once.
 

### 2019-03-06 Paper/paper.tex
descript mk-2

@@
 
+miniKanren is a relational programming language embedable in many languages[cite
+miniKanren.org?].
+
+The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
+an efficient and complete search strategy -- interleaving depth-first search (iDFS).
+iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
+organize their conde lines carefully. We proposed two search strategies and their
+implementations. The first strategy is breadth-first search. The second one is a
+modified iDFS.
+
 OUTLINE:
@@
 applications. In this example, the cost of each answer is the same as
-one more than the number of \texttt{*}s. The cost of \texttt{'()} is 1,
-the cost of \texttt{'(*)} is 2, etc.
+one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
+the cost of \texttt{'(*)} is 2, and so on.
 
@@
 
-For the above \texttt{run}, both search strategies produces answers in increasing order of costs, i.e.
-both of them are \emph{cost-respecting}.
-In more complicated cases, however, interleaving DFS might not produce answers in cost-repecting order.
-For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces answers in a seemingly random order.
-In contrast, the same run with BFS produces answers in an expected order (Fig.~\ref{conde-repeato-BFS}).
+For the above \texttt{run}, both search strategies produces answers in increasing
+order of costs, i.e. both of them are \emph{cost-respecting}. In more complicated
+cases, however, interleaving DFS might not produce answers in cost-repecting order.
+For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces
+answers in a seemingly random order. In contrast, the same run with BFS produces
+answers in an expected order (Fig.~\ref{conde-repeato-BFS}).
 
@@
 
-(eqv to Seres's BFS ?)
+In \texttt{mk-2} we set up an interface between streams and the rest of miniKanren,
+so that the optimization in \texttt{mk-3} is easier to present. As a side-effect, we
+also solve the problem of copying too many \texttt{cons} cells. We list all interface functions in Fig.~\ref{interface-functions}.
 
-Make irrelevant parts in mK representation-independent w.r.t. search space, and combine mature part and immature part with cons.
+\begin{figure}
+
+\begin{tabular}{|c|c|}
+\hline 
+interface function & meaning \\ 
+\hline 
+empty-inf & construct an empty stream \\ 
+\hline 
+unit-mature-inf & construct a stream with one answer \\ 
+\hline 
+unit-immature-stream & construct a stream with one thunk \\ 
+\hline 
+null-inf? & predicate whether a stream is empty \\ 
+\hline 
+mature-inf? & predicate whether a stream has some mature answers \\ 
+\hline 
+car-inf & take the first answer out of a mature stream \\ 
+\hline 
+cdr-inf & remove the first answer of a mature stream \\ 
+\hline 
+force-inf & get answers of higher cost \\ 
+\hline
+\end{tabular}
+	 \caption{interface functions and their meanings in mk-2 and mk-3}
+	 \label{interface-functions}
+\end{figure}
+
+The representation of stream in \texttt{mk-2} is a pair of mature part and immature part. The mature parts are lists of answers. And the immature part is either a thunk or \texttt{'()}.
+
+Changes in \texttt{mk-2} are mostly about setting up the interface, except the change in \texttt{append-inf} (Fig.~\ref{append-inf-2}).
+This version of \texttt{mk-2} essentially does the same thing as the \texttt{mk-1} version.
+
+\begin{figure}
+	 \lstinputlisting{Figures/append-inf-2.rkt}	
+	 \caption{\texttt{append-inf} in \texttt{mk-2}}
+	 \label{append-inf-2}
+\end{figure}
 

### 2019-03-13 Paper/paper.tex
remove timer
complete description of BFS

--- 2019-03-06 Paper/paper.tex
@@
 %
-%   last year submission deadline May 15, 2018
+%   miniKanren workshop deadline May 15, 2018
 %
@@
 \section{introduction}
+
+miniKanren is a relational programming language embedable in many languages[cite
+miniKanren.org?].
+
+The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
+an efficient and complete search strategy -- interleaving depth-first search (iDFS).
+iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
+organize their conde lines carefully. We proposed two search strategies and their
+implementations. The first strategy is breadth-first search. The second one is a
+modified iDFS.
 
@@
 strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
-which share the same portion as the second last.
+which share the same portion as the second last one.
 
@@
 
-\section{change search strategy}
+\section{breadth-first search}
 
-Now we change the search strategy and optimize the system.
-The whole process is completed in three steps, corresponding to 4 versions of miniKanren.
-The initial version, \texttt{mk-0}, is exactly the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
+In this section we change the search strategy to breadth-first search and optimize it.
+The whole process is completed in three steps, corresponding to 3 versions of miniKanren.
+We start with, \texttt{mk-0}, the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
 
@@
 \texttt{mk-1} is not efficient in two aspects.
-\texttt{append-inf} need to copy all \texttt{cons} cells of two input stream when the first one is infinite.
-Besides, \texttt{mk-1} generates answers of the same cost at once, even when only a small portion is queried.
-We solves the two problems in the next two subsections.
+\texttt{append-inf} need to copy all \texttt{cons} cells of two input streams when the first stream has a non-trivial immature part.
+Besides, \texttt{mk-1} computes answers of the same cost at once, even when only a portion is queried.
+We solves the two problems in the next subsections.
 
-\subsection{stepstone of optimization}
+\subsection{\texttt{mk-3}, optimized breadth-first search}
 
-(eqv to Seres's BFS ?)
+We avoid generating same-cost answers at once by expressing BFS with a queue.
+The elements of the queue are delayed computation, represented by thunks.
+Every \texttt{mk-1} stream has zero or one thunk, so we have no interesting way to manage it.
+Therefore we change the representation of immature parts from thunks to lists of thunks.
+As as consequence, we also change the way to combine mature and immature part from \texttt{append} to \texttt{cons}.
 
-Make irrelevant parts in mK representation-independent w.r.t. search space, and combine mature part and immature part with cons.
+After applying this two changes, stream representation becomes more complicated.
+It motivates us to set up an interface between stream functions and the rest of miniKanren.
+Listed in Fig.~\ref{interface} are all functions being aware of the stream representation, but \texttt{take-inf} and its helper function, which is explained later.
+The first three functions are constructors: \texttt{empty-inf} constructs an empty stream; \texttt{unit-mature-inf} constructs a stream with one mature solution; \texttt{unit-immature-inf} constructs a stream with one thunk.
+The \texttt{append-inf} in \texttt{mk-3} is relatively straightforwared compared with the \texttt{mk-1} version.
+\texttt{append-map-inf} is more tricky on how to construct the new immature part.
+We can follow the approach in mk-0 and mk-1 -- create a new thunk which invoke append-map-inf recursively when forced.
+But then we need to be careful: if we construct the thunk when the old immature part is an empty list, the resulting stream might be infinitely unproductive.
+Beside, all solutions of the next lowest cost in \texttt{s-inf} must be computed when the thunk is invoked.
+However sometimes only a portion of these solutions is required to answer a query.
+To avoid the trouble and the advanced computation, we choose to create a new thunk for every existing thunk.
+The next four functions are used only by \texttt{ifte} and \texttt{once}.
+Uninterested readers might skip them.
+\texttt{null-inf?} checks whether a stream is exausted.
+\texttt{mature-inf?} checks whether a stream has some mature solutions.
+\texttt{car-inf} takes the first solution out of a mature stream.
+\texttt{cdr-inf} drops the first solution of a mature stream.
+Finally, \texttt{force-inf} forces an a immature stream to do more computation.
 
-\subsection{optimization}
+\begin{figure}
+	 \lstinputlisting{Figures/interface.rkt}	
+	 \caption{Functions being aware of stream representation}
+	 \label{interface}
+\end{figure}
 
-The goal is to express BFS explicitly with queue, so that the system doesn't generate all answers of the same cost at once.
+The last interesting function is \texttt{take-inf} (Fig.~\ref{take-inf-3-1}).
+The parameter \texttt{vs} is a list of solutions.
+The next two parameters together represents a functional queue in a typical way.
+The first two \texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1.
+The third line runs when we exaust all solutions.
+The forth line re-shape the queue.
+The fifth and last line invoke the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
 
-Interesting changes: (1) put thunks in a list; (2) change force-inf (introduced in 4.B) so that it can make progress in all thunks (3) use a queue to manage thunks in take-inf.
+\begin{figure}
+	 \lstinputlisting{Figures/take-inf-3-1.rkt}	
+	 \caption{\texttt{take-inf} in \texttt{mk-3-1}}
+	 \label{take-inf-3-1}
+\end{figure}
 

### 2019-03-15 Paper/paper.tex
tuning

@@
 The order of the answers reflects the order miniKanren discovers them:
-the leftmost answer is the first one. This result is not suprising:
+the first answer in the list is first discovered. This result is not suprising:
 to generate the first answer, \texttt{'()}, miniKanren needs to apply
@@
 \texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
-The problem is that iDFS strategy prioritizes the first \texttt{conde} case
-considerablely. In general, when every conde case are equally productive, the iDFS
+iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
+considerablely. When every conde case are equally productive, the iDFS
 strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,

### 2019-03-16 Paper/paper.tex
balanced-iDFS

--- 2019-03-13 Paper/paper.tex
@@
 expect all clauses of this disjunction to share the same chance of being explored,
-as these clauses are written in parallel. The existing disjunctive operators in miniKanren,
-however, prioritize their clauses by the order of which these clauses are written down.
-We have devised a new search strategy that searches evenly in all clauses.
-Based on our statistics, miniKanren slows down by a constant factor after applying our search strategy.
+as these clauses are written in parallel. The existing disjunctive operators in
+miniKanren, however, prioritize their clauses by the order of which these clauses are
+written down. We have devised a new search strategy that searches evenly in all
+clauses. Based on our statistics, miniKanren slows down by a constant factor after
+applying our search strategy.
 (tested with very-recursiveo, need more tests)
+
+%TODO update "result" once having more test cases: quine, '(I love you).
 
@@
 
-miniKanren is a relational programming language embedable in many languages[cite
-miniKanren.org?].
+The best way to write a miniKanren program can depend on the search strategy.
+For example, with inteleaving depth-first search (iDFS), users sometimes need to order their conde clauses carefully to avoid starving later clauses.
+This is because iDFS spends half of computation effort on the first clause, a quater on the second, and so on.
+Seasoned miniKanreners usually know how to make use of this bias to optimize their programs.
+However, we believe search strategies less sensitive to conde clause order can also be useful.
+We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and answer order of some known miniKanren programs.
+The experiment is conducted within the miniKanren in \textit{The Reasoned Schemer, 2nd Edition}.
 
-The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
-an efficient and complete search strategy -- interleaving depth-first search (iDFS).
-iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
-organize their conde lines carefully. We proposed two search strategies and their
-implementations. The first strategy is breadth-first search. The second one is a
-modified iDFS.
+%TODO use microKanren instead?
 
-OUTLINE:
+%The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
+%an efficient and complete search strategy -- interleaving depth-first search (iDFS).
+%iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
+%organize their conde lines carefully. We propose and implement two search strategies,
+%breadth-first search (BFS) and balanced interleaving DFS (biDFS). With either of these
+%search strategy, miniKanren becomes less sensitive to the order of conde lines.
 
-( About miniKanren )
+Section 2 explains why iDFS biases toward left conde clauses. Section 2 is about the biDFS. Section 3 is about BFS.
 
-( Why the left clauses are explored more frequently? )
+\section{why iDFS put more effort computing left clauses}
 
-%TODO define iDFS = interleaving DFS in Introduction
+\texttt{conde} clauses are combined by \texttt{disj2}, right associatively.
+The core functionality of \texttt{disj2} is completed by \texttt{append-inf} (Fig.~\ref{disj2-and-append-inf}).
+When both input streams are infinite, the resulting mature part contains only the mature part of \texttt{s-inf}.
+The whole \texttt{t-inf} goes to the resulting immature part.
+However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed recursive call.
+Hence the search strategy spend computational effort evenly in two appended streams.
+As \texttt{disj2} is right associative, the left clauses are nested in less calls to \texttt{append-inf}, which implies that they are more likeyly being computed.
 
-( How to solve the problem? )
+\begin{figure}
+  \lstinputlisting{Figures/disj2.rkt}
+  \caption{\texttt{disj2} and \texttt{append-inf}}
+  \label{disj2-and-append-inf}
+\end{figure}
 
-( Summary of later sections )
+\section{balanced interleaving DFS}
 
-\section{cost of answers}
+A \texttt{conde} expression looks like a binary tree, if we consider \texttt{disj2}s as internal nodes and \texttt{conde} clauses as a terminal nodes.
+In fact, each of them is one of the most unbalanced binary trees.
+The basic idea of our first solution, balanced interleaving DFS, is to make the tree balanced.
+We introduce a function \texttt{disj*} and its helper \texttt{split} (Fig.~\ref{disj*}).
+\texttt{disj*} essentially construct a balanced \texttt{disj2} tree.
+\texttt{split} splits elements of \texttt{ls} into two even half and pass them to the continuation parameter \texttt{k}.
+
+\begin{figure}
+  \lstinputlisting{Figures/disj*.rkt}
+  \caption{\texttt{disj*}}
+  \label{disj*}
+\end{figure}
+
+\section{breadth-first search}
+
+In this section we change the search strategy to breadth-first search and optimize it.
+The whole process is completed in two steps.
+In the first step, from mk-0 to mk-1, BFS is introduced.
+In the second step, mk-1 to mk-3, BFS is optimized.
+The initial version, \texttt{mk-0}, is exactly the version in \emph{The Reasoned Schemer, 2nd Edition}.
+
+\subsection{cost of answers}
 
@@
 
-\section{breadth-first search}
-
-In this section we change the search strategy to breadth-first search and optimize it.
-The whole process is completed in three steps, corresponding to 3 versions of miniKanren.
-We start with, \texttt{mk-0}, the miniKanren in \emph{The Reasoned Schemer, 2nd Edition}.
-
 \subsection{from \texttt{mk-0} to \texttt{mk-1}}
@@
 Streams are cost respective when they are initially constructed by \texttt{==}.
-However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness when its first argument, \texttt{s-inf}, is infinite.
+However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness if its first input stream, \texttt{s-inf}, is infinite.
 The resulting mature part contains only the mature part of \texttt{s-inf}.
@@
 This \texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver.
-Two streams are swapped in the third \texttt{cond} clause, where \texttt{s?} is also changed accordingly.
+Two streams are swapped in the third \texttt{cond} clause, with \texttt{s?} flipped accordingly.
 

### 2019-03-17 Paper/paper.tex
update abstract

@@
 
-\title{BFS search in miniKanren}
+\title{miniKanren with fair search}
 \author{Kuang-Chen Lu}
@@
 expect all clauses of this disjunction to share the same chance of being explored,
-as these clauses are written in parallel. The existing disjunctive operators in
-miniKanren, however, prioritize their clauses by the order of which these clauses are
-written down. We have devised a new search strategy that searches evenly in all
-clauses. Based on our statistics, miniKanren slows down by a constant factor after
-applying our search strategy.
-(tested with very-recursiveo, need more tests)
+as these clauses are written in parallel. 
+% The existing disjunctive operators in miniKanren, however, prioritize their clauses
+The existing multiarity disjunctive operator in miniKanren, however, prioritize its clauses
+by the order of which these clauses are written down. 
+% We have devised a new search strategy that searches evenly in all clauses.
+We have devised two new search strategies that allocate computational effort fairly in all clauses.
 
-%TODO update "result" once having more test cases: quine, '(I love you).
+(TODO: evaluation of performance)
+
+%TODO test cases: quine, '(I love you).
 

### 2019-03-17 Paper/paper.tex
tuning Introduction

@@
 
-The best way to write a miniKanren program can depend on the search strategy.
-For example, with inteleaving depth-first search (iDFS), users sometimes need to order their conde clauses carefully to avoid starving later clauses.
-This is because iDFS spends half of computation effort on the first clause, a quater on the second, and so on.
-Seasoned miniKanreners usually know how to make use of this bias to optimize their programs.
-However, we believe search strategies less sensitive to conde clause order can also be useful.
-We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and answer order of some known miniKanren programs.
-The experiment is conducted within the miniKanren in \textit{The Reasoned Schemer, 2nd Edition}.
+With interleaving depth-first search, disjunctive operator allocates half computational effort to its first goal, and quater to the second, eighth to the third, and so on.
+Consequently, miniKanren programmers sometimes need to order their \texttt{conde} clauses carefully to prevent some clauses absorbing unproportional computational effort.
+For example, when a relational proof checker is used as a proof generator, the eliminational rules should comes later.
+%TODO KC: prefer an example from other literatures 
+Seasoned miniKanreners usually know how to make use of this unfair allocation to optimize their programs.
+However, we believe search strategies less sensitive to goal order can also be useful to little miniKanreners as well as seansoned ones.
+We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and query result of known miniKanren programs.
+The experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
 
-%TODO use microKanren instead?
+%TODO KC: Should we use microKanren instead?
 
@@
 %an efficient and complete search strategy -- interleaving depth-first search (iDFS).
-%iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
-%organize their conde lines carefully. We propose and implement two search strategies,
+%iDFS biases toward left \texttt{conde} lines. So miniKanren programmers sometimes need to
+%organize their \texttt{conde} lines carefully. We propose and implement two search strategies,
 %breadth-first search (BFS) and balanced interleaving DFS (biDFS). With either of these
-%search strategy, miniKanren becomes less sensitive to the order of conde lines.
+%search strategy, miniKanren becomes less sensitive to the order of \texttt{conde} lines.
 
-Section 2 explains why iDFS biases toward left conde clauses. Section 2 is about the biDFS. Section 3 is about BFS.
+(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 3 is about BFS.
 
@@
 iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
-considerablely. When every conde case are equally productive, the iDFS
+considerablely. When every \texttt{conde} case are equally productive, the iDFS
 strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,

### 2019-03-22 Paper/paper.tex
80ch per line

@@
 
-The syntax of a programming language should reflect its semantics.
-When using a disjunction operator in relational programming, a programmer would
-expect all clauses of this disjunction to share the same chance of being explored,
-as these clauses are written in parallel. 
-% The existing disjunctive operators in miniKanren, however, prioritize their clauses
-The existing multiarity disjunctive operator in miniKanren, however, prioritize its clauses
-by the order of which these clauses are written down. 
-% We have devised a new search strategy that searches evenly in all clauses.
-We have devised two new search strategies that allocate computational effort fairly in all clauses.
+The syntax of a programming language should reflect its semantics. When using a
+disjunction operator in relational programming, a programmer would expect all
+clauses of this disjunction to share the same chance of being explored, as
+these clauses are written in parallel. The existing multiarity disjunctive
+operator in miniKanren, however, prioritize its clauses by the order of which
+these clauses are written down. We have devised two new search strategies that
+allocate computational effort fairly in all clauses.
 
@@
 %TODO test cases: quine, '(I love you).
+
+%TODO 1. reformat LaTeX (80 chars per line)
+%TODO 2. stat quine
+%TODO 3. keep writing
 
@@
 
-With interleaving depth-first search, disjunctive operator allocates half computational effort to its first goal, and quater to the second, eighth to the third, and so on.
-Consequently, miniKanren programmers sometimes need to order their \texttt{conde} clauses carefully to prevent some clauses absorbing unproportional computational effort.
-For example, when a relational proof checker is used as a proof generator, the eliminational rules should comes later.
+With interleaving depth-first search, disjunctive operator allocates half
+computational effort to its first goal, and quater to the second, eighth to the
+third, and so on. If a goal that can generate planty of unwanted partial 
+solutions is placed at the beginning of a \texttt{conde} expressions, it might
+waste a lot computational resource. Consequently, miniKanren programmers 
+sometimes need to order their \texttt{conde} clauses carefully to prevent some 
+clauses absorbing unproportional computational effort. For example, when a 
+relational proof checker is used as a proof generator, the eliminational rules 
+should comes later.
 %TODO KC: prefer an example from other literatures
-Seasoned miniKanreners usually know how to make use of this unfair allocation to optimize their programs.
-However, we believe search strategies less sensitive to goal order can also be useful to little miniKanreners as well as seansoned ones.
-We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and query result of known miniKanren programs.
-The experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
+Seasoned miniKanreners usually know how to utilize the unfairness to optimize
+their programs. However, we believe search strategies less sensitive to goal
+order can also be useful to little miniKanreners as well as seansoned ones. We 
+propose two such search strategies, balanced interleaving DFS (biDFS) and
+breadth-first search (BFS), and observe how they affect the efficiency and
+query result of known miniKanren programs. The experiment is conducted with the
+miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
 
@@
 
-(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 3 is about BFS.
+(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is about BFS.
 
@@
 
-\texttt{conde} clauses are combined by \texttt{disj2}, right associatively.
-The core functionality of \texttt{disj2} is completed by \texttt{append-inf} (Fig.~\ref{disj2-and-append-inf}).
-When both input streams are infinite, the resulting mature part contains only the mature part of \texttt{s-inf}.
-The whole \texttt{t-inf} goes to the resulting immature part.
-However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed recursive call.
-Hence the search strategy spend computational effort evenly in two appended streams.
-As \texttt{disj2} is right associative, the left clauses are nested in less calls to \texttt{append-inf}, which implies that they are more likeyly being computed.
+\texttt{conde} clauses are combined by \texttt{disj2}, right associatively. The
+core functionality of \texttt{disj2} is completed by \texttt{append-inf} (Fig.~
+ref{disj2-and-append-inf}). When both input streams are infinite, the resulting
+mature part contains only the mature part of \texttt{s-inf}. The whole
+\texttt{t-inf} goes to the resulting immature part. However, \texttt{t-inf} and
+\texttt{s-inf} are swapped in the delayed recursive call. Hence the search
+strategy spend computational effort evenly in two appended streams. As
+\texttt{disj2} is right associative, the left clauses are nested in less calls
+to \texttt{append-inf}, which implies that they are more likeyly being
+computed.
 
@@
 
-A \texttt{conde} expression looks like a binary tree, if we consider \texttt{disj2}s as internal nodes and \texttt{conde} clauses as a terminal nodes.
-In fact, each of them is one of the most unbalanced binary trees.
-The basic idea of our first solution, balanced interleaving DFS, is to make the tree balanced.
-We introduce a function \texttt{disj*} and its helper \texttt{split} (Fig.~\ref{disj*}).
-\texttt{disj*} essentially construct a balanced \texttt{disj2} tree.
-\texttt{split} splits elements of \texttt{ls} into two even half and pass them to the continuation parameter \texttt{k}.
+A \texttt{conde} expression looks like a binary tree, if we consider 
+\texttt{disj2}s as internal nodes and \texttt{conde} clauses as a terminal 
+nodes. In fact, each of them is one of the most unbalanced binary trees. The 
+basic idea of our first solution, balanced interleaving DFS, is to make the 
+tree balanced. We introduce a function \texttt{disj*} and its helper 
+\texttt{split} (Fig.~\ref{disj*}). \texttt{disj*} essentially construct a 
+balanced \texttt{disj2} tree. \texttt{split} splits elements of \texttt{ls} 
+into two even half and pass them to the continuation parameter \texttt{k}.
 
@@
 
-In this section we change the search strategy to breadth-first search and optimize it.
-The whole process is completed in two steps.
-In the first step, from mk-0 to mk-1, BFS is introduced.
-In the second step, mk-1 to mk-3, BFS is optimized.
-The initial version, \texttt{mk-0}, is exactly the version in \emph{The Reasoned Schemer, 2nd Edition}.
+In this section we change the search strategy to breadth-first search and 
+optimize it. The whole process is completed in two steps. In the first step, 
+from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, BFS is 
+optimized. The initial version, \texttt{mk-0}, is exactly the version in 
+\emph{The Reasoned Schemer, 2nd Edition}.
 
@@
 
-For the above \texttt{run}, both search strategies produces answers in increasing
-order of costs, i.e. both of them are \emph{cost-respecting}. In more complicated
-cases, however, interleaving DFS might not produce answers in cost-repecting order.
-For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces
-answers in a seemingly random order. In contrast, the same run with BFS produces
-answers in an expected order (Fig.~\ref{conde-repeato-BFS}).
+For the above \texttt{run}, both search strategies produces answers in 
+increasing order of costs, i.e. both of them are \emph{cost-respecting}. In 
+more complicated cases, however, interleaving DFS might not produce answers in 
+cost-repecting order. For instance, with iDFS the \texttt{run} in Fig.~
+\ref{conde-repeato-iDFS} produces answers in a seemingly random order. In 
+contrast, the same run with BFS produces answers in an expected order (Fig.~
+\ref{conde-repeato-BFS}).
 
@@
 
-In \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by streams of answers.
-Streams can be finite or infinite.
-Finite streams are just lists.
-And infinite streams are improper lists, whose last \texttt{cdr} is a thunk returning another stream.
-We call the \texttt{car}s the \emph{mature} part, and the last \texttt{cdr} the \emph{immature} part.
+In \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by streams of 
+answers. Streams can be finite or infinite. Finite streams are just lists. And 
+infinite streams are improper lists, whose last \texttt{cdr} is a thunk 
+returning another stream. We call the \texttt{car}s the \emph{mature} part, and 
+the last \texttt{cdr} the \emph{immature} part.
 
 Streams are cost respective when they are initially constructed by \texttt{==}. 
-However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness if its first input stream, \texttt{s-inf}, is infinite.
-The resulting mature part contains only the mature part of \texttt{s-inf}.
-The whole \texttt{t-inf} goes to the resulting immature part.
+However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-
+inf-0}) breaks cost respectiveness if its first input stream, \texttt{s-inf}, 
+is infinite. The resulting mature part contains only the mature part of 
+\texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part.
 
@@
 
-The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) restores cost-respectiveness by combining the mature parts in the fashion of \texttt{append}.
-This \texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver.
-Two streams are swapped in the third \texttt{cond} clause, with \texttt{s?} flipped accordingly.
+The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) 
+restores cost-respectiveness by combining the mature parts in the fashion of 
+\texttt{append}. This \texttt{append-inf} calls its helper immediately, with 
+the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-
+inf} in the helper is the \texttt{s-inf} in the driver. Two streams are swapped 
+in the third \texttt{cond} clause, with \texttt{s?} flipped accordingly.
 
@@
 
-\texttt{mk-1} is not efficient in two aspects.
-\texttt{append-inf} need to copy all \texttt{cons} cells of two input streams when the first stream has a non-trivial immature part.
-Besides, \texttt{mk-1} computes answers of the same cost at once, even when only a portion is queried.
-We solves the two problems in the next subsections.
+\texttt{mk-1} is not efficient in two aspects. \texttt{append-inf} need to copy 
+all \texttt{cons} cells of two input streams when the first stream has a non-
+trivial immature part. Besides, \texttt{mk-1} computes answers of the same cost 
+at once, even when only a portion is queried. We solves the two problems in the 
+next subsections.
 
@@
 We avoid generating same-cost answers at once by expressing BFS with a queue. 
-The elements of the queue are delayed computation, represented by thunks.
-Every \texttt{mk-1} stream has zero or one thunk, so we have no interesting way to manage it.
-Therefore we change the representation of immature parts from thunks to lists of thunks.
-As as consequence, we also change the way to combine mature and immature part from \texttt{append} to \texttt{cons}.
+The elements of the queue are delayed computation, represented by thunks. Every 
+\texttt{mk-1} stream has zero or one thunk, so we have no interesting way to 
+manage it. Therefore we change the representation of immature parts from thunks 
+to lists of thunks. As as consequence, we also change the way to combine mature 
+and immature part from \texttt{append} to \texttt{cons}.
 
-After applying this two changes, stream representation becomes more complicated.
-It motivates us to set up an interface between stream functions and the rest of miniKanren.
-Listed in Fig.~\ref{interface} are all functions being aware of the stream representation, but \texttt{take-inf} and its helper function, which is explained later.
-The first three functions are constructors: \texttt{empty-inf} constructs an empty stream; \texttt{unit-mature-inf} constructs a stream with one mature solution; \texttt{unit-immature-inf} constructs a stream with one thunk.
-The \texttt{append-inf} in \texttt{mk-3} is relatively straightforwared compared with the \texttt{mk-1} version.
-\texttt{append-map-inf} is more tricky on how to construct the new immature part.
-We can follow the approach in mk-0 and mk-1 -- create a new thunk which invoke append-map-inf recursively when forced.
-But then we need to be careful: if we construct the thunk when the old immature part is an empty list, the resulting stream might be infinitely unproductive.
-Beside, all solutions of the next lowest cost in \texttt{s-inf} must be computed when the thunk is invoked.
-However sometimes only a portion of these solutions is required to answer a query.
-To avoid the trouble and the advanced computation, we choose to create a new thunk for every existing thunk.
-The next four functions are used only by \texttt{ifte} and \texttt{once}.
-Uninterested readers might skip them.
-\texttt{null-inf?} checks whether a stream is exausted.
-\texttt{mature-inf?} checks whether a stream has some mature solutions.
-\texttt{car-inf} takes the first solution out of a mature stream.
-\texttt{cdr-inf} drops the first solution of a mature stream.
-Finally, \texttt{force-inf} forces an a immature stream to do more computation.
+After applying this two changes, stream representation becomes more 
+complicated. It motivates us to set up an interface between stream functions 
+and the rest of miniKanren. Listed in Fig.~\ref{interface} are all functions 
+being aware of the stream representation, but \texttt{take-inf} and its helper 
+function, which is explained later. The first three functions are constructors: 
+\texttt{empty-inf} constructs an empty stream; \texttt{unit-mature-inf} 
+constructs a stream with one mature solution; \texttt{unit-immature-inf} 
+constructs a stream with one thunk. The \texttt{append-inf} in \texttt{mk-3} is 
+relatively straightforwared compared with the \texttt{mk-1} version. 
+\texttt{append-map-inf} is more tricky on how to construct the new immature 
+part. We can follow the approach in mk-0 and mk-1 -- create a new thunk which 
+invoke append-map-inf recursively when forced. But then we need to be careful: 
+if we construct the thunk when the old immature part is an empty list, the 
+resulting stream might be infinitely unproductive. Beside, all solutions of the 
+next lowest cost in \texttt{s-inf} must be computed when the thunk is invoked. 
+However sometimes only a portion of these solutions is required to answer a 
+query. To avoid the trouble and the advanced computation, we choose to create a 
+new thunk for every existing thunk. The next four functions are used only by 
+\texttt{ifte} and \texttt{once}. Uninterested readers might skip them. 
+\texttt{null-inf?} checks whether a stream is exausted. \texttt{mature-inf?} 
+checks whether a stream has some mature solutions. \texttt{car-inf} takes the 
+first solution out of a mature stream. \texttt{cdr-inf} drops the first 
+solution of a mature stream. Finally, \texttt{force-inf} forces an a immature 
+stream to do more computation.
 
@@
 The last interesting function is \texttt{take-inf} (Fig.~\ref{take-inf-3-1}). 
-The parameter \texttt{vs} is a list of solutions.
-The next two parameters together represents a functional queue in a typical way.
-The first two \texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1.
-The third line runs when we exaust all solutions.
-The forth line re-shape the queue.
-The fifth and last line invoke the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
+The parameter \texttt{vs} is a list of solutions. The next two parameters, 
+\texttt{P} and \texttt{Q}, together represent a queue. The first two 
+\texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1. 
+The third line runs when we exaust all solutions. The forth line re-shape the 
+queue. The fifth and last line invoke the first thunk in the queue and use the 
+mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, 
+and enqueuing \texttt{s-inf}'s thunks.
 

### 2019-03-29 Paper/paper.tex
more intro

@@
 
-\title{miniKanren with fair search}
+\title{miniKanren with fair search strategies}
 \author{Kuang-Chen Lu}
@@
 
+%TODO test cases: quine, '(I love you).
+
+%TODO 1. reformat LaTeX (80 chars per line)
+%TODO 2. stat quine
+%TODO 3. keep writing
+
+% Forget the issues about efficiency
+% Read the monad paper
+
 % body
@@
 these clauses are written down. We have devised two new search strategies that
-allocate computational effort fairly in all clauses.
-
-(TODO: evaluation of performance)
-
-%TODO test cases: quine, '(I love you).
-
-%TODO 1. reformat LaTeX (80 chars per line)
-%TODO 2. stat quine
-%TODO 3. keep writing
+% allocate computational effort fairly in all clauses.
+allocate computational effort more fairly in all clauses.
 
@@
 
-With interleaving depth-first search, disjunctive operator allocates half
-computational effort to its first goal, and quater to the second, eighth to the
-third, and so on. If a goal that can generate planty of unwanted partial 
+When every sub-goal of a disjunction produces infinite states, the existing 
+disjunctive operator allocates half computational effort to its first goal, and 
+quater to the second, eighth to the third, and so on. The unfairness provides 
+both opportunity and burden: miniKanren programmers can place more productive 
+goal at the beginning to optimize their programs; however, it might be a 
+catastrophe if a necessary goal is placed at the end. Seasoned miniKanreners 
+usually know how to utilize the unfairness to optimize their programs. However, 
+we believe search strategies less sensitive to goal order can also be useful to 
+little miniKanreners as well as seansoned ones. We propose two such search 
+strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), 
+and observe how they affect the efficiency and query result of known miniKanren 
+programs. The experiment is conducted with the miniKanren from \textit{The 
+Reasoned Schemer, 2nd Edition}.
+
+% ---from here to the end of this section are materials for this section---
+
+% Compare with Backtracking, Interleaving, and Terminating Monad Transformers
+The \texttt{interleaving} operator has trouble with \texttt{nevero}. Its 
+\texttt{conde} suffers from unfairness, but biDFS and BFS does not. This paper 
+defines \textit{unfairness} as: "a non-deterministic choice between two 
+alternatives tries every solution from the first alternative before any 
+solution from the second alternative".
+
+However, like Seres's work, this search cannot handle infinite failure.
+
+% Compare with The Algebra of Logic Programming by Seresall
+Seres's work is in Haskell, hence having an easy implementation of stream:
+List. Our work is in Scheme. So we have to be explicit about lazyness.
+Her definition of fairness is: "a fair search strategy would share the 
+computation effort more evenly between the two branches of the computation of 
+\texttt{||}, and a fair selection rule would allow one to chose the
+literals in a different order."
+
+Her interleaving DFS is the same as the interleaving in the monad paper, but 
+they are different from what's known as iDFS in miniKanren community.
+
+Her implementation of fair disjunction cannot handle nevero (or "infinite 
+failure" in her terminology): "Note that this implementation of operators does 
+not give breadth-first search of the search tree; it deals with infinite 
+success but not with infinite failure. Even in the interleaved implementation, 
+the first element of the answer list has to be computed before we can switch 
+branches; if this takes an infinite number of steps the other branch will never
+be reached."
+
+And her streams are all infinitely long, hence querying all answers doesn't 
+terminate.
+
+% Observation:
+Stream cannot model \texttt{nevero}... The system knows a stream by nevero has no end, but doesn't know the stream will never produce an item.
+
+If a goal that can generate planty of unwanted partial 
 solutions is placed at the beginning of a \texttt{conde} expressions, it might
-waste a lot computational resource. Consequently, miniKanren programmers 
+waste a lot computational effort. Consequently, miniKanren programmers 
 sometimes need to order their \texttt{conde} clauses carefully to prevent some 
@@
 %TODO KC: prefer an example from other literatures
-Seasoned miniKanreners usually know how to utilize the unfairness to optimize
-their programs. However, we believe search strategies less sensitive to goal
-order can also be useful to little miniKanreners as well as seansoned ones. We 
-propose two such search strategies, balanced interleaving DFS (biDFS) and
-breadth-first search (BFS), and observe how they affect the efficiency and
-query result of known miniKanren programs. The experiment is conducted with the
-miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
 

### 2019-03-29 Paper/paper.tex
more section 1

@@
 
+The unfairness of disjunction is not unawared. (KC: discuss existing works, 
+including the monad paper and Seres's paper).
+
 % ---from here to the end of this section are materials for this section---
@@
 
-If a goal that can generate planty of unwanted partial 
-solutions is placed at the beginning of a \texttt{conde} expressions, it might
-waste a lot computational effort. Consequently, miniKanren programmers 
-sometimes need to order their \texttt{conde} clauses carefully to prevent some 
-clauses absorbing unproportional computational effort. For example, when a 
-relational proof checker is used as a proof generator, the eliminational rules 
-should comes later.
-%TODO KC: prefer an example from other literatures
-
-%TODO KC: Should we use microKanren instead?
-
 %The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
@@
 
-(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is about BFS.
+% TODO: summarize following sections) Section 2 explains why iDFS biases toward 
+% left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is 
+% about BFS.
 
-\section{why iDFS put more effort computing left clauses}
+\section{\texttt{disj} is unfair}
+
+The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
+\texttt{disj2} right associatively. \texttt{disj2} is fair in the sence that it 
+allocates computational effort evenly to its two sub-goals. Unfortunately, the 
+fairness of \texttt{disj2} leads to the unfairness of \texttt{disj}, because the 
+first sub-goal of \texttt{disj} consumes half of all computational effort.
+
+% below are materials.
 
@@
 
-\begin{figure}
-  \lstinputlisting{Figures/disj2.rkt}
-  \caption{\texttt{disj2} and \texttt{append-inf}}
-  \label{disj2-and-append-inf}
-\end{figure}
+% \begin{figure}
+%   \lstinputlisting{Figures/disj2.rkt}
+%   \caption{\texttt{disj2} and \texttt{append-inf}}
+%   \label{disj2-and-append-inf}
+% \end{figure}
 

### 2019-03-31 Paper/paper.tex
more intro

--- 2019-03-22 Paper/paper.tex
@@
 
-With interleaving depth-first search, disjunctive operator allocates half
-computational effort to its first goal, and quater to the second, eighth to the
-third, and so on. If a goal that can generate planty of unwanted partial 
-solutions is placed at the beginning of a \texttt{conde} expressions, it might
-waste a lot computational resource. Consequently, miniKanren programmers 
-sometimes need to order their \texttt{conde} clauses carefully to prevent some 
-clauses absorbing unproportional computational effort. For example, when a 
-relational proof checker is used as a proof generator, the eliminational rules 
-should comes later.
-%TODO KC: prefer an example from other literatures
-Seasoned miniKanreners usually know how to utilize the unfairness to optimize
-their programs. However, we believe search strategies less sensitive to goal
-order can also be useful to little miniKanreners as well as seansoned ones. We 
-propose two such search strategies, balanced interleaving DFS (biDFS) and
-breadth-first search (BFS), and observe how they affect the efficiency and
-query result of known miniKanren programs. The experiment is conducted with the
-miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
+When every sub-goal of a disjunction produces infinite states, the existing 
+disjunctive operator allocates half computational effort to its first goal, 
+quater to the second, eighth to the third, and so on. The unfairness provides 
+both opportunity and burden: miniKanren users can place more frequently used 
+goal at the beginning to optimize their programs; however, it might be a 
+catastrophe if a goal that generate many useless partial solution is placed 
+before more important goals. Seasoned miniKanreners usually know how to utilize 
+the unfairness to optimize their programs. However, we believe search strategies 
+that is less sensitive to goal order can also be useful to little miniKanreners 
+as well as seansoned ones. We propose two such search strategies, balanced 
+interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
+affect the efficiency and the answer order of known miniKanren programs. The 
+experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
+2nd Edition}.
 
-%TODO KC: Should we use microKanren instead?
+\subsection{fairness}
 
-%The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
-%an efficient and complete search strategy -- interleaving depth-first search (iDFS).
-%iDFS biases toward left \texttt{conde} lines. So miniKanren programmers sometimes need to
-%organize their \texttt{conde} lines carefully. We propose and implement two search strategies,
-%breadth-first search (BFS) and balanced interleaving DFS (biDFS). With either of these
-%search strategy, miniKanren becomes less sensitive to the order of \texttt{conde} lines.
+A disjunction is fair if when a corresponding goal is queried, answers of 
+lower costs come first. The \emph{cost} of an answer the number of relation 
+applications needed to find the answer. This idea is borrowed from Silvija 
+Seres's work [*].
 
-(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is about BFS.
+Interleaving DFS, the search strategy of TRS2 miniKanren, is not fair. Among 
+the search strategies we devised, biDFS is not fair, but is more fair than 
+iDFS. And BFS is fair.
 
-\section{why iDFS put more effort computing left clauses}
+\subsection{related works}
 
-\texttt{conde} clauses are combined by \texttt{disj2}, right associatively. The
-core functionality of \texttt{disj2} is completed by \texttt{append-inf} (Fig.~
-ref{disj2-and-append-inf}). When both input streams are infinite, the resulting
-mature part contains only the mature part of \texttt{s-inf}. The whole
-\texttt{t-inf} goes to the resulting immature part. However, \texttt{t-inf} and
-\texttt{s-inf} are swapped in the delayed recursive call. Hence the search
-strategy spend computational effort evenly in two appended streams. As
-\texttt{disj2} is right associative, the left clauses are nested in less calls
-to \texttt{append-inf}, which implies that they are more likeyly being
-computed.
+The unfairness of disjunction has been noticed by Seres et al. Their complete 
+and fair search strategy is also named breadth-first search. Their BFS 
+is fair and is similar to ours. However, their Haskell implementation cannot be 
+translated to Scheme directly. This is partially due to the difference if 
+calling convensions of host languages. Another reason is that their search 
+space are infinite even when no answers exists. This is not feasible 
+in miniKanren, where users can query all answers.
+
+% TODO: summarize following sections) Section 2 explains why iDFS biases toward 
+% left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is 
+% about BFS.
+
+\section{representation of search space}
+
+``Stream'' is often used to name the representation of search space in 
+miniKanren. However, the search space is more like a stream of list, 
+because the information that a stream has no \texttt{car} is employed in all 
+complete miniKanren search strategies to redirect search effort. If the search 
+space is a normal stream, the information should have been used in a more 
+trivial way.
+
+In the rest of this paper, we call the \texttt{car}s of a stream 
+its \textit{mature part}, and the last \texttt{cdr} its \textit{immature part}.
+
+\section{why disj is unfair}
+
+The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
+\texttt{disj2}, right associatively. \texttt{disj2} is fair in the sence that 
+it allocates computational effort evenly to its two sub-goals. Unfortunately, 
+the way how \texttt{disj2} achieves fairness leads to the unfairness of 
+\texttt{disj}. The core functionality of \texttt{disj2} is completed by 
+\texttt{append-inf} (Fig.~ref{disj2-and-append-inf}). When both input streams 
+are infinite, the resulting mature part contains only the mature part of 
+\texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part. 
+However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed recursive 
+call. Hence the search strategy spend computational effort evenly in two 
+appended streams. As \texttt{disj} applys \texttt{disj2} right associatively, 
+the left clauses are more frequently explored.
 
@@
 
-In this section we change the search strategy to breadth-first search and 
-optimize it. The whole process is completed in two steps. In the first step, 
-from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, BFS is 
-optimized. The initial version, \texttt{mk-0}, is exactly the version in 
+In this section we change the search strategy to \textit{breadth-first search} 
+and optimize it. The whole process is completed in two steps. In the first 
+step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
+BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
 \emph{The Reasoned Schemer, 2nd Edition}.
@@
 
-The \emph{cost} of an answer is the number of relation applications needed to
-find the answer. This idea is borrowed from Silvija Seres's work [*].
 Now we illustrate the costs of answers by running a miniKanren relation.

### 2019-04-01 Paper/paper.tex
revise intro, biDFS.

@@
 
-\subsection{fairness}
-
-A disjunction is fair if when a corresponding goal is queried, answers of 
-lower costs come first. The \emph{cost} of an answer the number of relation 
-applications needed to find the answer. This idea is borrowed from Silvija 
-Seres's work [*].
-
-Interleaving DFS, the search strategy of TRS2 miniKanren, is not fair. Among 
-the search strategies we devised, biDFS is not fair, but is more fair than 
-iDFS. And BFS is fair.
-
-\subsection{related works}
+\section{related works}
 
@@
 is fair and is similar to ours. However, their Haskell implementation cannot be 
-translated to Scheme directly. This is partially due to the difference if 
-calling convensions of host languages. Another reason is that their search 
-space are infinite even when no answers exists. This is not feasible 
-in miniKanren, where users can query all answers.
+translated to Scheme directly. This is partially due to the difference in 
+calling convensions of host languages. Besides, their search space are infinite 
+even when no answers exists. This is not feasible in miniKanren, where 
+users can query all answers.
 
-% TODO: summarize following sections) Section 2 explains why iDFS biases toward 
-% left \texttt{conde} clauses. Section 3 is about the biDFS. Section 4 is 
-% about BFS.
+\section{fairness}
 
-\section{representation of search space}
+% KC: I changed the cost definition from ``... needed to *find* the answer''
+%                                     to ``... needed to *verify* the answer''
 
-``Stream'' is often used to name the representation of search space in 
-miniKanren. However, the search space is more like a stream of list, 
-because the information that a stream has no \texttt{car} is employed in all 
-complete miniKanren search strategies to redirect search effort. If the search 
-space is a normal stream, the information should have been used in a more 
-trivial way.
+A disjunction is fair if when a corresponding goal is queried, answers of 
+lower costs come first. The \emph{cost} of an answer the number of relation 
+applications needed to verify the answer. Now we illustrate the costs of answers 
+by running a miniKanren relation. Fig.~\ref{def-repeato} defines the relation 
+\texttt{repeato} that relates a term \texttt{x} with a list whose elements are 
+all \texttt{x}s.
 
-In the rest of this paper, we call the \texttt{car}s of a stream 
-its \textit{mature part}, and the last \texttt{cdr} its \textit{immature part}.
-
-\section{why disj is unfair}
-
-The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
-\texttt{disj2}, right associatively. \texttt{disj2} is fair in the sence that 
-it allocates computational effort evenly to its two sub-goals. Unfortunately, 
-the way how \texttt{disj2} achieves fairness leads to the unfairness of 
-\texttt{disj}. The core functionality of \texttt{disj2} is completed by 
-\texttt{append-inf} (Fig.~ref{disj2-and-append-inf}). When both input streams 
-are infinite, the resulting mature part contains only the mature part of 
-\texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part. 
-However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed recursive 
-call. Hence the search strategy spend computational effort evenly in two 
-appended streams. As \texttt{disj} applys \texttt{disj2} right associatively, 
-the left clauses are more frequently explored.
-
-\begin{figure}
-  \lstinputlisting{Figures/disj2.rkt}
-  \caption{\texttt{disj2} and \texttt{append-inf}}
-  \label{disj2-and-append-inf}
-\end{figure}
-
-\section{balanced interleaving DFS}
-
-A \texttt{conde} expression looks like a binary tree, if we consider 
-\texttt{disj2}s as internal nodes and \texttt{conde} clauses as a terminal 
-nodes. In fact, each of them is one of the most unbalanced binary trees. The 
-basic idea of our first solution, balanced interleaving DFS, is to make the 
-tree balanced. We introduce a function \texttt{disj*} and its helper 
-\texttt{split} (Fig.~\ref{disj*}). \texttt{disj*} essentially construct a 
-balanced \texttt{disj2} tree. \texttt{split} splits elements of \texttt{ls} 
-into two even half and pass them to the continuation parameter \texttt{k}.
-
-\begin{figure}
-  \lstinputlisting{Figures/disj*.rkt}
-  \caption{\texttt{disj*}}
-  \label{disj*}
-\end{figure}
-
-\section{breadth-first search}
-
-In this section we change the search strategy to \textit{breadth-first search} 
-and optimize it. The whole process is completed in two steps. In the first 
-step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
-BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
-\emph{The Reasoned Schemer, 2nd Edition}.
-
-\subsection{cost of answers}
-
-%TODO the meaning of resolution step in Silvija Seres's paper
-
-Now we illustrate the costs of answers by running a miniKanren relation.
-Fig.~\ref{def-repeato} defines the relation \texttt{repeato} that 
-relates a term \texttt{x} with a list whose elements are all \texttt{x}s.
+% COmmented out: This idea is borrowed from Silvija Seres's work [*].
+% KC: Seres didn't phrase it this way.
+%   We might need to compare our definition with Seres's one, instead of 
+%   saying the idea is borrowed.
 
@@
 The order of the answers reflects the order miniKanren discovers them:
-the first answer in the list is first discovered. This result is not suprising:
+the first answer in the list is first discovered. This order is not suprising:
 to generate the first answer, \texttt{'()}, miniKanren needs to apply
@@
 
-A list of answer is in the \emph{cost-respecting} order if no answer occurs
-before another answer of a lower cost. In the above example, the answers are
-cost-respecting. The iDFS search, however, does not generate cost-respecting
-answers in general. As an example, consider the following \texttt{run} of
-\texttt{repeato}.
+A query result (list of answers) is in the \emph{cost-respecting} order if no 
+answer occurs before another answer of a lower cost. In the above example, the 
+result is cost-respecting. The iDFS search, however, does not generate 
+cost-respecting answers in general. As an example, consider the following 
+\texttt{run} of \texttt{repeato}.
+
 \begin{center}
@@
 
-The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
+The results is not cost-respecting. For example, \texttt{'(a a)} occurs before
 \texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
@@
 strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
-which share the same portion as the second last one.
+which share the same portion as the second last one. In contrast, the same run 
+with BFS produces answers in an expected order.
 
-%TODO relation *application*
+\begin{center}
+  \begin{tabular}{c}
+   \lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+   \end{tabular}
+\end{center}
 
-For the above \texttt{run}, both search strategies produces answers in 
-increasing order of costs, i.e. both of them are \emph{cost-respecting}. In 
-more complicated cases, however, interleaving DFS might not produce answers in 
-cost-repecting order. For instance, with iDFS the \texttt{run} in Fig.~
-\ref{conde-repeato-iDFS} produces answers in a seemingly random order. In 
-contrast, the same run with BFS produces answers in an expected order (Fig.~
-\ref{conde-repeato-BFS}).
+% \section{representation of search space}
+% 
+% ``Stream'' is often used to name the representation of search space in 
+% miniKanren. However, the search space is more like a stream of list, because the 
+% information that a stream is thunk is employed to redirect search effort. If the 
+% search space is a normal stream, the information should have been used in a more 
+% trivial way. 
+% 
+% In the rest of this paper, we call the \texttt{car}s of a stream 
+% its \textit{mature part}, and the last \texttt{cdr} its \textit{immature part}.
+% 
+% \section{why disj is unfair}
+% 
+% The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
+% \texttt{disj2}, right associatively. Interestingly, although \texttt{disj} is 
+% unfair, \texttt{disj2} is fair. The core functionality of \texttt{disj2} is 
+% completed by \texttt{append-inf} (Fig.~ref{disj2-and-append-inf}). When both 
+% input streams are infinite, the resulting mature part contains only the mature 
+% part of \texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature 
+% part. However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed 
+% recursive call. Hence the search strategy spend computational effort evenly in 
+% two appended streams. As \texttt{disj} applys \texttt{disj2} right 
+% associatively, the left clauses are more frequently explored.
+% 
+% \begin{figure}
+%   \lstinputlisting{Figures/disj2.rkt}
+%   \caption{\texttt{disj2} and \texttt{append-inf}}
+%   \label{disj2-and-append-inf}
+% \end{figure}
 
-\lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+\section{balanced interleaving DFS}
+
+Our first solution, balanced interleaving DFS, is based on the observation that 
+a disjuction can be viewed as a binary tree, where \texttt{disj2}s are nodes 
+and sub-goals are leaves. In iDFS, the tree is in one of the most unbalanced 
+forms, because \texttt{disj} applys \texttt{disj2} right associatively. As 
+\texttt{disj2} allocates computational effort interleavingly to its two 
+sub-goals, a disjunction allocates half computational effort to its first 
+sub-goal, quater to the second, eighth to the third, and so on.
+
+The key idea of biDFS is to make disjunction trees balanced 
+(Fig.~\ref{balanced-disj}). We introduce a function \texttt{disj*} and its 
+helper \texttt{split}, and change the \texttt{disj} macro to call 
+\texttt{disj*} immediately. \texttt{disj*} essentially construct a balanced 
+\texttt{disj2} tree. The \texttt{split} helper splits elements of \texttt{ls} 
+into two lists of roughly the same length, then apply \texttt{k} to them.
+
+\begin{figure}
+  \lstinputlisting{Figures/balanced-disj.rkt}
+  \caption{\texttt{balanced-disj}}
+  \label{balanced-disj}
+\end{figure}
+
+\section{breadth-first search}
+
+In this section we change the search strategy to \textit{breadth-first search} 
+and optimize it. The whole process is completed in two steps. In the first 
+step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
+BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
+\emph{The Reasoned Schemer, 2nd Edition}.
 

### 2019-04-07 Paper/paper.tex
revise everything

@@
 goal at the beginning to optimize their programs; however, it might be a 
-catastrophe if a goal that generate many useless partial solution is placed 
-before more important goals. Seasoned miniKanreners usually know how to utilize 
+catastrophe if a goal that generate many useless states is placed before more 
+important goals. Seasoned miniKanreners usually know how to utilize 
 the unfairness to optimize their programs. However, we believe search strategies 
@@
 
-The unfairness of disjunction has been noticed by Seres et al. Their complete 
-and fair search strategy is also named breadth-first search. Their BFS 
-is fair and is similar to ours. However, their Haskell implementation cannot be 
-translated to Scheme directly. This is partially due to the difference in 
-calling convensions of host languages. Besides, their search space are infinite 
-even when no answers exists. This is not feasible in miniKanren, where 
-users can query all answers.
+% TODO rewrite, because Seres did provide a solution for possibly finite stream
+% The unfairness of disjunction has been noticed by Seres et 
+% al~\citet{seres1999algebra}. Their complete 
+% and fair search strategy is also named breadth-first search. Their BFS 
+% is fair and is similar to ours. However, their Haskell implementation cannot be 
+% translated to Scheme directly. This is partially due to the difference in 
+% calling convensions of host languages. Besides, their search space are infinite 
+% even when no answers exists. This is not feasible in miniKanren, where 
+% users can query all answers.
 
@@
 
-A disjunction is fair if when a corresponding goal is queried, answers of 
-lower costs come first. The \emph{cost} of an answer the number of relation 
-applications needed to verify the answer. Now we illustrate the costs of answers 
-by running a miniKanren relation. Fig.~\ref{def-repeato} defines the relation 
+A search strategy is \emph{fair} if answers of lower costs always come first. 
+The \emph{cost} of an answer the number of relation applications needed to 
+verify the answer. Now we illustrate the costs of answers by running a 
+miniKanren relation. Fig.~\ref{def-repeato} defines the relation 
 \texttt{repeato} that relates a term \texttt{x} with a list whose elements are 
@@
 to generate the first answer, \texttt{'()}, miniKanren needs to apply
-\texttt{repeato} only once and the later answers need more recursive
+\texttt{repeato} only once and the later answers need more relation
 applications. In this example, the cost of each answer is the same as
@@
 
-A query result (list of answers) is in the \emph{cost-respecting} order if no 
-answer occurs before another answer of a lower cost. In the above example, the 
-result is cost-respecting. The iDFS search, however, does not generate 
-cost-respecting answers in general. As an example, consider the following 
-\texttt{run} of \texttt{repeato}.
+% A query result (list of answers) is in the \emph{cost-respecting} order if no 
+% answer occurs before another answer of a lower cost. In the above example, the 
+% result is cost-respecting. The iDFS search, however, does not generate 
+% cost-respecting answers in general. As an example, consider the following 
+% \texttt{run} of \texttt{repeato}.
+
+In the above example, all search strategies look fair. However, the following 
+example points out that iDFS is not fair.
 
@@
 
-The results is not cost-respecting. For example, \texttt{'(a a)} occurs before
-\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
-iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
-considerablely. When every \texttt{conde} case are equally productive, the iDFS
-strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
-which share the same portion as the second last one. In contrast, the same run 
-with BFS produces answers in an expected order.
+With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
+associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
+the first \texttt{conde} case considerablely. When every \texttt{conde} case 
+are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
+$i$-th case, except the last case, which share the same portion as the second 
+last one. In contrast, the same run with BFS produces answers in an expected 
+order.
 
@@
 
-Our first solution, balanced interleaving DFS, is based on the observation that 
-a disjuction can be viewed as a binary tree, where \texttt{disj2}s are nodes 
-and sub-goals are leaves. In iDFS, the tree is in one of the most unbalanced 
-forms, because \texttt{disj} applys \texttt{disj2} right associatively. As 
-\texttt{disj2} allocates computational effort interleavingly to its two 
-sub-goals, a disjunction allocates half computational effort to its first 
-sub-goal, quater to the second, eighth to the third, and so on.
+Our first solution, balanced interleaving DFS (biDFS), is not fair as well. 
+However, it is less sensitive to goal order in disjucntion and is as efficient 
+as iDFS. This search strategy is based on the  observations that a disjuction 
+can be viewed as a binary tree, where \texttt{disj2}s are nodes 
+and sub-goals are leaves, and that the position of a leaf has direct relation 
+with its priority -- the deeper a leaf, the lower computational effort it is 
+shared. In iDFS, the tree is in one of the most unbalanced forms, because 
+\texttt{disj} applys \texttt{disj2} right associatively. Hence the goal order 
+is very important. The reason why the tree shape can determine priority is that 
+\texttt{disj2} allocates computational effort evenly to its two sub-goals.
 
-The key idea of biDFS is to make disjunction trees balanced 
-(Fig.~\ref{balanced-disj}). We introduce a function \texttt{disj*} and its 
-helper \texttt{split}, and change the \texttt{disj} macro to call 
-\texttt{disj*} immediately. \texttt{disj*} essentially construct a balanced 
-\texttt{disj2} tree. The \texttt{split} helper splits elements of \texttt{ls} 
-into two lists of roughly the same length, then apply \texttt{k} to them.
+The key idea of biDFS is to make the tree balanced (Fig.~\ref{balanced-disj}). 
+We introduce a function \texttt{disj*} and its helper \texttt{split}, and change 
+the \texttt{disj} macro to call \texttt{disj*} immediately. \texttt{disj*} 
+essentially construct a balanced \texttt{disj2} tree. The \texttt{split} helper 
+splits elements of \texttt{ls} into two lists of roughly the same length, then 
+apply \texttt{k} to them.
 
@@
 
-In this section we change the search strategy to \textit{breadth-first search} 
-and optimize it. The whole process is completed in two steps. In the first 
-step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
-BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
-\emph{The Reasoned Schemer, 2nd Edition}.
+%TODO compare with Seres's approach
 
-\subsection{from \texttt{mk-0} to \texttt{mk-1}}
+Breadth-first search (BFS) is fair. Our BFS is similar to the one by Seres et 
+al \citet{seres1999algebra}. We conjecture that the two strategies produce
+answers in the same order. ;; need more comparision
 
-In \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by streams of 
-answers. Streams can be finite or infinite. Finite streams are just lists. And 
-infinite streams are improper lists, whose last \texttt{cdr} is a thunk 
-returning another stream. We call the \texttt{car}s the \emph{mature} part, and 
-the last \texttt{cdr} the \emph{immature} part.
+In the first subsection, we change the search strategy from iDFS to BFS. In the 
+second subsection we optimize the search engine by using a queue to manage the 
+search order. The two subsections corresponds to two new version of miniKanren, 
+\texttt{mk-1} and \texttt{mk-2}. We refer to the original version from TRS2 as 
+\texttt{mk-0}.
 
-Streams are cost respective when they are initially constructed by \texttt{==}. 
-However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-
-inf-0}) breaks cost respectiveness if its first input stream, \texttt{s-inf}, 
-is infinite. The resulting mature part contains only the mature part of 
-\texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part.
+% In this section we change the search strategy to \textit{breadth-first search} 
+% and optimize it. The whole process is completed in two steps. In the first 
+% step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
+% BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
+% \emph{The Reasoned Schemer, 2nd Edition}.
+
+\subsection{change search strategy from iDFS to BFS}
+
+In both \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by 
+streams of  answers. The thunky streams in \texttt{mk-0} denote delayed 
+computation, however, they do not necessary mean an increment in cost. We use 
+the same kind of stream in \texttt{mk-1} but only put thunk at those places 
+where the cost of following answers is increased by one.
+
+To ease discussion, we call the \texttt{car}s of an stream its \emph{mature} 
+part, and the last \texttt{cdr} the \emph{immature} part. When the stream is 
+definitely finite, its immature part is an empty list, otherwise, it is a 
+thunk. We sometimes say a stream is immature to mean its mature part is empty.
+
+Streams denote cost correctly when they are constructed by \texttt{==}, 
+\texttt{succeed}, and \texttt{fail}. However, the \texttt{mk-0} version of 
+\texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness if its 
+first input stream, \texttt{s-inf},  is infinite. The resulting mature part 
+contains only the mature part of \texttt{s-inf}. If we want to encode the 
+cost information correctly, the resulting mature part should also contains the 
+mature part of \texttt{t-inf}.
 
@@
 The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) 
-restores cost-respectiveness by combining the mature parts in the fashion of 
-\texttt{append}. This \texttt{append-inf} calls its helper immediately, with 
-the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-
-inf} in the helper is the \texttt{s-inf} in the driver. Two streams are swapped 
-in the third \texttt{cond} clause, with \texttt{s?} flipped accordingly.
+gain fairness by combining the mature parts in the fashion of \texttt{append}. 
+This \texttt{append-inf} calls its helper immediately, with the first argument, 
+\texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is 
+the \texttt{s-inf} in the driver. Two streams are swapped in the third 
+\texttt{cond} clause, with \texttt{s?} flipped accordingly.
 
@@
 \texttt{mk-1} is not efficient in two aspects. \texttt{append-inf} need to copy 
-all \texttt{cons} cells of two input streams when the first stream has a non-
-trivial immature part. Besides, \texttt{mk-1} computes answers of the same cost 
+all \texttt{cons} cells of \emph{both} input streams when the first stream is 
+possibly infinite. Besides, \texttt{mk-1} computes answers of the same cost
 at once, even when only a portion is queried. We solves the two problems in the 
@@
 
-\subsection{\texttt{mk-3}, optimized breadth-first search}
+\subsection{optimize breadth-first search}
 
-We avoid generating same-cost answers at once by expressing BFS with a queue. 
-The elements of the queue are delayed computation, represented by thunks. Every 
-\texttt{mk-1} stream has zero or one thunk, so we have no interesting way to 
-manage it. Therefore we change the representation of immature parts from thunks 
-to lists of thunks. As as consequence, we also change the way to combine mature 
-and immature part from \texttt{append} to \texttt{cons}.
+We avoid generating same-cost answers at once by expressing BFS with a queue, 
+whose elements thunks that return a new stream. Every \texttt{mk-1} stream has 
+zero or one thunk, so we cannot manage it with queue in interesting 
+way. Therefore we change the representation of immature parts from thunks to 
+lists of thunks. As as consequence, we also change the way to combine mature and 
+immature part from \texttt{append} to \texttt{cons}.
 
 After applying this two changes, stream representation becomes more 
-complicated. It motivates us to set up an interface between stream functions 
+complicated. It motivates us to set up an interface between stream 
 and the rest of miniKanren. Listed in Fig.~\ref{interface} are all functions 
 being aware of the stream representation, but \texttt{take-inf} and its helper 
-function, which is explained later. The first three functions are constructors: 
+function, which are explained later. The first three functions are 
+constructors: 
 \texttt{empty-inf} constructs an empty stream; \texttt{unit-mature-inf} 
@@
 However sometimes only a portion of these solutions is required to answer a 
-query. To avoid the trouble and the advanced computation, we choose to create a 
-new thunk for every existing thunk. The next four functions are used only by 
+query. To avoid the trouble and the too-early computation, we choose to create 
+a new thunk for every existing thunk. The next four functions are used only by 
 \texttt{ifte} and \texttt{once}. Uninterested readers might skip them. 
@@
 
-\section*{references}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{citation}
 

### 2019-04-08 Paper/paper.tex
adding reasoned 2th bib

@@
 
-When every sub-goal of a disjunction produces infinite states, the existing 
-disjunctive operator allocates half computational effort to its first goal, 
-quater to the second, eighth to the third, and so on. The unfairness provides 
+Interleaving DFS, the search strategy of \texttt{cond$^e$} in
+miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
+by the order in which the claueses are written. Each clause of a
+\texttt{cond$^e$} takes a half of the current resource and passes the other half
+to its following clauses, except for the last clause that takes all of current
+resource. 
 both opportunity and burden: miniKanren users can place more frequently used 

### 2019-04-09 Paper/paper.tex
newcommend conde

@@
 
-% Forget the issues about efficiency
-% Read the monad paper
+\newcommand{\conde}{\texttt{cond$^e$} }
 
@@
 
-Interleaving DFS, the search strategy of \texttt{cond$^e$} in
+Interleaving DFS, the search strategy of \conde in
 miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
 by the order in which the claueses are written. Each clause of a
-\texttt{cond$^e$} takes a half of the current resource and passes the other half
+\conde takes a half of the current resource and passes the other half
 to its following clauses, except for the last clause that takes all of current
@@
 A search strategy is \emph{fair} if answers of lower costs always come first. 
-The \emph{cost} of an answer the number of relation applications needed to 
-verify the answer. Now we illustrate the costs of answers by running a 
-miniKanren relation. Fig.~\ref{def-repeato} defines the relation 
-\texttt{repeato} that relates a term \texttt{x} with a list whose elements are 
-all \texttt{x}s.
+The \emph{cost} of an answer is the number of relation applications. Now we 
+illustrate the costs of answers by running a miniKanren relation. 
+Fig.~\ref{def-repeato} defines the relation \texttt{repeato} that relates a term 
+\texttt{x} with a list whose elements are all \texttt{x}s.
 
@@
 associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
-the first \texttt{conde} case considerablely. When every \texttt{conde} case 
+the first \conde case considerablely. When every \conde case 
 are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
@@
 
+%TODO contributions
+%TODO future works
+
 \section*{acknowledgments}

### 2019-04-10 Paper/paper.tex
very brief conclusion

@@
 %
-% - deadline?
-%
-%   miniKanren workshop deadline May 15, 2018
+%  SUBMISSION DEADLINE: May 15, 2019
 %
@@
 
-%TODO test cases: quine, '(I love you).
-
-%TODO 1. reformat LaTeX (80 chars per line)
-%TODO 2. stat quine
-%TODO 3. keep writing
-
 \newcommand{\conde}{\texttt{cond$^e$} }
 
-% body
 \begin{document}
+% TODO how about making all disjunction trees complete by filling missing
+% leaves with nevero?
 
@@
 
-% TODO rewrite, because Seres did provide a solution for possibly finite stream
-% The unfairness of disjunction has been noticed by Seres et 
-% al~\citet{seres1999algebra}. Their complete 
-% and fair search strategy is also named breadth-first search. Their BFS 
-% is fair and is similar to ours. However, their Haskell implementation cannot be 
-% translated to Scheme directly. This is partially due to the difference in 
-% calling convensions of host languages. Besides, their search space are infinite 
-% even when no answers exists. This is not feasible in miniKanren, where 
-% users can query all answers.
-
 \section{fairness}
-
-% KC: I changed the cost definition from ``... needed to *find* the answer''
-%                                     to ``... needed to *verify* the answer''
 
@@
 
-% COmmented out: This idea is borrowed from Silvija Seres's work [*].
+% Commented out: This idea is borrowed from Silvija Seres's work [*].
 % KC: Seres didn't phrase it this way.
@@
 whose elements thunks that return a new stream. Every \texttt{mk-1} stream has 
-zero or one thunk, so we cannot manage it with queue in interesting 
-way. Therefore we change the representation of immature parts from thunks to 
+zero or one thunk, so it is uninteresting to manage them with queue . Therefore 
+we change the representation of immature parts from thunks to 
 lists of thunks. As as consequence, we also change the way to combine mature and 
@@
 being aware of the stream representation, but \texttt{take-inf} and its helper 
-function, which are explained later. The first three functions are 
-constructors: 
-\texttt{empty-inf} constructs an empty stream; \texttt{unit-mature-inf} 
-constructs a stream with one mature solution; \texttt{unit-immature-inf} 
-constructs a stream with one thunk. The \texttt{append-inf} in \texttt{mk-3} is 
-relatively straightforwared compared with the \texttt{mk-1} version. 
-\texttt{append-map-inf} is more tricky on how to construct the new immature 
-part. We can follow the approach in mk-0 and mk-1 -- create a new thunk which 
-invoke append-map-inf recursively when forced. But then we need to be careful: 
-if we construct the thunk when the old immature part is an empty list, the 
-resulting stream might be infinitely unproductive. Beside, all solutions of the 
-next lowest cost in \texttt{s-inf} must be computed when the thunk is invoked. 
-However sometimes only a portion of these solutions is required to answer a 
-query. To avoid the trouble and the too-early computation, we choose to create 
-a new thunk for every existing thunk. The next four functions are used only by 
-\texttt{ifte} and \texttt{once}. Uninterested readers might skip them. 
-\texttt{null-inf?} checks whether a stream is exausted. \texttt{mature-inf?} 
-checks whether a stream has some mature solutions. \texttt{car-inf} takes the 
-first solution out of a mature stream. \texttt{cdr-inf} drops the first 
-solution of a mature stream. Finally, \texttt{force-inf} forces an a immature 
-stream to do more computation.
+function, which are explained later.
+
+The first three functions are constructors: \texttt{empty-inf} constructs an 
+empty stream; \texttt{unit-mature-inf} constructs a stream with one mature 
+solution; \texttt{unit-immature-inf} constructs a stream with one thunk.
+
+The \texttt{append-inf} in \texttt{mk-3} is relatively straightforwared compared 
+with the \texttt{mk-1} version. \texttt{append-map-inf} is more tricky on how to 
+construct the new immature part. We can follow the approach in mk-0 and mk-1 -- 
+create a new thunk which invoke append-map-inf recursively when forced. But then 
+we need to be careful: if we construct the thunk when the old immature part is 
+an empty list, the resulting stream might be infinitely unproductive. Beside, 
+all solutions of the next lowest cost in \texttt{s-inf} must be computed when 
+the thunk is invoked. However sometimes only a portion of these solutions is 
+required to answer a query. To avoid the trouble and the too-early computation, 
+we choose to create a new thunk for every existing thunk.
+
+The next four functions are used only by \texttt{ifte} and \texttt{once}. 
+Uninterested readers might skip them. \texttt{null-inf?} checks whether a stream 
+is exausted. \texttt{mature-inf?} checks whether a stream has some mature 
+solutions. \texttt{car-inf} takes the first solution out of a mature stream. 
+\texttt{cdr-inf} drops the first solution of a mature stream. Finally, 
+\texttt{force-inf} forces an a immature stream to do more computation.
+
+\texttt{unit-mature-inf}, \texttt{append-map-inf}, \texttt{empty-inf} and 
+\texttt{append-inf} form a \emph{MonadPlus}, where they corresponds to 
+\texttt{unit}, \texttt{bind}, \texttt{mzero}, and \texttt{mplus} respectively.
 
@@
 
+We devise a new search strategy, balanced interleaving DFS. The key idea is to 
+make disjunction tree balanced. Changing search strategy from iDFS to biDFS is 
+not hard: 2 new functions and 1 modified macro.
+
+We also devise breadth-first search, which is similar to Seres's BFS. These two 
+BFSs have similar intuition, but whether they are equivalent is not clear yet. 
+Our optimization on BFS with queue, however, is new.
+
 \section*{acknowledgments}

### 2019-04-11 Paper/paper.tex
fix lots of grammar and spelling errors

@@
 miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
-by the order in which the claueses are written. Each clause of a
-\conde takes a half of the current resource and passes the other half
+by the order in which the clauses are written. Each clause of a
+\conde takes half of the current resource and passes the other half
 to its following clauses, except for the last clause that takes all of current
@@
 that is less sensitive to goal order can also be useful to little miniKanreners 
-as well as seansoned ones. We propose two such search strategies, balanced 
+as well as seasoned ones. We propose two such search strategies, balanced 
 interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
@@
 The order of the answers reflects the order miniKanren discovers them:
-the first answer in the list is first discovered. This order is not suprising:
+the first answer in the list is first discovered. This order is not surprising:
 to generate the first answer, \texttt{'()}, miniKanren needs to apply
@@
 associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
-the first \conde case considerablely. When every \conde case 
+the first \conde case considerably. When every \conde case 
 are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
@@
 shared. In iDFS, the tree is in one of the most unbalanced forms, because 
-\texttt{disj} applys \texttt{disj2} right associatively. Hence the goal order 
+\texttt{disj} applys \texttt{disj2} right associatively. Hence, the goal order 
 is very important. The reason why the tree shape can determine priority is that 
@@
 al \citet{seres1999algebra}. We conjecture that the two strategies produce
-answers in the same order. ;; need more comparision
+answers in the same order.
+%TODO need more comparison
 
@@
 second subsection we optimize the search engine by using a queue to manage the 
-search order. The two subsections corresponds to two new version of miniKanren, 
+search order. The two subsections corresponds to two new versions of miniKanren, 
 \texttt{mk-1} and \texttt{mk-2}. We refer to the original version from TRS2 as 
@@
 In both \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by 
-streams of  answers. The thunky streams in \texttt{mk-0} denote delayed 
+streams of answers. Thunk streams in \texttt{mk-0} denote delayed 
 computation, however, they do not necessary mean an increment in cost. We use 
@@
 
-To ease discussion, we call the \texttt{car}s of an stream its \emph{mature} 
-part, and the last \texttt{cdr} the \emph{immature} part. When the stream is 
+To ease discussion, we call the \texttt{car}s of a stream as its \emph{mature} 
+part, and its last \texttt{cdr} as its \emph{immature} part. When the stream is 
 definitely finite, its immature part is an empty list, otherwise, it is a 
@@
 contains only the mature part of \texttt{s-inf}. If we want to encode the 
-cost information correctly, the resulting mature part should also contains the 
+cost information correctly, the resulting mature part should also contain the 
 mature part of \texttt{t-inf}.
@@
 This \texttt{append-inf} calls its helper immediately, with the first argument, 
-\texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is 
-the \texttt{s-inf} in the driver. Two streams are swapped in the third 
-\texttt{cond} clause, with \texttt{s?} flipped accordingly.
+\texttt{s?}, set to \texttt{\#{}t}, which \texttt{s-inf} and \texttt{t-inf} haven't been swapped in the driver.
+They are swapped in the third \texttt{cond} clause, where \texttt{s?} is flipped accordingly.
 
@@
 possibly infinite. Besides, \texttt{mk-1} computes answers of the same cost
-at once, even when only a portion is queried. We solves the two problems in the 
+at once, even when only a portion is queried. We solve the two problems in the 
 next subsections.
@@
 whose elements thunks that return a new stream. Every \texttt{mk-1} stream has 
-zero or one thunk, so it is uninteresting to manage them with queue . Therefore 
+zero or one thunk, so it is uninteresting to manage them with queue . Therefore, 
 we change the representation of immature parts from thunks to 
-lists of thunks. As as consequence, we also change the way to combine mature and 
+lists of thunks. Consequently, we also change the way to combine mature and 
 immature part from \texttt{append} to \texttt{cons}.
@@
 
-The first three functions are constructors: \texttt{empty-inf} constructs an 
-empty stream; \texttt{unit-mature-inf} constructs a stream with one mature 
-solution; \texttt{unit-immature-inf} constructs a stream with one thunk.
+The first three functions are constructors: \texttt{empty-inf} makes an 
+empty stream; \texttt{unit-mature-inf} makes a stream with one mature 
+solution; \texttt{unit-immature-inf} makes a stream with one thunk.
 
-The \texttt{append-inf} in \texttt{mk-3} is relatively straightforwared compared 
+The \texttt{append-inf} in \texttt{mk-3} is relatively straightforward compared 
 with the \texttt{mk-1} version. \texttt{append-map-inf} is more tricky on how to 
@@
 all solutions of the next lowest cost in \texttt{s-inf} must be computed when 
-the thunk is invoked. However sometimes only a portion of these solutions is 
-required to answer a query. To avoid the trouble and the too-early computation, 
+the thunk is invoked. However, sometimes only a portion of these solutions is 
+required to answer a query. To avoid the trouble and too-early computation, 
 we choose to create a new thunk for every existing thunk.
@@
 Uninterested readers might skip them. \texttt{null-inf?} checks whether a stream 
-is exausted. \texttt{mature-inf?} checks whether a stream has some mature 
+is exhausted. \texttt{mature-inf?} checks whether a stream has some mature 
 solutions. \texttt{car-inf} takes the first solution out of a mature stream. 
 \texttt{cdr-inf} drops the first solution of a mature stream. Finally, 
-\texttt{force-inf} forces an a immature stream to do more computation.
+\texttt{force-inf} forces an immature stream to do more computation.
 
 \texttt{unit-mature-inf}, \texttt{append-map-inf}, \texttt{empty-inf} and 
-\texttt{append-inf} form a \emph{MonadPlus}, where they corresponds to 
+\texttt{append-inf} form a \emph{MonadPlus}, where they correspond to 
 \texttt{unit}, \texttt{bind}, \texttt{mzero}, and \texttt{mplus} respectively.
@@
 The last interesting function is \texttt{take-inf} (Fig.~\ref{take-inf-3-1}). 
-The parameter \texttt{vs} is a list of solutions. The next two parameters, 
-\texttt{P} and \texttt{Q}, together represent a queue. The first two 
-\texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1. 
-The third line runs when we exaust all solutions. The forth line re-shape the 
-queue. The fifth and last line invoke the first thunk in the queue and use the 
-mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, 
-and enqueuing \texttt{s-inf}'s thunks.
+Its first parameter, \texttt{vs}, is a list of solutions. The next two parameters, \texttt{P} and \texttt{Q}, together represents a queue. 
+The first two \texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1.
+The third line runs when both the answer list \texttt{vs} and the queue are empty, which means we have found all answers.
+The forth line re-shape the queue.
+The fifth and last line invoke the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
 
@@
 
-We also devise breadth-first search, which is similar to Seres's BFS. These two 
-BFSs have similar intuition, but whether they are equivalent is not clear yet. 
-Our optimization on BFS with queue, however, is new.
+We also devise breadth-first search, which is similar to Seres's BFS. It is not clear whether they are equivalent. Our optimization on BFS with queue, however, is new.
 

### 2019-04-25 Paper/paper.tex
rewrite intro

@@
 \begin{document}
-% TODO how about making all disjunction trees complete by filling missing
-% leaves with nevero?
 
@@
 
+%TODO our new searches also change the behavior of conj
 The syntax of a programming language should reflect its semantics. When using a
 disjunction operator in relational programming, a programmer would expect all
-clauses of this disjunction to share the same chance of being explored, as
-these clauses are written in parallel. The existing multiarity disjunctive
+clauses of this disjunct to share the same chance of being explored, as
+these clauses are written in parallel. The existing multi-arity disjunctive
 operator in miniKanren, however, prioritize its clauses by the order of which
 these clauses are written down. We have devised two new search strategies that
-% allocate computational effort fairly in all clauses.
 allocate computational effort more fairly in all clauses.
@@
 
-Interleaving DFS, the search strategy of \conde in
-miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
-by the order in which the clauses are written. Each clause of a
-\conde takes half of the current resource and passes the other half
-to its following clauses, except for the last clause that takes all of current
-resource. 
-both opportunity and burden: miniKanren users can place more frequently used 
-goal at the beginning to optimize their programs; however, it might be a 
-catastrophe if a goal that generate many useless states is placed before more 
-important goals. Seasoned miniKanreners usually know how to utilize 
-the unfairness to optimize their programs. However, we believe search strategies 
-that is less sensitive to goal order can also be useful to little miniKanreners 
-as well as seasoned ones. We propose two such search strategies, balanced 
-interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
-affect the efficiency and the answer order of known miniKanren programs. The 
-experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
-2nd Edition}.
+miniKanren programs, especially relational interpreters, have been proven to be useful in solving many problems \citep{byrd2017unified}.
+A subtlety in writing relational programs involving a large \conde expression, such as interpreters, is that the order of \conde clauses can affect the speed considerably.
+This is due to the biased allocation of computational resource.
+Interleaving DFS, the search strategy of \conde in miniKanren~\citep{friedman_reasoned_2018}, allocates half resource to the first \conde clause, a quarter to the second, an eighth to the third, and so on.
+Under the hood, it is the unfairness of \texttt{disj}.
 
-\section{related works}
+We address the unfairness of \texttt{disj} in this work.
+We propose two new search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS).
+biDFS is almost fair -- the maximal ratio of resource among disjunctive goals is bounded by a constant factor.
+BFS is completely fair.
+We prove that our BFS is equivalent to the BFS proposed by Seres et al~\citep{seres1999algebra}.
+We also observe how new search strategies affect the efficiency and the answer order of known miniKanren programs.
+
+% Interleaving DFS, the search strategy of \conde in
+% miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
+% by the order in which the clauses are written. Each clause of a
+% \conde takes half of the current resource and passes the other half
+% to its following clauses, except for the last clause that takes all of the current resource. 
+% The biased treatment provides both opportunity and burden: miniKanren users can place more frequently used 
+% goal at the beginning to optimize their programs; however, it might be a 
+% catastrophe if a goal that generates many useless states is placed before more 
+% important goals. Seasoned miniKanreners usually know how to utilize 
+% the unfairness to optimize their programs.
+However, we believe search strategies that is less sensitive to goal order can also be useful to little miniKanreners as well as seasoned ones.
+We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and the answer order of known miniKanren programs.
+The experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
 
@@
 illustrate the costs of answers by running a miniKanren relation. 
-Fig.~\ref{def-repeato} defines the relation \texttt{repeato} that relates a term 
+Fig.~\ref{def-repeato} defines a relation \texttt{repeato} which relates a term 
 \texttt{x} with a list whose elements are all \texttt{x}s.
 
-% Commented out: This idea is borrowed from Silvija Seres's work [*].
-% KC: Seres didn't phrase it this way.
-%   We might need to compare our definition with Seres's one, instead of 
-%   saying the idea is borrowed.
+%TODO compare our definition with Silvija's, Oleg's, and Edward's.
 
@@
 
-In the above example, all search strategies look fair. However, the following 
-example points out that iDFS is not fair.
+In the above example, every search strategy looks fair. However, the following 
+example exposes that iDFS is not fair.
 
@@
 With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
-associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
+associated with a higher cost. iDFS strategy is the cause since it prioritizes 
 the first \conde case considerably. When every \conde case 
@@
 
-% \section{representation of search space}
-% 
-% ``Stream'' is often used to name the representation of search space in 
-% miniKanren. However, the search space is more like a stream of list, because the 
-% information that a stream is thunk is employed to redirect search effort. If the 
-% search space is a normal stream, the information should have been used in a more 
-% trivial way. 
-% 
-% In the rest of this paper, we call the \texttt{car}s of a stream 
-% its \textit{mature part}, and the last \texttt{cdr} its \textit{immature part}.
-% 
-% \section{why disj is unfair}
-% 
-% The multiarity disjuction operator \texttt{disj} combine its sub-goals with 
-% \texttt{disj2}, right associatively. Interestingly, although \texttt{disj} is 
-% unfair, \texttt{disj2} is fair. The core functionality of \texttt{disj2} is 
-% completed by \texttt{append-inf} (Fig.~ref{disj2-and-append-inf}). When both 
-% input streams are infinite, the resulting mature part contains only the mature 
-% part of \texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature 
-% part. However, \texttt{t-inf} and \texttt{s-inf} are swapped in the delayed 
-% recursive call. Hence the search strategy spend computational effort evenly in 
-% two appended streams. As \texttt{disj} applys \texttt{disj2} right 
-% associatively, the left clauses are more frequently explored.
-% 
-% \begin{figure}
-%   \lstinputlisting{Figures/disj2.rkt}
-%   \caption{\texttt{disj2} and \texttt{append-inf}}
-%   \label{disj2-and-append-inf}
-% \end{figure}
+Running the same query with biDFS results in yet another answer list. biDFS 
+essentially organize disjunctive goals into a balanced tree. There is no way to 
+build a balanced and complete tree of size 3, so one clause is allocated more 
+resource than the other two.
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/run-conde-repeato-biDFS.rkt}
+	\end{tabular} 
+\end{center}
+
+If one insert a \texttt{(nevero)} as the forth clause, this run would results 
+in the same answer list as the run with BFS. However, just making every \conde 
+has $2^n$ clauses cannot turn biDFS to BFS.
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/run-conde-repeato-biDFS-1.rkt}
+	\end{tabular}
+\end{center}
 
@@
 
-Our first solution, balanced interleaving DFS (biDFS), is not fair as well. 
-However, it is less sensitive to goal order in disjucntion and is as efficient 
-as iDFS. This search strategy is based on the  observations that a disjuction 
-can be viewed as a binary tree, where \texttt{disj2}s are nodes 
-and sub-goals are leaves, and that the position of a leaf has direct relation 
-with its priority -- the deeper a leaf, the lower computational effort it is 
-shared. In iDFS, the tree is in one of the most unbalanced forms, because 
-\texttt{disj} applys \texttt{disj2} right associatively. Hence, the goal order 
-is very important. The reason why the tree shape can determine priority is that 
-\texttt{disj2} allocates computational effort evenly to its two sub-goals.
+Our first solution, balanced interleaving DFS (biDFS), like iDFS, is not fair . However, it is less sensitive to goal order in disjunct and is as efficient as iDFS.
 
-The key idea of biDFS is to make the tree balanced (Fig.~\ref{balanced-disj}). 
-We introduce a function \texttt{disj*} and its helper \texttt{split}, and change 
-the \texttt{disj} macro to call \texttt{disj*} immediately. \texttt{disj*} 
-essentially construct a balanced \texttt{disj2} tree. The \texttt{split} helper 
-splits elements of \texttt{ls} into two lists of roughly the same length, then 
-apply \texttt{k} to them.
+The reason why iDFS's \texttt{disj} prioritizes its left goals considerably is that the \texttt{disj} applys \texttt{disj2} right associatively, and that 
+\texttt{disj2} allocates resource evenly to its two sub-goals. If a disjunct 
+is viewed as a binary tree where \texttt{disj2}s are nodes and sub-goals are 
+leaves, the deeper a leaf locates, the lower resource it is shared. In iDFS, the tree is in one of the most unbalanced forms.
+
+The key idea of biDFS is to make the tree balanced.
+Fig.~\ref{balanced-disj} shows the difference between iDFS and biDFS.
+We introduce a function \texttt{disj*} and its helper \texttt{split}, and change the \texttt{disj} macro to call \texttt{disj*} immediately.
+\texttt{disj*} essentially construct a balanced \texttt{disj2} tree.
+The \texttt{split} helper splits elements of \texttt{ls} into two lists of roughly the same length, then apply \texttt{k} to the two sub-lists.
 
@@
 
-%TODO compare with Seres's approach
-
-Breadth-first search (BFS) is fair. Our BFS is similar to the one by Seres et 
-al \citet{seres1999algebra}. We conjecture that the two strategies produce
-answers in the same order.
-%TODO need more comparison
-
-In the first subsection, we change the search strategy from iDFS to BFS. In the 
-second subsection we optimize the search engine by using a queue to manage the 
-search order. The two subsections corresponds to two new versions of miniKanren, 
-\texttt{mk-1} and \texttt{mk-2}. We refer to the original version from TRS2 as 
-\texttt{mk-0}.
-
-% In this section we change the search strategy to \textit{breadth-first search} 
-% and optimize it. The whole process is completed in two steps. In the first 
-% step, from mk-0 to mk-1, BFS is introduced. In the second step, mk-1 to mk-3, 
-% BFS is optimized. The initial version, \texttt{mk-0}, is exactly the version in 
-% \emph{The Reasoned Schemer, 2nd Edition}.
+In this section, we describe our BFS and compare it with the one from Seres et 
+al \citep{seres1999algebra}.
+The first subsection is devoted to introducing BFS to miniKanren.
+This subsection results in a new version of miniKanren, \texttt{mk-1} (we call the original version \texttt{mk-0} for short).
+The second subsection describes the equivalent between \texttt{mk-1} and Silvija's BFS.
+In the third and last subsection, we optimize \texttt{mk-1} with the help of a queue, which results in \texttt{mk-2}, the final BFS version.
 
@@
 streams of answers. Thunk streams in \texttt{mk-0} denote delayed 
-computation, however, they do not necessary mean an increment in cost. We use 
+computation, however, they do not necessarily mean an increment in cost. We use 
 the same kind of stream in \texttt{mk-1} but only put thunk at those places 
-where the cost of following answers is increased by one.
+where an increment in cost happens.
 
-To ease discussion, we call the \texttt{car}s of a stream as its \emph{mature} 
+For convenience, we call the \texttt{car}s of a stream as its \emph{mature} 
 part, and its last \texttt{cdr} as its \emph{immature} part. When the stream is 
@@
 \texttt{succeed}, and \texttt{fail}. However, the \texttt{mk-0} version of 
-\texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness if its 
-first input stream, \texttt{s-inf},  is infinite. The resulting mature part 
-contains only the mature part of \texttt{s-inf}. If we want to encode the 
-cost information correctly, the resulting mature part should also contain the 
-mature part of \texttt{t-inf}.
+\texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks the rule when its first input stream, \texttt{s-inf}, has a non-trivial immature part.
+In this case, the resulting mature part contains only the mature part of \texttt{s-inf}.
+If we want to describe the cost information with thunks, the resulting mature part should also contain the mature part of \texttt{t-inf}.
 
@@
 This \texttt{append-inf} calls its helper immediately, with the first argument, 
-\texttt{s?}, set to \texttt{\#{}t}, which \texttt{s-inf} and \texttt{t-inf} haven't been swapped in the driver.
-They are swapped in the third \texttt{cond} clause, where \texttt{s?} is flipped accordingly.
+\texttt{s?}, set to \texttt{\#{}t}, which indicates whether \texttt{s-inf} and \texttt{t-inf} haven't been swapped in the driver.
+\texttt{s-inf} and \texttt{t-inf} are swapped in the third \texttt{cond} clause, where \texttt{s?} is flipped accordingly.
 
@@
 
-\texttt{mk-1} is not efficient in two aspects. \texttt{append-inf} need to copy 
+\texttt{mk-1} is inefficient in two aspects. \texttt{append-inf} need to copy 
 all \texttt{cons} cells of \emph{both} input streams when the first stream is 
-possibly infinite. Besides, \texttt{mk-1} computes answers of the same cost
-at once, even when only a portion is queried. We solve the two problems in the 
-next subsections.
+has a non-trivial immature part. Besides, \texttt{mk-1} computes answers of the same cost at once, even when only a small portion is queried. We solve the two problems in the next subsections.
+
+\subsection{compare our BFS with Seres's}
+
+;; under construction
 
@@
 We avoid generating same-cost answers at once by expressing BFS with a queue, 
-whose elements thunks that return a new stream. Every \texttt{mk-1} stream has 
-zero or one thunk, so it is uninteresting to manage them with queue . Therefore, 
-we change the representation of immature parts from thunks to 
-lists of thunks. Consequently, we also change the way to combine mature and 
-immature part from \texttt{append} to \texttt{cons}.
+whose elements are thunks that return a new stream.
+Every \texttt{mk-1} stream has zero or one thunk, so it is uninteresting to manage them with the queue.
+Therefore, we change the representation of immature parts from thunks to
+thunk lists.
+As a side effect, it is no longer convenient to combine the mature and immature part with \texttt{append}, which would mix answers and thunks in the same list.
+We choose \texttt{cons} as an alternative to \texttt{append}.
 
-After applying this two changes, stream representation becomes more 
-complicated. It motivates us to set up an interface between stream 
+After applying these two changes, stream representation becomes more 
+complicated, which motivates us to set up an interface between stream 
 and the rest of miniKanren. Listed in Fig.~\ref{interface} are all functions 
-being aware of the stream representation, but \texttt{take-inf} and its helper 
-function, which are explained later.
+being aware of the stream representation, except \texttt{take-inf} and its helper function (they are explained later).
 
 The first three functions are constructors: \texttt{empty-inf} makes an 
-empty stream; \texttt{unit-mature-inf} makes a stream with one mature 
-solution; \texttt{unit-immature-inf} makes a stream with one thunk.
+empty stream; \texttt{unit} makes a stream with one mature 
+solution; \texttt{step} makes a stream with one thunk.
 
-The \texttt{append-inf} in \texttt{mk-3} is relatively straightforward compared 
-with the \texttt{mk-1} version. \texttt{append-map-inf} is more tricky on how to 
-construct the new immature part. We can follow the approach in mk-0 and mk-1 -- 
-create a new thunk which invoke append-map-inf recursively when forced. But then 
-we need to be careful: if we construct the thunk when the old immature part is 
-an empty list, the resulting stream might be infinitely unproductive. Beside, 
-all solutions of the next lowest cost in \texttt{s-inf} must be computed when 
-the thunk is invoked. However, sometimes only a portion of these solutions is 
-required to answer a query. To avoid the trouble and too-early computation, 
-we choose to create a new thunk for every existing thunk.
+\texttt{append-inf} combines each sub-parts with \texttt{append}.
 
-The next four functions are used only by \texttt{ifte} and \texttt{once}. 
-Uninterested readers might skip them. \texttt{null-inf?} checks whether a stream 
-is exhausted. \texttt{mature-inf?} checks whether a stream has some mature 
+\texttt{append-map-inf} ...
+
+The next four functions are only depended on by \texttt{ifte} and \texttt{once}. \texttt{null-inf?} checks whether a stream is exhausted. \texttt{mature-inf?} checks whether a stream has some mature 
 solutions. \texttt{car-inf} takes the first solution out of a mature stream. 
@@
 
-\texttt{unit-mature-inf}, \texttt{append-map-inf}, \texttt{empty-inf} and 
+\texttt{unit}, \texttt{append-map-inf}, \texttt{empty-inf} and 
 \texttt{append-inf} form a \emph{MonadPlus}, where they correspond to 
@@
 The first two \texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1.
-The third line runs when both the answer list \texttt{vs} and the queue are empty, which means we have found all answers.
-The forth line re-shape the queue.
-The fifth and last line invoke the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
+The third line runs when both the answer list \texttt{vs} and the queue are empty, which means we have found all the answers.
+The fourth line re-shape the queue.
+The last line invokes the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
 
@@
 
+\section{quantitative evaluation}
+
+%TODO evalo (saying I love you), appendo, reverseo
+;; Kuang-Chen and Weixi plan to put '(I love you), quines, appendo, and reverso here
+
+\section{related works}
+
+;; under construction
+
+Edward points out a disjunct would be `fair' if its tree representation is balanced and full \citep{yang2010adventures}.
+
+Silvija et al \citep{seres1999algebra} also describe a breadth-first search strategy.
+We proof their BFS is equivalent to ours.
+However, ours looks simpler and runs about twice faster in comparison with a straightforward translation of their Haskell code.
+
 \section{conclusion}
 
+\subsection{others}
 %TODO contributions
@@
 We devise a new search strategy, balanced interleaving DFS. The key idea is to 
-make disjunction tree balanced. Changing search strategy from iDFS to biDFS is 
-not hard: 2 new functions and 1 modified macro.
+make disjunct trees balanced. Changing the search strategy from iDFS to biDFS is not hard: 2 new functions and 1 modified macro.
 
-We also devise breadth-first search, which is similar to Seres's BFS. It is not clear whether they are equivalent. Our optimization on BFS with queue, however, is new.
+We also devise breadth-first search, whose intuition is similar to Seres's BFS.
+And we have proved their equivalence. We optimize our BFS with a queue.
 

### 2019-04-28 Paper/paper.tex
fair

@@
 \newcommand{\conde}{\texttt{cond$^e$} }
+\newcommand{\conj}{\texttt{conj}}
+\newcommand{\disj}{\texttt{disj}}
 
@@
 A subtlety in writing relational programs involving a large \conde expression, such as interpreters, is that the order of \conde clauses can affect the speed considerably.
-This is due to the biased allocation of computational resource.
-Interleaving DFS, the search strategy of \conde in miniKanren~\citep{friedman_reasoned_2018}, allocates half resource to the first \conde clause, a quarter to the second, an eighth to the third, and so on.
-Under the hood, it is the unfairness of \texttt{disj}.
 
-We address the unfairness of \texttt{disj} in this work.
-We propose two new search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS).
-biDFS is almost fair -- the maximal ratio of resource among disjunctive goals is bounded by a constant factor.
-BFS is completely fair.
+Under the hood, \conde uses \texttt{conj} to combine goals within a clause, and \texttt{disj} to combine clauses.
+The \texttt{disj} in the current search strategy, interleaving DFS (iDFS), is unfair.
+It allocates half resource to its first goal, then allocates the other half to the rest similarly, except for the last clause that receives all the resource.
+This kind of \texttt{disj} prioritizes left clauses considerably in large \conde expressions.
+
+Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} fairness.
+
+We propose three new search strategies, balanced interleaving DFS (biDFS), which has almost fair \disj, fair DFS (fDFS), which has fair \disj, and breadth-first search (BFS), which has fair \disj and fair \conj.
+The almost fair \texttt{disj} (i.e.
+biDFS) doesn't always allocate resource evenly, however, the maximal ratio of resource is bounded by 2.
+Fair\texttt{disj} allocates resource evenly to goals in the same disjunct.
+BFS has both fair \texttt{disj} and fair \texttt{conj}, where answers are generated in increasing order of cost.
 We prove that our BFS is equivalent to the BFS proposed by Seres et al~\citep{seres1999algebra}.
-We also observe how new search strategies affect the efficiency and the answer order of known miniKanren programs.
+We also observe how new search strategies affect the efficiency and answer order of known miniKanren programs.
 
@@
 
-A search strategy is \emph{fair} if answers of lower costs always come first. 
-The \emph{cost} of an answer is the number of relation applications. Now we 
-illustrate the costs of answers by running a miniKanren relation. 
-Fig.~\ref{def-repeato} defines a relation \texttt{repeato} which relates a term 
-\texttt{x} with a list whose elements are all \texttt{x}s.
-
-%TODO compare our definition with Silvija's, Oleg's, and Edward's.
+We illustrate how a fair search strategy should behavior by running a miniKanren relation, \texttt{repeato} (Fig.~\ref{repeato}), which relates a term \texttt{x} with a non-empty list whose elements are all \texttt{x}s.
 
 \begin{figure}
-  \lstinputlisting{Figures/defrel-repeato.rkt}
-  \caption{\texttt{repeato}}
-  \label{def-repeato}
+	\lstinputlisting{Figures/repeato.rkt}
+	\caption{\texttt{repeato} and an example run}
+	\label{repeato}
 \end{figure}
 
-Consider the following \texttt{run} of \texttt{repeato}.
+\subsection{fair \texttt{disj}}
+
+In the following program, the three \conde clauses differs in trivial way.
+So we expect a search strategy with \emph{fair} \texttt{disj} would mix answers from each clause by grouping similar ones together.
+A search strategy is still considered fair if it permutes some lines of the answer list.
+
 \begin{center}
 	\begin{tabular}{c}
-  \lstinputlisting{Figures/run-repeato-1.rkt}
+		\lstinputlisting{Figures/repeato-fair-disj.rkt}
 	\end{tabular}
@@
 
-The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
-The order of the answers reflects the order miniKanren discovers them:
-the first answer in the list is first discovered. This order is not surprising:
-to generate the first answer, \texttt{'()}, miniKanren needs to apply
-\texttt{repeato} only once and the later answers need more relation
-applications. In this example, the cost of each answer is the same as
-one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
-the cost of \texttt{'(*)} is 2, and so on.
-
-% A query result (list of answers) is in the \emph{cost-respecting} order if no 
-% answer occurs before another answer of a lower cost. In the above example, the 
-% result is cost-respecting. The iDFS search, however, does not generate 
-% cost-respecting answers in general. As an example, consider the following 
-% \texttt{run} of \texttt{repeato}.
-
-In the above example, every search strategy looks fair. However, the following 
-example exposes that iDFS is not fair.
+\texttt{disj} in iDFS is not fair.
+Each clause takes half of the current resource and passes the other half to its following clauses, except for the last clause that takes all the current resource.
+Running the same query results in an answer list with about half of it being lists of \texttt{a}.
 
@@
 	\begin{tabular}{c}
-   \lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
+		\lstinputlisting{Figures/repeato-iDFS.rkt}
 	\end{tabular}
@@
 
-With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
-associated with a higher cost. iDFS strategy is the cause since it prioritizes 
-the first \conde case considerably. When every \conde case 
-are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
-$i$-th case, except the last case, which share the same portion as the second 
-last one. In contrast, the same run with BFS produces answers in an expected 
-order.
+Our biDFS is almost fair. It gives a similar result in this case, except that the \texttt{b} clause takes most resource.
 
@@
 	\begin{tabular}{c}
-   \lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+		\lstinputlisting{Figures/repeato-biDFS-1.rkt}
 	\end{tabular}
@@
 
-Running the same query with biDFS results in yet another answer list. biDFS 
-essentially organize disjunctive goals into a balanced tree. There is no way to 
-build a balanced and complete tree of size 3, so one clause is allocated more 
-resource than the other two.
+When the number of goals is a power of 2, biDFS would be fair.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/run-conde-repeato-biDFS.rkt}
+		\lstinputlisting{Figures/repeato-biDFS-2.rkt}
 	\end{tabular}
@@
 
-If one insert a \texttt{(nevero)} as the forth clause, this run would results 
-in the same answer list as the run with BFS. However, just making every \conde 
-has $2^n$ clauses cannot turn biDFS to BFS.
+\subsection{fair \texttt{conj}}
+
+In the following program, the three \conde clauses differs in trivial way.
+So we expect a search strategy with \emph{fair} \texttt{conj} would mix answers derived from each clause by grouping similar ones together.
+A search strategy is still considered fair if it permutes some lines of the answer list.
+Strategies with unfair \conj produces more answers from the \texttt{a} clause.
+The result with biDFS is similar, except that \texttt{b} and \texttt{c} are swapped.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/run-conde-repeato-biDFS-1.rkt}
+		\lstinputlisting{Figures/repeato-conj-1.rkt}
 	\end{tabular}
 \end{center}
+
+The program above has finite intermediate states (associating \texttt{x} to \texttt{'a}, \texttt{'b}, or \texttt{'c} respectively).
+Therefore, the result is a ``fair'' mix (in the sense of fair \texttt{disj}) of the three search spaces derived from each intermediate state.
+However, this approach is not applicable when the number of intermediate states is infinite.
+A solution also taken in \citep{seres1999algebra} is to organize answers as a stream of list, where each list has finite answer.
+And a \emph{fair} \texttt{conj} should allocate resource evenly among search spaces derived from states in the same bag.
+
+A natural way to bag answers is by their costs.
+The \emph{cost} of an answer is the number of relation applications required to find them (their depth in search tree).
+In the previous examples, the costs of each answer is equal to their lengths.
+In the following example, the cost is equal to the length of inner list plus the length of outer list.
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/repeato-conj-2.rkt}
+	\end{tabular}
+\end{center}
+
+% \section{fairness (old)}
+% 
+% A search strategy is \emph{fair} if answers of lower costs always come first. 
+% The \emph{cost} of an answer is the number of relation applications. Now we 
+% illustrate the costs of answers by running a miniKanren relation. 
+% Fig.~\ref{repeato} defines a relation \texttt{repeato} which relates a term 
+% \texttt{x} with a list whose elements are all \texttt{x}s.
+% 
+% %TODO compare our definition with Silvija's, Oleg's, and Edward's.
+% 
+% \begin{figure}
+%   \lstinputlisting{Figures/defrel-repeato.rkt}
+%   \caption{\texttt{repeato}}
+%   \label{def-repeato}
+% \end{figure}
+% 
+% Consider the following \texttt{run} of \texttt{repeato}.
+% \begin{center}
+%   \begin{tabular}{c}
+%   \lstinputlisting{Figures/run-repeato-1.rkt}
+%    \end{tabular}
+% \end{center}
+% 
+% The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
+% The order of the answers reflects the order miniKanren discovers them:
+% the first answer in the list is first discovered. This order is not surprising:
+% to generate the first answer, \texttt{'()}, miniKanren needs to apply
+% \texttt{repeato} only once and the later answers need more relation
+% applications. In this example, the cost of each answer is the same as
+% one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
+% the cost of \texttt{'(*)} is 2, and so on.
+% 
+% % A query result (list of answers) is in the \emph{cost-respecting} order if no 
+% % answer occurs before another answer of a lower cost. In the above example, the 
+% % result is cost-respecting. The iDFS search, however, does not generate 
+% % cost-respecting answers in general. As an example, consider the following 
+% % \texttt{run} of \texttt{repeato}.
+% 
+% In the above example, every search strategy looks fair. However, the following 
+% example exposes that iDFS is not fair.
+% 
+% \begin{center}
+%   \begin{tabular}{c}
+%    \lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
+%    \end{tabular}
+% \end{center}
+% 
+% With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
+% associated with a higher cost. iDFS strategy is the cause since it prioritizes 
+% the first \conde case considerably. When every \conde case 
+% are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
+% $i$-th case, except the last case, which share the same portion as the second 
+% last one. In contrast, the same run with BFS produces answers in an expected 
+% order.
+% 
+% \begin{center}
+%   \begin{tabular}{c}
+%    \lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+%    \end{tabular}
+% \end{center}
+% 
+% Running the same query with biDFS results in yet another answer list. biDFS 
+% essentially organize disjunctive goals into a balanced tree. There is no way to 
+% build a balanced and complete tree of size 3, so one clause is allocated more 
+% resource than the other two.
+% 
+% \begin{center}
+% 	\begin{tabular}{c}
+% 		\lstinputlisting{Figures/run-conde-repeato-biDFS.rkt}
+% 	\end{tabular} 
+% \end{center}
+% 
+% If one insert a \texttt{(nevero)} as the forth clause, this run would results 
+% in the same answer list as the run with BFS. However, just making every \conde 
+% has $2^n$ clauses cannot turn biDFS to BFS.
+% 
+% \begin{center}
+% 	\begin{tabular}{c}
+% 		\lstinputlisting{Figures/run-conde-repeato-biDFS-1.rkt}
+% 	\end{tabular}
+% \end{center}
 
@@
 \end{figure}
+
+\section{fair DFS}
 

### 2019-04-30 Paper/paper.tex
lots of update

--- 2019-04-25 Paper/paper.tex
@@
 
-%TODO our new searches also change the behavior of conj
-The syntax of a programming language should reflect its semantics. When using a
-disjunction operator in relational programming, a programmer would expect all
-clauses of this disjunct to share the same chance of being explored, as
-these clauses are written in parallel. The existing multi-arity disjunctive
-operator in miniKanren, however, prioritize its clauses by the order of which
-these clauses are written down. We have devised two new search strategies that
-allocate computational effort more fairly in all clauses.
+%TODO rewrite abstract
+%The syntax of a programming language should reflect its semantics.
+When using a disjunctive operator in relational programming, a programmer would expect all sub-goals of this disjunct to share the same chance of being explored, as these clauses are written in parallel.
+The existing multi-arity disjunctive operator in miniKanren, however, prioritize its clauses by the order of which these clauses are written down.
+We have devised two new search strategies that allocate computational effort more fairly in all clauses.
 
@@
 miniKanren programs, especially relational interpreters, have been proven to be useful in solving many problems \citep{byrd2017unified}.
-A subtlety in writing relational programs involving a large \conde expression, such as interpreters, is that the order of \conde clauses can affect the speed considerably.
-This is due to the biased allocation of computational resource.
-Interleaving DFS, the search strategy of \conde in miniKanren~\citep{friedman_reasoned_2018}, allocates half resource to the first \conde clause, a quarter to the second, an eighth to the third, and so on.
-Under the hood, it is the unfairness of \texttt{disj}.
+A subtlety in writing relational programs having large \conde expressions, such as interpreters, is that the order of \conde clauses can affect the speed considerably.
+When a \conde expression is large enough, the left clauses consume almost all the resource and the right ones are hardly explored.
+The unfair \disj{} of the current search strategy, interleaving DFS, is the cause.
+Under the hood, \conde uses \texttt{conj} to create a goal for each clause, and \texttt{disj} to combine these goals to one.
+The current \texttt{disj} allocates half resource to its first goal, then allocates the other half to the rest similarly, except for the last clause which takes all the resource.
 
-We address the unfairness of \texttt{disj} in this work.
-We propose two new search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS).
-biDFS is almost fair -- the maximal ratio of resource among disjunctive goals is bounded by a constant factor.
-BFS is completely fair.
-We prove that our BFS is equivalent to the BFS proposed by Seres et al~\citep{seres1999algebra}.
-We also observe how new search strategies affect the efficiency and the answer order of known miniKanren programs.
+Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} fairness.
+
+We propose three new search strategies, balanced interleaving DFS (biDFS), fair DFS (fDFS), and BFS.
+They have different characteristics of fairness (Table.~\ref{fairness}).
+We prove that our BFS and the BFS proposed by Seres et al~\citep{seres1999algebra} produce the same result when queried.
+But our code is shorter and runs faster.
+We also compare the efficiency of these new search strategies with the existing ones.
+
+\begin{table}
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline 
+		fairness & iDFS & biDFS & fDFS & BFS \\ 
+		\hline 
+		disj & unfair & almost-fair & fair & fair \\ 
+		\hline 
+		conj & unfair & unfair & unfair & fair \\ 
+		\hline 
+	\end{tabular} 
+	\caption{fairness of search strategies}
+	\label{fairness}
+\end{table}
 
@@
 
-A search strategy is \emph{fair} if answers of lower costs always come first. 
-The \emph{cost} of an answer is the number of relation applications. Now we 
-illustrate the costs of answers by running a miniKanren relation. 
-Fig.~\ref{def-repeato} defines a relation \texttt{repeato} which relates a term 
-\texttt{x} with a list whose elements are all \texttt{x}s.
-
-%TODO compare our definition with Silvija's, Oleg's, and Edward's.
+We demonstrate the aspects (\disj{} or \conj{}) and levels (unfair, almost-fair, or fair) of fairness by running queries about \texttt{repeato}, a relational definition that relates a term \texttt{x} with a non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
 
 \begin{figure}
-  \lstinputlisting{Figures/defrel-repeato.rkt}
-  \caption{\texttt{repeato}}
-  \label{def-repeato}
+	\lstinputlisting{Figures/repeato.rkt}
+	\caption{\texttt{repeato} and an example run}
+	\label{repeato}
 \end{figure}
 
-Consider the following \texttt{run} of \texttt{repeato}.
+\subsection{fair \texttt{disj}}
+
+In the following program, the three \conde clauses differ in a trivial way.
+So we expect lists of each sort constitute $1/4$ of the answer list.
+However, iDFS, the current search strategy, gives us much more lists of \texttt{a} than other sorts of lists.
+And some sorts (e.g.
+lists of \texttt{c}) are hardly found.
+The situation would be worse if we add more \conde clauses.
+
 \begin{center}
 	\begin{tabular}{c}
-  \lstinputlisting{Figures/run-repeato-1.rkt}
+		\lstinputlisting{Figures/repeato-disj-iDFS.rkt}
 	\end{tabular}
@@
 
-The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
-The order of the answers reflects the order miniKanren discovers them:
-the first answer in the list is first discovered. This order is not surprising:
-to generate the first answer, \texttt{'()}, miniKanren needs to apply
-\texttt{repeato} only once and the later answers need more relation
-applications. In this example, the cost of each answer is the same as
-one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
-the cost of \texttt{'(*)} is 2, and so on.
-
-% A query result (list of answers) is in the \emph{cost-respecting} order if no 
-% answer occurs before another answer of a lower cost. In the above example, the 
-% result is cost-respecting. The iDFS search, however, does not generate 
-% cost-respecting answers in general. As an example, consider the following 
-% \texttt{run} of \texttt{repeato}.
-
-In the above example, every search strategy looks fair. However, the following 
-example exposes that iDFS is not fair.
+On the contrary, search strategies with fair \disj{} (e.g. fDFS and BFS) give a nice answer list.
 
@@
 	\begin{tabular}{c}
-   \lstinputlisting{Figures/run-conde-repeato-iDFS.rkt}
+		\lstinputlisting{Figures/repeato-disj-fair.rkt}
 	\end{tabular}
@@
 
-With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
-associated with a higher cost. iDFS strategy is the cause since it prioritizes 
-the first \conde case considerably. When every \conde case 
-are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
-$i$-th case, except the last case, which share the same portion as the second 
-last one. In contrast, the same run with BFS produces answers in an expected 
-order.
+Search strategies with almost-fair \disj{} (e.g.
+biDFS) give the same result in this case.
+However, as its name suggests, almost-fair strategies are not always fair.
+Fortunately, the maximal ratio of the allocated resource is bounded by a constant.
+Our biDFS is fair when the number of goals is a power of 2, otherwise, some goals are allocated twice more resource than the others.
+In following example, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated more resource.
 
@@
 	\begin{tabular}{c}
-   \lstinputlisting{Figures/run-conde-repeato-BFS.rkt}
+		\lstinputlisting{Figures/repeato-disj-biDFS.rkt}
 	\end{tabular}
@@
 
-Running the same query with biDFS results in yet another answer list. biDFS 
-essentially organize disjunctive goals into a balanced tree. There is no way to 
-build a balanced and complete tree of size 3, so one clause is allocated more 
-resource than the other two.
+\subsection{fair \texttt{conj}}
+
+In the following program, the three \conde clauses differ in a trivial way.
+So we expect lists of each sort constitute  $1/4$ of the answer list.
+However, search strategies with unfair \conj{} gives us much more lists of \texttt{a} than other sorts of lists.
+And some sorts (e.g.
+lists of \texttt{c}) are hardly found.
+The situation would be worse if we add more \conde clauses.
+The result with biDFS, whose \conj{} is also unfair, is similar, but due to its different \disj{}, the position of \texttt{b} and \texttt{c} and swapped.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/run-conde-repeato-biDFS.rkt}
+		\lstinputlisting{Figures/repeato-conj-unfair.rkt}
 	\end{tabular}
@@
 
-If one insert a \texttt{(nevero)} as the forth clause, this run would results 
-in the same answer list as the run with BFS. However, just making every \conde 
-has $2^n$ clauses cannot turn biDFS to BFS.
+On the contrary, search strategies with fair \conj{} (e.g. BFS) give a nice answer list.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/run-conde-repeato-biDFS-1.rkt}
+		\lstinputlisting{Figures/repeato-conj-fair.rkt}
+	\end{tabular}
+\end{center}
+
+A more interesting situation is when the first conjunctive goal produces infinite many states.
+Consider the following example, a naive specification of fair \conj{} might require search strategies to produce all sorts of singleton lists, but no longer lists, which makes the strategies \emph{incomplete}.
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/repeato-conj-infinite-naive.rkt}
+	\end{tabular}
+\end{center}
+
+Fairness is good but is not good enough to kick away completeness.
+A solution also taken in \citep{seres1999algebra} is bagging states and requiring that search spaces derived from states in the same bag are treated fairly.
+A natural way to bag states is by their costs.
+The \emph{cost} of a state is its depth in the search tree (i.e.
+the number of calls to relational definitions required to find them) \citep{seres1999algebra}.
+BFS is more than fair -- it produces answers in increasing order of cost.
+Running the same program gives an answer list sorted by answers' costs.
+In this case, the cost of an answer is equal to the length of the inner lists plus the length of the outer list.
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/repeato-conj-infinite-sof.rkt}
 	\end{tabular}
@@
 
-Our first solution, balanced interleaving DFS (biDFS), like iDFS, is not fair . However, it is less sensitive to goal order in disjunct and is as efficient as iDFS.
-
-The reason why iDFS's \texttt{disj} prioritizes its left goals considerably is that the \texttt{disj} applys \texttt{disj2} right associatively, and that 
-\texttt{disj2} allocates resource evenly to its two sub-goals. If a disjunct 
-is viewed as a binary tree where \texttt{disj2}s are nodes and sub-goals are 
-leaves, the deeper a leaf locates, the lower resource it is shared. In iDFS, the tree is in one of the most unbalanced forms.
-
-The key idea of biDFS is to make the tree balanced.
-Fig.~\ref{balanced-disj} shows the difference between iDFS and biDFS.
-We introduce a function \texttt{disj*} and its helper \texttt{split}, and change the \texttt{disj} macro to call \texttt{disj*} immediately.
-\texttt{disj*} essentially construct a balanced \texttt{disj2} tree.
-The \texttt{split} helper splits elements of \texttt{ls} into two lists of roughly the same length, then apply \texttt{k} to the two sub-lists.
+Balanced interleaving DFS (biDFS) has almost-fair \disj{} and unfair \conj{}.
+The implementation of biDFS differs from iDFS in the \disj{} macro.
+We list the new \disj{} with its helpers in Fig.~\ref{balanced-disj}.
+The first helper function, \texttt{split}, takes a list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} into two sub-lists of roughly equal length, and returns the application of \texttt{k} to the two sub-lists.
+\texttt{disj*} takes a non-empty list of goals \texttt{gs} and returns a goal.
+With the help of \texttt{split}, it essentially constructs a \emph{balanced} binary tree where leaves are goals in \texttt{gs} and nodes are \texttt{disj2}, whence the name of this search strategy.
+In contrast, the \disj{} in iDFS essentially constructs the same sort of binary tree in one of the most unbalanced forms.
 
@@
 
+\section{fair DFS}
+
+Fair DFS (fDFS) has fair \disj{} and unfair \conj{}.
+The implementation of fDFS differs from iDFS's in \texttt{disj2} (Fig.~\ref{fDFS}).
+\texttt{disj2} is changed to call a new and fair version of \texttt{append-inf}.
+\texttt{append-inf/fair} immediately calls its helper, \texttt{append-inf/fair\^{}}, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which indicates that \texttt{s-inf} and \texttt{t-inf} haven't been swapped.
+The swapping happens in the third \texttt{cond} clause of the helper, where \texttt{s?} is changed accordingly.
+The first two \texttt{cond} clauses essentially copy the \texttt{car}s and stop recursion when one of the input spaces is obviously finite.
+The third clause, as we mentioned early, is just for swapping.
+When the fourth and last clause runs, we know that both \texttt{s-inf} and \texttt{t-inf} are ended with a thunk.
+In this case, a new thunk is constructed.
+The new thunk calls the driver recursively.
+Here changing the order of \texttt{t-inf} and \texttt{s-inf} won't hurt the fairness (though it will change the order of answers).
+We swapped them back so that answers are produced in a more natural order.
+
+\begin{figure}
+	\lstinputlisting{Figures/fDFS.rkt}
+	\caption{How fDFS differs from iDFS}
+	\label{fDFS}
+\end{figure}
+
 \section{breadth-first search}
 
-In this section, we describe our BFS and compare it with the one from Seres et 
-al \citep{seres1999algebra}.
-The first subsection is devoted to introducing BFS to miniKanren.
-This subsection results in a new version of miniKanren, \texttt{mk-1} (we call the original version \texttt{mk-0} for short).
-The second subsection describes the equivalent between \texttt{mk-1} and Silvija's BFS.
-In the third and last subsection, we optimize \texttt{mk-1} with the help of a queue, which results in \texttt{mk-2}, the final BFS version.
+Our BFS is fair in both \disj{} and \conj{}.
+Its implementation is based on fDFS (not iDFS).
+All we have to do is changing the use of \texttt{append-inf} in \texttt{append-map-inf} to \texttt{append-inf/fair}.
+After making this change, \texttt{append-inf} is useless.
 
-\subsection{change search strategy from iDFS to BFS}
+The implementation can be improved in two aspects.
+First, as we mentioned in section 2.2, our BFS bag states by their cost.
+However, in this implementation, it is unclear where this information is recorded.
+Second, \texttt{append-inf/fair} is space inefficient.
+It makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ is the ``length'' of each input search space.
+We address these issues in the first subsection.
 
-In both \texttt{mk-0} and \texttt{mk-1}, search spaces are represented by 
-streams of answers. Thunk streams in \texttt{mk-0} denote delayed 
-computation, however, they do not necessarily mean an increment in cost. We use 
-the same kind of stream in \texttt{mk-1} but only put thunk at those places 
-where an increment in cost happens.
+Both our BFS and Seres's BFS \citep{seres1999algebra} produce answers in increasing order of cost.
+So it is interesting to see if they are equivalent.
+We prove the equivalence in Coq.
+The details are in the second subsection.
 
-For convenience, we call the \texttt{car}s of a stream as its \emph{mature} 
-part, and its last \texttt{cdr} as its \emph{immature} part. When the stream is 
-definitely finite, its immature part is an empty list, otherwise, it is a 
-thunk. We sometimes say a stream is immature to mean its mature part is empty.
+% The first subsection describe an optimized BFS.
+The optimization makes the type of search space representation more clear and reduces time-complexity of some function.
+The second subsection compares the pure subset of the optimized BFS with the BFS found in \citep{seres1999algebra}.
+We prove the two BFSs return the same answer list.
 
-Streams denote cost correctly when they are constructed by \texttt{==}, 
-\texttt{succeed}, and \texttt{fail}. However, the \texttt{mk-0} version of 
-\texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks the rule when its first input stream, \texttt{s-inf}, has a non-trivial immature part.
-In this case, the resulting mature part contains only the mature part of \texttt{s-inf}.
-If we want to describe the cost information with thunks, the resulting mature part should also contain the mature part of \texttt{t-inf}.
+\subsection{optimized BFS}
+
+As we mentioned in section 2.2, our BFS bag states by their cost.
+The bagging information is recorded subtly -- the \texttt{car}s of a search space have cost 0 (they are in the same bag), and the costs of states in thunk are increased by one.
+It is even more difficult to see \texttt{append-inf/fair} and the modified \texttt{append-map-inf} respects the cost information.
+We make things clear by changing the type of search space, modify related function definitions, and introducing a few more functions.
+
+The new type is a pair whose \texttt{car} is a list of state (the bag), and whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search space.
+A falsy \texttt{cdr} indicates that the search space is obviously finite.
+
+Both modified functions and introduced ones are listed in Fig.~\ref{BFS-opt}.
+The first three functions in Fig.~\ref{BFS-opt} are search space constructor.
+They are newly introduced.
+\texttt{none} makes an empty search space.
+\texttt{unit} makes an space from one state.
+\texttt{step} makes a space from a thunk.
+The next function, \texttt{split}, is used to implement impure features (i.e.
+\texttt{ifte} and \texttt{once}).
+It takes a space \texttt{s-inf} and two continuations \texttt{ks} and \texttt{kf}.
+When \texttt{s-inf} contains some states, \texttt{ks} is called with the first state and the rest space.
+Otherwise, \texttt{kf} is called with no argument.
+Here `s' and `f' means `succeed' and `fail' respectively.
+The remaining functions do the same thing as before.
+Now it should be not difficult to see that \texttt{append-inf/fair} and \texttt{append-map-inf} do respect cost information.
+
+Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space inefficiency -- the use of \texttt{append} helps us to reuse the first bag of \texttt{t-inf}.
+
+Noted that some functions in the list constitute a \emph{MonadPlus}: \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and \texttt{append-inf} correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, and \texttt{mplus} respectively.
 
 \begin{figure}
-	 \lstinputlisting{Figures/append-inf-0.rkt}	
-	 \caption{\texttt{append-inf} in \texttt{mk-0}}
-	 \label{append-inf-0}
+	\lstinputlisting{Figures/BFS-opt.rkt}	
+	\caption{interface functions in optimized BFS}
+	\label{BFS-opt}
 \end{figure}
 
-The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) 
-gain fairness by combining the mature parts in the fashion of \texttt{append}. 
-This \texttt{append-inf} calls its helper immediately, with the first argument, 
-\texttt{s?}, set to \texttt{\#{}t}, which indicates whether \texttt{s-inf} and \texttt{t-inf} haven't been swapped in the driver.
-\texttt{s-inf} and \texttt{t-inf} are swapped in the third \texttt{cond} clause, where \texttt{s?} is flipped accordingly.
+\subsection{comparison with Silvija's BFS}
 
-\begin{figure}
-	 \lstinputlisting{Figures/append-inf-1.rkt}	
-	 \caption{\texttt{append-inf} in \texttt{mk-1}}
-	 \label{append-inf-1}
-\end{figure}
+In this section, we compare the pure subset of our optimized BFS with the BFS found in \citep{seres1999algebra}. We focus on the pure subset because Silvija's system is pure.
 
-\texttt{mk-1} is inefficient in two aspects. \texttt{append-inf} need to copy 
-all \texttt{cons} cells of \emph{both} input streams when the first stream is 
-has a non-trivial immature part. Besides, \texttt{mk-1} computes answers of the same cost at once, even when only a small portion is queried. We solve the two problems in the next subsections.
+To compare efficiency, we translate her Haskell code into Racket (See supplements for the translated code), and embed it into miniKanren.
+The translation is fairly straightforward due to the similarity in both logic programming system and search space representation.
+The translated code is less efficient when running our benchmark.
+Details about efficiency difference are in section 6.
 
-\subsection{compare our BFS with Seres's}
+We prove the two search strategies are equivalent in Coq.
+Since search space can be infinite, we should use a co-inductive data type.
+However, Coq is too strict in the guardedness condition to accept a direct translation of the implementations.
+Therefore, we prove core theorems with finite search space instead.
+In order to generalize the conclusion to the cases with infinite search space, we prove a few more theorems saying that whenever we query answers lower than some finite cost, we can restrict goals to truncate search spaces at some finite depth without changing the query result.
+(See supplements for the formal proof)
 
-;; under construction
-
-\subsection{optimize breadth-first search}
-
-We avoid generating same-cost answers at once by expressing BFS with a queue, 
-whose elements are thunks that return a new stream.
-Every \texttt{mk-1} stream has zero or one thunk, so it is uninteresting to manage them with the queue.
-Therefore, we change the representation of immature parts from thunks to
-thunk lists.
-As a side effect, it is no longer convenient to combine the mature and immature part with \texttt{append}, which would mix answers and thunks in the same list.
-We choose \texttt{cons} as an alternative to \texttt{append}.
-
-After applying these two changes, stream representation becomes more 
-complicated, which motivates us to set up an interface between stream 
-and the rest of miniKanren. Listed in Fig.~\ref{interface} are all functions 
-being aware of the stream representation, except \texttt{take-inf} and its helper function (they are explained later).
-
-The first three functions are constructors: \texttt{empty-inf} makes an 
-empty stream; \texttt{unit} makes a stream with one mature 
-solution; \texttt{step} makes a stream with one thunk.
-
-\texttt{append-inf} combines each sub-parts with \texttt{append}.
-
-\texttt{append-map-inf} ...
-
-The next four functions are only depended on by \texttt{ifte} and \texttt{once}. \texttt{null-inf?} checks whether a stream is exhausted. \texttt{mature-inf?} checks whether a stream has some mature 
-solutions. \texttt{car-inf} takes the first solution out of a mature stream. 
-\texttt{cdr-inf} drops the first solution of a mature stream. Finally, 
-\texttt{force-inf} forces an immature stream to do more computation.
-
-\texttt{unit}, \texttt{append-map-inf}, \texttt{empty-inf} and 
-\texttt{append-inf} form a \emph{MonadPlus}, where they correspond to 
-\texttt{unit}, \texttt{bind}, \texttt{mzero}, and \texttt{mplus} respectively.
-
-\begin{figure}
-	 \lstinputlisting{Figures/interface.rkt}	
-	 \caption{Functions being aware of stream representation}
-	 \label{interface}
-\end{figure}
-
-The last interesting function is \texttt{take-inf} (Fig.~\ref{take-inf-3-1}). 
-Its first parameter, \texttt{vs}, is a list of solutions. The next two parameters, \texttt{P} and \texttt{Q}, together represents a queue. 
-The first two \texttt{cond} lines are very similar to their counterparts in mk-0 and mk-1.
-The third line runs when both the answer list \texttt{vs} and the queue are empty, which means we have found all the answers.
-The fourth line re-shape the queue.
-The last line invokes the first thunk in the queue and use the mature part of the resulting stream, \texttt{s-inf}, as the new \texttt{vs}, and enqueuing \texttt{s-inf}'s thunks.
-
-\begin{figure}
-	 \lstinputlisting{Figures/take-inf-3-1.rkt}	
-	 \caption{\texttt{take-inf} in \texttt{mk-3-1}}
-	 \label{take-inf-3-1}
-\end{figure}
+;;TODO to be more specific?
 
@@
 
-%TODO evalo (saying I love you), appendo, reverseo
-;; Kuang-Chen and Weixi plan to put '(I love you), quines, appendo, and reverso here
+In this section, we compare the efficiency of search strategies.
+A concise description is in Table~\ref{compare-efficiency}.
+A hyphen means running out of memory.
+The first three benchmarks are taken from \citep{friedman_reasoned_2018}.
+Next two benchmarks about quine are modified from a similar test case in \citep{byrd2017unified}.
+The modifications are made to circumvent the need for symbolic constraint.
+Our version generates de Bruijnized expressions and forbids closures going into list.
+The two benchmarks differ in the \conde clause order of their relation interpreters.
+The last two benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love you)}.
+This benchmark is also inspired by \citep{byrd2017unified}.
+Again, they differ in the \conde clause order of their relation interpreters.
+The first one has elimination rules (i.e.
+application, \texttt{car}, and \texttt{cdr}) at the end, while the other has them at the beginning.
+We conjecture that iDFS would perform badly in the second case because elimination rules complicate the problem when running backward.
+Our statistics support our conjecture.
+
+In general, only iDFS and biDFS constantly perform well.
+Among them, biDFS seems to be less sensitive to change in \conde clause order (see the last four benchmarks).
+The other search strategies all have fair \disj{}.
+And they all perform badly in the \texttt{very-recursiveo} benchmark.
+However, the drawback of having fair \disj{} alone (i.e.
+fDFS) is not shown elsewhere.
+Fair \conj{} impose overhead constantly except in \texttt{appendo}.
+The reason might be that strategies with fair \conj{} tend to keep more intermediate states in the memory.
+Among the BFSs, our version performs better in most cases, and equally well elsewhere.
+
+\begin{table}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+	\hline 
+	benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  \\
+	\hline
+	very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
+	                & 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
+	                & 300000 & 2160 & 2836 &    - & 6137 &    - \\
+	\hline 
+	appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
+	         & 200 & 224 & 222 & 221 & 226 & 218 \\ 
+	         & 300 & 617 & 634 & 593 & 631 & 622 \\ 
+	\hline 
+	reverseo & 10 &   5 &   3 &   3 &     38 &     85 \\ 
+		     & 20 & 107 &  98 &  51 &   4862 &   5844 \\
+		     & 30 & 446 & 442 & 485 & 123288 & 132159 \\ 
+    \hline
+    quine-1 & 1 &  71 &  44 & 69 & - & - \\ 
+	        & 2 & 127 & 142 & 95 & - & - \\ 
+	        & 3 & 114 & 114 & 93 & - & - \\ 
+	\hline
+    quine-2 & 1 & 147 & 112 &  56 & - & - \\ 
+	        & 2 & 161 & 123 & 101 & - & - \\ 
+	        & 3 & 289 & 189 & 104 & - & - \\ 
+	\hline 
+	'(I love you)-1 &  99 & 56 & 15 & 22 &  74 & 165 \\ 
+	                & 198 & 53 & 72 & 55 &  47 &  74 \\
+	                & 297 & 72 & 90 & 44 & 181 & 365 \\ 
+    \hline
+    '(I love you)-2 &  99 & 242 &  61 & 16 &  66 &  99 \\ 
+	                & 198 & 445 & 110 & 60 &  42 &  64 \\
+	                & 297 & 476 & 146 & 49 & 186 & 322 \\ 
+	\hline 
+\end{tabular}
+\caption{The results of a quantitative evaluation: running times of benchmarks in milliseconds}
+\label{compare-efficiency}
+\end{table}
 
@@
 
-;; under construction
-
-Edward points out a disjunct would be `fair' if its tree representation is balanced and full \citep{yang2010adventures}.
+Edward points out a disjunct complex would be `fair' if it is a full and balanced tree \citep{yang2010adventures}.
 
@@
 We proof their BFS is equivalent to ours.
-However, ours looks simpler and runs about twice faster in comparison with a straightforward translation of their Haskell code.
+However, ours looks simpler and performs better in comparison with a straightforward translation of their Haskell code.
 
@@
 
-\subsection{others}
 %TODO contributions
-%TODO future works
 
-We devise a new search strategy, balanced interleaving DFS. The key idea is to 
-make disjunct trees balanced. Changing the search strategy from iDFS to biDFS is not hard: 2 new functions and 1 modified macro.
+% We devise a new search strategy, balanced interleaving DFS.
+The key idea is to make disjunct trees balanced.
+Changing the search strategy from iDFS to biDFS is not hard: 2 new functions and 1 modified macro.
 
-We also devise breadth-first search, whose intuition is similar to Seres's BFS.
-And we have proved their equivalence. We optimize our BFS with a queue.
+% We also devise breadth-first search, whose intuition is similar to Seres's BFS. And we have proved their equivalence. We optimize our BFS with a queue.
 

### 2019-04-30 Paper/paper.tex
revise

@@
 %TODO rewrite abstract
-%The syntax of a programming language should reflect its semantics.
-When using a disjunctive operator in relational programming, a programmer would expect all sub-goals of this disjunct to share the same chance of being explored, as these clauses are written in parallel.
-The existing multi-arity disjunctive operator in miniKanren, however, prioritize its clauses by the order of which these clauses are written down.
-We have devised two new search strategies that allocate computational effort more fairly in all clauses.
+%The syntax of a programming language should reflect its semantics. When using 
+%a disjunctive operator in relational programming, a programmer would expect 
+%all 
+%sub-goals of this disjunct to share the same chance of being explored, as 
+%these 
+%clauses are written in parallel. The existing multi-arity disjunctive operator 
+%in miniKanren, however, prioritize its clauses by the order of which these 
+%clauses are written down. We have devised two new search strategies that 
+%allocate computational effort more fairly in all clauses.
 
@@
 
-miniKanren programs, especially relational interpreters, have been proven to be useful in solving many problems \citep{byrd2017unified}.
-A subtlety in writing relational programs having large \conde expressions, such as interpreters, is that the order of \conde clauses can affect the speed considerably.
-When a \conde expression is large enough, the left clauses consume almost all the resource and the right ones are hardly explored.
-The unfair \disj{} of the current search strategy, interleaving DFS, is the cause.
-Under the hood, \conde uses \texttt{conj} to create a goal for each clause, and \texttt{disj} to combine these goals to one.
-The current \texttt{disj} allocates half resource to its first goal, then allocates the other half to the rest similarly, except for the last clause which takes all the resource.
+miniKanren programs, especially relational interpreters, have been proven to be 
+useful in solving many problems \citep{byrd2017unified}. A subtlety in writing 
+relational programs having large \conde expressions, such as interpreters, is 
+that the order of \conde clauses can affect the speed considerably. When a 
+\conde expression is large enough, the left clauses consume almost all the 
+resource and the right ones are hardly explored. The unfair \disj{} of the 
+current search strategy, interleaving DFS, is the cause. Under the hood, \conde 
+uses \texttt{conj} to create a goal for each clause, and \texttt{disj} to 
+combine these goals to one. The current \texttt{disj} allocates half resource 
+to its first goal, then allocates the other half to the rest similarly, except 
+for the last clause which takes all the resource.
 
-Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} fairness.
+Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} 
+fairness.
 
-We propose three new search strategies, balanced interleaving DFS (biDFS), fair DFS (fDFS), and BFS.
-They have different characteristics of fairness (Table.~\ref{fairness}).
-We prove that our BFS and the BFS proposed by Seres et al~\citep{seres1999algebra} produce the same result when queried.
-But our code is shorter and runs faster.
-We also compare the efficiency of these new search strategies with the existing ones.
+We propose three new search strategies, balanced interleaving DFS (biDFS), fair 
+DFS (fDFS), and BFS. They have different characteristics of fairness 
+(Table.~\ref{fairness}). We prove that our BFS and the BFS proposed by Seres et 
+al~\citep{seres1999algebra} produce the same result when queried. But our code 
+is shorter and runs faster. Because the two BFSs are equivalent, we do not 
+distinguish them in most places, except section 6 (quantitative evaluation).
 
@@
 % \conde takes half of the current resource and passes the other half
-% to its following clauses, except for the last clause that takes all of the current resource. 
-% The biased treatment provides both opportunity and burden: miniKanren users can place more frequently used 
+% to its following clauses, except for the last clause that takes all of the 
+%current resource. 
+% The biased treatment provides both opportunity and burden: miniKanren users 
+%can place more frequently used 
 % goal at the beginning to optimize their programs; however, it might be a 
-% catastrophe if a goal that generates many useless states is placed before more 
+% catastrophe if a goal that generates many useless states is placed before 
+%more 
 % important goals. Seasoned miniKanreners usually know how to utilize 
-% the unfairness to optimize their programs.
-However, we believe search strategies that is less sensitive to goal order can also be useful to little miniKanreners as well as seasoned ones.
-We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and the answer order of known miniKanren programs.
-The experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.
+% the unfairness to optimize their programs. However, we believe search 
+%strategies that is less sensitive to goal order can also be useful to little 
+%miniKanreners as well as seasoned ones. We propose two such search strategies, 
+%balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe 
+%how they affect the efficiency and the answer order of known miniKanren 
+%programs. The experiment is conducted with the miniKanren from \textit{The 
+%Reasoned Schemer, 2nd Edition}.
 
@@
 
-We demonstrate the aspects (\disj{} or \conj{}) and levels (unfair, almost-fair, or fair) of fairness by running queries about \texttt{repeato}, a relational definition that relates a term \texttt{x} with a non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
+We demonstrate the aspects (\disj{} or \conj{}) and levels (unfair, 
+almost-fair, or fair) of fairness by running queries about \texttt{repeato}, a 
+relational definition that relates a term \texttt{x} with a non-empty list 
+whose elements are \texttt{x} (Fig.~\ref{repeato}).
 
@@
 
-In the following program, the three \conde clauses differ in a trivial way.
-So we expect lists of each sort constitute $1/4$ of the answer list.
-However, iDFS, the current search strategy, gives us much more lists of \texttt{a} than other sorts of lists.
-And some sorts (e.g.
-lists of \texttt{c}) are hardly found.
-The situation would be worse if we add more \conde clauses.
+In the following program, the three \conde clauses differ in a trivial way. So 
+we expect lists of each sort constitute $1/4$ of the answer list. However, 
+iDFS, the current search strategy, gives us much more lists of \texttt{a} than 
+other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are hardly 
+found. The situation would be worse if we add more \conde clauses.
 
@@
 
-On the contrary, search strategies with fair \disj{} (e.g. fDFS and BFS) give a nice answer list.
+On the contrary, search strategies with fair \disj{} (e.g. fDFS and BFS) give a 
+nice answer list.
 
@@
 
-Search strategies with almost-fair \disj{} (e.g.
-biDFS) give the same result in this case.
-However, as its name suggests, almost-fair strategies are not always fair.
-Fortunately, the maximal ratio of the allocated resource is bounded by a constant.
-Our biDFS is fair when the number of goals is a power of 2, otherwise, some goals are allocated twice more resource than the others.
-In following example, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated more resource.
+Search strategies with almost-fair \disj{} (e.g. biDFS) give the same result in 
+this case. However, as its name suggests, almost-fair strategies are not always 
+fair. Fortunately, the maximal ratio of the allocated resource among 
+disjunctive goals is bounded by a constant. Our biDFS is fair when the number 
+of goals is a power of 2, otherwise, some goals are allocated twice more 
+resource than the others. In following example, the clauses of \texttt{b}, 
+\texttt{c}, and \texttt{d} are allocated more resource.
 
@@
 
-In the following program, the three \conde clauses differ in a trivial way.
-So we expect lists of each sort constitute  $1/4$ of the answer list.
-However, search strategies with unfair \conj{} gives us much more lists of \texttt{a} than other sorts of lists.
-And some sorts (e.g.
-lists of \texttt{c}) are hardly found.
-The situation would be worse if we add more \conde clauses.
-The result with biDFS, whose \conj{} is also unfair, is similar, but due to its different \disj{}, the position of \texttt{b} and \texttt{c} and swapped.
+In the following program, the three \conde clauses differ in a trivial way. So 
+we expect lists of each sort constitute  $1/4$ of the answer list. However, 
+search strategies with unfair \conj{} (e.g. iDFS, fDFS) give us much 
+more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
+of \texttt{c}) are hardly found. The situation would be worse if we add more 
+\conde clauses. The result with biDFS, whose \conj{} is also unfair, is 
+similar, but due to its different \disj{}, the position of \texttt{b} and 
+\texttt{c} and swapped.
 
@@
 
-On the contrary, search strategies with fair \conj{} (e.g. BFS) give a nice answer list.
+On the contrary, search strategies with fair \conj{} (e.g. BFS) give a nice 
+answer list.
 
@@
 
-A more interesting situation is when the first conjunctive goal produces infinite many states.
-Consider the following example, a naive specification of fair \conj{} might require search strategies to produce all sorts of singleton lists, but no longer lists, which makes the strategies \emph{incomplete}.
+A more interesting situation is when the first conjunctive goal produces 
+infinite many states. Consider the following example, a naive specification of 
+fair \conj{} might require search strategies to produce all sorts of singleton 
+lists, but no longer ones, which makes the strategies \emph{incomplete}.
 
@@
 
-Fairness is good but is not good enough to kick away completeness.
-A solution also taken in \citep{seres1999algebra} is bagging states and requiring that search spaces derived from states in the same bag are treated fairly.
-A natural way to bag states is by their costs.
-The \emph{cost} of a state is its depth in the search tree (i.e.
-the number of calls to relational definitions required to find them) \citep{seres1999algebra}.
-BFS is more than fair -- it produces answers in increasing order of cost.
-Running the same program gives an answer list sorted by answers' costs.
-In this case, the cost of an answer is equal to the length of the inner lists plus the length of the outer list.
+Fairness is good but is not good enough to kick away completeness. A solution  
+is bagging states and requiring that 
+search spaces derived from states in the same bag are treated fairly. A natural 
+way to bag states is by their costs.
+This approach is also taken in \citep{seres1999algebra}.
+The \emph{cost} of a state is its depth in 
+the search tree (i.e. the number of calls to relational definitions required to 
+find them) \citep{seres1999algebra}. BFS is more than fair -- it produces 
+answers in increasing order of cost. Running the same program gives an answer 
+list sorted by answers' costs. In this case, the cost of an answer is equal to 
+the length of the inner lists plus the length of the outer list.
+
+Our definition of fair \conj{} is difference from the one in 
+\citep{seres1999algebra}. They consider a \conj{} (or "selection rule" in their 
+words) is fair if it ``would allow one to choose the literals in different 
+order''\citep{seres1999algebra}. This requirement is not stronger than 
+\emph{completeness}. We prefer our definition because it avoids overlapping 
+with a known concept.
 
@@
 
-Balanced interleaving DFS (biDFS) has almost-fair \disj{} and unfair \conj{}.
-The implementation of biDFS differs from iDFS in the \disj{} macro.
-We list the new \disj{} with its helpers in Fig.~\ref{balanced-disj}.
-The first helper function, \texttt{split}, takes a list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} into two sub-lists of roughly equal length, and returns the application of \texttt{k} to the two sub-lists.
-\texttt{disj*} takes a non-empty list of goals \texttt{gs} and returns a goal.
-With the help of \texttt{split}, it essentially constructs a \emph{balanced} binary tree where leaves are goals in \texttt{gs} and nodes are \texttt{disj2}, whence the name of this search strategy.
-In contrast, the \disj{} in iDFS essentially constructs the same sort of binary tree in one of the most unbalanced forms.
-
 \begin{figure}
@@
 
+Balanced interleaving DFS (biDFS) has almost-fair \disj{} and unfair \conj{}. 
+The implementation of biDFS differs from iDFS in the \disj{} macro. We list the 
+new \disj{} with its helpers in Fig.~\ref{balanced-disj}. The first helper 
+function, \texttt{split}, takes a list of goals \texttt{ls} and a procedure 
+\texttt{k}, partitions \texttt{ls} into two sub-lists of roughly equal length, 
+and returns the application of \texttt{k} to the two sub-lists. \texttt{disj*} 
+takes a non-empty list of goals \texttt{gs} and returns a goal. With the help 
+of \texttt{split}, it essentially constructs a \emph{balanced} binary tree 
+where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}, whence 
+the name of this search strategy. In contrast, the \disj{} in iDFS essentially 
+constructs the same sort of binary tree in one of the most unbalanced forms.
+
 \section{fair DFS}
-
-Fair DFS (fDFS) has fair \disj{} and unfair \conj{}.
-The implementation of fDFS differs from iDFS's in \texttt{disj2} (Fig.~\ref{fDFS}).
-\texttt{disj2} is changed to call a new and fair version of \texttt{append-inf}.
-\texttt{append-inf/fair} immediately calls its helper, \texttt{append-inf/fair\^{}}, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which indicates that \texttt{s-inf} and \texttt{t-inf} haven't been swapped.
-The swapping happens in the third \texttt{cond} clause of the helper, where \texttt{s?} is changed accordingly.
-The first two \texttt{cond} clauses essentially copy the \texttt{car}s and stop recursion when one of the input spaces is obviously finite.
-The third clause, as we mentioned early, is just for swapping.
-When the fourth and last clause runs, we know that both \texttt{s-inf} and \texttt{t-inf} are ended with a thunk.
-In this case, a new thunk is constructed.
-The new thunk calls the driver recursively.
-Here changing the order of \texttt{t-inf} and \texttt{s-inf} won't hurt the fairness (though it will change the order of answers).
-We swapped them back so that answers are produced in a more natural order.
 
@@
 
+Fair DFS (fDFS) has fair \disj{} and unfair \conj{}. The implementation of fDFS 
+differs from iDFS's in \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is 
+changed to call a new and fair version of \texttt{append-inf}. 
+\texttt{append-inf/fair} immediately calls its helper, 
+\texttt{append-inf/fair\^{}}, with the first argument, \texttt{s?}, set to 
+\texttt{\#{}t}, which indicates that \texttt{s-inf} and \texttt{t-inf} haven't 
+been swapped. The swapping happens at the third \texttt{cond} clause in the 
+helper, where \texttt{s?} is updated accordingly. The first two \texttt{cond} 
+clauses essentially copy the \texttt{car}s and stop recursion when one of the 
+input spaces is obviously finite. The third clause, as we mentioned early, is 
+just for swapping. When the fourth and last clause runs, we know that both 
+\texttt{s-inf} and \texttt{t-inf} are ended with a thunk. In this case, a new 
+thunk is constructed. The new thunk calls the driver recursively. Here changing 
+the order of \texttt{t-inf} and \texttt{s-inf} won't hurt the fairness (though 
+it will change the order of answers). We swapped them back so that answers are 
+produced in a more natural order.
+
 \section{breadth-first search}
 
-Our BFS is fair in both \disj{} and \conj{}.
-Its implementation is based on fDFS (not iDFS).
-All we have to do is changing the use of \texttt{append-inf} in \texttt{append-map-inf} to \texttt{append-inf/fair}.
-After making this change, \texttt{append-inf} is useless.
+Our BFS is fair in both \disj{} and \conj{}. Its implementation is based on 
+fDFS (not iDFS). All we have to do is apply two trivial changes to 
+\texttt{append-map-inf}. First, rename it to \texttt{append-map-inf/fair}. 
+Second, replace its use of \texttt{append-inf} to \texttt{append-inf/fair}.
 
-The implementation can be improved in two aspects.
-First, as we mentioned in section 2.2, our BFS bag states by their cost.
-However, in this implementation, it is unclear where this information is recorded.
-Second, \texttt{append-inf/fair} is space inefficient.
-It makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ is the ``length'' of each input search space.
-We address these issues in the first subsection.
+The implementation can be improved in two aspects. First, as we mentioned in 
+section 2.2, our BFS bag states by their cost. However, in this implementation, 
+it is unclear where this information is recorded. Second, 
+\texttt{append-inf/fair} is space inefficient. It makes $O(n+m)$ new 
+\texttt{cons} cells every time, where $n$ and $m$ are the ``length''s of 
+input search spaces. We address these issues in the first subsection.
 
-Both our BFS and Seres's BFS \citep{seres1999algebra} produce answers in increasing order of cost.
-So it is interesting to see if they are equivalent.
-We prove the equivalence in Coq.
-The details are in the second subsection.
-
-% The first subsection describe an optimized BFS.
-The optimization makes the type of search space representation more clear and reduces time-complexity of some function.
-The second subsection compares the pure subset of the optimized BFS with the BFS found in \citep{seres1999algebra}.
-We prove the two BFSs return the same answer list.
+Both our BFS and Seres's BFS \citep{seres1999algebra} produce answers in 
+increasing order of cost. So it is interesting to see if they are equivalent. 
+We prove the so in Coq. The details are in the second subsection.
 
@@
 
-As we mentioned in section 2.2, our BFS bag states by their cost.
-The bagging information is recorded subtly -- the \texttt{car}s of a search space have cost 0 (they are in the same bag), and the costs of states in thunk are increased by one.
-It is even more difficult to see \texttt{append-inf/fair} and the modified \texttt{append-map-inf} respects the cost information.
-We make things clear by changing the type of search space, modify related function definitions, and introducing a few more functions.
-
-The new type is a pair whose \texttt{car} is a list of state (the bag), and whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search space.
-A falsy \texttt{cdr} indicates that the search space is obviously finite.
-
-Both modified functions and introduced ones are listed in Fig.~\ref{BFS-opt}.
-The first three functions in Fig.~\ref{BFS-opt} are search space constructor.
-They are newly introduced.
-\texttt{none} makes an empty search space.
-\texttt{unit} makes an space from one state.
-\texttt{step} makes a space from a thunk.
-The next function, \texttt{split}, is used to implement impure features (i.e.
-\texttt{ifte} and \texttt{once}).
-It takes a space \texttt{s-inf} and two continuations \texttt{ks} and \texttt{kf}.
-When \texttt{s-inf} contains some states, \texttt{ks} is called with the first state and the rest space.
-Otherwise, \texttt{kf} is called with no argument.
-Here `s' and `f' means `succeed' and `fail' respectively.
-The remaining functions do the same thing as before.
-Now it should be not difficult to see that \texttt{append-inf/fair} and \texttt{append-map-inf} do respect cost information.
-
-Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space inefficiency -- the use of \texttt{append} helps us to reuse the first bag of \texttt{t-inf}.
-
-Noted that some functions in the list constitute a \emph{MonadPlus}: \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and \texttt{append-inf} correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, and \texttt{mplus} respectively.
-
 \begin{figure}
 	\lstinputlisting{Figures/BFS-opt.rkt}	
-	\caption{interface functions in optimized BFS}
+	\caption{interface functions in optimized BFS (pure)}
 	\label{BFS-opt}
@@
 
+As we mentioned in section 2.2, our BFS bag states by their cost. The bagging 
+information is recorded subtly -- the \texttt{car}s of a search space have cost 
+0 (i.e. they are in the same bag), and the costs of states in thunk are 
+computed recursively then increased by one. It is even more difficult to see 
+\texttt{append-inf/fair} and the \texttt{append-map-inf/fair} respects the cost 
+information. We make things clear by changing the type of search space, modify 
+related function definitions, and introducing a few more functions.
+
+The new type is a pair whose \texttt{car} is a list of state (the bag), and 
+whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search 
+space. A falsy \texttt{cdr} indicates that the search space is obviously 
+finite.
+
+Functions related to the pure subset are listed in Fig.~\ref{BFS-opt}. The 
+first three functions in Fig.~\ref{BFS-opt} are search space constructor. 
+They are newly introduced. \texttt{none} makes an empty search space. 
+\texttt{unit} makes an space from one state. \texttt{step} makes a space from a 
+thunk. The remaining functions do the same thing as 
+before. Now it should be not difficult to see that \texttt{append-inf/fair} and 
+\texttt{append-map-inf} do respect cost information.
+
+Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space 
+inefficiency -- the use of \texttt{append} helps us to reuse the first bag of 
+\texttt{t-inf}.
+
+Noted that some functions in the list constitute a \emph{MonadPlus}: 
+\texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and \texttt{append-inf} 
+correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, and \texttt{mplus} 
+respectively.
+
+\begin{figure}
+	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
+	\caption{interface functions in optimized BFS (impure)}
+	\label{BFS-opt-cont}
+\end{figure}
+
+Functions implementing impure features are in Fig.~\ref{BFS-opt-cont}. The 
+first function, \texttt{elim}, is used to implement \texttt{ifte} and 
+\texttt{once}. It takes a space \texttt{s-inf} and two continuations 
+\texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some states, 
+\texttt{ks} is called with the first state and the rest space. Otherwise, 
+\texttt{kf} is called with no argument. Here `s' and `f' means `succeed' and 
+`fail' respectively. The remaining functions do the same thing as before.
+
 \subsection{comparison with Silvija's BFS}
 
-In this section, we compare the pure subset of our optimized BFS with the BFS found in \citep{seres1999algebra}. We focus on the pure subset because Silvija's system is pure.
+In this section, we compare the pure subset of our optimized BFS with the BFS 
+found in \citep{seres1999algebra}. We focus on the pure subset because 
+Silvija's system is pure.
 
-To compare efficiency, we translate her Haskell code into Racket (See supplements for the translated code), and embed it into miniKanren.
-The translation is fairly straightforward due to the similarity in both logic programming system and search space representation.
-The translated code is less efficient when running our benchmark.
-Details about efficiency difference are in section 6.
+To compare efficiency, we translate her Haskell code into Racket (See 
+supplements for the translated code), and embed it into miniKanren. The 
+translation is fairly straightforward due to the similarity in both logic 
+programming system and search space representation. The translated code is less 
+efficient when running our benchmark. Details about efficiency difference are 
+in section 6.
 
-We prove the two search strategies are equivalent in Coq.
-Since search space can be infinite, we should use a co-inductive data type.
-However, Coq is too strict in the guardedness condition to accept a direct translation of the implementations.
-Therefore, we prove core theorems with finite search space instead.
-In order to generalize the conclusion to the cases with infinite search space, we prove a few more theorems saying that whenever we query answers lower than some finite cost, we can restrict goals to truncate search spaces at some finite depth without changing the query result.
-(See supplements for the formal proof)
-
-;;TODO to be more specific?
+We prove the two search strategies are equivalent in Coq. Since search space 
+can be infinite, we should use a co-inductive data type. However, Coq is too 
+strict in the guardedness condition to accept a direct translation of the 
+implementations. Therefore, we prove core theorems with finite search space 
+instead. In order to generalize the conclusion to the cases with infinite 
+search space, we prove a few more theorems saying that whenever we query 
+answers lower than some finite cost, we can restrict goals to truncate search 
+spaces at some finite depth without changing the query result. (See supplements 
+for the formal proof)
 
@@
 
-In this section, we compare the efficiency of search strategies.
-A concise description is in Table~\ref{compare-efficiency}.
-A hyphen means running out of memory.
-The first three benchmarks are taken from \citep{friedman_reasoned_2018}.
-Next two benchmarks about quine are modified from a similar test case in \citep{byrd2017unified}.
-The modifications are made to circumvent the need for symbolic constraint.
-Our version generates de Bruijnized expressions and forbids closures going into list.
-The two benchmarks differ in the \conde clause order of their relation interpreters.
-The last two benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love you)}.
-This benchmark is also inspired by \citep{byrd2017unified}.
-Again, they differ in the \conde clause order of their relation interpreters.
-The first one has elimination rules (i.e.
-application, \texttt{car}, and \texttt{cdr}) at the end, while the other has them at the beginning.
-We conjecture that iDFS would perform badly in the second case because elimination rules complicate the problem when running backward.
-Our statistics support our conjecture.
+;;TODO check if reverso and appendo are absolutely the same as the ones in TRS2.
 
-In general, only iDFS and biDFS constantly perform well.
-Among them, biDFS seems to be less sensitive to change in \conde clause order (see the last four benchmarks).
-The other search strategies all have fair \disj{}.
-And they all perform badly in the \texttt{very-recursiveo} benchmark.
-However, the drawback of having fair \disj{} alone (i.e.
-fDFS) is not shown elsewhere.
-Fair \conj{} impose overhead constantly except in \texttt{appendo}.
-The reason might be that strategies with fair \conj{} tend to keep more intermediate states in the memory.
-Among the BFSs, our version performs better in most cases, and equally well elsewhere.
+In this section, we compare the efficiency of search strategies. A concise 
+description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
+memory. The first three benchmarks are taken from 
+\citep{friedman_reasoned_2018}. Next two benchmarks about quine are modified 
+from a similar test case in \citep{byrd2017unified}. The modifications are made 
+to circumvent the need for symbolic constraints (e.g. $\neq$, 
+\texttt{absento}). Our version generates de 
+Bruijnized expressions and forbids closures going into list. The two benchmarks 
+differ in the \conde clause order of their relation interpreters. The last two 
+benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
+you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
+sibling benchmarks differ in the \conde clause order of their relation 
+interpreters. The first one 
+has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
+end, while the other has them at the beginning. We conjecture that iDFS would 
+perform badly in the second case because elimination rules complicate the 
+problem when running backward. Our statistics support our conjecture.
+
+In general, only iDFS and biDFS constantly perform well. Among them, biDFS 
+seems to be less sensitive to change in \conde clause order (see the last four 
+benchmarks). The other search strategies all have fair \disj{}. And they all 
+perform badly in the \texttt{very-recursiveo} benchmark. However, the drawback 
+of having fair \disj{} alone (i.e. fDFS) is not shown elsewhere. Fair \conj{} 
+impose overhead constantly except in \texttt{appendo}. The reason might be that 
+strategies with fair \conj{} tend to keep more intermediate states in the 
+memory. Among the BFSs, our version performs better in most cases, and equally 
+well elsewhere.
 
@@
 \end{tabular}
-\caption{The results of a quantitative evaluation: running times of benchmarks in milliseconds}
+\caption{The results of a quantitative evaluation: running times of benchmarks 
+in milliseconds}
 \label{compare-efficiency}
@@
 
-Edward points out a disjunct complex would be `fair' if it is a full and balanced tree \citep{yang2010adventures}.
+Edward points out a disjunct complex would be `fair' if it is a full and 
+balanced tree \citep{yang2010adventures}.
 
-Silvija et al \citep{seres1999algebra} also describe a breadth-first search strategy.
-We proof their BFS is equivalent to ours.
-However, ours looks simpler and performs better in comparison with a straightforward translation of their Haskell code.
+Silvija et al \citep{seres1999algebra} also describe a breadth-first search 
+strategy. We proof their BFS is equivalent to ours. However, ours looks simpler 
+and performs better in comparison with a straightforward translation of their 
+Haskell code.
 
@@
 
-% We devise a new search strategy, balanced interleaving DFS.
-The key idea is to make disjunct trees balanced.
-Changing the search strategy from iDFS to biDFS is not hard: 2 new functions and 1 modified macro.
+% We devise a new search strategy, balanced interleaving DFS. The key idea is 
+%to make disjunct trees balanced. Changing the search strategy from iDFS to 
+%biDFS is not hard: 2 new functions and 1 modified macro.
 
-% We also devise breadth-first search, whose intuition is similar to Seres's BFS. And we have proved their equivalence. We optimize our BFS with a queue.
+% We also devise breadth-first search, whose intuition is similar to Seres's 
+%BFS. And we have proved their equivalence. We optimize our BFS with a queue.
 

### 2019-04-30 Paper/paper.tex
add abstract back; revise revise revise

@@
 
+The syntax of a programming language should reflect its semantics. When writing 
+a \conde expression in miniKanren, a programmer would expect all clauses share 
+the same chance of being explored, as these clauses are written in 
+parallel. The existing search strategy, interleaving DFS (iDFS), however, 
+prioritize its clauses by the order how they are written down. Similarly, when 
+a \conde is followed by another goal conjunctively, a programmer would expect 
+states in parallel share the same chance of being explored. Again, the answers 
+by iDFS is different from the expectation. We have devised three new search 
+strategies that have different level of fairness in \disj and \conj.
+
 %TODO rewrite abstract
@@
 DFS (fDFS), and BFS. They have different characteristics of fairness 
-(Table.~\ref{fairness}). We prove that our BFS and the BFS proposed by Seres et 
+(Table.~\ref{fairness}). We prove that the pure subset of our BFS and the BFS 
+proposed by Seres et
 al~\citep{seres1999algebra} produce the same result when queried. But our code 
 is shorter and runs faster. Because the two BFSs are equivalent, we do not 
-distinguish them in most places, except section 6 (quantitative evaluation).
+distinguish them in most places.
 
@@
 
-On the contrary, search strategies with fair \disj{} (e.g. fDFS and BFS) give a 
-nice answer list.
+We borrow the definition of \emph{fair} \disj{} from \cite{seres1999algebra}: 
+search strategies with \emph{fair} \disj{} should allocate resource evenly 
+among disjunctive goals. Running the same program with fDFS and BFS give the 
+following result.
 
@@
 
-Search strategies with almost-fair \disj{} (e.g. biDFS) give the same result in 
-this case. However, as its name suggests, almost-fair strategies are not always 
-fair. Fortunately, the maximal ratio of the allocated resource among 
-disjunctive goals is bounded by a constant. Our biDFS is fair when the number 
-of goals is a power of 2, otherwise, some goals are allocated twice more 
-resource than the others. In following example, the clauses of \texttt{b}, 
-\texttt{c}, and \texttt{d} are allocated more resource.
+We conceive a middle place between fair and unfair -- search strategies with 
+\emph{almost-fair} \disj{} should allocate resource so evenly among disjunctive 
+goals\citep{seres1999algebra} that the the maximal ratio of resource is bounded 
+by a constant. Our new search strategy, biDFS, has almost-fair \disj{}. It is 
+fair when the number of goals is a power of 2, otherwise, some goals are 
+allocated twice more resource than the others. In the previous example, it 
+gives the same result. And in the following example, where the \conde has 5 
+clause, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated 
+more resource.
 
@@
 more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
-of \texttt{c}) are hardly found. The situation would be worse if we add more 
-\conde clauses. The result with biDFS, whose \conj{} is also unfair, is 
-similar, but due to its different \disj{}, the position of \texttt{b} and 
-\texttt{c} and swapped.
+of \texttt{c}) are hardly found. Although iDFS's \disj{} is unfair in general, 
+it is fair when there is no call to relational definition in sub-goals, 
+including this case. The situation would be worse if we add more \conde 
+clauses. The result with biDFS, whose \conj{} is also unfair, is similar, but 
+due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
+swapped.
 
@@
 
-On the contrary, search strategies with fair \conj{} (e.g. BFS) give a nice 
-answer list.
+Intuitively, search strategies with fair \conj{} should produce each sort of 
+lists equally frequently. Indeed, BFS does so.
 
@@
 
-Fairness is good but is not good enough to kick away completeness. A solution  
-is bagging states and requiring that 
-search spaces derived from states in the same bag are treated fairly. A natural 
-way to bag states is by their costs.
-This approach is also taken in \citep{seres1999algebra}.
-The \emph{cost} of a state is its depth in 
-the search tree (i.e. the number of calls to relational definitions required to 
-find them) \citep{seres1999algebra}. BFS is more than fair -- it produces 
-answers in increasing order of cost. Running the same program gives an answer 
-list sorted by answers' costs. In this case, the cost of an answer is equal to 
-the length of the inner lists plus the length of the outer list.
+Our solution is requiring a search strategy with \emph{fair} \conj{} to 
+package states in bags, where each bag contains finite states, and to allocate 
+resource evenly among search spaces derived from states in the same bag. The 
+way to package depends on search strategy. And how to allocate resource among 
+search space related to different bags is intended left unspecified.
 
-Our definition of fair \conj{} is difference from the one in 
-\citep{seres1999algebra}. They consider a \conj{} (or "selection rule" in their 
-words) is fair if it ``would allow one to choose the literals in different 
-order''\citep{seres1999algebra}. This requirement is not stronger than 
-\emph{completeness}. We prefer our definition because it avoids overlapping 
-with a known concept.
+BFS packages states by their costs. The \emph{cost} of a state is its 
+depth in the search tree (i.e. the number of calls to relational definitions 
+required to find them) \citep{seres1999algebra}. In the following example, the 
+cost of an answer is equal to the length of the inner lists plus the length of 
+the outer list. Noted that BFS produces answers in increasing order of cost.
 
@@
 
-\section{balanced interleaving DFS}
+\section{balanced interleaving depth-first search}
 
@@
 
-\section{fair DFS}
+\section{fair depth-first search}
 
@@
 
-Our BFS is fair in both \disj{} and \conj{}. Its implementation is based on 
+BFS is fair in both \disj{} and \conj{}. Our implementation is based on 
 fDFS (not iDFS). All we have to do is apply two trivial changes to 
@@
 it is unclear where this information is recorded. Second, 
-\texttt{append-inf/fair} is space inefficient. It makes $O(n+m)$ new 
-\texttt{cons} cells every time, where $n$ and $m$ are the ``length''s of 
-input search spaces. We address these issues in the first subsection.
+\texttt{append-inf/fair} is extravagant in memory usage. It makes 
+$O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
+``length''s of input search spaces. We address these issues in the first 
+subsection.
 
@@
 increasing order of cost. So it is interesting to see if they are equivalent. 
-We prove the so in Coq. The details are in the second subsection.
+We prove so in Coq. The details are in the second subsection.
 
@@
 0 (i.e. they are in the same bag), and the costs of states in thunk are 
-computed recursively then increased by one. It is even more difficult to see 
+computed recursively then increased by one. It is even more subtle that
 \texttt{append-inf/fair} and the \texttt{append-map-inf/fair} respects the cost 
-information. We make things clear by changing the type of search space, modify 
-related function definitions, and introducing a few more functions.
+information. We make this facts obvious by changing the type of search space, 
+modifying related function definitions, and introducing a few more functions.
 
@@
 whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search 
-space. A falsy \texttt{cdr} indicates that the search space is obviously 
-finite.
+space. A falsy \texttt{cdr} means the search space is obviously finite.
 
-Functions related to the pure subset are listed in Fig.~\ref{BFS-opt}. The 
-first three functions in Fig.~\ref{BFS-opt} are search space constructor. 
-They are newly introduced. \texttt{none} makes an empty search space. 
+Functions related to the pure subset are listed in Fig.~\ref{BFS-opt} (the 
+others in Fig.~\ref{BFS-opt-cont}). The first three functions in 
+Fig.~\ref{BFS-opt} are search space constructor. \texttt{none} makes an empty 
+search space. 
 \texttt{unit} makes an space from one state. \texttt{step} makes a space from a 
-thunk. The remaining functions do the same thing as 
-before. Now it should be not difficult to see that \texttt{append-inf/fair} and 
-\texttt{append-map-inf} do respect cost information.
+thunk. The remaining functions do the same thing as before. Now it should be 
+not hard to see that \texttt{append-inf/fair} and \texttt{append-map-inf} do 
+respect cost information.
 
 Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space 
-inefficiency -- the use of \texttt{append} helps us to reuse the first bag of 
+extravagance -- the use of \texttt{append} helps us to reuse the first bag of 
 \texttt{t-inf}.
 
-Noted that some functions in the list constitute a \emph{MonadPlus}: 
+Noted that some functions here constitute a \emph{MonadPlus}: 
 \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and \texttt{append-inf} 
@@
 \texttt{kf} is called with no argument. Here `s' and `f' means `succeed' and 
-`fail' respectively. The remaining functions do the same thing as before.
+`fail' respectively. This function is an eliminator of search space, whence the 
+name. The remaining functions do the same thing as before.
 
@@
 To compare efficiency, we translate her Haskell code into Racket (See 
-supplements for the translated code), and embed it into miniKanren. The 
-translation is fairly straightforward due to the similarity in both logic 
-programming system and search space representation. The translated code is less 
-efficient when running our benchmark. Details about efficiency difference are 
-in section 6.
+supplements for the translated code). The translation is fairly straightforward 
+due to the similarity in both logic programming system and search space 
+representation. The translated code is longer and slower. Details about 
+efficiency difference are in section 6.
 
@@
 
-In this section, we compare the efficiency of search strategies. A concise 
-description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
-memory. The first three benchmarks are taken from 
-\citep{friedman_reasoned_2018}. Next two benchmarks about quine are modified 
-from a similar test case in \citep{byrd2017unified}. The modifications are made 
-to circumvent the need for symbolic constraints (e.g. $\neq$, 
-\texttt{absento}). Our version generates de 
-Bruijnized expressions and forbids closures going into list. The two benchmarks 
-differ in the \conde clause order of their relation interpreters. The last two 
-benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
-you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
-sibling benchmarks differ in the \conde clause order of their relation 
-interpreters. The first one 
-has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
-end, while the other has them at the beginning. We conjecture that iDFS would 
-perform badly in the second case because elimination rules complicate the 
-problem when running backward. Our statistics support our conjecture.
-
-In general, only iDFS and biDFS constantly perform well. Among them, biDFS 
-seems to be less sensitive to change in \conde clause order (see the last four 
-benchmarks). The other search strategies all have fair \disj{}. And they all 
-perform badly in the \texttt{very-recursiveo} benchmark. However, the drawback 
-of having fair \disj{} alone (i.e. fDFS) is not shown elsewhere. Fair \conj{} 
-impose overhead constantly except in \texttt{appendo}. The reason might be that 
-strategies with fair \conj{} tend to keep more intermediate states in the 
-memory. Among the BFSs, our version performs better in most cases, and equally 
-well elsewhere.
-
 \begin{table}
@@
 		\hline 
-	benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  \\
+		benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  
+		\\
 		\hline
@@
 	\end{tabular}
-\caption{The results of a quantitative evaluation: running times of benchmarks 
+	\caption{The results of a quantitative evaluation: running times of 
+	benchmarks 
 		in milliseconds}
@@
 \end{table}
+
+In this section, we compare the efficiency of search strategies. A concise 
+description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
+memory. The first three benchmarks are taken from 
+\citep{friedman_reasoned_2018}. Next two benchmarks about quine are modified 
+from a similar test case in \citep{byrd2017unified}. The modifications are made 
+to circumvent the need for symbolic constraints (e.g. $\neq$, 
+\texttt{absento}). Our version generates de 
+Bruijnized expressions and prevent closures getting into list. The two 
+benchmarks differ in the \conde clause order of their relation interpreters. 
+The last two 
+benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
+you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
+sibling benchmarks differ in the \conde clause order of their relation 
+interpreters. The first one 
+has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
+end, while the other has them at the beginning. We conjecture that iDFS would 
+perform badly in the second case because elimination rules complicate the 
+problem when running backward. The evaluation supports our conjecture.
+
+In general, only iDFS and biDFS constantly perform well. fDFS is just as 
+efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
+overhead in many cases. Among the three variants of DFS (they all have unfair 
+\conj{}), fDFS is most resistant to clause permutation, followd by biDFS then 
+iDFS. Among the two implementation of BFS, ours constantly performs as well or 
+better. Interestingly, every strategies with fair \disj{} suffers in 
+\texttt{very-recursiveo} and fDFS performs well elsewhere. Therefore, this 
+benchmark might be a special case. Fair \conj{} imposes overhead constantly 
+except in \texttt{appendo}. The reason might be that strategies with fair 
+\conj{} tend to keep more intermediate states in the memory.
 

### 2019-05-01 Paper/paper.tex
conclusion

@@
 
-%TODO rewrite abstract
 %The syntax of a programming language should reflect its semantics. When using 
@@
 way to package depends on search strategy. And how to allocate resource among 
-search space related to different bags is intended left unspecified.
+search space related to different bags is unspecified. Our definition of fair 
+\conj{} is orthogonal with completeness. For example, a naively fair strategy 
+is fair but not complete, while BFS is fair and complete.
 
@@
 \texttt{append-inf/fair} and the \texttt{append-map-inf/fair} respects the cost 
-information. We make this facts obvious by changing the type of search space, 
-modifying related function definitions, and introducing a few more functions.
+information. We make these facts more obvious by changing the type of search 
+space, modifying related function definitions, and introducing a few more 
+functions.
 
@@
 Functions related to the pure subset are listed in Fig.~\ref{BFS-opt} (the 
-others in Fig.~\ref{BFS-opt-cont}). The first three functions in 
+others in Fig.~\ref{BFS-opt-cont}). We take them apart because they are 
+compared with Seres's implementation later. The first three functions in 
 Fig.~\ref{BFS-opt} are search space constructor. \texttt{none} makes an empty 
-search space. 
-\texttt{unit} makes an space from one state. \texttt{step} makes a space from a 
-thunk. The remaining functions do the same thing as before. Now it should be 
-not hard to see that \texttt{append-inf/fair} and \texttt{append-map-inf} do 
-respect cost information.
+search space. \texttt{unit} makes an space from one state. \texttt{step} makes 
+a space from a thunk. The remaining functions do the same thing as before.
 
@@
 Functions implementing impure features are in Fig.~\ref{BFS-opt-cont}. The 
-first function, \texttt{elim}, is used to implement \texttt{ifte} and 
-\texttt{once}. It takes a space \texttt{s-inf} and two continuations 
-\texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some states, 
-\texttt{ks} is called with the first state and the rest space. Otherwise, 
-\texttt{kf} is called with no argument. Here `s' and `f' means `succeed' and 
-`fail' respectively. This function is an eliminator of search space, whence the 
-name. The remaining functions do the same thing as before.
+first function, \texttt{elim}, takes a space \texttt{s-inf} and two 
+continuations \texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some 
+states, \texttt{ks} is called with the first state and the rest space. 
+Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
+`succeed' and `fail' respectively. This function is an eliminator of search 
+space, whence the name. The remaining functions do the same thing as before.
 
@@
 
-%TODO contributions
+We analysis the definitions of fair \disj{} and fair \conj{}, then propose a 
+new definition of fair \conj{}. Our definition is orthogonal with completeness.
 
-% We devise a new search strategy, balanced interleaving DFS. The key idea is 
-%to make disjunct trees balanced. Changing the search strategy from iDFS to 
-%biDFS is not hard: 2 new functions and 1 modified macro.
+We devise three new search strategies: balanced interleaving DFS (biDFS), fair 
+DFS (fDFS), and BFS. biDFS has almost-fair \disj{} and unfair \conj{}. fDFS has 
+fair \disj{} and unfair \conj{}. BFS has both fair \disj{} and fair \conj{}.
 
-% We also devise breadth-first search, whose intuition is similar to Seres's 
-%BFS. And we have proved their equivalence. We optimize our BFS with a queue.
+Our quantitative evaluation shows that biDFS and fDFS are competitive 
+alternatives to iDFS, the current search strategy, and that BFS is less 
+practical.
+
+We prove our BFS is equivalent to the BFS in \citep{seres1999algebra}. Our code 
+is shorter and runs faster than a direct translation of their Haskell code.
 

### 2019-05-02 Paper/paper.tex
correct source of reverso
improve figure names

@@
 	\lstinputlisting{Figures/balanced-disj.rkt}
-	\caption{\texttt{balanced-disj}}
+	\caption{biDFS implementation}
 	\label{balanced-disj}
@@
 	\lstinputlisting{Figures/fDFS.rkt}
-	\caption{How fDFS differs from iDFS}
+	\caption{fDFS implementation}
 	\label{fDFS}
@@
 	\lstinputlisting{Figures/BFS-opt.rkt}	
-	\caption{interface functions in optimized BFS (pure)}
+	\caption{new and changed functions in optimized BFS that implements pure 
+	features}
 	\label{BFS-opt}
@@
 	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
-	\caption{interface functions in optimized BFS (impure)}
+	\caption{new and changed functions in optimized BFS that implements impure 
+		features}
 	\label{BFS-opt-cont}
@@
 found in \citep{seres1999algebra}. We focus on the pure subset because 
-Silvija's system is pure.
+Silvija's system is pure. Her system represents search spaces with streams of 
+lists of states, where each list is a bag.
 
@@
 
-;;TODO check if reverso and appendo are absolutely the same as the ones in TRS2.
-
 \begin{table}
@@
 		\hline 
-		reverseo & 10 &   5 &   3 &   3 &     38 &     85 \\ 
+		reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
 		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
@@
 description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
-memory. The first three benchmarks are taken from 
-\citep{friedman_reasoned_2018}. Next two benchmarks about quine are modified 
-from a similar test case in \citep{byrd2017unified}. The modifications are made 
+memory. The first two benchmarks are taken from 
+\citep{friedman_reasoned_2018}. \texttt{reverso} is from 
+\citep{rozplokhas2018improving}. Next two benchmarks 
+about quine are modified from a similar test case in \citep{byrd2017unified}. 
+The modifications are made 
 to circumvent the need for symbolic constraints (e.g. $\neq$, 

### 2019-05-02 Paper/paper.tex
iDFS->DFSi, because iDFS is already a thing

@@
 the same chance of being explored, as these clauses are written in 
-parallel. The existing search strategy, interleaving DFS (iDFS), however, 
+parallel. The existing search strategy, interleaving DFS (DFS$_\textrm{i}$), however, 
 prioritize its clauses by the order how they are written down. Similarly, when 
@@
 states in parallel share the same chance of being explored. Again, the answers 
-by iDFS is different from the expectation. We have devised three new search 
+by DFS$_\textrm{i}$ is different from the expectation. We have devised three new search 
 strategies that have different level of fairness in \disj and \conj.
@@
 
-We propose three new search strategies, balanced interleaving DFS (biDFS), fair 
-DFS (fDFS), and BFS. They have different characteristics of fairness 
+We propose three new search strategies, balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
+DFS (DFS$_\textrm{f}$), and BFS. They have different characteristics of fairness 
 (Table.~\ref{fairness}). We prove that the pure subset of our BFS and the BFS 
@@
 		\hline 
-		fairness & iDFS & biDFS & fDFS & BFS \\ 
+		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS \\ 
 		\hline 
@@
 %miniKanreners as well as seasoned ones. We propose two such search strategies, 
-%balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe 
+%balanced interleaving DFS (DFS$_\textrm{bi}$) and breadth-first search (BFS), and observe 
 %how they affect the efficiency and the answer order of known miniKanren 
@@
 we expect lists of each sort constitute $1/4$ of the answer list. However, 
-iDFS, the current search strategy, gives us much more lists of \texttt{a} than 
+DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a} than 
 other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are hardly 
@@
 search strategies with \emph{fair} \disj{} should allocate resource evenly 
-among disjunctive goals. Running the same program with fDFS and BFS give the 
+among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS give the 
 following result.
@@
 goals\citep{seres1999algebra} that the the maximal ratio of resource is bounded 
-by a constant. Our new search strategy, biDFS, has almost-fair \disj{}. It is 
+by a constant. Our new search strategy, DFS$_\textrm{bi}$, has almost-fair \disj{}. It is 
 fair when the number of goals is a power of 2, otherwise, some goals are 
@@
 we expect lists of each sort constitute $1/4$ of the answer list. However, 
-search strategies with unfair \conj{} (e.g. iDFS, fDFS) give us much 
+search strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$) give us much 
 more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
-of \texttt{c}) are hardly found. Although iDFS's \disj{} is unfair in general, 
+of \texttt{c}) are hardly found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
 it is fair when there is no call to relational definition in sub-goals, 
 including this case. The situation would be worse if we add more \conde 
-clauses. The result with biDFS, whose \conj{} is also unfair, is similar, but 
+clauses. The result with DFS$_\textrm{bi}$, whose \conj{} is also unfair, is similar, but 
 due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
@@
 	\lstinputlisting{Figures/balanced-disj.rkt}
-	\caption{biDFS implementation}
+	\caption{DFS$_\textrm{bi}$ implementation}
 	\label{balanced-disj}
@@
 
-Balanced interleaving DFS (biDFS) has almost-fair \disj{} and unfair \conj{}. 
-The implementation of biDFS differs from iDFS in the \disj{} macro. We list the 
+Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair \conj{}. 
+The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ in the \disj{} macro. We list the 
 new \disj{} with its helpers in Fig.~\ref{balanced-disj}. The first helper 
@@
 where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}, whence 
-the name of this search strategy. In contrast, the \disj{} in iDFS essentially 
+the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$ essentially 
 constructs the same sort of binary tree in one of the most unbalanced forms.
@@
 	\lstinputlisting{Figures/fDFS.rkt}
-	\caption{fDFS implementation}
+	\caption{DFS$_\textrm{f}$ implementation}
 	\label{fDFS}
@@
 
-Fair DFS (fDFS) has fair \disj{} and unfair \conj{}. The implementation of fDFS 
-differs from iDFS's in \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is 
+Fair DFS (DFS$_\textrm{f}$) has fair \disj{} and unfair \conj{}. The implementation of DFS$_\textrm{f}$ 
+differs from DFS$_\textrm{i}$'s in \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is 
 changed to call a new and fair version of \texttt{append-inf}. 
@@
 BFS is fair in both \disj{} and \conj{}. Our implementation is based on 
-fDFS (not iDFS). All we have to do is apply two trivial changes to 
+DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). All we have to do is apply two trivial changes to 
 \texttt{append-map-inf}. First, rename it to \texttt{append-map-inf/fair}. 
@@
 		\hline 
-		benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  
+		benchmark & size & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & optimized BFS & Silvija's BFS  
 		\\
@@
 has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
-end, while the other has them at the beginning. We conjecture that iDFS would 
+end, while the other has them at the beginning. We conjecture that DFS$_\textrm{i}$ would 
 perform badly in the second case because elimination rules complicate the 
@@
 
-In general, only iDFS and biDFS constantly perform well. fDFS is just as 
+In general, only DFS$_\textrm{i}$ and DFS$_\textrm{bi}$ constantly perform well. DFS$_\textrm{f}$ is just as 
 efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
 overhead in many cases. Among the three variants of DFS (they all have unfair 
-\conj{}), fDFS is most resistant to clause permutation, followd by biDFS then 
-iDFS. Among the two implementation of BFS, ours constantly performs as well or 
+\conj{}), DFS$_\textrm{f}$ is most resistant to clause permutation, followd by DFS$_\textrm{bi}$ then 
+DFS$_\textrm{i}$. Among the two implementation of BFS, ours constantly performs as well or 
 better. Interestingly, every strategies with fair \disj{} suffers in 
-\texttt{very-recursiveo} and fDFS performs well elsewhere. Therefore, this 
+\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. Therefore, this 
 benchmark might be a special case. Fair \conj{} imposes overhead constantly 
@@
 
-We devise three new search strategies: balanced interleaving DFS (biDFS), fair 
-DFS (fDFS), and BFS. biDFS has almost-fair \disj{} and unfair \conj{}. fDFS has 
+We devise three new search strategies: balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
+DFS (DFS$_\textrm{f}$), and BFS. DFS$_\textrm{bi}$ has almost-fair \disj{} and unfair \conj{}. DFS$_\textrm{f}$ has 
 fair \disj{} and unfair \conj{}. BFS has both fair \disj{} and fair \conj{}.
 
-Our quantitative evaluation shows that biDFS and fDFS are competitive 
-alternatives to iDFS, the current search strategy, and that BFS is less 
+Our quantitative evaluation shows that DFS$_\textrm{bi}$ and DFS$_\textrm{f}$ are competitive 
+alternatives to DFS$_\textrm{i}$, the current search strategy, and that BFS is less 
 practical.

### 2019-05-02 Paper/paper.tex
make file and notes
sec 1

@@
 \usepackage{textcomp}
+\usepackage{trackchanges}
+
+\addeditor{MVC}
 
@@
 \section{introduction}
+\NOTE[MVC]{We need clear definitions of the following: fair, almost-fair, and unfair. Either use bullet points, or definition environment. Google ``latex math definition.''}
+\NOTE[MVC]{A quick intro to miniKanren would be nice here.}
 
@@
 useful in solving many problems \citep{byrd2017unified}. A subtlety in writing 
-relational programs having large \conde expressions, such as interpreters, is 
+relational programs having \conde expressions with large number of clauses,
+such as interpreters, is 
 that the order of \conde clauses can affect the speed considerably. When a 
 \conde expression is large enough, the left clauses consume almost all the 
-resource and the right ones are hardly explored. The unfair \disj{} of the 
-current search strategy, interleaving DFS, is the cause. Under the hood, \conde 
-uses \texttt{conj} to create a goal for each clause, and \texttt{disj} to 
-combine these goals to one. The current \texttt{disj} allocates half resource 
-to its first goal, then allocates the other half to the rest similarly, except 
-for the last clause which takes all the resource.
+resources and the right ones are barely explored. The cause is the unfair
+search strategy, interleaving DFS(DFS$_\textrm{i}$). In a \conde expression,
+each clause takes half of the received resources and pass the other half
+to the remaining clauses, except for the last clause that takes all resources
+it receives.
 
+\NOTE[MVC]{A motivation is needed. Why do people want fairness?}
+\NOTE[MVC]{\texttt{conj} fairness is not defined.}
 Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} 
 fairness. 
-
 We propose three new search strategies, balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
 DFS (DFS$_\textrm{f}$), and BFS. They have different characteristics of fairness 
-(Table.~\ref{fairness}). We prove that the pure subset of our BFS and the BFS 
+(Fig.~\ref{fairness}). We prove that the pure subset of our BFS and the BFS 
 proposed by Seres et
 al~\citep{seres1999algebra} produce the same result when queried. But our code 
-is shorter and runs faster. Because the two BFSs are equivalent, we do not 
-distinguish them in most places.
+is simpler and runs faster on our benchmarks. Because the two BFSs are equivalent,
+we do not distinguish them in most places.
 
-\begin{table}
+\begin{figure}[tbp]
 	\begin{tabular}{|c|c|c|c|c|}
@@
 	\label{fairness}
-\end{table}
+\end{figure}
 
@@
 DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a} than 
-other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are hardly 
+other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are rarely 
 found. The situation would be worse if we add more \conde clauses.
@@
 more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
-of \texttt{c}) are hardly found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
+of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
 it is fair when there is no call to relational definition in sub-goals, 

### 2019-05-02 Paper/paper.tex
sort is a tricky word because it has math meanings, use a more specified descriptor, like letter abcd, instead.

@@
 \NOTE[MVC]{We need clear definitions of the following: fair, almost-fair, and unfair. Either use bullet points, or definition environment. Google ``latex math definition.''}
-\NOTE[MVC]{A quick intro to miniKanren would be nice here.}
+\NOTE[MVC]{A quick intro to miniKanren would be nice here. We should mention The Reasoned Schemer, 2nd and say DFSi is used there.}
 
@@
 In the following program, the three \conde clauses differ in a trivial way. So 
-we expect lists of each sort constitute $1/4$ of the answer list. However, 
-DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a} than 
-other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are rarely 
+we expect lists of each letter constitute $1/4$ of the answer list. However, 
+DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a}s than 
+lists of other letters. And some letters (e.g. lists of \texttt{c}) are rarely 
 found. The situation would be worse if we add more \conde clauses.
@@
 In the following program, the three \conde clauses differ in a trivial way. So 
-we expect lists of each sort constitute $1/4$ of the answer list. However, 
+we expect lists of each letter constitute $1/4$ of the answer list. However, 
 search strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$) give us much 
-more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
+more lists of \texttt{a}s than lists of other letters. And some letters (e.g. lists 
 of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
@@
 
-Intuitively, search strategies with fair \conj{} should produce each sort of 
+Intuitively, search strategies with fair \conj{} should produce each letter of 
 lists equally frequently. Indeed, BFS does so.

### 2019-05-02 Paper/paper.tex
state->answer

@@
 a \conde is followed by another goal conjunctively, a programmer would expect 
-states in parallel share the same chance of being explored. Again, the answers 
+answers in parallel share the same chance of being explored. Again, the answers 
 by DFS$_\textrm{i}$ is different from the expectation. We have devised three new search 
@@
 
-We demonstrate the aspects (\disj{} or \conj{}) and levels (unfair, 
-almost-fair, or fair) of fairness by running queries about \texttt{repeato}, a 
+In this section, we demonstrate the aspects (\disj{} or \conj{}) and levels
+(unfair, almost-fair, or fair) of fairness by running queries about
+\texttt{repeato}, a 
 relational definition that relates a term \texttt{x} with a non-empty list 
@@
 
-In the following program, the three \conde clauses differ in a trivial way. So 
-we expect lists of each letter constitute $1/4$ of the answer list. However, 
-DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a}s than 
-lists of other letters. And some letters (e.g. lists of \texttt{c}) are rarely 
-found. The situation would be worse if we add more \conde clauses.
+Given the following program, it is natural to expect lists of each letter
+constitute $1/4$ in the answer. However, DFS$_\textrm{i}$, the current search
+strategy, results in much more lists of \texttt{a}s than lists of other
+letters. And some letters, e.g. \texttt{c} and \texttt{d}, are rarely seen.
+The situation would be exacerbated if \conde contains more clauses.
 
@@
 We borrow the definition of \emph{fair} \disj{} from \cite{seres1999algebra}: 
-search strategies with \emph{fair} \disj{} should allocate resource evenly 
+search strategies with \emph{fair} \disj{} should allocate resources evenly 
 among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS give the 
@@
 
-We conceive a middle place between fair and unfair -- search strategies with 
-\emph{almost-fair} \disj{} should allocate resource so evenly among disjunctive 
-goals\citep{seres1999algebra} that the the maximal ratio of resource is bounded 
-by a constant. Our new search strategy, DFS$_\textrm{bi}$, has almost-fair \disj{}. It is 
+Now we are in a middle place between fair and unfair -- search strategies
+with  \emph{almost-fair} \disj{} should allocate resources so evenly among
+disjunctive  goals\citep{seres1999algebra} that the the maximal ratio of
+resources is bounded by a constant. Our new search strategy,
+DFS$_\textrm{bi}$, has almost-fair \disj{}. It is
 fair when the number of goals is a power of 2, otherwise, some goals are 
-allocated twice more resource than the others. In the previous example, it 
+allocated twice more resources than the others. In the previous example,
+DFS$_\textrm{bi}$
 gives the same result. And in the following example, where the \conde has 5 
 clause, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated 
-more resource.
+more resources.
 
@@
 A more interesting situation is when the first conjunctive goal produces 
-infinite many states. Consider the following example, a naive specification of 
+infinite many answers. Consider the following example, a naive specification of 
 fair \conj{} might require search strategies to produce all sorts of singleton 
@@
 Our solution is requiring a search strategy with \emph{fair} \conj{} to 
-package states in bags, where each bag contains finite states, and to allocate 
-resource evenly among search spaces derived from states in the same bag. The 
-way to package depends on search strategy. And how to allocate resource among 
+package answers in bags, where each bag contains finite answers, and to allocate 
+resources evenly among search spaces derived from answers in the same bag. The 
+way to package depends on search strategy. And how to allocate resources among 
 search space related to different bags is unspecified. Our definition of fair 
@@
 
-BFS packages states by their costs. The \emph{cost} of a state is its 
+BFS packages answers by their costs. The \emph{cost} of a answer is its 
 depth in the search tree (i.e. the number of calls to relational definitions 
@@
 The implementation can be improved in two aspects. First, as we mentioned in 
-section 2.2, our BFS bag states by their cost. However, in this implementation, 
+section 2.2, our BFS bag answers by their cost. However, in this implementation, 
 it is unclear where this information is recorded. Second, 
@@
 
-As we mentioned in section 2.2, our BFS bag states by their cost. The bagging 
+As we mentioned in section 2.2, our BFS bag answers by their cost. The bagging 
 information is recorded subtly -- the \texttt{car}s of a search space have cost 
-0 (i.e. they are in the same bag), and the costs of states in thunk are 
+0 (i.e. they are in the same bag), and the costs of answers in thunk are 
 computed recursively then increased by one. It is even more subtle that
@@
 
-The new type is a pair whose \texttt{car} is a list of state (the bag), and 
+The new type is a pair whose \texttt{car} is a list of answers (the bag), and 
 whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search 
@@
 Fig.~\ref{BFS-opt} are search space constructor. \texttt{none} makes an empty 
-search space. \texttt{unit} makes an space from one state. \texttt{step} makes 
+search space. \texttt{unit} makes an space from one answer. \texttt{step} makes 
 a space from a thunk. The remaining functions do the same thing as before.
@@
 continuations \texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some 
-states, \texttt{ks} is called with the first state and the rest space. 
+answers, \texttt{ks} is called with the first answer and the rest space. 
 Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
@@
 Silvija's system is pure. Her system represents search spaces with streams of 
-lists of states, where each list is a bag.
+lists of answers, where each list is a bag.
 
@@
 except in \texttt{appendo}. The reason might be that strategies with fair 
-\conj{} tend to keep more intermediate states in the memory.
+\conj{} tend to keep more intermediate answers in the memory.
 

### 2019-05-02 Paper/paper.tex
tuning

@@
 \NOTE[MVC]{A quick intro to miniKanren would be nice here. We should mention The Reasoned Schemer, 2nd and say DFSi is used there.}
+\NOTE[MVC]{We should cite the monad paper in introduction.}
 
@@
 Given the following program, it is natural to expect lists of each letter
-constitute $1/4$ in the answer. However, DFS$_\textrm{i}$, the current search
-strategy, results in much more lists of \texttt{a}s than lists of other
-letters. And some letters, e.g. \texttt{c} and \texttt{d}, are rarely seen.
-The situation would be exacerbated if \conde contains more clauses.
+constitute $1/4$ in the answer. DFS$_\textrm{i}$, the current search
+strategy, however, results in many more lists of \texttt{a}s than lists
+of other letters. And some letters, e.g. \texttt{c} and \texttt{d}, are
+rarely seen. The situation would be exacerbated if \conde contains more clauses.
 
@@
 fair when the number of goals is a power of 2, otherwise, some goals are 
-allocated twice more resources than the others. In the previous example,
+allocated twice as many resources than the others. In the previous example,
 DFS$_\textrm{bi}$
@@
 lists, but no longer ones, which makes the strategies \emph{incomplete}. 
+\NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
 
@@
 is fair but not complete, while BFS is fair and complete. 
+\NOTE[MVC]{Also here, complete w.r.t what?}
 
@@
 the outer list. Noted that BFS produces answers in increasing order of cost.
+\NOTE[MVC]{Here inner and outer are very confusing. Can you be more specified?}
 
@@
 of \texttt{split}, it essentially constructs a \emph{balanced} binary tree 
-where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}, whence 
-the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$ essentially 
-constructs the same sort of binary tree in one of the most unbalanced forms.
+where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}s, hence 
+the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$
+constructs the binary tree with the same nodes but in the unbalanced form.
 
@@
 
+\NOTE[MVC]{Though bag is well known, people rarely say ``bagging''. How about putting information in a bag, or something better?}
+\NOTE[MVC]{What is the bagging information?}
 As we mentioned in section 2.2, our BFS bag answers by their cost. The bagging 
@@
 
-\subsection{comparison with Silvija's BFS}
+\subsection{comparison with the BFS of  \citep{seres1999algebra}}
 
@@
 found in \citep{seres1999algebra}. We focus on the pure subset because 
-Silvija's system is pure. Her system represents search spaces with streams of 
+Silvija's system is pure. Their system represents search spaces with streams of 
 lists of answers, where each list is a bag.
@@
 To compare efficiency, we translate her Haskell code into Racket (See 
-supplements for the translated code). The translation is fairly straightforward 
-due to the similarity in both logic programming system and search space 
-representation. The translated code is longer and slower. Details about 
-efficiency difference are in section 6.
+supplements for the translated code). The translation is direct 
+due to the similarity in both logic programming systems and search space 
+representations. The translated code is longer and slower. Details about 
+difference in efficiency are in section 6.
 
+\NOTE[MVC]{This is way too much into Coq. What we want to say here is that
+  for any number n and goal g, (run n g) our system generates the same result
+as Seres' does.}
 We prove the two search strategies are equivalent in Coq. Since search space 
@@
 memory. The first two benchmarks are taken from 
-\citep{friedman_reasoned_2018}. \texttt{reverso} is from 
-\citep{rozplokhas2018improving}. Next two benchmarks 
+\citet{friedman_reasoned_2018}. \texttt{reverso} is from 
+\citet{rozplokhas2018improving}. Next two benchmarks 
 about quine are modified from a similar test case in \citep{byrd2017unified}. 
@@
 Bruijnized expressions and prevent closures getting into list. The two 
-benchmarks differ in the \conde clause order of their relation interpreters. 
+benchmarks differ in the \conde clause order of their relational interpreters. 
 The last two 
@@
 you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
-sibling benchmarks differ in the \conde clause order of their relation 
+sibling benchmarks differ in the \conde clause order of their relational 
 interpreters. The first one 

### 2019-05-04 Paper/paper.tex
improve intro

@@
 \addeditor{MVC}
+\addeditor{LKC}
 
@@
 
+\newtheorem{defn}{Definition}[section]
+
 \begin{document}
@@
 the same chance of being explored, as these clauses are written in 
-parallel. The existing search strategy, interleaving DFS (DFS$_\textrm{i}$), however, 
-prioritize its clauses by the order how they are written down. Similarly, when 
-a \conde is followed by another goal conjunctively, a programmer would expect 
-answers in parallel share the same chance of being explored. Again, the answers 
-by DFS$_\textrm{i}$ is different from the expectation. We have devised three new search 
-strategies that have different level of fairness in \disj and \conj.
+parallel. The existing search strategy, interleaving DFS (DFS$_\textrm{i}$), 
+however, prioritize its clauses by the order how they are written down. 
+Similarly, when a \conde is followed by another goal conjunctively, a 
+programmer would expect answers in parallel share the same chance of being 
+explored. Again, the answers by DFS$_\textrm{i}$ is different from the 
+expectation. We have devised three new search strategies that have different 
+level of fairness in \disj and \conj.
 
@@
 \section{introduction}
-\NOTE[MVC]{We need clear definitions of the following: fair, almost-fair, and unfair. Either use bullet points, or definition environment. Google ``latex math definition.''}
-\NOTE[MVC]{A quick intro to miniKanren would be nice here. We should mention The Reasoned Schemer, 2nd and say DFSi is used there.}
-\NOTE[MVC]{We should cite the monad paper in introduction.}
 
-miniKanren programs, especially relational interpreters, have been proven to be 
-useful in solving many problems \citep{byrd2017unified}. A subtlety in writing 
-relational programs having \conde expressions with large number of clauses,
-such as interpreters, is 
-that the order of \conde clauses can affect the speed considerably. When a 
-\conde expression is large enough, the left clauses consume almost all the 
-resources and the right ones are barely explored. The cause is the unfair
-search strategy, interleaving DFS(DFS$_\textrm{i}$). In a \conde expression,
-each clause takes half of the received resources and pass the other half
-to the remaining clauses, except for the last clause that takes all resources
-it receives.
+miniKanren is a family of relational programming languages. miniKanren 
+programs, especially relational interpreters, have been proven to be 
+useful in solving many problems by \citet{byrd2017unified}.
 
-\NOTE[MVC]{A motivation is needed. Why do people want fairness?}
-\NOTE[MVC]{\texttt{conj} fairness is not defined.}
-Being aware of \texttt{disj} fairness, we also investigate \texttt{conj} 
-fairness. 
-We propose three new search strategies, balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
-DFS (DFS$_\textrm{f}$), and BFS. They have different characteristics of fairness 
-(Fig.~\ref{fairness}). We prove that the pure subset of our BFS and the BFS 
-proposed by Seres et
-al~\citep{seres1999algebra} produce the same result when queried. But our code 
-is simpler and runs faster on our benchmarks. Because the two BFSs are equivalent,
-we do not distinguish them in most places.
+A subtlety in writing miniKanren programs with large \conde expressions, such 
+as relational interpreters, is that the order of \conde clauses sometimes 
+affect the speed considerably. This phenomenon appears when running with the 
+miniKanren in \citet{friedman_reasoned_2018}, one of the most well-understood 
+implementation. This is because for all \conde expressions with more than two 
+clauses, the clauses are given different ``search priority''. Left clauses are 
+given higher priorities. This biased treatment causes 2 problems when a \conde 
+expression has many clauses: the right-most clause can hardly contribute to 
+query result; and the efficiency of the whole program might depend largely on 
+the order of these clauses.
+
+\NOTE[LKC]{Should I explain ``state'' and ``search space'' here?}
+
+Under the hood, \conde clauses are combined with \disj{}. The \disj{} 
+implementation in \citep{friedman_reasoned_2018} is not \emph{fair}.
+
+\begin{defn}[fair \disj]
+	A \disj{} is fair iff it allocates computational resource evenly among 
+	search spaces derived from disjunctive goals. \citet{seres1999algebra}
+\end{defn}
+
+A closely related concept is \emph{almost-fair} \disj.
+
+\begin{defn}[almost-fair \disj]
+	A \disj{} is almost-fair iff it allocates computational resource so evenly 
+	among search spaces derived from disjunctive goals that the maximal ratio 
+	of resources is bounded by a constant.
+\end{defn}
+
+The \disj{} in \citet{friedman_reasoned_2018}, or more precisely, in its search 
+strategy, interleaving DFS(DFS$_\textrm{i}$), is neither fair nor almost-fair. 
+Fair depth-first search (DFS$_\textrm{f}$), a new search strategy in this 
+paper, has fair \disj. And balanced interleaving depth-first search 
+(DFS$_\textrm{bi}$), another new strategy, has almost-fair \disj. Breath-first 
+search (BFS), a known strategy \citet{seres1999algebra}, has fair \disj{} and 
+\emph{fair \conj{}}.
+
+\begin{defn}[fair \conj]
+	A \conj{} is fair iff it allocates computational resource evenly among 
+	search spaces derived from states in the same bag, where bags are finite 
+	list of states.
+\end{defn}
+
+A comparison of fairness of search strategies is in Fig.~\ref{fairness}.
+
+To summarize our contribution, we
+\begin{itemize}
+	\item propose a new concept, almost-fair \disj{}.
+	\item propose a new definition of fair \conj{}.
+	\item propose and implement balanced interleaving depth-first search 
+	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \disj{}.
+	\item propose and implement fair depth-first search (DFS$_\textrm{f}$), a 
+	new search strategy with fair \disj{}.
+	\item implement in a new way breath-first search (BFS), a search strategy 
+	with fair \disj{} and fair \conj{}
+	(our code runs faster in all benchmarks and is simpler)
+	\item prove our BFS implementation is equivalent with the one by 
+	\citet{seres1999algebra}.
+\end{itemize}
 
@@
 % Interleaving DFS, the search strategy of \conde in
-% miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
+% miniKanren~\citet{friedman_reasoned_2018}, allocates computational resource
 % by the order in which the clauses are written. Each clause of a
@@
 
-In this section, we demonstrate the aspects (\disj{} or \conj{}) and levels
-(unfair, almost-fair, or fair) of fairness by running queries about
-\texttt{repeato}, a 
-relational definition that relates a term \texttt{x} with a non-empty list 
-whose elements are \texttt{x} (Fig.~\ref{repeato}).
+In this section, we elaborate fairness by running queries about 
+\texttt{repeato}, a relational definition that relates a term \texttt{x} with a 
+non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
 
@@
 
-Given the following program, it is natural to expect lists of each letter
+Given the following program, it is natural to expect lists of each letter to
 constitute $1/4$ in the answer. DFS$_\textrm{i}$, the current search
@@
 
-We borrow the definition of \emph{fair} \disj{} from \cite{seres1999algebra}: 
+We borrow the definition of \emph{fair} \disj{} from \citet{seres1999algebra}: 
 search strategies with \emph{fair} \disj{} should allocate resources evenly 
-among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS give the 
-following result.
+among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS 
+give the following result.
 
@@
 with  \emph{almost-fair} \disj{} should allocate resources so evenly among
-disjunctive  goals\citep{seres1999algebra} that the the maximal ratio of
-resources is bounded by a constant. Our new search strategy,
+disjunctive goals that the maximal ratio of resources is bounded by a constant. 
+Our new search strategy,
 DFS$_\textrm{bi}$, has almost-fair \disj{}. It is
@@
 In the following program, the three \conde clauses differ in a trivial way. So 
-we expect lists of each letter constitute $1/4$ of the answer list. However, 
-search strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$) give us much 
-more lists of \texttt{a}s than lists of other letters. And some letters (e.g. lists 
+we expect lists of each letter constitute $1/4$ of the answer list. Search 
+strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$), 
+however, give us many more lists of \texttt{a}s than lists of other letters. 
+And some letters (e.g. lists 
 of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
@@
 \begin{center}
-	\begin{tabular}{c}
+	\begin{tabular}{c|c}
 		\lstinputlisting{Figures/repeato-conj-fair.rkt}
@@
 \NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
+\NOTE[LKC]{I am a bit confused. I assume completeness is a well-known concept 
+in the context of logic programming. For example, this paper doesn't cite any 
+source when it talks about completeness.
+
+Hemann, Jason, et al. "A small embedding of logic programming with a simple 
+complete search." ACM SIGPLAN Notices. Vol. 52. No. 2. ACM, 2016.}
 
@@
 
-Our solution is requiring a search strategy with \emph{fair} \conj{} to 
+Our solution requires a search strategy with \emph{fair} \conj{} to 
 package answers in bags, where each bag contains finite answers, and to allocate 
@@
 depth in the search tree (i.e. the number of calls to relational definitions 
-required to find them) \citep{seres1999algebra}. In the following example, the 
-cost of an answer is equal to the length of the inner lists plus the length of 
-the outer list. Noted that BFS produces answers in increasing order of cost.
+required to find them) \citet{seres1999algebra}. In the following example, 
+every answer is a list of list of symbol. The cost of each of them is equal to 
+the length of the inner lists plus the length of the outer list. In addition to 
+being fair, BFS also produces answers in increasing order of cost.
 \NOTE[MVC]{Here inner and outer are very confusing. Can you be more specified?}
+\NOTE[LKC]{updated}
 
@@
 clauses essentially copy the \texttt{car}s and stop recursion when one of the 
-input spaces is obviously finite. The third clause, as we mentioned early, is 
+input spaces is obviously finite. The third clause, as we mentioned above, is 
 just for swapping. When the fourth and last clause runs, we know that both 
@@
 
-The implementation can be improved in two aspects. First, as we mentioned in 
-section 2.2, our BFS bag answers by their cost. However, in this implementation, 
-it is unclear where this information is recorded. Second, 
+The implementation can be improved in two ways. First, as mentioned in 
+section 2.2, BFS puts answers in bags and answers of the same cost are in the 
+same bag. In this implementation, however, it is unclear where this information 
+is recorded. Second, 
 \texttt{append-inf/fair} is extravagant in memory usage. It makes 
@@
 
-Both our BFS and Seres's BFS \citep{seres1999algebra} produce answers in 
+Both our BFS and Seres's BFS \citet{seres1999algebra} produce answers in 
 increasing order of cost. So it is interesting to see if they are equivalent. 
@@
 \NOTE[MVC]{What is the bagging information?}
-As we mentioned in section 2.2, our BFS bag answers by their cost. The bagging 
+\NOTE[LKC]{It's just cost... You're right. I should have be more direct.}
+
+As mentioned in section 2.2, BFS puts answers in bags and answers of the 
+same cost are in the same bag. The cost
 information is recorded subtly -- the \texttt{car}s of a search space have cost 
@@
 Functions related to the pure subset are listed in Fig.~\ref{BFS-opt} (the 
-others in Fig.~\ref{BFS-opt-cont}). We take them apart because they are 
-compared with Seres's implementation later. The first three functions in 
-Fig.~\ref{BFS-opt} are search space constructor. \texttt{none} makes an empty 
-search space. \texttt{unit} makes an space from one answer. \texttt{step} makes 
-a space from a thunk. The remaining functions do the same thing as before.
+others in Fig.~\ref{BFS-opt-cont}). They are compared with 
+\citeauthor{seres1999algebra}'s implementation later. The first three functions 
+in Fig.~\ref{BFS-opt} are search space constructors. \texttt{none} makes an 
+empty search space; \texttt{unit} makes a space from one answer; and 
+\texttt{step} makes a space from a thunk. The remaining functions do the same 
+thing as before.
 
@@
 
-Noted that some functions here constitute a \emph{MonadPlus}: 
-\texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and \texttt{append-inf} 
-correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, and \texttt{mplus} 
-respectively.
+\citet{kiselyov2005backtracking} has shown that a \emph{MonadPlus} hides in 
+implementations of logic programming system. Our BFS implementation is not an 
+exception: \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and 
+\texttt{append-inf} correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, 
+and \texttt{mplus} respectively.
 
@@
 `succeed' and `fail' respectively. This function is an eliminator of search 
-space, whence the name. The remaining functions do the same thing as before.
+space, hence the name. The remaining functions do the same thing as before.
 
-\subsection{comparison with the BFS of  \citep{seres1999algebra}}
+\subsection{comparison with the BFS of \citet{seres1999algebra}}
 
 In this section, we compare the pure subset of our optimized BFS with the BFS 
-found in \citep{seres1999algebra}. We focus on the pure subset because 
+found in \citet{seres1999algebra}. We focus on the pure subset because 
 Silvija's system is pure. Their system represents search spaces with streams of 
@@
 
-\NOTE[MVC]{This is way too much into Coq. What we want to say here is that
-  for any number n and goal g, (run n g) our system generates the same result
-as Seres' does.}
-We prove the two search strategies are equivalent in Coq. Since search space 
-can be infinite, we should use a co-inductive data type. However, Coq is too 
-strict in the guardedness condition to accept a direct translation of the 
-implementations. Therefore, we prove core theorems with finite search space 
-instead. In order to generalize the conclusion to the cases with infinite 
-search space, we prove a few more theorems saying that whenever we query 
-answers lower than some finite cost, we can restrict goals to truncate search 
-spaces at some finite depth without changing the query result. (See supplements 
-for the formal proof)
+We prove in Coq that the two BFSs are equivalent, i.e. \texttt{(run n g)} 
+produces the same result (See supplements for the formal proof).
 
@@
 \citet{rozplokhas2018improving}. Next two benchmarks 
-about quine are modified from a similar test case in \citep{byrd2017unified}. 
+about quine are modified from a similar test case in \citet{byrd2017unified}. 
 The modifications are made 
@@
 benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
-you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
+you)}. This benchmark is also inspired by \citet{byrd2017unified}. Again, the 
 sibling benchmarks differ in the \conde clause order of their relational 
@@
 better. Interestingly, every strategies with fair \disj{} suffers in 
-\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. Therefore, this 
+\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
+Therefore, this 
 benchmark might be a special case. Fair \conj{} imposes overhead constantly 
@@
 Edward points out a disjunct complex would be `fair' if it is a full and 
-balanced tree \citep{yang2010adventures}.
+balanced tree \citet{yang2010adventures}.
 
-Silvija et al \citep{seres1999algebra} also describe a breadth-first search 
-strategy. We proof their BFS is equivalent to ours. However, ours looks simpler 
+Silvija et al \citet{seres1999algebra} also describe a breadth-first search 
+strategy. We proof their BFS is equivalent to ours. But our code looks simpler 
 and performs better in comparison with a straightforward translation of their 
@@
 
-We prove our BFS is equivalent to the BFS in \citep{seres1999algebra}. Our code 
+We prove our BFS is equivalent to the BFS in \citet{seres1999algebra}. Our code 
 is shorter and runs faster than a direct translation of their Haskell code.

### 2019-05-04 Paper/paper.tex
intro

@@
 \newcommand{\disj}{\texttt{disj}}
+\newcommand{\clisting}[1]{
+\begin{center}
+  \begin{tabular}{c}
+	\lstinputlisting{#1}
+    \end{tabular}
+\end{center}
+}
 
@@
 
-miniKanren is a family of relational programming languages. miniKanren 
-programs, especially relational interpreters, have been proven to be 
+miniKanren is a family of relational programming languages.
+\citet{friedman_reasoned_2018} introduce miniKanren and its implementation
+in the The Reasoned Schemer, 2nd Ed(TR2). miniKanren programs, especially
+relational interpreters, have been proven to be 
 useful in solving many problems by \citet{byrd2017unified}.
 
-A subtlety in writing miniKanren programs with large \conde expressions, such 
+\conde is the flagship disjunction operator in miniKanren. A subtlety arises
+when a \conde contains many disjunction clauses: not every clause has the equal
+chance to contribute to the answers. As an example, consider the following
+relation \texttt{repeato} and its invocation.
+\clisting{Figures/repeato.rkt}
+Next, consider the following disjuction of invoking \texttt{repeato} with
+four different letters.
+\clisting{Figures/example.rkt}
+\conde intuitively corresponds to \texttt{or} in logic. An unsuspicious beginner
+would expect each letter to contribute equally to the result, as following. 
+\clisting{Figures/run-repeato-fair.rkt}
+The \conde in TR2, however, generates a less expected result.
+\clisting{Figures/run-repeato-idfs.rkt}
+
+A subtlety arises when 
+A subtlety in writing miniKanren programs with \conde expressions with many
+clauses, such 
 as relational interpreters, is that the order of \conde clauses sometimes 
@@
 In this section, we elaborate fairness by running queries about 
-\texttt{repeato}, a relational definition that relates a term \texttt{x} with a 
+\texttt{repeato2}, a relational definition that relates a term \texttt{x} with a 
 non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
@@
 	\caption{\texttt{repeato} and an example run}
-	\label{repeato}
+	\label{repeato2}
 \end{figure}

### 2019-05-04 Paper/paper.tex
intro

@@
 }
+\newcommand{\DFSi}[0]{
+  DFS$_\textrm{i}$
+}
 
@@
 when a \conde contains many disjunction clauses: not every clause has the equal
-chance to contribute to the answers. As an example, consider the following
+chance to contribute to the result. As an example, consider the following
 relation \texttt{repeato} and its invocation.
@@
 \clisting{Figures/example.rkt}
-\conde intuitively corresponds to \texttt{or} in logic. An unsuspicious beginner
-would expect each letter to contribute equally to the result, as following. 
+\conde intuitively corresponds to \texttt{or} in logic. And thus an unsuspicious
+beginner would expect each letter to contribute equally to the result, as
+following.
 \clisting{Figures/run-repeato-fair.rkt}
@@
 
-A subtlety arises when 
-A subtlety in writing miniKanren programs with \conde expressions with many
-clauses, such 
-as relational interpreters, is that the order of \conde clauses sometimes 
-affect the speed considerably. This phenomenon appears when running with the 
-miniKanren in \citet{friedman_reasoned_2018}, one of the most well-understood 
-implementation. This is because for all \conde expressions with more than two 
-clauses, the clauses are given different ``search priority''. Left clauses are 
-given higher priorities. This biased treatment causes 2 problems when a \conde 
-expression has many clauses: the right-most clause can hardly contribute to 
-query result; and the efficiency of the whole program might depend largely on 
-the order of these clauses.
+\conde implements interleaving DFS(\DFSi), the cause of this unexpected result.
+In a \conde, each clause takes a half of its received computational resources
+and pass the other half to its following clauses, except for the last clause
+that takes all resources it receives. In the example above, the letters
+\texttt{c} and \texttt{d} are allocated with less resources than \texttt{a},
+and thus \texttt{c} and \texttt{d} barely contribute to the result.
+
+\DFSi is powerful for an expert. By carefully organizing the order of \conde
+clauses, a miniKanren program can explore more ``interesting'' clauses than
+those uninteresting ones, and thus use computational resources efficiently.
+A little miniKanrener, however, may beg to differ--understanding
+implementation details and fiddling with clauses order is not the first
+priority of a beginner.
+
+There is another reason that miniKanren could use more search strategies than
+just \DFSi. In many applications, there does not exist one order that serves
+for all purposes. For example, a relational dependent type checker contains
+clauses for constructors that build data and clauses for eliminators that use
+data. When this type checker is used to generate simple and shallow programs,
+the clauses of constructors should be put in the front of \conde.
+When performing proof search for complicated programs, the clauses of eliminator
+should take the focus. With \DFSi, these two uses can not be efficient at the
+same time. In fact, to make on use efficient, the other one must be drastically
+slow.
 

### 2019-05-05 Paper/paper-slatex.tex
revise intro; revise fairness - fair disj

--- 2019-05-04 Paper/paper.tex
@@
 
-\addeditor{MVC}
-\addeditor{LKC}
+%% slatex
+\usepackage{slatex}
+\setkeyword{defrel conde fresh run}
+\setspecialsymbol{==}{$\equiv$}
+\setspecialsymbol{conde}{\textbf{cond$^e$}}
+\setspecialsymbol{append-inf}{append$^\infty$}
+\setspecialsymbol{append-inf/fair}{append$^\infty_f$}
+\setspecialsymbol{append-inf/fair^}{append$^\infty_f$\textasciicircum}
+\setspecialsymbol{append-map-inf}{append-map$^\infty$}
+\setspecialsymbol{append-map-inf/fair}{append-map$^\infty_f$}
+\setspecialsymbol{repeato}{repeat$^o$}
+\setspecialsymbol{appendo}{append$^o$}
+\setspecialsymbol{very-recursiveo}{very-recursive$^o$}
+\setspecialsymbol{g1}{$g_1$}
+\setspecialsymbol{g2}{$g_2$}
+\setspecialsymbol{g3}{$g_3$}
+\setspecialsymbol{gs1}{$gs_1$}
+\setspecialsymbol{gs2}{$gs_2$}
+\setspecialsymbol{ks}{$k_s$}
+\setspecialsymbol{kf}{$k_f$}
+\setspecialsymbol{s-inf}{s$^\infty$}
+\setspecialsymbol{t-inf}{t$^\infty$}
+\setspecialsymbol{prod}{$\times$}
+\setspecialsymbol{->}{$\rightarrow$}
+\setspecialsymbol{#|}{\texttt{\#{}|}}
+\setspecialsymbol{|#}{\texttt{|\#{}}}
+\def\variablefont#1{{\tt#1\/}} 
+\def\datafont#1{{\tt#1\/}} 
+\def\constantfont#1{{\tt#1\/}}
 
+%% scheme-list configuration
 \lstset{
@@
 }
-%% scheme-list .
+
+\addeditor{MVC}
+\addeditor{LKC}
 
@@
 
-\newcommand{\conde}{\texttt{cond$^e$} }
-\newcommand{\conj}{\texttt{conj}}
-\newcommand{\disj}{\texttt{disj}}
+\newtheorem{defn}{Definition}[section]
 
-\newtheorem{defn}{Definition}[section]
+% abbreviations
+\newcommand{\dfsi}[0]{DFS$_\textrm{i}$}
+\newcommand{\dfsbi}[0]{DFS$_\textrm{bi}$}
+\newcommand{\dfsf}[0]{DFS$_\textrm{f}$}
 
@@
 The syntax of a programming language should reflect its semantics. When writing 
-a \conde expression in miniKanren, a programmer would expect all clauses share 
-the same chance of being explored, as these clauses are written in 
+a \scheme|conde| expression in miniKanren, a programmer would expect all clauses 
+share the same chance of being explored, as these clauses are written in 
 parallel. The existing search strategy, interleaving DFS (DFS$_\textrm{i}$), 
 however, prioritize its clauses by the order how they are written down. 
-Similarly, when a \conde is followed by another goal conjunctively, a 
+Similarly, when a \scheme|conde| is followed by another goal conjunctively, a 
 programmer would expect answers in parallel share the same chance of being 
@@
 expectation. We have devised three new search strategies that have different 
-level of fairness in \disj and \conj.
-
-%The syntax of a programming language should reflect its semantics. When using 
-%a disjunctive operator in relational programming, a programmer would expect 
-%all 
-%sub-goals of this disjunct to share the same chance of being explored, as 
-%these 
-%clauses are written in parallel. The existing multi-arity disjunctive operator 
-%in miniKanren, however, prioritize its clauses by the order of which these 
-%clauses are written down. We have devised two new search strategies that 
-%allocate computational effort more fairly in all clauses.
+level of fairness in \scheme|disj| and \scheme|conj|.
 
@@
 programs, especially relational interpreters, have been proven to be
-useful in solving many problems by \citet{byrd2017unified}.
+useful in solving many problems by \citet{byrd2017unified}. A subtlety in 
+writing miniKanren programs with large \scheme|conde| expressions, such as 
+relational interpreters, is that the order of \scheme|conde| clauses sometimes 
+affect the speed considerably. This phenomenon also appears when running 
+miniKanren programs with the implementation in \citet{friedman_reasoned_2018}, 
+one of the most well-understood implementation. This is because the search 
+strategy of this implementation, interleaving depth-first search (\dfsi), gives 
+left clauses higher ``search priority'' when a \scheme|conde| has more than two 
+clauses. The situation is exacerbated as the number of clauses increases. This 
+unfair treatment causes two problems when a \scheme|conde| expression has many 
+clauses: the right-most clause can hardly contribute to query result; and 
+programmers might need to tweak the clause order to maximize their programs' 
+efficiency, depending on the distribution of queries.
 
-A subtlety in writing miniKanren programs with large \conde expressions, such 
-as relational interpreters, is that the order of \conde clauses sometimes 
-affect the speed considerably. This phenomenon appears when running with the 
-miniKanren in \citet{friedman_reasoned_2018}, one of the most well-understood 
-implementation. This is because for all \conde expressions with more than two 
-clauses, the clauses are given different ``search priority''. Left clauses are 
-given higher priorities. This biased treatment causes 2 problems when a \conde 
-expression has many clauses: the right-most clause can hardly contribute to 
-query result; and the efficiency of the whole program might depend largely on 
-the order of these clauses.
-
-\NOTE[LKC]{Should I explain ``state'' and ``search space'' here?}
-
-Under the hood, \conde clauses are combined with \disj{}. The \disj{} 
-implementation in \citep{friedman_reasoned_2018} is not \emph{fair}.
-
-\begin{defn}[fair \disj]
-	A \disj{} is fair iff it allocates computational resource evenly among 
-	search spaces derived from disjunctive goals. \citet{seres1999algebra}
-\end{defn}
-
-A closely related concept is \emph{almost-fair} \disj.
-
-\begin{defn}[almost-fair \disj]
-	A \disj{} is almost-fair iff it allocates computational resource so evenly 
-	among search spaces derived from disjunctive goals that the maximal ratio 
-	of resources is bounded by a constant.
-\end{defn}
-
-The \disj{} in \citet{friedman_reasoned_2018}, or more precisely, in its search 
-strategy, interleaving DFS(DFS$_\textrm{i}$), is neither fair nor almost-fair. 
-Fair depth-first search (DFS$_\textrm{f}$), a new search strategy in this 
-paper, has fair \disj. And balanced interleaving depth-first search 
-(DFS$_\textrm{bi}$), another new strategy, has almost-fair \disj. Breath-first 
-search (BFS), a known strategy \citet{seres1999algebra}, has fair \disj{} and 
-\emph{fair \conj{}}.
-
-\begin{defn}[fair \conj]
-	A \conj{} is fair iff it allocates computational resource evenly among 
-	search spaces derived from states in the same bag, where bags are finite 
-	list of states.
-\end{defn}
-
-A comparison of fairness of search strategies is in Fig.~\ref{fairness}.
+The specification that every clause in the same \scheme|conde| is given equal 
+``search priority'' is called fair \scheme|disj|. And search strategies with 
+\emph{almost-fair} \scheme|disj| should give every clauss in the same 
+\scheme|conde| similar priority. A related concept, fair \scheme|conj| is more 
+complicated. We defer it to the next section.
 
@@
 \begin{itemize}
-	\item propose a new concept, almost-fair \disj{}.
-	\item propose a new definition of fair \conj{}.
+    \item analyze an existing concept, fair \scheme|disj| by 
+\citet{seres1999algebra}.
+	\item propose a new concept, almost-fair \scheme|disj|.
+	\item propose a new definition of fair \scheme|conj|.
 	\item propose and implement balanced interleaving depth-first search 
-	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \disj{}.
+	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \scheme|disj|.
 	\item propose and implement fair depth-first search (DFS$_\textrm{f}$), a 
-	new search strategy with fair \disj{}.
+	new search strategy with fair \scheme|disj|.
 	\item implement in a new way breath-first search (BFS), a search strategy 
-	with fair \disj{} and fair \conj{}
+	with fair \scheme|disj| and fair \scheme|conj|
 	(our code runs faster in all benchmarks and is simpler)
@@
 
-\begin{figure}[tbp]
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline 
-		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS \\ 
-		\hline 
-		disj & unfair & almost-fair & fair & fair \\ 
-		\hline 
-		conj & unfair & unfair & unfair & fair \\ 
-		\hline 
-	\end{tabular} 
-	\caption{fairness of search strategies}
-	\label{fairness}
-\end{figure}
+% A comparison of fairness of search strategies is in Fig.~\ref{fairness}.
 
-% Interleaving DFS, the search strategy of \conde in
-% miniKanren~\citet{friedman_reasoned_2018}, allocates computational resource
-% by the order in which the clauses are written. Each clause of a
-% \conde takes half of the current resource and passes the other half
-% to its following clauses, except for the last clause that takes all of the 
-%current resource. 
-% The biased treatment provides both opportunity and burden: miniKanren users 
-%can place more frequently used 
-% goal at the beginning to optimize their programs; however, it might be a 
-% catastrophe if a goal that generates many useless states is placed before 
-%more 
-% important goals. Seasoned miniKanreners usually know how to utilize 
-% the unfairness to optimize their programs. However, we believe search 
-%strategies that is less sensitive to goal order can also be useful to little 
-%miniKanreners as well as seasoned ones. We propose two such search strategies, 
-%balanced interleaving DFS (DFS$_\textrm{bi}$) and breadth-first search (BFS), and observe 
-%how they affect the efficiency and the answer order of known miniKanren 
-%programs. The experiment is conducted with the miniKanren from \textit{The 
-%Reasoned Schemer, 2nd Edition}.
+% \begin{figure}[tbp]
+% 	\begin{tabular}{|c|c|c|c|c|}
+% 		\hline 
+% 		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS \\ 
+% 		\hline 
+% 		disj & unfair & almost-fair & fair & fair \\ 
+% 		\hline 
+% 		conj & unfair & unfair & unfair & fair \\ 
+% 		\hline 
+% 	\end{tabular} 
+% 	\caption{fairness of search strategies}
+% 	\label{fairness}
+% \end{figure}
 
@@
 
-In this section, we elaborate fairness by running queries about 
-\texttt{repeato}, a relational definition that relates a term \texttt{x} with a 
-non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
+Before going further into fairness, we would like to give a short review about 
+state, search space, and goal, because fairness is defined in terms of them. 
+Every answer given by miniKanren corresponds to a state. Each state records a 
+way how some relations can be satisfied. In our case, the state is just a 
+subsitution associating logic variables with terms. In more expressive 
+miniKanrens (e.g. miniKanren with with symbolic constraints 
+\citep{hemann2017framework}), states can include more information. A search 
+space is a collection of states. And a goal is a function from a state to a 
+search space. Goals check their inputs and produces possibly extended states. A 
+goal might fail for some input, in which case the output search space would be 
+empty.
+
+Now we elaborate fairness by running queries about \scheme|repeato|, a 
+relational definition that relates a term \scheme|x| with a non-empty list whose 
+elements are \scheme|x| (Fig.~\ref{repeato}).
+
+% 
+% \begin{defn}[fair \scheme|conj|]
+% A \scheme|conj| is fair iff it allocates computational resource evenly to 
+% search spaces derived from states in the same bag, where bags are finite 
+% list of states.
+% \end{defn}
 
 \begin{figure}
-	\lstinputlisting{Figures/repeato.rkt}
-	\caption{\texttt{repeato} and an example run}
+	\schemeinput{Figures/repeato.rkt}
+	\caption{\texttt{repeat$^o$} and an example run}
 	\label{repeato}
@@
 constitute $1/4$ in the answer. DFS$_\textrm{i}$, the current search
-strategy, however, results in many more lists of \texttt{a}s than lists
-of other letters. And some letters, e.g. \texttt{c} and \texttt{d}, are
-rarely seen. The situation would be exacerbated if \conde contains more clauses.
+strategy, however, results in many more lists of \scheme|a|s than lists
+of other letters. And some letters, e.g. \scheme|c| and \scheme|d|, are
+rarely seen. The situation would be exacerbated if \scheme|conde| 
+contains more clauses.
 
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-iDFS.rkt}
-	\end{tabular}
+    \begin{schemeregion}
+    \schemeinput{Figures/repeato-disj-iDFS.rkt}
+    \end{schemeregion}
 \end{center}
 
-We borrow the definition of \emph{fair} \disj{} from \citet{seres1999algebra}: 
-search strategies with \emph{fair} \disj{} should allocate resources evenly 
-among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS 
-give the following result.
+Under the hood, the \scheme|conde| here is allocating computational effort to 
+four trivially different search space. The unfair \scheme|disj| in 
+\dfsi{} allocates much more effort to the first search space. On the contrary, 
+fair \scheme|disj|s would allocate effort evenly to each search space.
 
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-fair.rkt}
-	\end{tabular}
+    \begin{schemeregion}
+    \schemeinput{Figures/repeato-disj-DFSf.rkt}
+    \end{schemeregion}
 \end{center}
 
-Now we are in a middle place between fair and unfair -- search strategies
-with  \emph{almost-fair} \disj{} should allocate resources so evenly among
-disjunctive goals that the maximal ratio of resources is bounded by a constant. 
-Our new search strategy,
-DFS$_\textrm{bi}$, has almost-fair \disj{}. It is
-fair when the number of goals is a power of 2, otherwise, some goals are 
-allocated twice as many resources than the others. In the previous example,
-DFS$_\textrm{bi}$
-gives the same result. And in the following example, where the \conde has 5 
-clause, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated 
-more resources.
+\begin{center}
+    \begin{schemeregion}
+    \schemeinput{Figures/repeato-disj-BFS.rkt}
+    \end{schemeregion}
+\end{center}
+
+Running the same program again with almost-fair \scheme|disj| 
+(e.g. DFS$_\textrm{bi}$) gives the same result. Almost-fair, however, is not 
+completely fair, as shown by the following example.
 
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-biDFS.rkt}
-	\end{tabular}
+    \begin{schemeregion}
+    \schemeinput{Figures/repeato-disj-biDFS.rkt}
+    \end{schemeregion}
 \end{center}
+
+DFS$_\textrm{bi}$ is fair only when the number of goals is a power of 2, 
+otherwise, some goals are allocated twice as many resources than the others. In 
+the above example, where the \scheme|conde| has five clauses, the clauses of 
+\scheme|b|, \scheme|c|, and \scheme|d| are allocated more resources.
+
+We end this subsection with precise definitions of all levels of 
+\scheme|disj| fairness.
+
+Our definition of \emph{fair} \scheme|disj| is slightly generalize from the one 
+by \citet{seres1999algebra}. Their definition is for binary disjunct. We 
+generalize it to multi-arity one.
+
+\begin{defn}[fair \scheme|disj|]
+A \scheme|disj| is fair iff it allocates computational resource evenly to 
+search spaces produced by goals in the same disjunct (e.g. clauses in the 
+same 
+\scheme|conde|).
+\end{defn}
+
+\begin{defn}[almost-fair \scheme|disj|]
+A \scheme|disj| is almost-fair iff it allocates computational resource so 
+evenly to search spaces produced by goals in the same disjunct that the maximal 
+ratio of resources is bounded by a constant.
+\end{defn}
+
+\begin{defn}[unfair \scheme|disj|]
+A \scheme|disj| is unfair iff it is not even almost-fair.
+\end{defn}
 
@@
 
-In the following program, the three \conde clauses differ in a trivial way. So 
+In the following program, the three \scheme|conde| clauses differ in a trivial way. So 
 we expect lists of each letter constitute $1/4$ of the answer list. Search 
-strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$), 
-however, give us many more lists of \texttt{a}s than lists of other letters. 
+strategies with unfair \scheme|conj| (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$), 
+however, give us many more lists of \scheme|a|s than lists of other letters. 
 And some letters (e.g. lists 
-of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
+of \scheme|c|) are rarely found. Although DFS$_\textrm{i}$'s \scheme|disj| is unfair in general, 
 it is fair when there is no call to relational definition in sub-goals, 
-including this case. The situation would be worse if we add more \conde 
-clauses. The result with DFS$_\textrm{bi}$, whose \conj{} is also unfair, is similar, but 
-due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
+including this case. The situation would be worse if we add more \scheme|conde| 
+clauses. The result with DFS$_\textrm{bi}$, whose \scheme|conj| is also unfair, is similar, but 
+due to its different \scheme|disj|, the position of \scheme|b| and \scheme|c| are 
 swapped.
@@
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-unfair.rkt}
-	\end{tabular}
+	\begin{schemeregion}
+    \schemeinput{Figures/repeato-conj-iDFS.rkt}
+	\end{schemeregion}
 \end{center}
 
-Intuitively, search strategies with fair \conj{} should produce each letter of 
+\begin{center}
+	\begin{schemeregion}
+    \schemeinput{Figures/repeato-conj-fDFS.rkt}
+	\end{schemeregion}
+\end{center}
+
+Intuitively, search strategies with fair \scheme|conj| should produce each letter of 
 lists equally frequently. Indeed, BFS does so.
@@
 \begin{center}
-	\begin{tabular}{c|c}
-		\lstinputlisting{Figures/repeato-conj-fair.rkt}
-	\end{tabular}
+	\begin{schemeregion}
+    \schemeinput{Figures/repeato-conj-fair.rkt}
+	\end{schemeregion}
 \end{center}
@@
 infinite many answers. Consider the following example, a naive specification of 
-fair \conj{} might require search strategies to produce all sorts of singleton 
+fair \scheme|conj| might require search strategies to produce all sorts of singleton 
 lists, but no longer ones, which makes the strategies \emph{incomplete}.
+
 \NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
+
 \NOTE[LKC]{I am a bit confused. I assume completeness is a well-known concept 
@@
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-infinite-naive.rkt}
-	\end{tabular}
+	\begin{schemeregion}
+    \schemeinput{Figures/repeato-conj-infinite-naive.rkt}
+	\end{schemeregion}
 \end{center}
 
-Our solution requires a search strategy with \emph{fair} \conj{} to 
+Our solution requires a search strategy with \emph{fair} \scheme|conj| to 
 package answers in bags, where each bag contains finite answers, and to allocate 
@@
 search space related to different bags is unspecified. Our definition of fair 
-\conj{} is orthogonal with completeness. For example, a naively fair strategy 
+\scheme|conj| is orthogonal with completeness. For example, a naively fair strategy 
 is fair but not complete, while BFS is fair and complete. 
@@
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-infinite-sof.rkt}
-	\end{tabular}
+	\begin{schemeregion}
+		\schemeinput{Figures/repeato-conj-infinite-sof.rkt}
+	\end{schemeregion}
 \end{center}
@@
 \begin{figure}
-	\lstinputlisting{Figures/balanced-disj.rkt}
+	\schemeinput{Figures/balanced-disj.rkt}
 	\caption{DFS$_\textrm{bi}$ implementation}
@@
 
-Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair \conj{}. 
-The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ in the \disj{} macro. We list the 
-new \disj{} with its helpers in Fig.~\ref{balanced-disj}. The first helper 
-function, \texttt{split}, takes a list of goals \texttt{ls} and a procedure 
-\texttt{k}, partitions \texttt{ls} into two sub-lists of roughly equal length, 
-and returns the application of \texttt{k} to the two sub-lists. \texttt{disj*} 
-takes a non-empty list of goals \texttt{gs} and returns a goal. With the help 
-of \texttt{split}, it essentially constructs a \emph{balanced} binary tree 
-where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}s, hence 
-the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$
+Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \scheme|disj| and unfair \scheme|conj|. 
+The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ in the \scheme|disj| macro. We list the 
+new \scheme|disj| with its helpers in Fig.~\ref{balanced-disj}. The first helper 
+function, \scheme{split}, takes a list of goals \scheme{ls} and a procedure 
+\scheme{k}, partitions \scheme{ls} into two sub-lists of roughly equal length, 
+and returns the application of \scheme{k} to the two sub-lists. \scheme{disj*} 
+takes a non-empty list of goals \scheme{gs} and returns a goal. With the help 
+of \scheme{split}, it essentially constructs a \emph{balanced} binary tree 
+where leaves are elements of \scheme{gs} and nodes are \scheme{disj2}s, hence 
+the name of this search strategy. In contrast, the \scheme|disj| in DFS$_\textrm{i}$
 constructs the binary tree with the same nodes but in the unbalanced form.
@@
 \begin{figure}
-	\lstinputlisting{Figures/fDFS.rkt}
+	\schemeinput{Figures/fDFS.rkt}
 	\caption{DFS$_\textrm{f}$ implementation}
@@
 
-Fair DFS (DFS$_\textrm{f}$) has fair \disj{} and unfair \conj{}. The implementation of DFS$_\textrm{f}$ 
-differs from DFS$_\textrm{i}$'s in \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is 
-changed to call a new and fair version of \texttt{append-inf}. 
-\texttt{append-inf/fair} immediately calls its helper, 
-\texttt{append-inf/fair\^{}}, with the first argument, \texttt{s?}, set to 
-\texttt{\#{}t}, which indicates that \texttt{s-inf} and \texttt{t-inf} haven't 
-been swapped. The swapping happens at the third \texttt{cond} clause in the 
-helper, where \texttt{s?} is updated accordingly. The first two \texttt{cond} 
-clauses essentially copy the \texttt{car}s and stop recursion when one of the 
+Fair DFS (DFS$_\textrm{f}$) has fair \scheme|disj| and unfair \scheme|conj|. The implementation of DFS$_\textrm{f}$ 
+differs from DFS$_\textrm{i}$'s in \scheme{disj2} (Fig.~\ref{fDFS}). \scheme{disj2} is 
+changed to call a new and fair version of \scheme{append-inf}. 
+\scheme{append-inf/fair} immediately calls its helper, 
+\scheme{append-inf/fair^}, with the first argument, \scheme{s?}, set to 
+\scheme{#t}, which indicates that \scheme{s-inf} and \scheme{t-inf} haven't 
+been swapped. The swapping happens at the third \scheme{cond} clause in the 
+helper, where \scheme{s?} is updated accordingly. The first two \scheme{cond} 
+clauses essentially copy the \scheme{car}s and stop recursion when one of the 
 input spaces is obviously finite. The third clause, as we mentioned above, is 
 just for swapping. When the fourth and last clause runs, we know that both 
-\texttt{s-inf} and \texttt{t-inf} are ended with a thunk. In this case, a new 
+\scheme{s-inf} and \scheme{t-inf} are ended with a thunk. In this case, a new 
 thunk is constructed. The new thunk calls the driver recursively. Here changing 
-the order of \texttt{t-inf} and \texttt{s-inf} won't hurt the fairness (though 
+the order of \scheme{t-inf} and \scheme{s-inf} won't hurt the fairness (though 
 it will change the order of answers). We swapped them back so that answers are 
@@
 
-BFS is fair in both \disj{} and \conj{}. Our implementation is based on 
+BFS is fair in both \scheme|disj| and \scheme|conj|. Our implementation is based on 
 DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). All we have to do is apply two trivial changes to 
-\texttt{append-map-inf}. First, rename it to \texttt{append-map-inf/fair}. 
-Second, replace its use of \texttt{append-inf} to \texttt{append-inf/fair}.
+\scheme{append-map-inf}. First, rename it to \scheme{append-map-inf/fair}. 
+Second, replace its use of \scheme{append-inf} to \scheme{append-inf/fair}.
 
@@
 is recorded. Second, 
-\texttt{append-inf/fair} is extravagant in memory usage. It makes 
-$O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
+\scheme{append-inf/fair} is extravagant in memory usage. It makes 
+$O(n+m)$ new \scheme{cons} cells every time, where $n$ and $m$ are the 
 ``length''s of input search spaces. We address these issues in the first 
@@
 \begin{figure}
-	\lstinputlisting{Figures/BFS-opt.rkt}	
+	\schemeinput{Figures/BFS-opt.rkt}	
 	\caption{new and changed functions in optimized BFS that implements pure 
@@
 same cost are in the same bag. The cost
-information is recorded subtly -- the \texttt{car}s of a search space have cost 
+information is recorded subtly -- the \scheme{car}s of a search space have cost 
 0 (i.e. they are in the same bag), and the costs of answers in thunk are 
 computed recursively then increased by one. It is even more subtle that
-\texttt{append-inf/fair} and the \texttt{append-map-inf/fair} respects the cost 
+\scheme{append-inf/fair} and the \scheme{append-map-inf/fair} respects the cost 
 information. We make these facts more obvious by changing the type of search 
@@
 
-The new type is a pair whose \texttt{car} is a list of answers (the bag), and 
-whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search 
-space. A falsy \texttt{cdr} means the search space is obviously finite.
+The new type is a pair whose \scheme{car} is a list of answers (the bag), and 
+whose \scheme{cdr} is either a \scheme{#f} or a thunk returning a search 
+space. A falsy \scheme{cdr} means the search space is obviously finite.
 
@@
 \citeauthor{seres1999algebra}'s implementation later. The first three functions 
-in Fig.~\ref{BFS-opt} are search space constructors. \texttt{none} makes an 
-empty search space; \texttt{unit} makes a space from one answer; and 
-\texttt{step} makes a space from a thunk. The remaining functions do the same 
+in Fig.~\ref{BFS-opt} are search space constructors. \scheme{none} makes an 
+empty search space; \scheme{unit} makes a space from one answer; and 
+\scheme{step} makes a space from a thunk. The remaining functions do the same 
 thing as before.
 
-Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space 
-extravagance -- the use of \texttt{append} helps us to reuse the first bag of 
-\texttt{t-inf}.
+Luckily, the change in \scheme{append-inf/fair} also fixes the miserable space 
+extravagance -- the use of \scheme{append} helps us to reuse the first bag of 
+\scheme{t-inf}.
 
@@
 implementations of logic programming system. Our BFS implementation is not an 
-exception: \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and 
-\texttt{append-inf} correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, 
-and \texttt{mplus} respectively.
+exception: \scheme{none}, \scheme{unit}, \scheme{append-map-inf}, and 
+\scheme{append-inf} correspond to \scheme{mzero}, \scheme{unit}, \scheme{bind}, 
+and \scheme{mplus} respectively.
 
 \begin{figure}
-	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
+	\schemeinput{Figures/BFS-opt-cont.rkt}	
 	\caption{new and changed functions in optimized BFS that implements impure 
@@
 Functions implementing impure features are in Fig.~\ref{BFS-opt-cont}. The 
-first function, \texttt{elim}, takes a space \texttt{s-inf} and two 
-continuations \texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some 
-answers, \texttt{ks} is called with the first answer and the rest space. 
-Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
+first function, \scheme{elim}, takes a space \scheme{s-inf} and two 
+continuations \scheme{ks} and \scheme{kf}. When \scheme{s-inf} contains some 
+answers, \scheme{ks} is called with the first answer and the rest space. 
+Otherwise, \scheme{kf} is called with no argument. Here `s' and `f' means 
 `succeed' and `fail' respectively. This function is an eliminator of search 
@@
 
-We prove in Coq that the two BFSs are equivalent, i.e. \texttt{(run n g)} 
+We prove in Coq that the two BFSs are equivalent, i.e. \scheme{(run n g)} 
 produces the same result (See supplements for the formal proof).
@@
 memory. The first two benchmarks are taken from 
-\citet{friedman_reasoned_2018}. \texttt{reverso} is from 
+\citet{friedman_reasoned_2018}. \scheme{reverso} is from 
 \citet{rozplokhas2018improving}. Next two benchmarks 
@@
 to circumvent the need for symbolic constraints (e.g. $\neq$, 
-\texttt{absento}). Our version generates de 
+\scheme{absento}). Our version generates de 
 Bruijnized expressions and prevent closures getting into list. The two 
-benchmarks differ in the \conde clause order of their relational interpreters. 
+benchmarks differ in the \scheme|conde| clause order of their relational interpreters. 
 The last two 
-benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
+benchmarks are about synthesizing expressions that evaluate to \scheme{'(I love 
 you)}. This benchmark is also inspired by \citet{byrd2017unified}. Again, the 
-sibling benchmarks differ in the \conde clause order of their relational 
+sibling benchmarks differ in the \scheme|conde| clause order of their relational 
 interpreters. The first one 
-has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
+has elimination rules (i.e. application, \scheme{car}, and \scheme{cdr}) at the 
 end, while the other has them at the beginning. We conjecture that DFS$_\textrm{i}$ would 
@@
 In general, only DFS$_\textrm{i}$ and DFS$_\textrm{bi}$ constantly perform well. DFS$_\textrm{f}$ is just as 
-efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
+efficient in all benchmarks but \scheme{very-recursiveo}. Both BFS have obvious 
 overhead in many cases. Among the three variants of DFS (they all have unfair 
-\conj{}), DFS$_\textrm{f}$ is most resistant to clause permutation, followd by DFS$_\textrm{bi}$ then 
+\scheme|conj|), DFS$_\textrm{f}$ is most resistant to clause permutation, followd by DFS$_\textrm{bi}$ then 
 DFS$_\textrm{i}$. Among the two implementation of BFS, ours constantly performs as well or 
-better. Interestingly, every strategies with fair \disj{} suffers in 
-\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
+better. Interestingly, every strategies with fair \scheme|disj| suffers in 
+\scheme{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
 Therefore, this 
-benchmark might be a special case. Fair \conj{} imposes overhead constantly 
-except in \texttt{appendo}. The reason might be that strategies with fair 
-\conj{} tend to keep more intermediate answers in the memory.
+benchmark might be a special case. Fair \scheme|conj| imposes overhead constantly 
+except in \scheme{appendo}. The reason might be that strategies with fair 
+\scheme|conj| tend to keep more intermediate answers in the memory.
 
@@
 
-We analysis the definitions of fair \disj{} and fair \conj{}, then propose a 
-new definition of fair \conj{}. Our definition is orthogonal with completeness.
+We analysis the definitions of fair \scheme|disj| and fair \scheme|conj|, then propose a 
+new definition of fair \scheme|conj|. Our definition is orthogonal with completeness.
 
 We devise three new search strategies: balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
-DFS (DFS$_\textrm{f}$), and BFS. DFS$_\textrm{bi}$ has almost-fair \disj{} and unfair \conj{}. DFS$_\textrm{f}$ has 
-fair \disj{} and unfair \conj{}. BFS has both fair \disj{} and fair \conj{}.
+DFS (DFS$_\textrm{f}$), and BFS. DFS$_\textrm{bi}$ has almost-fair \scheme|disj| and unfair \scheme|conj|. DFS$_\textrm{f}$ has 
+fair \scheme|disj| and unfair \scheme|conj|. BFS has both fair \scheme|disj| and fair \scheme|conj|.
 

### 2019-05-05 Paper/paper.tex
intro

@@
 
-\newcommand{\conde}{\texttt{cond$^e$} }
+\newcommand{\conde}{\texttt{cond$^e$}}
 \newcommand{\conj}{\texttt{conj}}
@@
 }
-\newcommand{\DFSi}[0]{
-  DFS$_\textrm{i}$
-}
+\newcommand{\DFSi}[0]{DFS$_\textrm{i}$}
+\newcommand{\DFSf}[0]{DFS$_\textrm{f}$}
+\newcommand{\BFS }[0]{BFS}
 
@@
 The syntax of a programming language should reflect its semantics. When writing 
-a \conde expression in miniKanren, a programmer would expect all clauses share 
-the same chance of being explored, as these clauses are written in 
-parallel. The existing search strategy, interleaving DFS (DFS$_\textrm{i}$), 
+a \conde{} expression in miniKanren, a programmer would expect all clauses 
+share the same chance of being explored, as these clauses are written in 
+parallel. The existing search strategy, interleaving \DFSi{}, 
 however, prioritize its clauses by the order how they are written down. 
-Similarly, when a \conde is followed by another goal conjunctively, a 
+Similarly, when a \conde{} is followed by another goal conjunctively, a 
 programmer would expect answers in parallel share the same chance of being 
@@
 expectation. We have devised three new search strategies that have different 
-level of fairness in \disj and \conj.
+level of fairness in \disj{} and \conj{}.
 
@@
 in the The Reasoned Schemer, 2nd Ed(TR2). miniKanren programs, especially
-relational interpreters, have been proven to be 
-useful in solving many problems by \citet{byrd2017unified}.
+relational interpreters, have been proven to be useful in solving many problems 
+by \citet{byrd2017unified}.
 
-\conde is the flagship disjunction operator in miniKanren. A subtlety arises
-when a \conde contains many disjunction clauses: not every clause has the equal
-chance to contribute to the result. As an example, consider the following
+% \conde is the flagship disjunction operator in miniKanren.
+A subtlety arises when a \conde contains many clauses: not every clause has the 
+equal chance to contribute to the result. As an example, consider the following 
 relation \texttt{repeato} and its invocation.
+
 \clisting{Figures/repeato.rkt}
-Next, consider the following disjuction of invoking \texttt{repeato} with
-four different letters.
+
+Next, consider the following disjuction of invoking \texttt{repeato} with four 
+different letters.
+
 \clisting{Figures/example.rkt}
+
 \conde intuitively corresponds to \texttt{or} in logic. And thus an unsuspicious
@@
 following.
+
 \clisting{Figures/run-repeato-fair.rkt}
+
 The \conde in TR2, however, generates a less expected result.
+
 \clisting{Figures/run-repeato-idfs.rkt}
 
-\conde implements interleaving DFS(\DFSi), the cause of this unexpected result.
-In a \conde, each clause takes a half of its received computational resources
-and pass the other half to its following clauses, except for the last clause
-that takes all resources it receives. In the example above, the letters
-\texttt{c} and \texttt{d} are allocated with less resources than \texttt{a},
-and thus \texttt{c} and \texttt{d} barely contribute to the result.
+The miniKanren in TR2 implements interleaving DFS(\DFSi), the cause of this 
+unexpected result. With this search strategy, each \conde clause takes a half 
+of its received computational resources and pass the other half to its 
+following clauses, except for the last clause that takes all resources it 
+receives. In the example above, the \texttt{a} clause takes half of all 
+recourses. And the \texttt{b} clause takes a quarter. Thus \texttt{c} and 
+\texttt{d} barely contribute to the result.
 
-\DFSi is powerful for an expert. By carefully organizing the order of \conde
-clauses, a miniKanren program can explore more ``interesting'' clauses than
-those uninteresting ones, and thus use computational resources efficiently.
-A little miniKanrener, however, may beg to differ--understanding
+%In the example above, the letters \texttt{c} and \texttt{d} are 
+%allocated with less resources than \texttt{a}, and thus \texttt{c} and 
+%\texttt{d} barely contribute to the result.
+
+\DFSi{} is sometimes powerful for an expert. By carefully organizing the order 
+of \conde{} clauses, a miniKanren program can explore more ``interesting'' 
+clauses than those uninteresting ones, and thus use computational resources 
+efficiently. A little miniKanrener, however, may beg to differ--understanding
 implementation details and fiddling with clauses order is not the first
@@
 should take the focus. With \DFSi, these two uses can not be efficient at the
-same time. In fact, to make on use efficient, the other one must be drastically
+same time. In fact, to make one use efficient, the other one must be drastically
 slow.
 
-\NOTE[LKC]{Should I explain ``state'' and ``search space'' here?}
-
-Under the hood, \conde clauses are combined with \disj{}. The \disj{} 
-implementation in \citep{friedman_reasoned_2018} is not \emph{fair}.
-
-\begin{defn}[fair \disj]
-	A \disj{} is fair iff it allocates computational resource evenly among 
-	search spaces derived from disjunctive goals. \citet{seres1999algebra}
-\end{defn}
-
-A closely related concept is \emph{almost-fair} \disj.
-
-\begin{defn}[almost-fair \disj]
-	A \disj{} is almost-fair iff it allocates computational resource so evenly 
-	among search spaces derived from disjunctive goals that the maximal ratio 
-	of resources is bounded by a constant.
-\end{defn}
-
-The \disj{} in \citet{friedman_reasoned_2018}, or more precisely, in its search 
-strategy, interleaving DFS(DFS$_\textrm{i}$), is neither fair nor almost-fair. 
-Fair depth-first search (DFS$_\textrm{f}$), a new search strategy in this 
-paper, has fair \disj. And balanced interleaving depth-first search 
-(DFS$_\textrm{bi}$), another new strategy, has almost-fair \disj. Breath-first 
-search (BFS), a known strategy \citet{seres1999algebra}, has fair \disj{} and 
-\emph{fair \conj{}}.
-
-\begin{defn}[fair \conj]
-	A \conj{} is fair iff it allocates computational resource evenly among 
-	search spaces derived from states in the same bag, where bags are finite 
-	list of states.
-\end{defn}
-
-A comparison of fairness of search strategies is in Fig.~\ref{fairness}.
+The specification that every clause in the same \conde{} is given equal 
+``search priority'' is called fair \disj{}. And search strategies with 
+almost-fair \disj{} give every clauss in the same \conde{} similar priority. 
+Fair \conj{}, a related concept, is more complicated. We defer it to the next 
+section.
 
@@
 \begin{itemize}
+	\item analyze an existing concept, fair \disj{} by 
+	\citet{seres1999algebra}.
 	\item propose a new concept, almost-fair \disj{}.
-	\item propose a new definition of fair \conj{}.
+	\item propose a new definition of fair \disj{}.
 	\item propose and implement balanced interleaving depth-first search 
@@
 	\item implement in a new way breath-first search (BFS), a search strategy 
-	with fair \disj{} and fair \conj{}
+	with fair \disj{} and fair \conj{}.
 	(our code runs faster in all benchmarks and is simpler)
@@
 
-\begin{figure}[tbp]
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline 
-		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS \\ 
-		\hline 
-		disj & unfair & almost-fair & fair & fair \\ 
-		\hline 
-		conj & unfair & unfair & unfair & fair \\ 
-		\hline 
-	\end{tabular} 
-	\caption{fairness of search strategies}
-	\label{fairness}
-\end{figure}
-
-% Interleaving DFS, the search strategy of \conde in
-% miniKanren~\citet{friedman_reasoned_2018}, allocates computational resource
-% by the order in which the clauses are written. Each clause of a
-% \conde takes half of the current resource and passes the other half
-% to its following clauses, except for the last clause that takes all of the 
-%current resource. 
-% The biased treatment provides both opportunity and burden: miniKanren users 
-%can place more frequently used 
-% goal at the beginning to optimize their programs; however, it might be a 
-% catastrophe if a goal that generates many useless states is placed before 
-%more 
-% important goals. Seasoned miniKanreners usually know how to utilize 
-% the unfairness to optimize their programs. However, we believe search 
-%strategies that is less sensitive to goal order can also be useful to little 
-%miniKanreners as well as seasoned ones. We propose two such search strategies, 
-%balanced interleaving DFS (DFS$_\textrm{bi}$) and breadth-first search (BFS), and observe 
-%how they affect the efficiency and the answer order of known miniKanren 
-%programs. The experiment is conducted with the miniKanren from \textit{The 
-%Reasoned Schemer, 2nd Edition}.
+%\begin{figure}[tbp]
+%	\begin{tabular}{|c|c|c|c|c|}
+%		\hline 
+%		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & 
+%BFS \\ 
+%		\hline 
+%		disj & unfair & almost-fair & fair & fair \\ 
+%		\hline 
+%		conj & unfair & unfair & unfair & fair \\ 
+%		\hline 
+%	\end{tabular} 
+%	\caption{fairness of search strategies}
+%	\label{fairness}
+%\end{figure}
 
@@
 
-In this section, we elaborate fairness by running queries about 
-\texttt{repeato2}, a relational definition that relates a term \texttt{x} with a 
-non-empty list whose elements are \texttt{x} (Fig.~\ref{repeato}).
+In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
+Before going further into fairness, we would like to give a short review about 
+state, search space, and goal, because fairness is defined in terms of them. 
+Every answer given by miniKanren corresponds to a state. Each state records a 
+way how some relations can be satisfied. In our case, the state is just a 
+subsitution associating logic variables with terms. In more expressive 
+miniKanrens (e.g. miniKanren with with symbolic constraints 
+\citep{hemann2017framework}), states can include more information. A search 
+space is a collection of states. And a goal is a function from a state to a 
+search space. Goals check their input states and outputs possibly extended 
+states. A goal might fail for some inputs, in which case the output search 
+space would be empty.
 
-\begin{figure}
-	\lstinputlisting{Figures/repeato.rkt}
-	\caption{\texttt{repeato} and an example run}
-	\label{repeato2}
-\end{figure}
+Now we elaborate fairness by running more queries about \texttt{repeato}.
 
@@
 strategy, however, results in many more lists of \texttt{a}s than lists
-of other letters. And some letters, e.g. \texttt{c} and \texttt{d}, are
+of other letters. And some letters  (e.g. \texttt{c} and \texttt{d}) are
 rarely seen. The situation would be exacerbated if \conde contains more clauses.
@@
 
-We borrow the definition of \emph{fair} \disj{} from \citet{seres1999algebra}: 
-search strategies with \emph{fair} \disj{} should allocate resources evenly 
-among disjunctive goals. Running the same program with DFS$_\textrm{f}$ and BFS 
-give the following result.
+Under the hood, the \conde here is allocating computational effort to 
+four trivially different search space. The unfair \disj{} in 
+\DFSi{} allocates much more effort to the first search space. On the contrary, 
+fair \disj{} would allocate effort evenly to each search space.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-fair.rkt}
+		\lstinputlisting{Figures/repeato-disj-DFSf.rkt}
+	\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{c}
+	\lstinputlisting{Figures/repeato-disj-BFS.rkt}
 \end{tabular}
@@
 
-Now we are in a middle place between fair and unfair -- search strategies
-with  \emph{almost-fair} \disj{} should allocate resources so evenly among
-disjunctive goals that the maximal ratio of resources is bounded by a constant. 
-Our new search strategy,
-DFS$_\textrm{bi}$, has almost-fair \disj{}. It is
-fair when the number of goals is a power of 2, otherwise, some goals are 
-allocated twice as many resources than the others. In the previous example,
-DFS$_\textrm{bi}$
-gives the same result. And in the following example, where the \conde has 5 
-clause, the clauses of \texttt{b}, \texttt{c}, and \texttt{d} are allocated 
-more resources.
+Running the same program again with almost-fair \disj 
+(e.g. DFS$_\textrm{bi}$) gives the same result. Almost-fair, however, is not 
+completely fair, as shown by the following example.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-biDFS.rkt}
+		\lstinputlisting{Figures/repeato-disj-DFSbi.rkt}
 	\end{tabular}
 \end{center}
+
+DFS$_\textrm{bi}$ is fair only when the number of goals is a power of 2, 
+otherwise, some goals would be allocated twice as many resources than the 
+others. In the above example, where the \conde has five clauses, the clauses of 
+\texttt{b}, \texttt{c}, and \texttt{d} are allocated more resources.
+
+We end this subsection with precise definitions of all levels of 
+\disj{} fairness. Our definition of \emph{fair} \disj{} is slightly generalize 
+from the one by \citet{seres1999algebra}. Their definition is for binary 
+disjunct. We generalize it to multi-arity one.
+
+\begin{defn}[fair \disj{}]
+	A \disj{} is fair iff it allocates computational resource evenly to 
+	search spaces produced by goals in the same disjunct (e.g. clauses in the 
+	same 
+	\conde).
+\end{defn}
+
+\begin{defn}[almost-fair \disj{}]
+	A \disj{} is almost-fair iff it allocates computational resource so 
+	evenly to search spaces produced by goals in the same disjunct that the 
+	maximal 
+	ratio of resources is bounded by a constant.
+\end{defn}
+
+\begin{defn}[unfair \disj{}]
+	A \disj{} is unfair iff it is not even almost-fair.
+\end{defn}
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-unfair.rkt}
+		\lstinputlisting{Figures/repeato-conj-DFSi.rkt}
 	\end{tabular}
@@
 being fair, BFS also produces answers in increasing order of cost.
-\NOTE[MVC]{Here inner and outer are very confusing. Can you be more specified?}
-\NOTE[LKC]{updated}
 
@@
 
-BFS is fair in both \disj{} and \conj{}. Our implementation is based on 
-DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). All we have to do is apply two trivial changes to 
-\texttt{append-map-inf}. First, rename it to \texttt{append-map-inf/fair}. 
-Second, replace its use of \texttt{append-inf} to \texttt{append-inf/fair}.
+BFS has both fair \disj{} and fair \conj{}. Our implementation is based on 
+DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFS{} based on \DFSf{} 
+all we have to do is renaming 
+\texttt{append-map-inf} to \texttt{append-map-inf/fair}, then replacing its use 
+of \texttt{append-inf} to \texttt{append-inf/fair}.
 

### 2019-05-05 Paper/paper.tex
bullet points

@@
 \begin{itemize}
-	\item analyze an existing concept, fair \disj{} by 
-	\citet{seres1999algebra}.
-	\item propose a new concept, almost-fair \disj{}.
-	\item propose a new definition of fair \disj{}.
 	\item propose and implement balanced interleaving depth-first search 
@@
 	\item implement in a new way breath-first search (BFS), a search strategy 
-	with fair \disj{} and fair \conj{}.
-	(our code runs faster in all benchmarks and is simpler)
-	\item prove our BFS implementation is equivalent with the one by 
-	\citet{seres1999algebra}.
+	with fair \disj{} and fair \conj{}. (our code runs faster in all 
+benchmarks and is simpler). And we prove formally that our BFS implementation 
+is equivalent to the one by \citet{seres1999algebra}.
 \end{itemize}

### 2019-05-05 Paper/paper.tex
emph sec 2

@@
 ``search priority'' is called fair \disj{}. And search strategies with 
-almost-fair \disj{} give every clauss in the same \conde{} similar priority. 
+almost-fair \disj{} give every clauses in the same \conde{} similar priority. 
 Fair \conj{}, a related concept, is more complicated. We defer it to the next 
@@
 
-%\begin{figure}[tbp]
-%	\begin{tabular}{|c|c|c|c|c|}
-%		\hline 
-%		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & 
-%BFS \\ 
-%		\hline 
-%		disj & unfair & almost-fair & fair & fair \\ 
-%		\hline 
-%		conj & unfair & unfair & unfair & fair \\ 
-%		\hline 
-%	\end{tabular} 
-%	\caption{fairness of search strategies}
-%	\label{fairness}
-%\end{figure}
-
-\section{fairness}
+\section{search strategies and fairness}
 
@@
 state, search space, and goal, because fairness is defined in terms of them. 
-Every answer given by miniKanren corresponds to a state. Each state records a 
-way how some relations can be satisfied. In our case, the state is just a 
-subsitution associating logic variables with terms. In more expressive 
+Each \emph{state} records a way how some relations can be satisfied. Every 
+answer given by miniKanren corresponds to a state. In our case, the state is 
+just a substitution associating logic variables with terms. In more expressive 
 miniKanrens (e.g. miniKanren with with symbolic constraints 
-\citep{hemann2017framework}), states can include more information. A search 
-space is a collection of states. And a goal is a function from a state to a 
-search space. Goals check their input states and outputs possibly extended 
-states. A goal might fail for some inputs, in which case the output search 
-space would be empty.
+\citep{hemann2017framework}), states can include more information. A 
+\emph{search space} is a collection of states. And a \emph{goal} is a function 
+from a state to a search space. Goals check their input states and outputs 
+possibly extended states. A goal might fail for some inputs, in which case the 
+output search space would be empty.
 

### 2019-05-05 Paper/paper.tex
simpl def of state

@@
 state, search space, and goal, because fairness is defined in terms of them. 
-Each \emph{state} records a way how some relations can be satisfied. Every 
-answer given by miniKanren corresponds to a state. In our case, the state is 
-just a substitution associating logic variables with terms. In more expressive 
-miniKanrens (e.g. miniKanren with with symbolic constraints 
-\citep{hemann2017framework}), states can include more information. A 
-\emph{search space} is a collection of states. And a \emph{goal} is a function 
-from a state to a search space. Goals check their input states and outputs 
-possibly extended states. A goal might fail for some inputs, in which case the 
-output search space would be empty.
+A \emph{state} is a collection of constraints. Every answer given by 
+miniKanren corresponds to a state. A \emph{search space} is a collection of 
+states. And a \emph{goal} is a function from a state to a search space. Goals 
+check their input states and outputs possibly extended states. A goal might fail 
+for some inputs, in which case the output search space would be empty.
 

### 2019-05-05 Paper/paper.tex
logical \tt{or}

@@
 programmer would expect answers in parallel share the same chance of being 
-explored. Again, the answers by DFS$_\textrm{i}$ is different from the 
+explored. Again, the answers by \DFSi{} is different from the 
 expectation. We have devised three new search strategies that have different 
@@
 
-\conde intuitively corresponds to \texttt{or} in logic. And thus an unsuspicious
-beginner would expect each letter to contribute equally to the result, as
-following.
+\conde intuitively relates its clauses with logical \texttt{or}. And thus an 
+unsuspicious beginner would expect each letter to contribute equally to the 
+result, as following.
 
@@
 miniKanren corresponds to a state. A \emph{search space} is a collection of 
-states. And a \emph{goal} is a function from a state to a search space. Goals 
-check their input states and outputs possibly extended states. A goal might fail 
-for some inputs, in which case the output search space would be empty.
+states. And a \emph{goal} is a function from a state to a search space.
+
+% Goals check their input states and outputs possibly extended states. A goal 
+% might fail for some inputs, in which case the output search space would be 
+% empty.
 
@@
 lists, but no longer ones, which makes the strategies \emph{incomplete}.
+
 \NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
-\NOTE[LKC]{I am a bit confused. I assume completeness is a well-known concept 
-in the context of logic programming. For example, this paper doesn't cite any 
-source when it talks about completeness.
-
-Hemann, Jason, et al. "A small embedding of logic programming with a simple 
-complete search." ACM SIGPLAN Notices. Vol. 52. No. 2. ACM, 2016.}
 
@@
 \end{center}
+
+%TODO describe DFSi here
 

### 2019-05-06 Paper/paper-slatex.tex
fair conj

@@
 programs, especially relational interpreters, have been proven to be
-useful in solving many problems by \citet{byrd2017unified}. A subtlety in 
-writing miniKanren programs with large \scheme|conde| expressions, such as 
-relational interpreters, is that the order of \scheme|conde| clauses sometimes 
-affect the speed considerably. This phenomenon also appears when running 
-miniKanren programs with the implementation in \citet{friedman_reasoned_2018}, 
-one of the most well-understood implementation. This is because the search 
-strategy of this implementation, interleaving depth-first search (\dfsi), gives 
-left clauses higher ``search priority'' when a \scheme|conde| has more than two 
-clauses. The situation is exacerbated as the number of clauses increases. This 
-unfair treatment causes two problems when a \scheme|conde| expression has many 
-clauses: the right-most clause can hardly contribute to query result; and 
-programmers might need to tweak the clause order to maximize their programs' 
-efficiency, depending on the distribution of queries.
+useful in solving many problems by \citet{byrd2017unified}.
+
+A subtlety in writing miniKanren programs with large \scheme|conde| expressions, 
+such as relational interpreters, is that the order of \scheme|conde| clauses 
+sometimes affect the speed considerably. This phenomenon also appears when 
+running miniKanren programs with the implementation in 
+\citet{friedman_reasoned_2018}, one of the most well-understood implementation. 
+This is because the search strategy of this implementation, interleaving 
+depth-first search (\dfsi), gives left clauses higher ``search priority'' when a 
+\scheme|conde| has more than two clauses. The situation is exacerbated as the 
+number of clauses increases. This unfair treatment causes two problems when a 
+\scheme|conde| expression has many clauses: the right-most clause can hardly 
+contribute to query result; and programmers might need to tweak the clause order 
+to maximize their programs' efficiency, depending on the distribution of 
+queries.
 
@@
 space is a collection of states. And a goal is a function from a state to a 
-search space. Goals check their inputs and produces possibly extended states. A 
-goal might fail for some input, in which case the output search space would be 
-empty.
+search space. Goals check their input states and outputs possibly extended 
+states. A goal might fail for some inputs, in which case the output search 
+space would be empty.
 

### 2019-05-06 Paper/paper.tex
fair conj

@@
 }
-\newcommand{\DFSi}[0]{DFS$_\textrm{i}$}
-\newcommand{\DFSf}[0]{DFS$_\textrm{f}$}
+\newcommand{\DFSi }[0]{DFS$_\textrm{i}$}
+\newcommand{\DFSf }[0]{DFS$_\textrm{f}$}
+\newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
 \newcommand{\BFS  }[0]{BFS}
@@
 The miniKanren in TR2 implements interleaving DFS(\DFSi), the cause of this 
-unexpected result. With this search strategy, each \conde clause takes a half 
+unexpected result. With this search strategy, each clause takes a half 
 of its received computational resources and pass the other half to its 
@@
 Given the following program, it is natural to expect lists of each letter to
-constitute $1/4$ in the answer. DFS$_\textrm{i}$, the current search
+constitute $1/4$ in the answer. \DFSi, the current search
 strategy, however, results in many more lists of \texttt{a}s than lists
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-iDFS.rkt}
+		\lstinputlisting{Figures/repeato-disj-DFSi.rkt}
 	\end{tabular}
@@
 
-Under the hood, the \conde here is allocating computational effort to 
+Under the hood, the \conde here is allocating computational resource to 
 four trivially different search space. The unfair \disj{} in 
-\DFSi{} allocates much more effort to the first search space. On the contrary, 
-fair \disj{} would allocate effort evenly to each search space.
+\DFSi{} allocates many more resources to the first search space. On the 
+contrary, fair \disj{} would allocate resources evenly to each search space.
 
@@
 
-Running the same program again with almost-fair \disj 
-(e.g. DFS$_\textrm{bi}$) gives the same result. Almost-fair, however, is not 
+Running the same program again with almost-fair \disj {} (e.g. 
+DFS$_\textrm{bi}$) gives the same result. Almost-fair, however, is not 
 completely fair, as shown by the following example.
@@
 
-DFS$_\textrm{bi}$ is fair only when the number of goals is a power of 2, 
+\DFSbi{} is fair only when the number of goals is a power of 2, 
 otherwise, some goals would be allocated twice as many resources than the 
@@
 from the one by \citet{seres1999algebra}. Their definition is for binary 
-disjunct. We generalize it to multi-arity one.
+disjunction. We generalize it to multi-arity one.
 
@@
 A \disj{} is fair iff it allocates computational resource evenly to 
-	search spaces produced by goals in the same disjunct (e.g. clauses in the 
-	same 
-	\conde).
+search spaces produced by goals in the same disjunction (i.e. clauses in 
+the same \conde).
 \end{defn}
@@
 \begin{defn}[almost-fair \disj{}]
-	A \disj{} is almost-fair iff it allocates computational resource so 
-	evenly to search spaces produced by goals in the same disjunct that the 
-	maximal 
-	ratio of resources is bounded by a constant.
+A \disj{} is almost-fair iff it allocates computational resource so evenly to 
+search spaces produced by goals in the same disjunction that the maximal ratio 
+of resources is bounded by a constant.
 \end{defn}
@@
 
-In the following program, the three \conde clauses differ in a trivial way. So 
-we expect lists of each letter constitute $1/4$ of the answer list. Search 
-strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$), 
-however, give us many more lists of \texttt{a}s than lists of other letters. 
-And some letters (e.g. lists 
-of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
-it is fair when there is no call to relational definition in sub-goals, 
-including this case. The situation would be worse if we add more \conde 
-clauses. The result with DFS$_\textrm{bi}$, whose \conj{} is also unfair, is similar, but 
-due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
-swapped.
+Given the following program, it is natural to expect lists of each letter to
+constitute $1/4$ in the answer. Search strategies with unfair \conj{} (e.g. 
+\DFSi, \DFSbi, \DFSf), however, results in many more lists of \texttt{a}s than 
+lists of other letters. And some letters are rarely seen. The situation would 
+be exacerbated if \conde contains more clauses.
+
+\NOTE[LKC]{Should I add a footnote?
+
+``
+Although 
+DFS$_\textrm{i}$'s \disj{} is unfair in general, it is fair when there is no 
+call to relational definition in \conde{} clauses (including this case).
+''}
 
@@
 
-Intuitively, search strategies with fair \conj{} should produce each letter of 
-lists equally frequently. Indeed, BFS does so.
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/repeato-conj-DFSf.rkt}
+	\end{tabular}
+\end{center}
+
+\begin{center}
+	\begin{tabular}{c}
+		\lstinputlisting{Figures/repeato-conj-DFSbi.rkt}
+	\end{tabular}
+\end{center}
+
+Under the hood, the \conde{} and the call to \texttt{repeato} are connected by 
+\conj{}. The \conde{} goal outputs a search space including four trivially 
+different states. These states are then supplied individually to 
+\texttt{(repeato x q)} goal, producing four search spaces. In the examples 
+above, the \conj{}s are allocating more computational resources to the state of 
+\texttt{a}. On the contrary, fair \conj{} would allocate resources evenly to 
+each search space.
 
@@
 
-A more interesting situation is when the first conjunctive goal produces 
-infinite many answers. Consider the following example, a naive specification of 
-fair \conj{} might require search strategies to produce all sorts of singleton 
-lists, but no longer ones, which makes the strategies \emph{incomplete}.
-
-\NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
+A more interesting situation is when the first conjunct produces infinite many 
+answers. Consider the following example, a naive specification of fair \conj{} 
+might require search strategies to produce all sorts of singleton lists, but no 
+longer ones, which makes the strategies incomplete. A search strategy is 
+\emph{complete} iff it can find out all the answers in finite time, otherwise, 
+it is \emph{imcomplete}.
 
@@
 
-Our solution requires a search strategy with \emph{fair} \conj{} to 
-package answers in bags, where each bag contains finite answers, and to allocate 
-resources evenly among search spaces derived from answers in the same bag. The 
-way to package depends on search strategy. And how to allocate resources among 
-search space related to different bags is unspecified. Our definition of fair 
-\conj{} is orthogonal with completeness. For example, a naively fair strategy 
-is fair but not complete, while BFS is fair and complete. 
-\NOTE[MVC]{Also here, complete w.r.t what?}
+Our solution requires a search strategy with \emph{fair} \conj{} to organize
+states in bags in search spaces, where each bag contains finite states, and 
+to allocate resources evenly among search spaces derived from states in the 
+same bag. It is up to a search strategy designer to decide by what criteria to 
+put states in the same bag, and how to allocate resources among search spaces 
+related to different bags.
 
-BFS packages answers by their costs. The \emph{cost} of a answer is its 
-depth in the search tree (i.e. the number of calls to relational definitions 
-required to find them) \citet{seres1999algebra}. In the following example, 
-every answer is a list of list of symbol. The cost of each of them is equal to 
-the length of the inner lists plus the length of the outer list. In addition to 
-being fair, BFS also produces answers in increasing order of cost.
+BFS puts states of the same cost in the same bag, and allocate resources 
+carefully among search spaces related to different bags such that answers are 
+produced in increasing order of cost. The \emph{cost} of a answer is its depth 
+in the search tree (i.e. the number of calls to relational definitions required 
+to find them) \citet{seres1999algebra}. In the following example, the cost of 
+each answer is equal to the length of the inner lists plus the length of the 
+outer list.
 
@@
 
-%TODO describe DFSi here
+We end this subsection with precise definitions of all levels of \conj{} 
+fairness.
+
+% Our definition of fair \conj{} is orthogonal with completeness. For 
+% example, a naively fair strategy is fair but not complete, while BFS is fair and 
+% complete.
+
+\begin{defn}[fair \conj{}]
+A \conj{} is fair iff it allocates computational resource evenly to 
+search spaces produced from states in the same bag. A bag is a finite 
+collection of state. And search strategies with fair \conj{} should represent 
+search spaces with possibly infinite collection of state. 
+\end{defn}
+
+\begin{defn}[unfair \conj{}]
+A \conj{} is unfair iff it is not fair.
+\end{defn}
+
+\section{interleaving depth-first search}
+
+In this section we review the implementation of interleaving depth-first search 
+(\DFSi). ... ...
 
@@
 the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$
-constructs the binary tree with the same nodes but in the unbalanced form.
+constructs the binary tree with the same nodes but in an unbalanced form.
 
@@
 changed to call a new and fair version of \texttt{append-inf}. 
-\texttt{append-inf/fair} immediately calls its helper, 
-\texttt{append-inf/fair\^{}}, with the first argument, \texttt{s?}, set to 
-\texttt{\#{}t}, which indicates that \texttt{s-inf} and \texttt{t-inf} haven't 
-been swapped. The swapping happens at the third \texttt{cond} clause in the 
-helper, where \texttt{s?} is updated accordingly. The first two \texttt{cond} 
-clauses essentially copy the \texttt{car}s and stop recursion when one of the 
-input spaces is obviously finite. The third clause, as we mentioned above, is 
-just for swapping. When the fourth and last clause runs, we know that both 
-\texttt{s-inf} and \texttt{t-inf} are ended with a thunk. In this case, a new 
-thunk is constructed. The new thunk calls the driver recursively. Here changing 
-the order of \texttt{t-inf} and \texttt{s-inf} won't hurt the fairness (though 
-it will change the order of answers). We swapped them back so that answers are 
-produced in a more natural order.
+\texttt{append-inf/fair} immediately calls its helper, \texttt{loop}, with the 
+first argument, \texttt{s?}, set to \texttt{\#{}t}, which indicates that 
+\texttt{s-inf} and \texttt{t-inf} haven't been swapped. The swapping happens at 
+the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
+accordingly. The first two \texttt{cond} clauses essentially copy the 
+\texttt{car}s and stop recursion when one of the input spaces is obviously 
+finite. The third clause, as we mentioned above, is just for swapping. When the 
+fourth and last clause runs, we know that both \texttt{s-inf} and \texttt{t-inf} 
+are ended with a thunk. In this case, a new thunk is constructed. The new thunk 
+calls the driver recursively. Here changing the order of \texttt{t-inf} and 
+\texttt{s-inf} won't hurt the fairness (though it will change the order of 
+answers). We swapped them back so that answers are produced in a more natural 
+order.
 
@@
 \end{figure}
-
-\NOTE[MVC]{Though bag is well known, people rarely say ``bagging''. How about putting information in a bag, or something better?}
-\NOTE[MVC]{What is the bagging information?}
-\NOTE[LKC]{It's just cost... You're right. I should have be more direct.}
 

### 2019-05-06 Paper/paper.tex
sec DFSi

@@
 
+\NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}
+
 %The syntax of a programming language should reflect its semantics. When using 
@@
 \citet{friedman_reasoned_2018} introduce miniKanren and its implementation
-in the The Reasoned Schemer, 2nd Ed(TR2). miniKanren programs, especially
+in \emph{The Reasoned Schemer, 2nd Ed} (TR2). miniKanren programs, especially
 relational interpreters, have been proven to be useful in solving many problems 
@@
 % \conde is the flagship disjunction operator in miniKanren.
-A subtlety arises when a \conde contains many clauses: not every clause has the 
+A subtlety arises when a \conde contains many clauses: not every clause has an 
 equal chance to contribute to the result. As an example, consider the following 
@@
 
-Next, consider the following disjuction of invoking \texttt{repeato} with four 
+Next, consider the following disjunction of invoking \texttt{repeato} with four 
 different letters.
@@
 unsuspicious beginner would expect each letter to contribute equally to the 
-result, as following.
+result, as follows.
 
@@
 The miniKanren in TR2 implements interleaving DFS(\DFSi), the cause of this 
-unexpected result. With this search strategy, each clause takes a half 
+unexpected result. With this search strategy, each clause takes half 
 of its received computational resources and pass the other half to its 
@@
 clauses for constructors that build data and clauses for eliminators that use
-data. When this type checker is used to generate simple and shallow programs,
+data. When the type checker is used to generate simple and shallow programs,
 the clauses of constructors should be put in the front of \conde.
-When performing proof search for complicated programs, the clauses of eliminator
-should take the focus. With \DFSi, these two uses can not be efficient at the
-same time. In fact, to make one use efficient, the other one must be drastically
-slow.
+When performing proof searches for complicated programs, the clauses of 
+eliminator should take the focus. With \DFSi, these two uses cannot be 
+efficient at the same time. In fact, to make one use efficient, the other one 
+must be drastically slow.
 
@@
 ``search priority'' is called fair \disj{}. And search strategies with 
-almost-fair \disj{} give every clauses in the same \conde{} similar priority. 
+almost-fair \disj{} give every clause in the same \conde{} similar priority. 
 Fair \conj{}, a related concept, is more complicated. We defer it to the next 
@@
 	\item propose and implement balanced interleaving depth-first search 
-	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \disj{}.
-	\item propose and implement fair depth-first search (DFS$_\textrm{f}$), a 
+	(\DFSbi{}), a new search strategy with almost-fair \disj{}.
+	\item propose and implement fair depth-first search (\DFSf{}), a 
 	new search strategy with fair \disj{}.
@@
 state, search space, and goal, because fairness is defined in terms of them. 
-A \emph{state} is a collection of constraints. Every answer given by 
-miniKanren corresponds to a state. A \emph{search space} is a collection of 
-states. And a \emph{goal} is a function from a state to a search space.
+A \emph{state} is a collection of constraints. Every answer corresponds to a 
+state. A \emph{search space} is a collection of states. And a \emph{goal} is a 
+function from a state to a search space.
 
@@
 \begin{defn}[fair \disj{}]
-A \disj{} is fair iff it allocates computational resource evenly to 
+A \disj{} is fair if and only if it allocates computational resource evenly to 
 search spaces produced by goals in the same disjunction (i.e. clauses in 
@@
 \begin{defn}[almost-fair \disj{}]
-A \disj{} is almost-fair iff it allocates computational resource so evenly to 
+A \disj{} is almost-fair if and only if it allocates computational resource so 
+evenly to 
 search spaces produced by goals in the same disjunction that the maximal ratio 
@@
 \begin{defn}[unfair \disj{}]
-A \disj{} is unfair iff it is not even almost-fair.
+A \disj{} is unfair if and only if it is not even almost-fair.
 \end{defn}
@@
 \subsection{fair \texttt{conj}}
+
+\NOTE[LKC]{Checked grammer of text before this line}
 
@@
 \begin{center}
-	\begin{tabular}{c|c}
+	\begin{tabular}{c}
 		\lstinputlisting{Figures/repeato-conj-fair.rkt}
@@
 In this section we review the implementation of interleaving depth-first search 
-(\DFSi). ... ...
+(\DFSi). This review is for comparison with other search strategies in this 
+paper. Thus we focus on parts that are changed later. TRS2 
+\citep{friedman_reasoned_2018} provides a comprehensive description of the 
+whole miniKanren implementation.
+
+\begin{figure}
+    \lstinputlisting{Figures/DFSi.rkt}
+    \caption{implementation of \DFSi}
+    \label{DFSi}
+\end{figure}
+
+Fig.~\ref{DFSi} shows part of the implementation of \DFSi{}. We follow a
+convention to name variables bound to states with `s', to name variables bound 
+to goals with `g', and to name variables bound to search spaces with a suffix 
+`-inf'. The first function, \texttt{disj2}, implements binary disjunction. 
+\texttt{append-inf} is its helper, which compose two disjunctive search spaces. 
+The following function, \texttt{conj2}, implements binary conjunction. It applys 
+the \emph{first} goal to the input state, then applys the second goal to 
+states in the resulting search space. The latter process is done with a helper 
+function. \texttt{append-map-inf} applys its input goal to states in its input 
+search spaces and compose the resulting search spaces. It reuse 
+\texttt{append-inf} for search space composition. The following three 
+definitions introduces syntactic sugars that miniKanren users are more familiar 
+with. The first two definitions say disjunction and disjunction are 
+right-associative. The next and last definition says \conde{} relates its 
+clauses disjunctively, and goals in the same clause conjunctively.
 
@@
 
-Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair \conj{}. 
-The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ in the \disj{} macro. We list the 
-new \disj{} with its helpers in Fig.~\ref{balanced-disj}. The first helper 
-function, \texttt{split}, takes a list of goals \texttt{ls} and a procedure 
-\texttt{k}, partitions \texttt{ls} into two sub-lists of roughly equal length, 
-and returns the application of \texttt{k} to the two sub-lists. \texttt{disj*} 
-takes a non-empty list of goals \texttt{gs} and returns a goal. With the help 
-of \texttt{split}, it essentially constructs a \emph{balanced} binary tree 
-where leaves are elements of \texttt{gs} and nodes are \texttt{disj2}s, hence 
-the name of this search strategy. In contrast, the \disj{} in DFS$_\textrm{i}$
-constructs the binary tree with the same nodes but in an unbalanced form.
+Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
+\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
+in the \disj{} macro. We list the new \disj{} with its helpers in 
+Fig.~\ref{balanced-disj}. The first helper function, \texttt{split}, takes a 
+list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
+into two sub-lists of roughly equal length, and returns the application of 
+\texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
+\texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
+constructs a \emph{balanced} binary tree where leaves are elements of 
+\texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
+strategy. In contrast, the \disj{} in DFS$_\textrm{i}$ constructs the binary 
+tree with the same collection of leaf nodes but in a particularly unbalanced 
+form.
 
@@
 
-Fair DFS (DFS$_\textrm{f}$) has fair \disj{} and unfair \conj{}. The implementation of DFS$_\textrm{f}$ 
-differs from DFS$_\textrm{i}$'s in \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is 
-changed to call a new and fair version of \texttt{append-inf}. 
-\texttt{append-inf/fair} immediately calls its helper, \texttt{loop}, with the 
-first argument, \texttt{s?}, set to \texttt{\#{}t}, which indicates that 
+Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
+implementation of \DFSf{} differs from \DFSi{}'s in 
+\texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is changed to call a new and 
+fair version of \texttt{append-inf}. \texttt{append-inf/fair} immediately calls 
+its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
+\texttt{\#{}t}, which indicates that 
 \texttt{s-inf} and \texttt{t-inf} haven't been swapped. The swapping happens at 
@@
 \texttt{s-inf} won't hurt the fairness (though it will change the order of 
-answers). We swapped them back so that answers are produced in a more natural 
+answers). We swap them back so that answers are produced in a more natural 
 order.
@@
 BFS has both fair \disj{} and fair \conj{}. Our implementation is based on 
-DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFS{} based on \DFSf{} 
-all we have to do is renaming 
-\texttt{append-map-inf} to \texttt{append-map-inf/fair}, then replacing its use 
-of \texttt{append-inf} to \texttt{append-inf/fair}.
+DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFS{} based on \DFSf{}, 
+we need \texttt{append-map-inf/fair} in addition to \texttt{append-inf/fair}. 
+The only difference between \texttt{append-map-inf/fair} and 
+\texttt{append-map-inf} is that the former calls \texttt{append-inf/fair} 
+instead of \texttt{append-inf}.
 
@@
 same bag. In this implementation, however, it is unclear where this information 
-is recorded. Second, 
-\texttt{append-inf/fair} is extravagant in memory usage. It makes 
-$O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
+is recorded. Second, \texttt{append-inf/fair} is extravagant in memory usage. It 
+makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
 ``length''s of input search spaces. We address these issues in the first 

### 2019-05-07 Paper/paper.tex
grammer checked

@@
 longer ones, which makes the strategies incomplete. A search strategy is 
-\emph{complete} iff it can find out all the answers in finite time, otherwise, 
+\emph{complete} iff it can find out all the answers within finite time, 
+otherwise, 
 it is \emph{imcomplete}.
@@
 
-In this section we review the implementation of interleaving depth-first search 
+In this section, we review the implementation of interleaving depth-first 
+search 
 (\DFSi). This review is for comparison with other search strategies in this 
@@
 \texttt{append-inf} is its helper, which compose two disjunctive search spaces. 
-The following function, \texttt{conj2}, implements binary conjunction. It applys 
-the \emph{first} goal to the input state, then applys the second goal to 
+The following function, \texttt{conj2}, implements binary conjunction. It 
+applies 
+the \emph{first} goal to the input state, then applies the second goal to 
 states in the resulting search space. The latter process is done with a helper 
@@
 \texttt{append-inf} for search space composition. The following three 
-definitions introduces syntactic sugars that miniKanren users are more familiar 
+definitions introduce syntactic sugars that miniKanren users are more familiar 
 with. The first two definitions say disjunction and disjunction are 

### 2019-05-18 Paper/paper.tex
new DFSbi

@@
 \conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
-in the \disj{} macro. We list the new \disj{} with its helpers in 
-Fig.~\ref{balanced-disj}. The first helper function, \texttt{split}, takes a 
-list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
-into two sub-lists of roughly equal length, and returns the application of 
-\texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
-\texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
-constructs a \emph{balanced} binary tree where leaves are elements of 
-\texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
-strategy. In contrast, the \disj{} in DFS$_\textrm{i}$ constructs the binary 
-tree with the same collection of leaf nodes but in a particularly unbalanced 
-form.
+in the \disj{} macro. We list the new \disj{} with its helper in 
+Fig.~\ref{balanced-disj}. The helper \code{disj+} builds a balanced binary tree 
+whose leaves are the goals and whose nodes are \code{disj2}, hence the name of 
+this search strategy. The first argument 
+to \code{disj+} is the goals. And the next two arguments accumulate goals in 
+the left and right subtrees. The first clause says that when there is one goal, 
+the tree is the goal itself. When there is more goals, they are partitioned 
+into two sub-lists. The partition is done by repetitively dispatch the first 
+two goals (the last clause), until no goal remains (the second clause) or one 
+goal remains (the third clause). In contrast, the \disj{} in DFS$_\textrm{i}$ 
+constructs the binary tree with the same collection of leaf nodes but in a 
+particularly unbalanced form.
+
+% The first helper function, \texttt{split}, takes a 
+% list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
+% into two sub-lists of roughly equal length, and returns the application of 
+% \texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
+% \texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
+% constructs a \emph{balanced} binary tree where leaves are elements of 
+% \texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
+% strategy.
 

### 2019-05-18 Paper/paper.tex
fix typo in DFSbi

@@
 in the \disj{} macro. We list the new \disj{} with its helper in 
-Fig.~\ref{balanced-disj}. The helper \code{disj+} builds a balanced binary tree 
-whose leaves are the goals and whose nodes are \code{disj2}, hence the name of 
+Fig.~\ref{balanced-disj}. The helper \texttt{disj+} builds a balanced binary 
+tree 
+whose leaves are the goals and whose nodes are \texttt{disj2}, hence the name 
+of 
 this search strategy. The first argument 
-to \code{disj+} is the goals. And the next two arguments accumulate goals in 
+to \texttt{disj+} is the goals. And the next two arguments accumulate goals in 
 the left and right subtrees. The first clause says that when there is one goal, 

### 2019-05-19 Paper/paper.tex
minor improvements

--- 2019-05-18 Paper/paper.tex
@@
 share the same chance of being explored, as these clauses are written in 
-parallel. The existing search strategy, interleaving \DFSi{}, 
+parallel. The existing search strategy, interleaving depth-first search 
+(\DFSi{}), 
 however, prioritize its clauses by the order how they are written down. 
@@
 
-The miniKanren in TR2 implements interleaving DFS(\DFSi), the cause of this 
+The miniKanren in TR2 implements interleaving DFS (\DFSi), the cause of this 
 unexpected result. With this search strategy, each clause takes half 
@@
 otherwise, some goals would be allocated twice as many resources than the 
-others. In the above example, where the \conde has five clauses, the clauses of 
-\texttt{b}, \texttt{c}, and \texttt{d} are allocated more resources.
+others. In the above example, where the \conde{} has five clauses, the clauses 
+of \texttt{b}, \texttt{c}, and \texttt{d} are allocated more resources.
 
@@
 \conj{}. The \conde{} goal outputs a search space including four trivially 
-different states. These states are then supplied individually to 
-\texttt{(repeato x q)} goal, producing four search spaces. In the examples 
-above, the \conj{}s are allocating more computational resources to the state of 
-\texttt{a}. On the contrary, fair \conj{} would allocate resources evenly to 
-each search space.
+different states. Then the next conjunctive goal, \texttt{(repeato x q)}, is 
+applied to each of these states, producing four trivially different search 
+spaces. In the examples above, the \conj{}s are allocating more computational 
+resources to the search space of \texttt{a}. On the contrary, fair \conj{} 
+would allocate resources evenly to each search space.
 
@@
 longer ones, which makes the strategies incomplete. A search strategy is 
-\emph{complete} iff it can find out all the answers within finite time, 
-otherwise, 
-it is \emph{imcomplete}.
+\emph{complete} if and only if it can find out all the answers within finite 
+time, otherwise, it is \emph{incomplete}.
 
@@
 in the search tree (i.e. the number of calls to relational definitions required 
-to find them) \citet{seres1999algebra}. In the following example, the cost of 
+to find them) \citep{seres1999algebra}. In the following example, the cost of 
 each answer is equal to the length of the inner lists plus the length of the 
@@
 \begin{defn}[fair \conj{}]
-A \conj{} is fair iff it allocates computational resource evenly to 
+A \conj{} is fair if and only if it allocates computational resource evenly to 
 search spaces produced from states in the same bag. A bag is a finite 
@@
 \begin{defn}[unfair \conj{}]
-A \conj{} is unfair iff it is not fair.
+A \conj{} is unfair if and only if it is not fair.
 \end{defn}
@@
 `-inf'. The first function, \texttt{disj2}, implements binary disjunction. 
-\texttt{append-inf} is its helper, which compose two disjunctive search spaces. 
+\texttt{append-inf} is its helper, which composes two disjunctive search 
+spaces. 
 The following function, \texttt{conj2}, implements binary conjunction. It 
@@
 states in the resulting search space. The latter process is done with a helper 
-function. \texttt{append-map-inf} applys its input goal to states in its input 
-search spaces and compose the resulting search spaces. It reuse 
+function. \texttt{append-map-inf} applies its input goal to states in its input 
+search spaces and compose the resulting search spaces. It reuses 
 \texttt{append-inf} for search space composition. The following three 
@@
 	\lstinputlisting{Figures/balanced-disj.rkt}
-	\caption{DFS$_\textrm{bi}$ implementation}
+	\caption{implementation of DFS$_\textrm{bi}$}
 	\label{balanced-disj}
@@
 Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
-\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
+\conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
+DFS$_\textrm{i}$'s 
 in the \disj{} macro. We list the new \disj{} with its helper in 
-Fig.~\ref{balanced-disj}. The helper \code{disj+} builds a balanced binary tree 
-whose leaves are the goals and whose nodes are \code{disj2}, hence the name of 
+Fig.~\ref{balanced-disj}. The helper \texttt{disj+} builds a balanced binary 
+tree 
+whose leaves are the goals and whose nodes are \texttt{disj2}s, hence the name 
+of 
 this search strategy. The first argument 
-to \code{disj+} is the goals. And the next two arguments accumulate goals in 
+to \texttt{disj+} is a list of all goals. And the next two arguments accumulate 
+goals in 
 the left and right subtrees. The first clause says that when there is one goal, 
-the tree is the goal itself. When there is more goals, they are partitioned 
-into two sub-lists. The partition is done by repetitively dispatch the first 
-two goals (the last clause), until no goal remains (the second clause) or one 
-goal remains (the third clause). In contrast, the \disj{} in DFS$_\textrm{i}$ 
-constructs the binary tree with the same collection of leaf nodes but in a 
-particularly unbalanced form.
+the tree is the goal itself. When there are more goals, the first argument is 
+partitioned into two sub-lists. The partition is done by repetitively 
+dispatching the first two goals (the last clause), until no goal remains (the 
+second clause) or one goal remains (the third clause). In contrast, the \disj{} 
+in DFS$_\textrm{i}$ constructs the binary tree with the same collection of leaf 
+nodes but in a particularly unbalanced form.
 
@@
 	\lstinputlisting{Figures/fDFS.rkt}
-	\caption{DFS$_\textrm{f}$ implementation}
+	\caption{implementation of DFS$_\textrm{f}$}
 	\label{fDFS}
@@
 implementations of logic programming system. Our BFS implementation is not an 
-exception: \texttt{none}, \texttt{unit}, \texttt{append-map-inf}, and 
-\texttt{append-inf} correspond to \texttt{mzero}, \texttt{unit}, \texttt{bind}, 
+exception: \texttt{append-map-inf/fair} is like \texttt{bind}, 
+but takes arguments in reversed order; \texttt{none}, \texttt{unit}, and 
+\texttt{append-inf/fair} correspond to \texttt{mzero}, \texttt{unit}, 
 and \texttt{mplus} respectively.
@@
 Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
-`succeed' and `fail' respectively. This function is an eliminator of search 
-space, hence the name. The remaining functions do the same thing as before.
+`succeed' and `fail' respectively. This function is like an eliminator of 
+search space, hence the name. The remaining functions do the same thing as 
+before.
 
@@
 due to the similarity in both logic programming systems and search space 
-representations. The translated code is longer and slower. Details about 
+representations. The translated code is longer and slower than our BFS 
+implementation. Details about 
 difference in efficiency are in section 6.
@@
 
-We devise three new search strategies: balanced interleaving DFS (DFS$_\textrm{bi}$), fair 
-DFS (DFS$_\textrm{f}$), and BFS. DFS$_\textrm{bi}$ has almost-fair \disj{} and unfair \conj{}. DFS$_\textrm{f}$ has 
-fair \disj{} and unfair \conj{}. BFS has both fair \disj{} and fair \conj{}.
+We devise two new search strategies (i.e. balanced interleaving DFS 
+(DFS$_\textrm{bi}$) and fair DFS (DFS$_\textrm{f}$)) and devise a new 
+implementation of BFS. These strategies have different features 
+in fairness: $_\textrm{bi}$ has almost-fair \disj{} and unfair \conj{}. 
+DFS$_\textrm{f}$ has fair \disj{} and unfair \conj{}. BFS has both fair \disj{} 
+and fair \conj{}.
 

### 2019-05-20 Paper/paper.tex
bracket to paranthesis

@@
 (\DFSi{}), 
-however, prioritize its clauses by the order how they are written down. 
+however, prioritizes its clauses by the order how they are written down. 
 Similarly, when a \conde{} is followed by another goal conjunctively, a 
-programmer would expect answers in parallel share the same chance of being 
+programmer would expect states in parallel share the same chance of being 
 explored. Again, the answers by \DFSi{} is different from the 
@@
 
-% \conde is the flagship disjunction operator in miniKanren.
-A subtlety arises when a \conde contains many clauses: not every clause has an 
+\NOTE[LKC]{Shall we delete the sentence about relational interpreters? It is 
+misleading: it is emphasizing relational interpreters, but we say nothing 
+further about them later.}
+
+% \conde{} is the flagship disjunction operator in miniKanren.
+A subtlety arises 
+when a \conde{} contains many clauses: not every clause has an 
 equal chance to contribute to the result. As an example, consider the following 
@@
 
-\conde intuitively relates its clauses with logical \texttt{or}. And thus an 
+\conde{} intuitively relates its clauses with logical \texttt{or}. And thus an 
 unsuspicious beginner would expect each letter to contribute equally to the 
@@
 
-The \conde in TR2, however, generates a less expected result.
+The \conde{} in TR2, however, generates a less expected result.
 
@@
 ``search priority'' is called fair \disj{}. And search strategies with 
-almost-fair \disj{} give every clause in the same \conde{} similar priority. 
+almost-fair \disj{} give every clause similar priority. 
 Fair \conj{}, a related concept, is more complicated. We defer it to the next 
@@
 	\item implement in a new way breath-first search (BFS), a search strategy 
-	with fair \disj{} and fair \conj{}. (our code runs faster in all 
-benchmarks and is simpler). And we prove formally that our BFS implementation 
-is equivalent to the one by \citet{seres1999algebra}.
+	with fair \disj{} and fair \conj{}. And we prove formally that our BFS 
+implementation is equivalent to the one by \citet{seres1999algebra}. Our code 
+runs faster in all benchmarks and is simpler. 
 \end{itemize}
@@
 Given the following program, it is natural to expect lists of each letter to
-constitute $1/4$ in the answer. \DFSi, the current search
+constitute $1/4$ in the query result. \DFSi, the current search
 strategy, however, results in many more lists of \texttt{a}s than lists
 of other letters. And some letters  (e.g. \texttt{c} and \texttt{d}) are
-rarely seen. The situation would be exacerbated if \conde contains more clauses.
+rarely seen. The situation would be exacerbated if \conde{} contains more 
+clauses.
 
@@
 
-Under the hood, the \conde here is allocating computational resource to 
+Under the hood, the \conde{} here is allocating computational resource to 
 four trivially different search space. The unfair \disj{} in 
@@
 lists of other letters. And some letters are rarely seen. The situation would 
-be exacerbated if \conde contains more clauses.
+be exacerbated if \conde{} contains more clauses.
 
@@
 	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-fair.rkt}
+		\lstinputlisting{Figures/repeato-conj-BFS.rkt}
 	\end{tabular}
@@
 \begin{figure}
-	\lstinputlisting{Figures/balanced-disj.rkt}
-	\caption{implementation of DFS$_\textrm{bi}$}
+	\lstinputlisting{Figures/DFSbi.rkt}
+	\caption{implementation of \DFSbi{}}
 	\label{balanced-disj}
@@
 \begin{figure}
-	\lstinputlisting{Figures/fDFS.rkt}
-	\caption{implementation of DFS$_\textrm{f}$}
+	\lstinputlisting{Figures/DFSf.rkt}
+	\caption{implementation of \DFSf{}}
 	\label{fDFS}
@@
 Bruijnized expressions and prevent closures getting into list. The two 
-benchmarks differ in the \conde clause order of their relational interpreters. 
+benchmarks differ in the \conde{} clause order of their relational 
+interpreters. 
 The last two 
@@
 you)}. This benchmark is also inspired by \citet{byrd2017unified}. Again, the 
-sibling benchmarks differ in the \conde clause order of their relational 
+sibling benchmarks differ in the \conde{} clause order of their relational 
 interpreters. The first one 

### 2019-05-20 Paper/paper.tex
improve typesetting

@@
   morecomment=[l]{;,\#{}lang},
-  mathescape=true
+  mathescape=true,
+  literate={-inf}{{$^\infty$}}1 {/fair}{{$_{fair}$}}3
+  		   {→}{{$\rightarrow$}}1
+  		   {×}{{$\times$}}1
+  		   {conde}{{cond$^e$}}4
+  		   {repeato}{{repeat$^o$}}6
 }
@@
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-disj-DFSf.rkt}
-	\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{c}
+	\begin{tabular}{l|r}
+		\lstinputlisting{Figures/repeato-disj-DFSf.rkt} &
 		\lstinputlisting{Figures/repeato-disj-BFS.rkt}
@@
 \begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-DFSi.rkt}
-	\end{tabular}
-\end{center}
-
-\begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-DFSf.rkt}
-	\end{tabular}
-\end{center}
-
-\begin{center}
-	\begin{tabular}{c}
-		\lstinputlisting{Figures/repeato-conj-DFSbi.rkt}
+\begin{tabular}{l|c|r}
+    \lstinputlisting{Figures/repeato-conj-DFSi.rkt} &
+    \lstinputlisting{Figures/repeato-conj-DFSf.rkt} &
+    \lstinputlisting{Figures/repeato-conj-DFSbi.rkt} \\
 \end{tabular}

### 2019-05-20 Paper/paper.tex
more typesetting improv.

@@
   basicstyle=\ttfamily,
-  morekeywords={run,conde,run*,defrel,==,fresh},
+  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
   alsodigit={!\$\%&*+-./:<=>?@^_~},
@@
   mathescape=true,
-  literate={-inf}{{$^\infty$}}1 {/fair}{{$_{fair}$}}3
-  		   {→}{{$\rightarrow$}}1
-  		   {×}{{$\times$}}1
-  		   {conde}{{cond$^e$}}4
-  		   {repeato}{{repeat$^o$}}6
+  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
+  		   {→}{{$\rightarrow$}}{1}
+  		   {×}{{$\times$}}{1}
+  		   {==}{{$\equiv$}}{1}
+  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
+  		   {repeato}{{repeat$^o$}}{6}
 }

### 2019-05-20 Paper/paper.tex
correcting sec. 2

@@
 resources to the search space of \texttt{a}. On the contrary, fair \conj{} 
-would allocate resources evenly to each search space.
+would allocate resources evenly to each search space. For example,
 
@@
 A more interesting situation is when the first conjunct produces infinite many 
-answers. Consider the following example, a naive specification of fair \conj{} 
+states. Consider the following example, a naive specification of fair \conj{} 
 might require search strategies to produce all sorts of singleton lists, but no 
@@
 in the search tree (i.e. the number of calls to relational definitions required 
-to find them) \citep{seres1999algebra}. In the following example, the cost of 
-each answer is equal to the length of the inner lists plus the length of the 
-outer list.
+to find them) \citep{seres1999algebra}. In the following example, every answer 
+is a list of list of symbols, where inner lists are the same. Here the 
+cost of each answer is equal to the length of its inner lists plus the length 
+of its outer list.
 
@@
 collection of state. And search strategies with fair \conj{} should represent 
-search spaces with possibly infinite collection of state. 
+search spaces with possibly infinite collection of bags. 
 \end{defn}
@@
 In this section, we review the implementation of interleaving depth-first 
-search 
-(\DFSi). This review is for comparison with other search strategies in this 
-paper. Thus we focus on parts that are changed later. TRS2 
+search (\DFSi). We focus on parts that are relevant to this paper. TRS2 
 \citep{friedman_reasoned_2018} provides a comprehensive description of the 
 whole miniKanren implementation.
+
+\begin{figure}
+	\lstinputlisting{Figures/conde.rkt}
+	\caption{implementation of \conde}
+	\label{conde}
+\end{figure}
+
+The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
+strategies. It relates clauses disjunctively, and goals in the same 
+clause conjunctively.
 
@@
 
-Fig.~\ref{DFSi} shows part of the implementation of \DFSi{}. We follow a
-convention to name variables bound to states with `s', to name variables bound 
-to goals with `g', and to name variables bound to search spaces with a suffix 
-`-inf'. The first function, \texttt{disj2}, implements binary disjunction. 
+Fig.~\ref{DFSi} shows parts that are later compared with other search 
+strategies. We follow some conventions to name variables: variables bound to 
+states are named \texttt{s}; variables bound to goals are named `g' (possibly 
+with subscript); variables bound to search spaces have names ending with 
+$^\infty$. The first function, \texttt{disj2}, implements binary disjunction. 
 \texttt{append-inf} is its helper, which composes two disjunctive search 
-spaces. 
-The following function, \texttt{conj2}, implements binary conjunction. It 
-applies 
-the \emph{first} goal to the input state, then applies the second goal to 
-states in the resulting search space. The latter process is done with a helper 
-function. \texttt{append-map-inf} applies its input goal to states in its input 
-search spaces and compose the resulting search spaces. It reuses 
-\texttt{append-inf} for search space composition. The following three 
-definitions introduce syntactic sugars that miniKanren users are more familiar 
-with. The first two definitions say disjunction and disjunction are 
-right-associative. The next and last definition says \conde{} relates its 
-clauses disjunctively, and goals in the same clause conjunctively.
+spaces. The following function, \texttt{conj2}, implements binary conjunction. 
+It applies the \emph{first} goal to the input state, then applies the second 
+goal to states in the resulting search space. The latter process is done with a 
+helper function. \texttt{append-map-inf} applies its input goal to states in 
+its input search spaces and compose the resulting search spaces. It reuses 
+\texttt{append-inf} for search space composition. The following two definitions 
+say disjunctive operator and conjunctive operator are right-associative.
 

### 2019-05-20 Paper/paper.tex
more fixes

@@
 strategies. We follow some conventions to name variables: variables bound to 
-states are named \texttt{s}; variables bound to goals are named `g' (possibly 
-with subscript); variables bound to search spaces have names ending with 
-$^\infty$. The first function, \texttt{disj2}, implements binary disjunction. 
-\texttt{append-inf} is its helper, which composes two disjunctive search 
-spaces. The following function, \texttt{conj2}, implements binary conjunction. 
+states are named \texttt{s}; variables bound to goals are named \texttt{g} 
+(possibly with subscript); variables bound to search spaces have names ending 
+with $^\infty$. The first function, \texttt{disj2}, implements binary 
+disjunction. if and only if is its helper, which composes two disjunctive 
+search spaces. The following function, \texttt{conj2}, implements binary 
+conjunction. 
 It applies the \emph{first} goal to the input state, then applies the second 
 goal to states in the resulting search space. The latter process is done with a 
-helper function. \texttt{append-map-inf} applies its input goal to states in 
-its input search spaces and compose the resulting search spaces. It reuses 
-\texttt{append-inf} for search space composition. The following two definitions 
-say disjunctive operator and conjunctive operator are right-associative.
+helper function. \texttt{append-map$^\infty$} applies its input goal to states 
+in its input search spaces and compose the resulting search spaces. It reuses 
+\texttt{append$^\infty$} for search space composition. The following and last 
+two definitions say disjunctive operator and conjunctive operator are 
+right-associative.
 
@@
 \conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
-DFS$_\textrm{i}$'s 
-in the \disj{} macro. We list the new \disj{} with its helper in 
-Fig.~\ref{balanced-disj}. The helper \texttt{disj+} builds a balanced binary 
-tree 
-whose leaves are the goals and whose nodes are \texttt{disj2}s, hence the name 
-of 
-this search strategy. The first argument 
-to \texttt{disj+} is a list of all goals. And the next two arguments accumulate 
-goals in 
-the left and right subtrees. The first clause says that when there is one goal, 
-the tree is the goal itself. When there are more goals, the first argument is 
-partitioned into two sub-lists. The partition is done by repetitively 
-dispatching the first two goals (the last clause), until no goal remains (the 
-second clause) or one goal remains (the third clause). In contrast, the \disj{} 
-in DFS$_\textrm{i}$ constructs the binary tree with the same collection of leaf 
-nodes but in a particularly unbalanced form.
+DFS$_\textrm{i}$'s in the \disj{} macro. We list the new \disj{} with its 
+helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
+goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
+whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
+The first ``argument'' to \texttt{disj+} is the goals. And the next two 
+``arguments'' accumulate goals to be put in the left and right subtrees. When 
+there is only one goal, the tree is the goal itself. This case is handled in 
+the first clause. When there are more goals, we partition the list of goals 
+into two sublists of roughly equal lengths and recur on the two sublists. The 
+partition is done by repetitively dispatching the first two goals in the list 
+to the accumulators, until only 
+zero or one goal remains. The two base cases of the partition are handled by 
+the second and the third clauses respectively. And the dispatching is done at 
+the fourth and last clause. In contrast, the \disj{} in \DFSi{} constructs the 
+binary tree in a particularly unbalanced form.
 
@@
 \texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is changed to call a new and 
-fair version of \texttt{append-inf}. \texttt{append-inf/fair} immediately calls 
+fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
+immediately 
+calls 
 its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
 \texttt{\#{}t}, which indicates that 
-\texttt{s-inf} and \texttt{t-inf} haven't been swapped. The swapping happens at 
+\texttt{s$^\infty$} and \texttt{t$^\infty$} haven't been swapped. The swapping 
+happens at 
 the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
@@
 finite. The third clause, as we mentioned above, is just for swapping. When the 
-fourth and last clause runs, we know that both \texttt{s-inf} and \texttt{t-inf} 
-are ended with a thunk. In this case, a new thunk is constructed. The new thunk 
-calls the driver recursively. Here changing the order of \texttt{t-inf} and 
-\texttt{s-inf} won't hurt the fairness (though it will change the order of 
-answers). We swap them back so that answers are produced in a more natural 
-order.
+fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
+\texttt{t$^\infty$} are ended with a thunk and they have been swapped. In this 
+case, a new thunk is constructed. Here changing the order of 
+\texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
+will change the order of answers). We swap them back so that answers are 
+produced in a more natural order.
 
@@
 DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFS{} based on \DFSf{}, 
-we need \texttt{append-map-inf/fair} in addition to \texttt{append-inf/fair}. 
-The only difference between \texttt{append-map-inf/fair} and 
-\texttt{append-map-inf} is that the former calls \texttt{append-inf/fair} 
-instead of \texttt{append-inf}.
+we need \texttt{append-map$^\infty_{fair}$} in addition to 
+\texttt{append$^\infty_{fair}$}. 
+The only difference between \texttt{append-map$^\infty$} and 
+\texttt{append-map$^\infty_{fair}$} is that the latter calls 
+\texttt{append$^\infty_{fair}$} instead of \texttt{append$^\infty$}.
 
@@
 same bag. In this implementation, however, it is unclear where this information 
-is recorded. Second, \texttt{append-inf/fair} is extravagant in memory usage. It 
+is recorded. Second, \texttt{append$^\infty_{fair}$} is extravagant in memory 
+usage. It 
 makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
@@
 computed recursively then increased by one. It is even more subtle that
-\texttt{append-inf/fair} and the \texttt{append-map-inf/fair} respects the cost 
+\texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
+respects 
+the cost 
 information. We make these facts more obvious by changing the type of search 
@@
 others in Fig.~\ref{BFS-opt-cont}). They are compared with 
-\citeauthor{seres1999algebra}'s implementation later. The first three functions 
-in Fig.~\ref{BFS-opt} are search space constructors. \texttt{none} makes an 
-empty search space; \texttt{unit} makes a space from one answer; and 
+\citeauthor{seres1999algebra}'s implementation in our proof. The first three 
+functions in Fig.~\ref{BFS-opt} are search space constructors. \texttt{none} 
+makes an empty search space; \texttt{unit} makes a space from one answer; and 
 \texttt{step} makes a space from a thunk. The remaining functions do the same 
@@
 
-Luckily, the change in \texttt{append-inf/fair} also fixes the miserable space 
+Luckily, the change in \texttt{append$^\infty_{fair}$} also fixes the miserable 
+space 
 extravagance -- the use of \texttt{append} helps us to reuse the first bag of 
-\texttt{t-inf}.
+\texttt{t$^\infty$}.
 
@@
 implementations of logic programming system. Our BFS implementation is not an 
-exception: \texttt{append-map-inf/fair} is like \texttt{bind}, 
+exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
 but takes arguments in reversed order; \texttt{none}, \texttt{unit}, and 
-\texttt{append-inf/fair} correspond to \texttt{mzero}, \texttt{unit}, 
+\texttt{append$^\infty_{fair}$} correspond to \texttt{mzero}, \texttt{unit}, 
 and \texttt{mplus} respectively.
@@
 Functions implementing impure features are in Fig.~\ref{BFS-opt-cont}. The 
-first function, \texttt{elim}, takes a space \texttt{s-inf} and two 
-continuations \texttt{ks} and \texttt{kf}. When \texttt{s-inf} contains some 
+first function, \texttt{elim}, takes a space \texttt{s$^\infty$} and two 
+continuations \texttt{ks} and \texttt{kf}. When \texttt{s$^\infty$} contains 
+some 
 answers, \texttt{ks} is called with the first answer and the rest space. 
@@
 found in \citet{seres1999algebra}. We focus on the pure subset because 
-Silvija's system is pure. Their system represents search spaces with streams of 
+their system is pure. Their system represents search spaces with streams of 
 lists of answers, where each list is a bag.
 
-To compare efficiency, we translate her Haskell code into Racket (See 
+To compare efficiency, we translate their Haskell code into Racket (See 
 supplements for the translated code). The translation is direct 
@@
 to circumvent the need for symbolic constraints (e.g. $\neq$, 
-\texttt{absento}). Our version generates de 
+\texttt{absent$^o$}). Our version generates de 
 Bruijnized expressions and prevent closures getting into list. The two 
@@
 Therefore, this 
-benchmark might be a special case. Fair \conj{} imposes overhead constantly 
-except in \texttt{appendo}. The reason might be that strategies with fair 
-\conj{} tend to keep more intermediate answers in the memory.
+benchmark might be a special case. Fair \conj{} imposes considerable overhead 
+constantly except in \texttt{appendo}. The reason might be that strategies with 
+fair \conj{} tend to keep more intermediate answers in the memory.
 
@@
 Silvija et al \citet{seres1999algebra} also describe a breadth-first search 
-strategy. We proof their BFS is equivalent to ours. But our code looks simpler 
+strategy. We proof their BFS is equivalent to ours. But our code is shorter
 and performs better in comparison with a straightforward translation of their 

### 2019-05-21 Paper/paper.tex
deadline
change disj macro folloing the suggestion by Dan

@@
 
-%%% NOTE %%%
-%
-%  SUBMISSION DEADLINE: May 15, 2019
-%
-%%%%%%%%%%%%
-
 \newcommand{\conde}{\texttt{cond$^e$}}
@@
 \begin{document}
+
+\NOTE[LKC]{submission deadline: Mon 27 May 2019}
 
@@
 \begin{figure}
-	\lstinputlisting{Figures/DFSi.rkt}
-	\caption{implementation of \DFSi}
-	\label{DFSi}
+	\lstinputlisting{Figures/DFSi-0.rkt}
+	\caption{implementation of \DFSi{} (Part I)}
+	\label{DFSi-0}
 \end{figure}
 
-Fig.~\ref{DFSi} shows parts that are later compared with other search 
+\begin{figure}
+	\lstinputlisting{Figures/DFSi-1.rkt}
+	\caption{implementation of \DFSi{} (Part II)}
+	\label{DFSi-1}
+\end{figure}
+
+Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} shows parts that are later compared 
+with other search 
 strategies. We follow some conventions to name variables: variables bound to 
@@
 (possibly with subscript); variables bound to search spaces have names ending 
-with $^\infty$. The first function, \texttt{disj2}, implements binary 
-disjunction. if and only if is its helper, which composes two disjunctive 
-search spaces. The following function, \texttt{conj2}, implements binary 
-conjunction. 
+with $^\infty$. Fig.~\ref{DFSi-0} shows the implementation of disjunction. The 
+first function, \texttt{disj2}, implements binary disjunction. It applies the 
+two disjunctive goals to the input state \texttt{s} and composes the two 
+resulting search spaces with \texttt{append$^\infty$}. The following syntax 
+definitions say disjunctive operator is right-associative. Fig.~\ref{DFSi-1} 
+shows the implementation of conjunction. The first function, \texttt{conj2}, 
+implements binary conjunction. 
 It applies the \emph{first} goal to the input state, then applies the second 
@@
 in its input search spaces and compose the resulting search spaces. It reuses 
-\texttt{append$^\infty$} for search space composition. The following and last 
-two definitions say disjunctive operator and conjunctive operator are 
-right-associative.
+\texttt{append$^\infty$} for search space composition. The following syntax 
+definitions say conjunctive operator is also right-associative.
 
@@
 whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
-The first ``argument'' to \texttt{disj+} is the goals. And the next two 
-``arguments'' accumulate goals to be put in the left and right subtrees. When 
-there is only one goal, the tree is the goal itself. This case is handled in 
-the first clause. When there are more goals, we partition the list of goals 
-into two sublists of roughly equal lengths and recur on the two sublists. The 
-partition is done by repetitively dispatching the first two goals in the list 
-to the accumulators, until only 
-zero or one goal remains. The two base cases of the partition are handled by 
-the second and the third clauses respectively. And the dispatching is done at 
-the fourth and last clause. In contrast, the \disj{} in \DFSi{} constructs the 
+The new helper, \texttt{disj+}, takes two additional `arguments'. They 
+accumulate goals to be put in the left and right subtrees. The first clause 
+handles the case where there is only one goal. In this case, the tree is the 
+goal itself. When there are more goals, we partition the list of goals 
+into two sublists of roughly equal lengths and recur on the two sublists. Goals 
+are moved to the accumulators in the fourth and last clause. As we are moving 
+two goals each time, there are two base cases: (1) no goal remains; (2) one 
+goal remains. These two base cases are handled in the second clause and the 
+third clause respectively. In contrast, the \disj{} in \DFSi{} constructs the 
 binary tree in a particularly unbalanced form.
-
-% The first helper function, \texttt{split}, takes a 
-% list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
-% into two sub-lists of roughly equal length, and returns the application of 
-% \texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
-% \texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
-% constructs a \emph{balanced} binary tree where leaves are elements of 
-% \texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
-% strategy.
 

### 2019-05-21 Paper/paper.tex
rewrite abstract

@@
 
-The syntax of a programming language should reflect its semantics. When writing 
-a \conde{} expression in miniKanren, a programmer would expect all clauses 
-share the same chance of being explored, as these clauses are written in 
-parallel. The existing search strategy, interleaving depth-first search 
-(\DFSi{}), 
-however, prioritizes its clauses by the order how they are written down. 
-Similarly, when a \conde{} is followed by another goal conjunctively, a 
-programmer would expect states in parallel share the same chance of being 
-explored. Again, the answers by \DFSi{} is different from the 
-expectation. We have devised three new search strategies that have different 
-level of fairness in \disj{} and \conj{}.
+We describe fairness levels in disjunction implementation and conjunction 
+implementation. Specifically, a disjunction implementation can be fair, 
+almost-fair, or unfair. And a conjunction implementation can be fair or unfair. 
+We compare the fairness level of four search strategies: interleaving 
+depth-first search (DFSi), balanced interleaving depth-first search (DFSbi), 
+fair depth-first search (DFSf), and breadth-first search (BFS). DFSi is one of 
+the best-understood search strategies in miniKanren community. DFSbi and DFSf 
+are new. And we present a new implementation of BFS. We demonstrate by a 
+quantitative evaluation that DFSbi and DFSf are competitive alternatives to 
+DFSi, and that BFS is less practical.
 
-\NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}
+% The syntax of a programming language should reflect its semantics. When writing 
+% a \conde{} expression in miniKanren, a programmer would expect all clauses 
+% share the same chance of being explored, as these clauses are written in 
+% parallel. The existing search strategy, interleaving depth-first search 
+% (\DFSi{}), 
+% however, prioritizes its clauses by the order how they are written down. 
+% Similarly, when a \conde{} is followed by another goal conjunctively, a 
+% programmer would expect states in parallel share the same chance of being 
+% explored. Again, the answers by \DFSi{} is different from the 
+% expectation. We have devised three new search strategies that have different 
+% level of fairness in \disj{} and \conj{}.
+% 
+% \NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}
 

### 2019-05-21 Paper/paper.tex
These are in Paper

@@
 \addeditor{LKC}
+\addeditor{DPF}
 
@@
 
-\title{miniKanren with fair search strategies}
+\title{Towards a miniKanren with fair search strategies}
 \author{Kuang-Chen Lu}
@@
 
+\newcommand{\BFSopt}[0]{BFS$_\textrm{opt}$}
+
+\newcommand{\BFSeff}[0]{BFS$_\textrm{eff}$}
+
+\newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
 \newtheorem{defn}{Definition}[section]
@@
 
-We describe fairness levels in disjunction implementation and conjunction 
-implementation. Specifically, a disjunction implementation can be fair, 
-almost-fair, or unfair. And a conjunction implementation can be fair or unfair. 
-We compare the fairness level of four search strategies: interleaving 
-depth-first search (DFSi), balanced interleaving depth-first search (DFSbi), 
-fair depth-first search (DFSf), and breadth-first search (BFS). DFSi is one of 
-the best-understood search strategies in miniKanren community. DFSbi and DFSf 
-are new. And we present a new implementation of BFS. We demonstrate by a 
-quantitative evaluation that DFSbi and DFSf are competitive alternatives to 
-DFSi, and that BFS is less practical.
+  We describe fairness levels in disjunction and conjunction
+  implementations.  Specifically, a disjunction implementation can be
+  fair, almost-fair, or unfair. And a conjunction implementation can
+  be fair or unfair.  We compare the fairness level of four search
+  strategies: the standard miniKanren interleaving depth-first search (\DFSi),
+  the balanced interleaving depth-first search (\DFSbi), the fair depth-first
+  search (\DFSf), and the standard breadth-first search (\BFSser).  
+  \DFSbi{} and \DFSf{} are new. And we present a new implementation of 
+  \BFSser. Using a quantitative evaluation, we argue that
+  \DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
+  and that \BFSopt{} is more efficient than the standard \BFSser.
 
@@
 miniKanren is a family of relational programming languages.
-\citet{friedman_reasoned_2018} introduce miniKanren and its implementation
-in \emph{The Reasoned Schemer, 2nd Ed} (TR2). miniKanren programs, especially
-relational interpreters, have been proven to be useful in solving many problems 
-by \citet{byrd2017unified}.
+\citet{friedman_reasoned_2018} introduce miniKanren and its
+implementation in \emph{The Reasoned Schemer, 2nd Ed}
+(TRS2). miniKanren programs, have been proven to be useful in solving 
+many problems as in miniKanren.org.\citet{byrd2017unified}.
+
+% miniKanren is a family of relational programming languages.
+% \citet{friedman_reasoned_2018} introduce miniKanren and its implementation
+% in \emph{The Reasoned Schemer, 2nd Ed} (TRS2). miniKanren programs, especially
+% relational interpreters, have been proven to be useful in solving many problems 
+% as in \citet{byrd2017unified}.
+
+\NOTE[DPF]{I think that the abbreviations for the search strategies
+should not come up until the Introduction.}
+
+\NOTE[DPF]{When we talk about complete and incomplete, I think we should
+make it explicit that we are only talking about (run n (x y z) g ...) and
+not (run* (x y z) g ...), but an alternative could be something like is
+a stream that is always growing.  There is a term for this, likes makes
+progress, but my mind is hiding the word from me.  It will come to me, but
+not at this moment.}
 
@@
 further about them later.}
-
+\NOTE[DPF]{I have deleted the sentence.}
 % \conde{} is the flagship disjunction operator in miniKanren.
@@
 receives. In the example above, the \texttt{a} clause takes half of all 
-recourses. And the \texttt{b} clause takes a quarter. Thus \texttt{c} and 
+resourses. And the \texttt{b} clause takes a quarter. Thus \texttt{c} and 
 \texttt{d} barely contribute to the result.
@@
 efficiently. A little miniKanrener, however, may beg to differ--understanding
-implementation details and fiddling with clauses order is not the first
+implementation details and fiddling with clause order is not the first
 priority of a beginner.
@@
 almost-fair \disj{} give every clause similar priority. 
-Fair \conj{}, a related concept, is more complicated. We defer it to the next 
+Fair \conj{}, a related concept, is more subtle. We defer it to the next 
 section.
@@
 	new search strategy with fair \disj{}.
-	\item implement in a new way breath-first search (BFS), a search strategy 
-	with fair \disj{} and fair \conj{}. And we prove formally that our BFS 
-implementation is equivalent to the one by \citet{seres1999algebra}. Our code 
-runs faster in all benchmarks and is simpler. 
+	\item implement in a new way breath-first search (\BFSopt), 
+        a search strategy 
+	with fair \disj{} and fair \conj{}. And we prove formally that our 
+\BFSopt{} implementation is semantically equivalent to the one 
+by \citet{seres1999algebra}, however, Our code 
+runs faster in all benchmarks and we believe it is simpler.
 \end{itemize}
@@
 
-Under the hood, the \conde{} here is allocating computational resource to 
+Under the hood, the \conde{} here is allocating computational resources to 
 four trivially different search space. The unfair \disj{} in 
@@
 from the one by \citet{seres1999algebra}. Their definition is for binary 
-disjunction. We generalize it to multi-arity one.
+disjunction. We generalize it to a multi-arity one.
 
 \begin{defn}[fair \disj{}]
-A \disj{} is fair if and only if it allocates computational resource evenly to 
+A \disj{} is fair if and only if it allocates computational resources evenly to 
 search spaces produced by goals in the same disjunction (i.e. clauses in 
@@
 \begin{defn}[almost-fair \disj{}]
-A \disj{} is almost-fair if and only if it allocates computational resource so 
-evenly to 
-search spaces produced by goals in the same disjunction that the maximal ratio 
-of resources is bounded by a constant.
+A \disj{} is almost-fair if and only if it allocates computational resources
+evenly to search spaces produced by goals in the same disjunction that 
+the maximal ratio of resources is bounded by a constant.
 \end{defn}
@@
 
-A more interesting situation is when the first conjunct produces infinite many 
-states. Consider the following example, a naive specification of fair \conj{} 
+A more interesting situation is when the first conjunct produces an unbounded
+number of states. Consider the following example, a naive specification of fair \conj{} 
 might require search strategies to produce all sorts of singleton lists, but no 
 longer ones, which makes the strategies incomplete. A search strategy is 
-\emph{complete} if and only if it can find out all the answers within finite 
+\emph{complete} if and only if it can determine all the answers within finite 
 time, otherwise, it is \emph{incomplete}.
@@
 
-BFS puts states of the same cost in the same bag, and allocate resources 
-carefully among search spaces related to different bags such that answers are 
-produced in increasing order of cost. The \emph{cost} of a answer is its depth 
-in the search tree (i.e. the number of calls to relational definitions required 
-to find them) \citep{seres1999algebra}. In the following example, every answer 
-is a list of list of symbols, where inner lists are the same. Here the 
-cost of each answer is equal to the length of its inner lists plus the length 
-of its outer list.
+\BFSser{} puts states of the same cost in the same bag, and allocates
+resources carefully among search spaces related to different bags such
+that answers are produced in increasing order of cost. The \emph{cost}
+of an answer is its depth in the search tree (i.e., the number of
+calls to relations required to find them) \citep{seres1999algebra}. In
+the following example, every answer is a list of list of symbols,
+where inner lists are the same. Here the cost of each answer is equal
+to the length of its inner lists plus the length of its outer list.
 
@@
 \begin{defn}[fair \conj{}]
-A \conj{} is fair if and only if it allocates computational resource evenly to 
+A \conj{} is fair if and only if it allocates computational resources evenly to 
 search spaces produced from states in the same bag. A bag is a finite 
-collection of state. And search strategies with fair \conj{} should represent 
-search spaces with possibly infinite collection of bags. 
+collection of states. And search strategies with fair \conj{} should represent 
+search spaces with possibly unbounded collections of bags. 
 \end{defn}
@@
 
-Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} shows parts that are later compared 
+\NOTE[DPF]{If we use the name subscript, the subscripts should use an underscore and we should do it for gunderscorel and gundescorer. If we can use an l that
+looks less like a 1, that would even be better.  Look at the l in TLT.}
+
+Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} show parts that are later compared 
 with other search 
@@
 (possibly with subscript); variables bound to search spaces have names ending 
-with $^\infty$. Fig.~\ref{DFSi-0} shows the implementation of disjunction. The 
+with $^\infty$. Fig.~\ref{DFSi-0} shows the implementation of \disj. The 
 first function, \texttt{disj2}, implements binary disjunction. It applies the 
@@
 resulting search spaces with \texttt{append$^\infty$}. The following syntax 
-definitions say disjunctive operator is right-associative. Fig.~\ref{DFSi-1} 
-shows the implementation of conjunction. The first function, \texttt{conj2}, 
+definitions say \disj{} is right-associative. Fig.~\ref{DFSi-1} 
+shows the implementation of \conj. The first function, \texttt{conj2}, 
 implements binary conjunction. 
@@
 goal to states in the resulting search space. The latter process is done with a 
-helper function. \texttt{append-map$^\infty$} applies its input goal to states 
-in its input search spaces and compose the resulting search spaces. It reuses 
+the helper function \texttt{append-map$^\infty$} that applies its input goal to states 
+in its input search spaces and composes the resulting search spaces. It reuses 
 \texttt{append$^\infty$} for search space composition. The following syntax 
-definitions say conjunctive operator is also right-associative.
+definitions say \conj{} is also right-associative.
 
@@
 
-Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
+Balanced interleaving DFS (DFS$_\textrm{bi}$) has an almost-fair \disj{} and unfair 
 \conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
@@
 into two sublists of roughly equal lengths and recur on the two sublists. Goals 
-are moved to the accumulators in the fourth and last clause. As we are moving 
+are moved to the accumulators in the last clause. As we are moving 
 two goals each time, there are two base cases: (1) no goal remains; (2) one 
-goal remains. These two base cases are handled in the second clause and the 
-third clause respectively. In contrast, the \disj{} in \DFSi{} constructs the 
+goal remains. These two new base cases are handled in the second clause and the 
+third clause, respectively. In contrast, the \disj{} in \DFSi{} constructs the 
 binary tree in a particularly unbalanced form.
@@
 \section{fair depth-first search}
+
+\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more efficient? It shouldn't be?}
 
@@
 \texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
-will change the order of answers). We swap them back so that answers are 
+changes the order of answers). We swap them back so that answers are 
 produced in a more natural order.
+
+\NOTE[DPF]{When or where do you swap them back?}
 
@@
 
-BFS has both fair \disj{} and fair \conj{}. Our implementation is based on 
-DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFS{} based on \DFSf{}, 
+\BFSser{} has both fair \disj{} and fair \conj{}. Our implementation is based on 
+DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFSopt{} based on \DFSf{}, 
 we need \texttt{append-map$^\infty_{fair}$} in addition to 
@@
 The implementation can be improved in two ways. First, as mentioned in 
-section 2.2, BFS puts answers in bags and answers of the same cost are in the 
+section 2.2, \BFSser puts answers in bags and answers of the same cost are in the 
 same bag. In this implementation, however, it is unclear where this information 
@@
 
-Both our BFS and Seres's BFS \citet{seres1999algebra} produce answers in 
+Both \BFSser{} \citet{seres1999algebra} and BFSopt{} produce answers in 
 increasing order of cost. So it is interesting to see if they are equivalent. 
@@
 
+\NOTE[DPF]{Never refer to a literal section like 2.2. Instead
+stick a label where it starts right near the section number and
+stick another label where the subsection starts.
+Then ref the two labels and place a period between them.}.
+
 As mentioned in section 2.2, BFS puts answers in bags and answers of the 
@@
 information is recorded subtly -- the \texttt{car}s of a search space have cost 
-0 (i.e. they are in the same bag), and the costs of answers in thunk are 
+0 (i.e. they are all in the same bag), and the costs of answers in thunk are 
 computed recursively then increased by one. It is even more subtle that
 \texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
-respects 
-the cost 
-information. We make these facts more obvious by changing the type of search 
-space, modifying related function definitions, and introducing a few more 
-functions.
+respects the cost information. We make these facts more obvious by 
+changing the type of search space, modifying related function definitions, 
+and introducing a few more functions.
 
@@
 makes an empty search space; \texttt{unit} makes a space from one answer; and 
-\texttt{step} makes a space from a thunk. The remaining functions do the same 
-thing as before.
+\texttt{step} makes a space from a thunk. The remaining functions as before.
 
@@
 space 
-extravagance -- the use of \texttt{append} helps us to reuse the first bag of 
+extravagance---the use of \texttt{append} helps us to reuse the first bag of 
 \texttt{t$^\infty$}.
@@
 \citet{kiselyov2005backtracking} has shown that a \emph{MonadPlus} hides in 
-implementations of logic programming system. Our BFS implementation is not an 
-exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
+implementations of logic programming system. The \BFSopt{} implementation is not 
+an exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
 but takes arguments in reversed order; \texttt{none}, \texttt{unit}, and 
@@
 
-\subsection{comparison with the BFS of \citet{seres1999algebra}}
+\subsection{comparison with the BFSser and BFSopt}
 
-In this section, we compare the pure subset of our optimized BFS with the BFS 
+In this section, we compare the pure subset of \BFSopt{} with the BFS 
 found in \citet{seres1999algebra}. We focus on the pure subset because 
@@
 due to the similarity in both logic programming systems and search space 
-representations. The translated code is longer and slower than our BFS 
+representations. The translated code is longer and slower than BFSopt
 implementation. Details about 
-difference in efficiency are in section 6.
+difference in efficiency are in section 7.
 
-We prove in Coq that the two BFSs are equivalent, i.e. \texttt{(run n g)} 
+We prove in Coq that \BFSser{} and \BFSopt{} are semantically equivalent, i.e. \texttt{(run n ? g)} 
 produces the same result (See supplements for the formal proof).
@@
 		\hline 
-		benchmark & size & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & optimized BFS & Silvija's BFS  
+		benchmark & size & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS$_\textrm{opt}$ & BFS$_\textrm{ser}$  
 		\\
@@
 
-In this section, we compare the efficiency of search strategies. A concise 
-description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
-memory. The first two benchmarks are taken from 
-\citet{friedman_reasoned_2018}. \texttt{reverso} is from 
-\citet{rozplokhas2018improving}. Next two benchmarks 
+Here we compare the efficiency of search strategies. A concise 
+description is in Table~\ref{compare-efficiency}. A hyphen means ``running out of 
+memory.'' The first two benchmarks are taken from 
+TRS2. \texttt{reverso} is from 
+\citet{rozplokhas2018improving}. The next two benchmarks 
 about quine are modified from a similar test case in \citet{byrd2017unified}. 
@@
 benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
-you)}. This benchmark is also inspired by \citet{byrd2017unified}. Again, the 
+you)}. This benchmark is from \citet{byrd2017unified}. Again, the 
 sibling benchmarks differ in the \conde{} clause order of their relational 
@@
 perform badly in the second case because elimination rules complicate the 
-problem when running backward. The evaluation supports our conjecture.
+problem when synthesizing (i.e., our evaluation supports our conjecture.)
 
@@
 overhead in many cases. Among the three variants of DFS (they all have unfair 
-\conj{}), DFS$_\textrm{f}$ is most resistant to clause permutation, followd by DFS$_\textrm{bi}$ then 
+\conj{}), DFS$_\textrm{f}$ is most resistant to clause permutation, followed by DFS$_\textrm{bi}$ then 
 DFS$_\textrm{i}$. Among the two implementation of BFS, ours constantly performs as well or 
-better. Interestingly, every strategies with fair \disj{} suffers in 
+better. Interestingly, every strategy with fair \disj{} suffers in 
 \texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
@@
 
-Edward points out a disjunct complex would be `fair' if it is a full and 
-balanced tree \citet{yang2010adventures}.
+Yang \citet{yang2010adventures} points out a disjunct complex would be `fair' 
+if it were a full and balanced tree .
 
-Silvija et al \citet{seres1999algebra} also describe a breadth-first search 
-strategy. We proof their BFS is equivalent to ours. But our code is shorter
-and performs better in comparison with a straightforward translation of their 
-Haskell code.
+Seres et al \citet{seres1999algebra} also describe a breadth-first search 
+strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But our codeis shorter and performs better in comparison with a straightforward 
+translation of their Haskell code.
 
@@
 
-We analysis the definitions of fair \disj{} and fair \conj{}, then propose a 
+We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
 new definition of fair \conj{}. Our definition is orthogonal with completeness.
@@
 implementation of BFS. These strategies have different features 
-in fairness: $_\textrm{bi}$ has almost-fair \disj{} and unfair \conj{}. 
-DFS$_\textrm{f}$ has fair \disj{} and unfair \conj{}. BFS has both fair \disj{} 
-and fair \conj{}.
+in fairness: $_\textrm{bi}$ has an almost-fair \disj{} and unfair \conj{}. 
+DFS$_\textrm{f}$ has fair \disj{} and unfair \conj{}. \BFSopt{} has both fair
+\disj{} and fair \conj{}.
 
 Our quantitative evaluation shows that DFS$_\textrm{bi}$ and DFS$_\textrm{f}$ are competitive 
-alternatives to DFS$_\textrm{i}$, the current search strategy, and that BFS is less 
-practical.
+alternatives to DFS$_\textrm{i}$, the current search strategy, and that 
+\BFSopt is less practical than 
+\NOTE[DPF]{what}
 
-We prove our BFS is equivalent to the BFS in \citet{seres1999algebra}. Our code 
-is shorter and runs faster than a direct translation of their Haskell code.
+We prove that \BFSopt{} is equivalent to \BFSser in \citet{seres1999algebra}. 
+Our optimized code is shorter and runs faster than a direct translation 
+of their Haskell code.
 

### 2019-05-22 Paper/paper.tex
Changed a NOTE.

@@
 
+\NOTE[DPF]{We should reference the earliest paper (See Will Byrd vita)
+
 \end{abstract}
@@
 make it explicit that we are only talking about (run n (x y z) g ...) and
-not (run* (x y z) g ...), but an alternative could be something like is
-a stream that is always growing.  There is a term for this, likes makes
-progress, but my mind is hiding the word from me.  It will come to me, but
-not at this moment.}
+not (run* (x y z) g ...), but an alternative is that a stream is \emph{productive}
+or \emph{unproductive}.}
 

### 2019-05-22 Paper/paper.tex
Someone should use the tex macros that have already been written and get rid of looking at these extra long objects that require a steady hand.  They are all over the place, for example \DFSi{}.  I am up to 2.2 on perhaps my final pass over the paper before it is submitted.

@@
   search (\DFSf), and the standard breadth-first search (\BFSser).  
-  \DFSbi{} and \DFSf{} are new. And we present a new implementation of 
-  \BFSser. Using a quantitative evaluation, we argue that
+  \DFSbi{} and \DFSf{} are new. And we present a new, more efficient
+  and simpler implementation of \BFSser. Using quantitative evaluation, 
+  we argue that
   \DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
@@
 
-\NOTE[DPF]{We should reference the earliest paper (See Will Byrd vita)
-
 \end{abstract}
@@
 should not come up until the Introduction.}
+
+\NOTE[DPF]{We should reference the earliest paper (See Will Byrd vita)}
 
@@
 
-The miniKanren in TR2 implements interleaving DFS (\DFSi), the cause of this 
+The miniKanren in TRS2 implements interleaving DFS (\DFSi), the cause of this 
 unexpected result. With this search strategy, each clause takes half 
-of its received computational resources and pass the other half to its 
+of its received computational resources and passes the other half to its 
 following clauses, except for the last clause that takes all resources it 
@@
 There is another reason that miniKanren could use more search strategies than
-just \DFSi. In many applications, there does not exist one order that serves
-for all purposes. For example, a relational dependent type checker contains
+just \DFSi. In many applications, there does not exist one order that serves all purposes. For example, a relational dependent type checker contains
 clauses for constructors that build data and clauses for eliminators that use
 data. When the type checker is used to generate simple and shallow programs,
-the clauses of constructors should be put in the front of \conde.
-When performing proof searches for complicated programs, the clauses of 
-eliminator should take the focus. With \DFSi, these two uses cannot be 
+the clauses for constructors should be put at the top of the
+\conde{} clauses.
+When performing proof searches for complicated programs, the clauses for 
+eliminators should be put at the top of \conde{} clauses. With \DFSi, these two uses cannot be 
 efficient at the same time. In fact, to make one use efficient, the other one 
-must be drastically slow.
+must be more sluggish.
 
@@
 almost-fair \disj{} give every clause similar priority. 
-Fair \conj{}, a related concept, is more subtle. We defer it to the next 
-section.
+Fair \conj{}, a related concept, is more subtle. The discussion of fair
+\conj{} is covered in the next section.
 
@@
 In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
-Before going further into fairness, we would like to give a short review about 
-state, search space, and goal, because fairness is defined in terms of them. 
-A \emph{state} is a collection of constraints. Every answer corresponds to a 
-state. A \emph{search space} is a collection of states. And a \emph{goal} is a 
-function from a state to a search space.
+Before going further into fairness, we give a short review of the terms:
+\emph{state}, search \emph{space}, \emph{goal}.
+A \emph{state} is a collection of constraints. (Here, we restrict 
+constraints to unification constraints. Every answer corresponds to a 
+state. A space is a collection of states. And a \emph{goal} is a 
+function from a state to a space.
 
@@
 of other letters. And some letters  (e.g. \texttt{c} and \texttt{d}) are
-rarely seen. The situation would be exacerbated if \conde{} contains more 
-clauses.
+rarely seen. The situation would be exacerbated if \conde{} would have
+contained more clauses.
 
@@
 Under the hood, the \conde{} here is allocating computational resources to 
-four trivially different search space. The unfair \disj{} in 
+four trivially different search spaces. The unfair \disj{} in 
 \DFSi{} allocates many more resources to the first search space. On the 
@@
 We end this subsection with precise definitions of all levels of 
-\disj{} fairness. Our definition of \emph{fair} \disj{} is slightly generalize 
-from the one by \citet{seres1999algebra}. Their definition is for binary 
-disjunction. We generalize it to a multi-arity one.
+\disj{} fairness. Our definition of \emph{fair} \disj{} is slightly 
+more general
+than the one in \citet{seres1999algebra}. Their definition is only
+for binary disjunction. We generalize it to a multi-arity one.
 
@@
 A \disj{} is fair if and only if it allocates computational resources evenly to 
-search spaces produced by goals in the same disjunction (i.e. clauses in 
-the same \conde).
+search spaces produced by goals in the same disjunction 
+(i.e., clauses in the same \conde).
 \end{defn}
@@
 \begin{defn}[unfair \disj{}]
-A \disj{} is unfair if and only if it is not even almost-fair.
+A \disj{} is unfair if and only if it is not almost-fair.
 \end{defn}
@@
 lists of other letters. And some letters are rarely seen. The situation would 
-be exacerbated if \conde{} contains more clauses.
+be exacerbated if \conde{} were to contain more clauses.
 
-\NOTE[LKC]{Should I add a footnote?
+\NOTE[LKC]{Should I add a footnote?}
 
@@
 DFS$_\textrm{i}$'s \disj{} is unfair in general, it is fair when there is no 
-call to relational definition in \conde{} clauses (including this case).
-''}
+call to a relational definition 
+in \conde{} clauses (including this case).
 

### 2019-05-22 Paper/paper.tex
simple fixes

@@
 \newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
+
+\newcommand{\veryrecursiveo}[0]{\texttt{very-recursive$^o$}}
+\newcommand{\appendo}[0]{\texttt{append$^o$}}
+\newcommand{\reverso}[0]{\texttt{revers$^o$}}
+
 \newtheorem{defn}{Definition}[section]
@@
 A \emph{state} is a collection of constraints. (Here, we restrict 
-constraints to unification constraints. Every answer corresponds to a 
-state. A space is a collection of states. And a \emph{goal} is a 
+constraints to unification constraints.) Every answer corresponds to a 
+state. A \emph{space} is a collection of states. And a \emph{goal} is a 
 function from a state to a space.
-
-% Goals check their input states and outputs possibly extended states. A goal 
-% might fail for some inputs, in which case the output search space would be 
-% empty.
 
@@
 lists of other letters. And some letters are rarely seen. The situation would 
-be exacerbated if \conde{} were to contain more clauses.
-
-\NOTE[LKC]{Should I add a footnote?}
-
-``
-Although 
+be exacerbated if \conde{} were to contain more clauses. Although 
 DFS$_\textrm{i}$'s \disj{} is unfair in general, it is fair when there is no 
-call to a relational definition 
-in \conde{} clauses (including this case).
+call to a relational definition in \conde{} clauses (including this case).
 
@@
 		\hline
-		very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
+		\veryrecursiveo{} & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
 		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
@@
 		\hline 
-		appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
+		\appendo{}  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
 		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
@@
 		\hline 
-		reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
+		\reverso{} & 10 &   5 &   3 &   3 &     38 &     85 \\ 
 		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
@@
 memory.'' The first two benchmarks are taken from 
-TRS2. \texttt{reverso} is from 
+TRS2. \reverso{} is from 
 \citet{rozplokhas2018improving}. The next two benchmarks 
@@
 In general, only DFS$_\textrm{i}$ and DFS$_\textrm{bi}$ constantly perform well. DFS$_\textrm{f}$ is just as 
-efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
+efficient in all benchmarks but \veryrecursiveo{}. Both BFS have obvious 
 overhead in many cases. Among the three variants of DFS (they all have unfair 
@@
 better. Interestingly, every strategy with fair \disj{} suffers in 
-\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
+\veryrecursiveo{} and DFS$_\textrm{f}$ performs well elsewhere. 
 Therefore, this 
 benchmark might be a special case. Fair \conj{} imposes considerable overhead 
-constantly except in \texttt{appendo}. The reason might be that strategies with 
+constantly except in \appendo{}. The reason might be that strategies with 
 fair \conj{} tend to keep more intermediate answers in the memory.
@@
 alternatives to DFS$_\textrm{i}$, the current search strategy, and that 
-\BFSopt is less practical than 
+\BFSopt is less practical than other search strategies.
 \NOTE[DPF]{what}
+\NOTE[LKC]{fixed}
 

### 2019-05-22 Paper/paper.tex
trivial
g_

@@
   		   {repeato}{{repeat$^o$}}{6}
+  		   {g0}{{g$_0$}}{1}
+  		   {g1}{{g$_1$}}{1}
+  		   {g2}{{g$_2$}}{1}
+  		   {gl}{{g$_l$}}{1}
+  		   {gr}{{g$_r$}}{1}
 }
@@
 
-\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more efficient? It shouldn't be?}
+\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more 
+efficient? It shouldn't be?}
 

### 2019-05-22 Paper/paper.tex
NOTE swap back

@@
 \texttt{t$^\infty$} are ended with a thunk and they have been swapped. In this 
-case, a new thunk is constructed. Here changing the order of 
-\texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
-changes the order of answers). We swap them back so that answers are 
-produced in a more natural order.
+case, a new thunk is constructed. 
+The new thunk swapped two search spaces back before recursion. This is 
+unnecessary for fairness. We do it such that answers are produced in a more 
+natural order.
+
+% Here changing the order of 
+% \texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
+% changes the order of answers). We swap them back so that answers are 
+% produced in a more natural order.
 
 \NOTE[DPF]{When or where do you swap them back?}
+\NOTE[LKC]{fixed}
 

### 2019-05-22 Paper/paper.tex
dan

--- 2019-05-22 Paper/paper.tex
@@
 \newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
-
-\newcommand{\veryrecursiveo}[0]{\texttt{very-recursive$^o$}}
-\newcommand{\appendo}[0]{\texttt{append$^o$}}
-\newcommand{\reverso}[0]{\texttt{revers$^o$}}
-
 \newtheorem{defn}{Definition}[section]
@@
 	with fair \disj{} and fair \conj{}. And we prove formally that our 
-\BFSopt{} implementation is semantically equivalent to the one 
-by \citet{seres1999algebra}, however, Our code 
-runs faster in all benchmarks and we believe it is simpler.
+\BFSopt{} implementation is semantically equivalent to \BFSser
+however, Our code runs faster in all benchmarks and we believe it is simpler.
 \end{itemize}
@@
 A \emph{state} is a collection of constraints. (Here, we restrict 
-constraints to unification constraints.) Every answer corresponds to a 
-state. A \emph{space} is a collection of states. And a \emph{goal} is a 
+constraints to unification constraints. Every answer corresponds to a 
+state. A space is a collection of states. And a \emph{goal} is a 
 function from a state to a space.
+
+% Goals check their input states and outputs possibly extended states. A goal 
+% might fail for some inputs, in which case the output search space would be 
+% empty.
 
@@
 lists of other letters. And some letters are rarely seen. The situation would 
-be exacerbated if \conde{} were to contain more clauses. Although 
+be exacerbated if \conde{} were to contain more clauses.
+
+\NOTE[LKC]{Should I add a footnote?}
+
+``
+Although 
 DFS$_\textrm{i}$'s \disj{} is unfair in general, it is fair when there is no 
-call to a relational definition in \conde{} clauses (including this case).
+call to a relational definition 
+in \conde{} clauses (including this case).
 
@@
 number of states. Consider the following example, a naive specification of fair \conj{} 
-might require search strategies to produce all sorts of singleton lists, but no 
-longer ones, which makes the strategies incomplete. A search strategy is 
-\emph{complete} if and only if it can determine all the answers within finite 
+might require search strategies to produce all sorts of singleton lists, but there
+would not be any lists of length two or longer, which makes the strategies incomplete. 
+A search strategy is \emph{complete} if and only if it can determine all the answers within finite 
 time, otherwise, it is \emph{incomplete}.
+
+\NOTE[DPF]{Does this assume that we never use run*, since in fact, the paper does not
+include and uses of run*.  Something should be mentioned around here.}
 
@@
 calls to relations required to find them) \citep{seres1999algebra}. In
-the following example, every answer is a list of list of symbols,
+the following example, every answer is a list of a list of symbols,
 where inner lists are the same. Here the cost of each answer is equal
-to the length of its inner lists plus the length of its outer list.
+to the length of its inner list plus the length of its outer list.
 
@@
 In this section, we review the implementation of interleaving depth-first 
-search (\DFSi). We focus on parts that are relevant to this paper. TRS2 
-\citep{friedman_reasoned_2018} provides a comprehensive description of the 
-whole miniKanren implementation.
+search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
+chapter 10 and the appendix, ``Connecting the wires,'' 
+provides a comprehensive description of the 
+miniKanren 
+implementation but limited to unification constraints ($\equiv$).
 
@@
 
-\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more efficient? It shouldn't be?}
+\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more efficient? It shouldn't be}
 
@@
 The new type is a pair whose \texttt{car} is a list of answers (the bag), and 
-whose \texttt{cdr} is either a \texttt{\#{}f} or a thunk returning a search 
+whose \texttt{cdr} is either \texttt{\#{}f} or a thunk returning a search 
 space. A falsy \texttt{cdr} means the search space is obviously finite.
@@
 some 
-answers, \texttt{ks} is called with the first answer and the rest space. 
+answers, \texttt{ks} is called with the first answer and the rest of the space. 
 Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
 `succeed' and `fail' respectively. This function is like an eliminator of 
-search space, hence the name. The remaining functions do the same thing as 
+search spaces, hence the name. The remaining functions do the same thing as 
 before.
@@
 
-In this section, we compare the pure subset of \BFSopt{} with the BFS 
-found in \citet{seres1999algebra}. We focus on the pure subset because 
-their system is pure. Their system represents search spaces with streams of 
+In this section, we compare the pure subset of \BFSopt{} with the 
+\BFSser{}. We focus on the pure subset because \BFSser{} is pure.
+and represents search spaces with streams of 
 lists of answers, where each list is a bag.
 
-To compare efficiency, we translate their Haskell code into Racket (See 
-supplements for the translated code). The translation is direct 
+To compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See supplements for the translated code). The translation is direct 
 due to the similarity in both logic programming systems and search space 
-representations. The translated code is longer and slower than BFSopt
-implementation. Details about 
-difference in efficiency are in section 7.
+representations. The translated code is longer and slower than \BFSopt{}'s implementation. Details about 
+differences in efficiency are in the table below.
 
-We prove in Coq that \BFSser{} and \BFSopt{} are semantically equivalent, i.e. \texttt{(run n ? g)} 
+We use Coq to show that \BFSser{} and \BFSopt{} are 
+semantically equivalent, (i.e., \texttt{(run n ? g)} 
 produces the same result (See supplements for the formal proof).
@@
 		\hline
-		\veryrecursiveo{} & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
+		very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
 		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
@@
 		\hline 
-		\appendo{}  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
+		appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
 		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
@@
 		\hline 
-		\reverso{} & 10 &   5 &   3 &   3 &     38 &     85 \\ 
+		reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
 		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
@@
 memory.'' The first two benchmarks are taken from 
-TRS2. \reverso{} is from 
+TRS2. \texttt{reverso} is from 
 \citet{rozplokhas2018improving}. The next two benchmarks 
@@
 \texttt{absent$^o$}). Our version generates de 
-Bruijnized expressions and prevent closures getting into list. The two 
+Bruijnized expressions and prevents closures from being inside a list. The two 
 benchmarks differ in the \conde{} clause order of their relational 
@@
 
+\NOTE[DPF]{Below, veryrecursiveo (if possible, should have its o raised.)
+One way to do this is to have a different macro.  In the table there are
+other occurrences that need their names with a different macro.}
+
 In general, only DFS$_\textrm{i}$ and DFS$_\textrm{bi}$ constantly perform well. DFS$_\textrm{f}$ is just as 
-efficient in all benchmarks but \veryrecursiveo{}. Both BFS have obvious 
+efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
 overhead in many cases. Among the three variants of DFS (they all have unfair 
@@
 better. Interestingly, every strategy with fair \disj{} suffers in 
-\veryrecursiveo{} and DFS$_\textrm{f}$ performs well elsewhere. 
+\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
 Therefore, this 
 benchmark might be a special case. Fair \conj{} imposes considerable overhead 
-constantly except in \appendo{}. The reason might be that strategies with 
+constantly except in \texttt{appendo}. The reason might be that strategies with 
 fair \conj{} tend to keep more intermediate answers in the memory.
@@
 
-Yang \citet{yang2010adventures} points out a disjunct complex would be `fair' 
-if it were a full and balanced tree .
+\citet{yang2010adventures} points out a disjunct complex would be `fair' 
+if it were a full and balanced tree.
 
-Seres et al \citet{seres1999algebra} also describe a breadth-first search 
-strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But our codeis shorter and performs better in comparison with a straightforward 
-translation of their Haskell code.
+\citet{seres1999algebra} also describe a breadth-first search 
+strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But,
+The implementation of \BFSopt is shorter and performs better in comparison with a straightforward translation of their Haskell code.
 
@@
 alternatives to DFS$_\textrm{i}$, the current search strategy, and that 
-\BFSopt is less practical than other search strategies.
-\NOTE[DPF]{what}
-\NOTE[LKC]{fixed}
+\BFSopt is less practical than 
+\NOTE[DPF]{what?}
 
-We prove that \BFSopt{} is equivalent to \BFSser in \citet{seres1999algebra}. 
+We prove that \BFSopt{} is equivalent to \BFSser. 
 Our optimized code is shorter and runs faster than a direct translation 
 of their Haskell code.
+
+% We acknowledge that we are making large claims about efficiency given
+% that we have just a few benchmarks, but our intuition is based on
+% sound principles.
+
+\NOTE[DPF]{Finish this paragraph with a clarification and you may
+place this anywhere in the conclusion. This may require some consultation with Weixi.}
 

### 2019-05-22 Paper/paper.tex
lots of corrections

@@
 
-%% scheme-list :
-\usepackage{listings}
 \usepackage{color}
 \usepackage{textcomp}
+\usepackage{hyperref}
+
 \usepackage{trackchanges}
@@
 
+\usepackage{listings}
 \lstset{
@@
   		   {repeato}{{repeat$^o$}}{6}
+  		   {g0}{{g$_0$}}{2}
+  		   {g1}{{g$_1$}}{2}
+  		   {g2}{{g$_2$}}{2}
+  		   {gl}{{g$_l$}}{2}
+  		   {gr}{{g$_r$}}{2}
+  		   {DFSi }{{DFS$_i$}}{3}
+  		   {DFSbi}{{DFS$_{bi}$}}{3}
+  		   {DFSf }{{DFS$_f$}}{3}
+  		   {BFSser}{{BFS$_{ser}$}}{3}
 }
@@
 }
+
+\newcommand{\veryrecursiveo}{\texttt{very-recursive$^o$}}
+\newcommand{\appendo}{\texttt{append$^o$}}
+\newcommand{\reverso}{\texttt{revers$^o$}}
+
 \newcommand{\DFSi }[0]{DFS$_\textrm{i}$}
@@
 \newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
-\newcommand{\BFS  }[0]{BFS}
+\newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
 
-\newcommand{\BFSopt}[0]{BFS$_\textrm{opt}$}
-
-\newcommand{\BFSeff}[0]{BFS$_\textrm{eff}$}
-
-\newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
 \newtheorem{defn}{Definition}[section]
@@
 \DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
-  and that \BFSopt{} is more efficient than the standard \BFSser.
+and that our \BFSser{} implementation is more efficient than the current one.
 
-% The syntax of a programming language should reflect its semantics. When writing 
+% The syntax of a programming language should reflect its semantics. When 
+%writing 
 % a \conde{} expression in miniKanren, a programmer would expect all clauses 
@@
 %
-% \NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}
-
-%The syntax of a programming language should reflect its semantics. When using 
-%a disjunctive operator in relational programming, a programmer would expect 
-%all 
-%sub-goals of this disjunct to share the same chance of being explored, as 
-%these 
-%clauses are written in parallel. The existing multi-arity disjunctive operator 
-%in miniKanren, however, prioritize its clauses by the order of which these 
-%clauses are written down. We have devised two new search strategies that 
-%allocate computational effort more fairly in all clauses.
 
@@
 miniKanren is a family of relational programming languages.
-\citet{friedman_reasoned_2018} introduce miniKanren and its
-implementation in \emph{The Reasoned Schemer, 2nd Ed}
-(TRS2). miniKanren programs, have been proven to be useful in solving 
-many problems as in miniKanren.org.\citet{byrd2017unified}.
+\citep{Friedman:2005:RS:1121583} \citet{friedman_reasoned_2018} introduce 
+miniKanren and its
+implementation in \emph{The Reason Schemer} 
+and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
+proved that miniKanren programs are useful in solving many problems as in 
+miniKanren.org.
 
@@
 should not come up until the Introduction.}
-
-\NOTE[DPF]{We should reference the earliest paper (See Will Byrd vita)}
+\NOTE[LKC]{Do you mean they should not come up in Abstract?}
 
@@
 or \emph{unproductive}.}
+\NOTE[LKC]{I have added a sentence at the place where we define
+completeness.}
 
-\NOTE[LKC]{Shall we delete the sentence about relational interpreters? It is 
-misleading: it is emphasizing relational interpreters, but we say nothing 
-further about them later.}
-\NOTE[DPF]{I have deleted the sentence.}
 % \conde{} is the flagship disjunction operator in miniKanren.
@@
 There is another reason that miniKanren could use more search strategies than
-just \DFSi. In many applications, there does not exist one order that serves all purposes. For example, a relational dependent type checker contains
+just \DFSi. In many applications, there does not exist one order that serves all
+purposes. For example, a relational dependent type checker contains
 clauses for constructors that build data and clauses for eliminators that use
-data. When the type checker is used to generate simple and shallow programs,
-the clauses for constructors should be put at the top of the
-\conde{} clauses.
+data. When the type checker is generating simple and shallow programs,
+the clauses for constructors had better be at the top of the
+\conde{} expression.
 When performing proof searches for complicated programs, the clauses for 
-eliminators should be put at the top of \conde{} clauses. With \DFSi, these two uses cannot be 
-efficient at the same time. In fact, to make one use efficient, the other one 
-must be more sluggish.
+eliminators had better be at the top of the \conde{} expression. With \DFSi, 
+these two uses cannot be efficient at the same time. In fact, to make one use 
+efficient, the other one must be more sluggish.
 
-The specification that every clause in the same \conde{} is given equal 
-``search priority'' is called fair \disj{}. And search strategies with 
+The specification that gives every clause in the same \conde{} equal 
+``search priority'' is fair \disj{}. And search strategies with 
 almost-fair \disj{} give every clause similar priority. 
-Fair \conj{}, a related concept, is more subtle. The discussion of fair
-\conj{} is covered in the next section.
+Fair \conj{}, a related concept, is more subtle. We cover it in the next 
+section.
 
@@
 	new search strategy with fair \disj{}.
-	\item implement in a new way breath-first search (\BFSopt), 
-        a search strategy 
-	with fair \disj{} and fair \conj{}. And we prove formally that our 
-\BFSopt{} implementation is semantically equivalent to \BFSser
-however, Our code runs faster in all benchmarks and we believe it is simpler.
+	\item implement in a new way breath-first search (\BFSser), a search 
+strategy with fair \disj{} and fair \conj{}. And we prove formally that our 
+\BFSser{} implementation is semantically equivalent to \BFSser{}.
+Our code runs faster in all benchmarks and we believe it is simpler.
 \end{itemize}
@@
 A \emph{state} is a collection of constraints. (Here, we restrict 
-constraints to unification constraints. Every answer corresponds to a 
+constraints to unification constraints.) Every answer corresponds to a 
 state. A space is a collection of states. And a \emph{goal} is a 
@@
 
-% Goals check their input states and outputs possibly extended states. A goal 
+% Goals check their input states and outpust possibly extended states. A goal 
 % might fail for some inputs, in which case the output search space would be 
@@
 Running the same program again with almost-fair \disj {} (e.g. 
-DFS$_\textrm{bi}$) gives the same result. Almost-fair, however, is not 
+\DFSbi{}) gives the same result. Almost-fair, however, is not 
 completely fair, as shown by the following example.
@@
 \DFSbi{} is fair only when the number of goals is a power of 2, 
-otherwise, some goals would be allocated twice as many resources than the 
-others. In the above example, where the \conde{} has five clauses, the clauses 
-of \texttt{b}, \texttt{c}, and \texttt{d} are allocated more resources.
+otherwise, it allocates some goals twice as many resources as the 
+others. In the above example, where the \conde{} has five clauses, \DFSbi{} 
+allocates more resources to the clauses of \texttt{b}, \texttt{c}, and 
+\texttt{d}.
 
@@
 A \disj{} is almost-fair if and only if it allocates computational resources
-evenly to search spaces produced by goals in the same disjunction that 
+so evenly to search spaces produced by goals in the same disjunction that 
 the maximal ratio of resources is bounded by a constant.
 \end{defn}
+
+\NOTE[LKC]{I might be wrong, but `\emph{so} evenly ... that the maximal ...' 
+looks more natural to me}
 
@@
 \subsection{fair \texttt{conj}}
+\label{sec:fairconj}
 
-\NOTE[LKC]{Checked grammer of text before this line}
+\NOTE[LKC]{I change `1/4 in the answer' to `1/4 in the answer list'. }
 
 Given the following program, it is natural to expect lists of each letter to
-constitute $1/4$ in the answer. Search strategies with unfair \conj{} (e.g. 
+constitute $1/4$ in the answer list. Search strategies with unfair \conj{} 
+(e.g. 
 \DFSi, \DFSbi, \DFSf), however, results in many more lists of \texttt{a}s than 
@@
 be exacerbated if \conde{} were to contain more clauses.
-
-\NOTE[LKC]{Should I add a footnote?}
-
-``
-Although 
-DFS$_\textrm{i}$'s \disj{} is unfair in general, it is fair when there is no 
-call to a relational definition 
-in \conde{} clauses (including this case).
+Although some strategies have different level of fairness in \disj{}, they 
+have the same behavior when there is no call to a relational definition in 
+\conde{} clauses (including this case).
 
@@
 \conj{}. The \conde{} goal outputs a search space including four trivially 
-different states. Then the next conjunctive goal, \texttt{(repeato x q)}, is 
-applied to each of these states, producing four trivially different search 
-spaces. In the examples above, the \conj{}s are allocating more computational 
+different states. 
+Applying the next conjunctive goal, \texttt{(repeato x q)}, produces four 
+trivially different search spaces.
+In the examples above, all search strategies allocate more computational 
 resources to the search space of \texttt{a}. On the contrary, fair \conj{} 
@@
 A more interesting situation is when the first conjunct produces an unbounded
-number of states. Consider the following example, a naive specification of fair \conj{} 
-might require search strategies to produce all sorts of singleton lists, but there
-would not be any lists of length two or longer, which makes the strategies incomplete. 
-A search strategy is \emph{complete} if and only if it can determine all the answers within finite 
-time, otherwise, it is \emph{incomplete}.
+number of states. Consider the following example, a naive specification of 
+fair \conj{} 
+might require search strategies to produce all sorts of singleton lists, but 
+there
+would not be any lists of length two or longer, which makes the strategies 
+incomplete. 
+A search strategy is \emph{complete} if and only if ``every correct answer 
+would be discovered after some finite time'' \cite{seres1999algebra}, 
+otherwise, it is \emph{incomplete}. In the 
+context of miniKanren, a search strategy is complete means that every correct 
+answer has a positition in large enough answer lists.
 
-\NOTE[DPF]{Does this assume that we never use run*, since in fact, the paper does not
-include and uses of run*.  Something should be mentioned around here.}
+\NOTE[DPF]{Does this assume that we never use run*, since in fact, the paper 
+does not include and uses of run*.  Something should be mentioned around here.}
+\NOTE[LKC]{We never use run* in this paper because fairness is only 
+interested when we have an unbounded number of answers. However, it is 
+perfectly fine to use run* with any search strategies.}
 
@@
 resources carefully among search spaces related to different bags such
-that answers are produced in increasing order of cost. The \emph{cost}
+that it produces answers in increasing order of cost. The \emph{cost}
 of an answer is its depth in the search tree (i.e., the number of
@@
 fairness.
-
-% Our definition of fair \conj{} is orthogonal with completeness. For 
-% example, a naively fair strategy is fair but not complete, while BFS is fair and 
-% complete.
 
@@
 search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
-chapter 10 and the appendix, ``Connecting the wires,'' 
+chapter 10 and the appendix, ``Connecting the wires'', 
 provides a comprehensive description of the 
@@
 
-\NOTE[DPF]{If we use the name subscript, the subscripts should use an underscore and we should do it for gunderscorel and gundescorer. If we can use an l that
-looks less like a 1, that would even be better.  Look at the l in TLT.}
+\NOTE[DPF]{If we use the name subscript, the subscripts should use an 
+underscore and we should do it for gunderscorel and gundescorer. If we can use 
+an l that looks less like a 1, that would even be better.  Look at the l in 
+TLT.}
+\NOTE[LKC]{I have turned those `subscripts' to real subscripts.}
 
@@
 with other search 
-strategies. We follow some conventions to name variables: variables bound to 
-states are named \texttt{s}; variables bound to goals are named \texttt{g} 
-(possibly with subscript); variables bound to search spaces have names ending 
-with $^\infty$. Fig.~\ref{DFSi-0} shows the implementation of \disj. The 
+strategies. We follow some conventions to name variables: \texttt{s}s name 
+states; \texttt{g}s (possibly with subscript) name goals; 
+variables ending with $^\infty$ name search spaces. Fig.~\ref{DFSi-0} shows the 
+implementation of \disj. The 
 first function, \texttt{disj2}, implements binary disjunction. It applies the 
@@
 It applies the \emph{first} goal to the input state, then applies the second 
-goal to states in the resulting search space. The latter process is done with a 
-the helper function \texttt{append-map$^\infty$} that applies its input goal to states 
+goal to states in the resulting search space. The helper function 
+\texttt{append-map$^\infty$} applies its input goal to states 
 in its input search spaces and composes the resulting search spaces. It reuses 
@@
 
-Balanced interleaving DFS (DFS$_\textrm{bi}$) has an almost-fair \disj{} and unfair 
-\conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
-DFS$_\textrm{i}$'s in the \disj{} macro. We list the new \disj{} with its 
+Balanced interleaving DFS (\DFSbi{}) has an almost-fair \disj{} and unfair 
+\conj{}. The implementation of \DFSbi{} differs from 
+\DFSi{}'s in the \disj{} macro. We list the new \disj{} with its 
 helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
@@
 goal itself. When there are more goals, we partition the list of goals 
-into two sublists of roughly equal lengths and recur on the two sublists. Goals 
-are moved to the accumulators in the last clause. As we are moving 
+into two sublists of roughly equal lengths and recur on the two sublists. We 
+move goals to the accumulators in the last clause. As we are moving 
 two goals each time, there are two base cases: (1) no goal remains; (2) one 
-goal remains. These two new base cases are handled in the second clause and the 
+goal remains. We handle these two new base cases in the second clause and the 
 third clause, respectively. In contrast, the \disj{} in \DFSi{} constructs the 
@@
 
-\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more efficient? It shouldn't be}
+\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more 
+efficient? It shouldn't be}
+\NOTE[LKC]{I did for efficiency. I have re-ordered two cases back.}
 
@@
 implementation of \DFSf{} differs from \DFSi{}'s in 
-\texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is changed to call a new and 
+\texttt{disj2} (Fig.~\ref{fDFS}). The new \texttt{disj2} calls a new and 
 fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
@@
 its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
-\texttt{\#{}t}, which indicates that 
-\texttt{s$^\infty$} and \texttt{t$^\infty$} haven't been swapped. The swapping 
+\texttt{\#{}t}, which indicates that we haven't swapped
+\texttt{s$^\infty$} and \texttt{t$^\infty$}. The swapping 
 happens at 
@@
 fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
-\texttt{t$^\infty$} are ended with a thunk and they have been swapped. In this 
-case, a new thunk is constructed. Here changing the order of 
-\texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
-changes the order of answers). We swap them back so that answers are 
-produced in a more natural order.
+\texttt{t$^\infty$} are ended with a thunk and we have swapped them. In this 
+case, we construct a new thunk. The new thunk swaps two spaces back in the
+recursive call. This is unnecessary for fairness. We do it to produce answers 
+in a more natural order.
 
 \NOTE[DPF]{When or where do you swap them back?}
+\NOTE[LKC]{In the recursion}
 
@@
 
-\BFSser{} has both fair \disj{} and fair \conj{}. Our implementation is based on 
-DFS$_\textrm{f}$ (not DFS$_\textrm{i}$). To implement \BFSopt{} based on \DFSf{}, 
+\BFSser{} has both fair \disj{} and fair \conj{}. Our implementation is based 
+on \DFSf{} (not \DFSi{}). To implement \BFSser{} based on \DFSf{}, 
 we need \texttt{append-map$^\infty_{fair}$} in addition to 
@@
 
-The implementation can be improved in two ways. First, as mentioned in 
-section 2.2, \BFSser puts answers in bags and answers of the same cost are in the 
+The implementation is improvable in two ways. First, as mentioned in 
+\autoref{sec:fairconj}, \BFSser{} puts answers in bags and answers of the same 
+cost are in the 
 same bag. In this implementation, however, it is unclear where this information 
@@
 
-Both \BFSser{} \citet{seres1999algebra} and BFSopt{} produce answers in 
-increasing order of cost. So it is interesting to see if they are equivalent. 
-We prove so in Coq. The details are in the second subsection.
+%Both \BFSser{} \citet{seres1999algebra} and \BFSopt{} produce answers in 
+%increasing order of cost. So it is interesting to see if they are equivalent. 
+%We prove so in Coq. The details are in the second subsection.
+
+We prove formally our implementation is equivalent to the original one by 
+\citet{seres1999algebra}. The details are in the second subsection.
 
@@
 stick another label where the subsection starts.
-Then ref the two labels and place a period between them.}.
+Then ref the two labels and place a period between them.}
+\NOTE[LKC]{Got it! Fixed}
 
-As mentioned in section 2.2, BFS puts answers in bags and answers of the 
+As mentioned in \autoref{sec:fairconj}, BFS puts answers in bags and 
+answers of the 
 same cost are in the same bag. The cost
 information is recorded subtly -- the \texttt{car}s of a search space have cost 
-0 (i.e. they are all in the same bag), and the costs of answers in thunk are 
-computed recursively then increased by one. It is even more subtle that
+0 (i.e. they are all in the same bag), and every thunk indicates an increment 
+in cost. It is even more subtle that
 \texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
@@
 
-Functions related to the pure subset are listed in Fig.~\ref{BFS-opt} (the 
-others in Fig.~\ref{BFS-opt-cont}). They are compared with 
+We list functions related to the pure subset in Fig.~\ref{BFS-opt} (the 
+others in Fig.~\ref{BFS-opt-cont}). We compare these functions with 
 \citeauthor{seres1999algebra}'s implementation in our proof. The first three 
@@
 \citet{kiselyov2005backtracking} has shown that a \emph{MonadPlus} hides in 
-implementations of logic programming system. The \BFSopt{} implementation is not 
-an exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
+implementations of logic programming system. Our \BFSser{} implementation is 
+not an exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
 but takes arguments in reversed order; \texttt{none}, \texttt{unit}, and 
@@
 some 
-answers, \texttt{ks} is called with the first answer and the rest of the space. 
-Otherwise, \texttt{kf} is called with no argument. Here `s' and `f' means 
-`succeed' and `fail' respectively. This function is like an eliminator of 
+answers, it calls \texttt{ks} with the first answer and the rest of the space. 
+Otherwise, it calls \texttt{kf} with no argument. Here `s' and `f' means 
+`succeed' and `fail' respectively. This function is similar to an eliminator of 
 search spaces, hence the name. The remaining functions do the same thing as 
@@
 
-\subsection{comparison with the BFSser and BFSopt}
+\subsection{compare our implementation with the original one}
 
-In this section, we compare the pure subset of \BFSopt{} with the 
-\BFSser{}. We focus on the pure subset because \BFSser{} is pure.
-and represents search spaces with streams of 
+In this section, we compare the pure subset of our implementation with the 
+original one. We focus on the pure subset because the original system is pure.
+\citeauthor{seres1999algebra} represent search spaces with streams of 
 lists of answers, where each list is a bag.
@@
 due to the similarity in both logic programming systems and search space 
-representations. The translated code is longer and slower than \BFSopt{}'s implementation. Details about 
-differences in efficiency are in the table below.
+representations. The translated code is longer and slower than our 
+implementation. Details about differences in efficiency are in the table below.
 
-We use Coq to show that \BFSser{} and \BFSopt{} are 
+We use Coq to show that the two implementations are 
 semantically equivalent, (i.e., \texttt{(run n ? g)} 
@@
 		\hline 
-		benchmark & size & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & BFS$_\textrm{opt}$ & BFS$_\textrm{ser}$  
+		benchmark & size & \DFSi{} & \DFSbi{} & \DFSf{} & 
+		our \BFSser{} & original \BFSser{}  
 		\\
 		\hline
-		very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
+		\veryrecursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
 		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
@@
 		\hline 
-		appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
+		\appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
 		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
@@
 		\hline 
-		reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
+		\reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
 		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
@@
 description is in Table~\ref{compare-efficiency}. A hyphen means ``running out of 
-memory.'' The first two benchmarks are taken from 
+memory.'' The first two benchmarks are from 
 TRS2. \texttt{reverso} is from 
@@
 has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
-end, while the other has them at the beginning. We conjecture that DFS$_\textrm{i}$ would 
+end, while the other has them at the beginning. We conjecture that \DFSi{} 
+would 
 perform badly in the second case because elimination rules complicate the 
@@
 other occurrences that need their names with a different macro.}
+\NOTE[LKC]{Fixed}
 
-In general, only DFS$_\textrm{i}$ and DFS$_\textrm{bi}$ constantly perform well. DFS$_\textrm{f}$ is just as 
-efficient in all benchmarks but \texttt{very-recursiveo}. Both BFS have obvious 
+In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} 
+is just as 
+efficient in all benchmarks but \veryrecursiveo. Both BFS have obvious 
 overhead in many cases. Among the three variants of DFS (they all have unfair 
-\conj{}), DFS$_\textrm{f}$ is most resistant to clause permutation, followed by DFS$_\textrm{bi}$ then 
-DFS$_\textrm{i}$. Among the two implementation of BFS, ours constantly performs as well or 
+\conj{}), \DFSf{} is most resistant to clause permutation, followed by 
+\DFSbi{} then 
+\DFSi{}. Among the two implementation of BFS, ours constantly performs as well 
+or 
 better. Interestingly, every strategy with fair \disj{} suffers in 
-\texttt{very-recursiveo} and DFS$_\textrm{f}$ performs well elsewhere. 
+\veryrecursiveo and \DFSf{} performs well elsewhere. 
 Therefore, this 
@@
 
-\citet{seres1999algebra} also describe a breadth-first search 
-strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But,
-The implementation of \BFSopt is shorter and performs better in comparison with a straightforward translation of their Haskell code.
+\citet{seres1999algebra} describe a breadth-first search 
+strategy. We present another implementation. Our implementation is semantically 
+equivalent to theirs. But, ours is shorter and performs better in comparison 
+with a straightforward translation of their Haskell code.
+
+%\citet{seres1999algebra} also describe a breadth-first search 
+%strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But,
+%The implementation of \BFSopt is shorter and performs better in comparison 
+%with a straightforward translation of their Haskell code.
 
@@
 We devise two new search strategies (i.e. balanced interleaving DFS 
-(DFS$_\textrm{bi}$) and fair DFS (DFS$_\textrm{f}$)) and devise a new 
+(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
 implementation of BFS. These strategies have different features 
 in fairness: $_\textrm{bi}$ has an almost-fair \disj{} and unfair \conj{}. 
-DFS$_\textrm{f}$ has fair \disj{} and unfair \conj{}. \BFSopt{} has both fair
+\DFSf{} has fair \disj{} and unfair \conj{}. \BFSser{} has both fair
 \disj{} and fair \conj{}.
 
-Our quantitative evaluation shows that DFS$_\textrm{bi}$ and DFS$_\textrm{f}$ are competitive 
-alternatives to DFS$_\textrm{i}$, the current search strategy, and that 
-\BFSopt is less practical than 
+Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are 
+competitive 
+alternatives to \DFSi{}, the current search strategy, and that 
+\BFSser{} is less practical than other strategies.
 \NOTE[DPF]{what?}
+\NOTE[LKC]{other search strategies}
 
-We prove that \BFSopt{} is equivalent to \BFSser. 
-Our optimized code is shorter and runs faster than a direct translation 
-of their Haskell code.
+We present another implementation of \BFSser. Our implementation is 
+semantically equivalent to the original one. But, ours is shorter and performs 
+better in comparison with a straightforward translation of their Haskell code.
+
+%We prove that \BFSopt{} is equivalent to \BFSser. 
+%Our optimized code is shorter and runs faster than a direct translation 
+%of their Haskell code.
 
@@
 \NOTE[DPF]{Finish this paragraph with a clarification and you may
-place this anywhere in the conclusion. This may require some consultation with Weixi.}
+place this anywhere in the conclusion. This may require some consultation with 
+Weixi.}
+\NOTE[LKC]{I will do it later.}
 

### 2019-05-23 Paper/paper.tex
Too many changes to worry about.

@@
   		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
+                   {appendo}{{append$^o$}}{6}
   		   {repeato}{{repeat$^o$}}{6}
@@
 miniKanren and its
-implementation in \emph{The Reason Schemer} 
+implementation in \emph{The Reasoned Schemer} 
 and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
-proved that miniKanren programs are useful in solving many problems as in 
-miniKanren.org.
+demonstrated that miniKanren programs are useful in solving several problems.
+miniKanren.org contains the seeds of many more problems and their solutions.
 
-% miniKanren is a family of relational programming languages.
-% \citet{friedman_reasoned_2018} introduce miniKanren and its implementation
-% in \emph{The Reasoned Schemer, 2nd Ed} (TRS2). miniKanren programs, especially
-% relational interpreters, have been proven to be useful in solving many problems 
-% as in \citet{byrd2017unified}.
+\NOTE[DPF]{Yes, that is what I mean. And furthermore, I think that changing opt
+to imp (for improved) makes more sense.  We may be optimizing, but it seems more
+like an improvement.  I did change some of them from optimized to improved.
+In my letter wrt to using
+BFSopt or BFSimp, it still makes more sense to me.  Perhaps it should be part
+of the title that we have improved on the the standard BFS implementation.}
+\NOTE[LKC]{Do you mean they should not come up in Abstract?}
+\NOTE[DPF]{When you rewrite the abstract and drop the abbreviations, remember when
+you are rewriting the Introduction and introducing the abbreviations, that you should
+explain the ser of BFSser using a reference.}
 
-\NOTE[DPF]{I think that the abbreviations for the search strategies
-should not come up until the Introduction.}
-\NOTE[LKC]{Do you mean they should not come up in Abstract?}
-
-\NOTE[DPF]{When we talk about complete and incomplete, I think we should
-make it explicit that we are only talking about (run n (x y z) g ...) and
-not (run* (x y z) g ...), but an alternative is that a stream is \emph{productive}
-or \emph{unproductive}.}
-\NOTE[LKC]{I have added a sentence at the place where we define
-completeness.}
-
-% \conde{} is the flagship disjunction operator in miniKanren.
 A subtlety arises 
 when a \conde{} contains many clauses: not every clause has an 
-equal chance to contribute to the result. As an example, consider the following 
+equal chance of contributing to the result. As an example, consider the following 
 relation \texttt{repeato} and its invocation.
@@
 
-The \conde{} in TR2, however, generates a less expected result.
+The \conde{} in TRS2, however, generates a less expected result.
 
@@
 
-To summarize our contribution, we
+To summarize our contributions, we
 \begin{itemize}
@@
 Before going further into fairness, we give a short review of the terms:
-\emph{state}, search \emph{space}, \emph{goal}.
+\emph{state}, search \emph{space}, and \emph{goal}.
 A \emph{state} is a collection of constraints. (Here, we restrict 
@@
 of other letters. And some letters  (e.g. \texttt{c} and \texttt{d}) are
-rarely seen. The situation would be exacerbated if \conde{} would have
+rarely seen. The situation would be exacerbated if the \conde{} would have
 contained more clauses.
@@
 
-\NOTE[LKC]{I might be wrong, but `\emph{so} evenly ... that the maximal ...' 
-looks more natural to me}
-
 \begin{defn}[unfair \disj{}]
@@
 be exacerbated if \conde{} were to contain more clauses.
-Although some strategies have different level of fairness in \disj{}, they 
+Although some strategies have a different level of fairness in \disj{}, they 
 have the same behavior when there is no call to a relational definition in 
@@
 context of miniKanren, a search strategy is complete means that every correct 
-answer has a positition in large enough answer lists.
+answer has a position in large enough answer lists.
 
-\NOTE[DPF]{Does this assume that we never use run*, since in fact, the paper 
-does not include and uses of run*.  Something should be mentioned around here.}
+\NOTE[DPF]{I think that should be said as directly as in your note.}
 \NOTE[LKC]{We never use run* in this paper because fairness is only 
-interested when we have an unbounded number of answers. However, it is 
+interesting when we have an unbounded number of answers. However, it is 
 perfectly fine to use run* with any search strategies.}
@@
 to the length of its inner list plus the length of its outer list.
+
+\NOTE[DPF]{Next to the last line of the above paragraph the word same
+has too many meanings.  It could be have the same cost or it could be
+failing to distinguish two list that would be the same if we substituted
+a b for an a.  It needs to be clarified.  It might help to work out
+the actual numbers}
 
@@
 
-\NOTE[DPF]{If we use the name subscript, the subscripts should use an 
-underscore and we should do it for gunderscorel and gundescorer. If we can use 
-an l that looks less like a 1, that would even be better.  Look at the l in 
-TLT.}
+\NOTE[DPF]{This came out fabulous.  I think I spotted some missed opportunities
+later, which I will point out with additional notes.}
 \NOTE[LKC]{I have turned those `subscripts' to real subscripts.}
@@
 
-\NOTE[DPF]{Why does the pair? case precede the null? case? Is it simply more 
-efficient? It shouldn't be}
-\NOTE[LKC]{I did for efficiency. I have re-ordered two cases back.}
-
 \begin{figure}
@@
 
-\NOTE[DPF]{When or where do you swap them back?}
+\NOTE[DPF]{When or where do you swap them back? This could be still clearer.}
 \NOTE[LKC]{In the recursion}
@@
 
-\subsection{optimized BFS}
+\subsection{improved BFS}
 
@@
 
-\NOTE[DPF]{Never refer to a literal section like 2.2. Instead
-stick a label where it starts right near the section number and
-stick another label where the subsection starts.
-Then ref the two labels and place a period between them.}
-\NOTE[LKC]{Got it! Fixed}
-
-As mentioned in \autoref{sec:fairconj}, BFS puts answers in bags and 
+As mentioned in \autoref{sec:fairconj}, \BFSser{} puts answers in bags and 
 answers of the 
 same cost are in the same bag. The cost
-information is recorded subtly -- the \texttt{car}s of a search space have cost 
+information is recorded subtly---the \texttt{car}s of a search space have cost 
 0 (i.e. they are all in the same bag), and every thunk indicates an increment 
@@
 makes an empty search space; \texttt{unit} makes a space from one answer; and 
-\texttt{step} makes a space from a thunk. The remaining functions as before.
+\texttt{step} makes a space from a thunk. The remaining functions are as before.
 
@@
 
-\citet{kiselyov2005backtracking} has shown that a \emph{MonadPlus} hides in 
+\citet{kiselyov2005backtracking} have shown that a \emph{MonadPlus} hides in 
 implementations of logic programming system. Our \BFSser{} implementation is 
@@
 \texttt{append$^\infty_{fair}$} correspond to \texttt{mzero}, \texttt{unit}, 
-and \texttt{mplus} respectively.
+and \texttt{mplus}, respectively.
 
@@
 	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
-	\caption{new and changed functions in optimized BFS that implements impure 
+	\caption{new and changed functions in improved BFS that implement impure 
 		features}
@@
 answers, it calls \texttt{ks} with the first answer and the rest of the space. 
-Otherwise, it calls \texttt{kf} with no argument. Here `s' and `f' means 
-`succeed' and `fail' respectively. This function is similar to an eliminator of 
-search spaces, hence the name. The remaining functions do the same thing as 
-before.
+Otherwise, it calls \texttt{kf} with no argument. Here `s' means
+`succeed' and `f' means `fail'. This function is similar to an eliminator of 
+search spaces, hence the name. The remaining functions are as before.
 
@@
 
-\NOTE[DPF]{Below, veryrecursiveo (if possible, should have its o raised.)
-One way to do this is to have a different macro.  In the table there are
-other occurrences that need their names with a different macro.}
-\NOTE[LKC]{Fixed}
-
 In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} 
 is just as 
-efficient in all benchmarks but \veryrecursiveo. Both BFS have obvious 
-overhead in many cases. Among the three variants of DFS (they all have unfair 
-\conj{}), \DFSf{} is most resistant to clause permutation, followed by 
+efficient in all benchmarks but \veryrecursiveo. Both implementations of BFS have obvious 
+overhead in many cases. Among the three variants of DFS, which all all have unfair \conj{}),
+\DFSf{} is most resistant to clause permutation, followed by 
 \DFSbi{} then 
-\DFSi{}. Among the two implementation of BFS, ours constantly performs as well 
+\DFSi{}. Among the two implementation of BFS, our improved \BFSser{} constantly performs as well 
 or 
 better. Interestingly, every strategy with fair \disj{} suffers in 
-\veryrecursiveo and \DFSf{} performs well elsewhere. 
+\veryrecursiveo{} and \DFSf{} performs well elsewhere. 
 Therefore, this 
 benchmark might be a special case. Fair \conj{} imposes considerable overhead 
-constantly except in \texttt{appendo}. The reason might be that strategies with 
+constantly except in \appendo. The reason might be that strategies with 
 fair \conj{} tend to keep more intermediate answers in the memory.
+
+\NOTE[DPF]{appendo is not raised, though I tried.}
 
@@
 
-\citet{yang2010adventures} points out a disjunct complex would be `fair' 
+\citet{yang2010adventures} points out that a disjunct complex would be `fair' 
 if it were a full and balanced tree.
@@
 implementation of BFS. These strategies have different features 
-in fairness: $_\textrm{bi}$ has an almost-fair \disj{} and unfair \conj{}. 
+in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
 \DFSf{} has fair \disj{} and unfair \conj{}. \BFSser{} has both fair
@@
 alternatives to \DFSi{}, the current search strategy, and that 
-\BFSser{} is less practical than other strategies.
-\NOTE[DPF]{what?}
+\BFSser{} is less practical than other breadth-first strategies.
+\NOTE[DPF]{I think what I have is okay, now.}
 \NOTE[LKC]{other search strategies}

### 2019-05-23 Paper/paper.tex
raise one reverso
have shown -> have demonstrated
eliminate abbrev. in Abstract; repeato -> repeat^o

@@
 \newcommand{\reverso}{\texttt{revers$^o$}}
+\newcommand{\repeato}{\texttt{repeat$^o$}}
 
@@
 be fair or unfair.  We compare the fairness level of four search
-strategies: the standard miniKanren interleaving depth-first search (\DFSi),
-the balanced interleaving depth-first search (\DFSbi), the fair depth-first
-search (\DFSf), and the standard breadth-first search (\BFSser).
-\DFSbi{} and \DFSf{} are new. And we present a new, more efficient
-and simpler implementation of \BFSser. Using quantitative evaluation, 
-we argue that
-\DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
-and that our \BFSser{} implementation is more efficient than the current one.
+strategies: the standard miniKanren interleaving depth-first search,
+the balanced interleaving depth-first search, the fair depth-first
+search, and the standard breadth-first search.
+The two non-standard depth-first searches are new. And we present a new, more 
+efficient and simpler implementation of the standard breadth-first search. Using 
+quantitative evaluation, we argue that the two new depth-first searches are 
+competitive alternatives to the standard one, 
+and that our standard breadth-first search implementation is more efficient than 
+the current one.
+
+% We describe fairness levels in disjunction and conjunction
+% implementations.  Specifically, a disjunction implementation can be
+% fair, almost-fair, or unfair. And a conjunction implementation can
+% be fair or unfair.  We compare the fairness level of four search
+% strategies: the standard miniKanren interleaving depth-first search (\DFSi),
+% the balanced interleaving depth-first search (\DFSbi), the fair depth-first
+% search (\DFSf), and the standard breadth-first search (\BFSser).
+% \DFSbi{} and \DFSf{} are new. And we present a new, more efficient
+% and simpler implementation of \BFSser. Using quantitative evaluation, 
+% we argue that
+% \DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
+% and that our \BFSser{} implementation is more efficient than the current one.
 
@@
 equal chance of contributing to the result. As an example, consider the following 
-relation \texttt{repeato} and its invocation.
+relation \repeato{} and its invocation.
 
@@
 
-Next, consider the following disjunction of invoking \texttt{repeato} with four 
+Next, consider the following disjunction of invoking \repeato{} with four 
 different letters.
@@
 
-Now we elaborate fairness by running more queries about \texttt{repeato}.
+Now we elaborate fairness by running more queries about \repeato{}.
 
@@
 
-Under the hood, the \conde{} and the call to \texttt{repeato} are connected by 
+Under the hood, the \conde{} and the call to \repeato{} are connected by 
 \conj{}. The \conde{} goal outputs a search space including four trivially 
@@
 
-\citet{kiselyov2005backtracking} have shown that a \emph{MonadPlus} hides in 
+\citet{kiselyov2005backtracking} have demonstrated that a \emph{MonadPlus} 
+hides in 
 implementations of logic programming system. Our \BFSser{} implementation is 
@@
 memory.'' The first two benchmarks are from 
-TRS2. \texttt{reverso} is from 
+TRS2. \reverso is from 
 \citet{rozplokhas2018improving}. The next two benchmarks 
@@
 \NOTE[DPF]{appendo is not raised, though I tried.}
+\NOTE[LKC]{Which appendo is not raised? I couldn't find one.}
 

### 2019-05-23 Paper/paper.tex
leading sentences

@@
   		   {gr}{{g$_r$}}{2}
-  		   {DFSi }{{DFS$_i$}}{3}
-  		   {DFSbi}{{DFS$_{bi}$}}{3}
-  		   {DFSf }{{DFS$_f$}}{3}
-  		   {BFSser}{{BFS$_{ser}$}}{3}
+  		   {DFSi }{{DFS$_\textrm{i}$}}{3}
+  		   {DFSbi}{{DFS$_\textrm{bi}$}}{3}
+  		   {DFSf }{{DFS$_\textrm{f}$}}{3}
 }
@@
 \newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
+\newcommand{\BFS}[0]{BFS}
 \newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
+\newcommand{\BFSimp}[0]{BFS$_\textrm{imp}$}
 
@@
 competitive alternatives to the standard one, 
-and that our standard breadth-first search implementation is more efficient than 
+and that our breadth-first search implementation is more efficient than 
 the current one.
@@
 \citep{Friedman:2005:RS:1121583} \citet{friedman_reasoned_2018} introduce 
-miniKanren and its
-implementation in \emph{The Reasoned Schemer} 
+miniKanren and its implementation in \emph{The Reasoned Schemer} 
 and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
@@
 
-\NOTE[DPF]{Yes, that is what I mean. And furthermore, I think that changing opt
-to imp (for improved) makes more sense.  We may be optimizing, but it seems more
-like an improvement.  I did change some of them from optimized to improved.
-In my letter wrt to using
-BFSopt or BFSimp, it still makes more sense to me.  Perhaps it should be part
-of the title that we have improved on the the standard BFS implementation.}
-\NOTE[LKC]{Do you mean they should not come up in Abstract?}
-\NOTE[DPF]{When you rewrite the abstract and drop the abbreviations, remember when
-you are rewriting the Introduction and introducing the abbreviations, that you should
-explain the ser of BFSser using a reference.}
+\NOTE[DPF]{... Perhaps it should be part of the title that we have improved on 
+the the standard BFS implementation.}
+\NOTE[DPF]{When you rewrite the abstract and drop the abbreviations, remember 
+when you are rewriting the Introduction and introducing the abbreviations, that 
+you should explain the ser of BFSser using a reference.}
+\NOTE[LKC]{I have rewritten the abstract and explain the `ser' in the ending 
+paragraph of introduction, where we list contributions.}
 
@@
 The miniKanren in TRS2 implements interleaving DFS (\DFSi), the cause of this 
-unexpected result. With this search strategy, each clause takes half 
+unexpected result. With this search strategy, each \conde{} clause takes half 
 of its received computational resources and passes the other half to its 
@@
 clauses than those uninteresting ones, and thus use computational resources 
-efficiently. A little miniKanrener, however, may beg to differ--understanding
-implementation details and fiddling with clause order is not the first
-priority of a beginner.
+efficiently.
 
+% A little miniKanrener, however, may beg to differ--understanding
+% implementation details and fiddling with clause order is not the first
+% priority of a beginner.
+
+\DFSi{} is not always the best choice. For instance, it might be less 
+desirable for little miniKanreners -- understanding implementation details and 
+fiddling with clause order is not their first priority. 
 There is another reason that miniKanren could use more search strategies than
@@
 \begin{itemize}
-	\item propose and implement balanced interleaving depth-first search 
-	(\DFSbi{}), a new search strategy with almost-fair \disj{}.
-	\item propose and implement fair depth-first search (\DFSf{}), a 
-	new search strategy with fair \disj{}.
-	\item implement in a new way breath-first search (\BFSser), a search 
-strategy with fair \disj{} and fair \conj{}. And we prove formally that our 
-\BFSser{} implementation is semantically equivalent to \BFSser{}.
-Our code runs faster in all benchmarks and we believe it is simpler.
+	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
+depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
+	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
+a new search strategy with fair \disj{}.
+	\item implement in a new way the standard breath-first search (\BFS), a 
+search strategy with fair \disj{} and fair \conj{}. We name the current 
+implementation by \citeauthor{seres1999algebra} as \BFSser{}, and our 
+new implementation as \BFSimp{}. We prove formally that they are semantically 
+equivalent. \BFSimp{}, however, runs faster in all benchmarks and is shorter, 
+thus being an \textbf{imp}rovement. 
 \end{itemize}
@@
 
-Now we elaborate fairness by running more queries about \repeato{}.
+\NOTE[LKC]{The following paragraph is extended to include an explanation on 
+\texttt{run*}}
+
+Now we elaborate fairness by running more queries about \repeato{}. We never use 
+\texttt{run*} in this paper because fairness is more interesting when we have 
+an unbounded number of answers. However, it is perfectly fine to use 
+\texttt{run*} with any search strategies.
 
@@
 \NOTE[DPF]{I think that should be said as directly as in your note.}
+\NOTE[LKC]{I state this fact at the beginning of this section.}
 \NOTE[LKC]{We never use run* in this paper because fairness is only 
@@
 
-\BFSser{} puts states of the same cost in the same bag, and allocates
+\BFS{} puts states of the same cost in the same bag, and allocates
 resources carefully among search spaces related to different bags such
@@
 the following example, every answer is a list of a list of symbols,
-where inner lists are the same. Here the cost of each answer is equal
-to the length of its inner list plus the length of its outer list.
+where inner lists in the same outer list are identical. Here the cost of each 
+answer is equal
+to the length of its inner list plus the length of its outer list. For example,
+the cost of \texttt{((a) (a))} is $1 + 2 = 3$.
 
@@
 the actual numbers}
+\NOTE[LKC]{I have rewritten the relevant sentences.}
 
@@
 
-In this section, we review the implementation of interleaving depth-first 
-search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
-chapter 10 and the appendix, ``Connecting the wires'', 
-provides a comprehensive description of the 
-miniKanren 
-implementation but limited to unification constraints ($\equiv$).
-
-\begin{figure}
-	\lstinputlisting{Figures/conde.rkt}
-	\caption{implementation of \conde}
-	\label{conde}
-\end{figure}
-
-The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
-strategies. It relates clauses disjunctively, and goals in the same 
-clause conjunctively.
-
 \begin{figure}
@@
 
-\NOTE[DPF]{This came out fabulous.  I think I spotted some missed opportunities
-later, which I will point out with additional notes.}
-\NOTE[LKC]{I have turned those `subscripts' to real subscripts.}
-
+In this section, we review the implementation of interleaving depth-first 
+search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
+chapter 10 and the appendix, ``Connecting the wires'', 
+provides a comprehensive description of the 
+miniKanren 
+implementation but limited to unification constraints ($\equiv$).
 Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} show parts that are later compared 
@@
 definitions say \conj{} is also right-associative.
+% \begin{figure}
+% 	\lstinputlisting{Figures/conde.rkt}
+% 	\caption{implementation of \conde}
+% 	\label{conde}
+% \end{figure}
+% 
+% The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
+% strategies. It relates clauses disjunctively, and goals in the same 
+% clause conjunctively.
+
+\NOTE[DPF]{This came out fabulous. I think I spotted some missed opportunities
+later, which I will point out with additional notes.}
+\NOTE[LKC]{I think we can simply remove \conde{} code and its accompany 
+description.}
 
@@
 fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
-\texttt{t$^\infty$} are ended with a thunk and we have swapped them. In this 
-case, we construct a new thunk. The new thunk swaps two spaces back in the
-recursive call. This is unnecessary for fairness. We do it to produce answers 
-in a more natural order.
+\texttt{t$^\infty$} are ended with a thunk, and that we have swapped them. In 
+this case, we construct a new thunk. The new thunk swaps two spaces back in the
+recursive call to \texttt{loop}. This is unnecessary for fairness. We do it to 
+produce answers in a more natural order.
 
 \NOTE[DPF]{When or where do you swap them back? This could be still clearer.}
-\NOTE[LKC]{In the recursion}
+\NOTE[LKC]{Improved.}
 
@@
 
-\BFSser{} has both fair \disj{} and fair \conj{}. Our implementation is based 
-on \DFSf{} (not \DFSi{}). To implement \BFSser{} based on \DFSf{}, 
-we need \texttt{append-map$^\infty_{fair}$} in addition to 
-\texttt{append$^\infty_{fair}$}. 
-The only difference between \texttt{append-map$^\infty$} and 
-\texttt{append-map$^\infty_{fair}$} is that the latter calls 
-\texttt{append$^\infty_{fair}$} instead of \texttt{append$^\infty$}.
+\BFS{} has both fair \disj{} and fair \conj{}. An easy implementation is based 
+on \DFSf{} (not \DFSi{}): (1) replace \texttt{append$^\infty$} with 
+\texttt{append$^\infty_{fair}$} in \texttt{append-map$^\infty$}'s body (2) 
+rename \texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$}.
 
-The implementation is improvable in two ways. First, as mentioned in 
-\autoref{sec:fairconj}, \BFSser{} puts answers in bags and answers of the same 
-cost are in the 
-same bag. In this implementation, however, it is unclear where this information 
-is recorded. Second, \texttt{append$^\infty_{fair}$} is extravagant in memory 
-usage. It 
+% Our implementation is based 
+% on \DFSf{} (not \DFSi{}). To implement \BFS{} based on \DFSf{}, 
+% we need \texttt{append-map$^\infty_{fair}$} in addition to 
+% \texttt{append$^\infty_{fair}$}. 
+% The only difference between \texttt{append-map$^\infty$} and 
+% \texttt{append-map$^\infty_{fair}$} is that the latter calls 
+% \texttt{append$^\infty_{fair}$} instead of \texttt{append$^\infty$}.
+
+\NOTE[LKC]{Applying the above changes won't result in \BFSser, but yet 
+another implementation of \BFS.}
+
+% This implementation is improvable in two ways. First, as mentioned in 
+% \autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
+% cost are in the same bag. In this implementation, however, it is unclear where 
+% this information is recorded. Second, \texttt{append$^\infty_{fair}$} is 
+% extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
+% time, where $n$ and $m$ are the ``length''s of input search spaces.
+
+This implementation is improvable in two ways. 
+First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
+answers of the same cost are in the same bag. In this implementation, however, 
+we manage cost information subtly---the \texttt{car}s of a search space have 
+cost 0 (i.e. they are all in the same bag), and every thunk indicates an 
+increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
+and the \texttt{append-map$^\infty_{fair}$} respects the cost information. 
+Second, \texttt{append$^\infty_{fair}$} is extravagant in memory usage. It 
 makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
-``length''s of input search spaces. We address these issues in the first 
-subsection.
+``length''s of input search spaces.
 
-%Both \BFSser{} \citet{seres1999algebra} and \BFSopt{} produce answers in 
-%increasing order of cost. So it is interesting to see if they are equivalent. 
-%We prove so in Coq. The details are in the second subsection.
+\NOTE[LKC]{Should I point out that \DFSf{} also has the miserable space 
+extravagance?}
 
-We prove formally our implementation is equivalent to the original one by 
-\citet{seres1999algebra}. The details are in the second subsection.
+In the following subsections, we firstly describe \BFSimp{}, an improved \BFS{} 
+implementation which manages cost information in a more clear way and is less 
+extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}, the 
+current implementation by \citeauthor{seres1999algebra}.
 
@@
 \begin{figure}
-	\lstinputlisting{Figures/BFS-opt.rkt}	
+	\lstinputlisting{Figures/BFSimp.rkt}	
 	\caption{new and changed functions in optimized BFS that implements pure 
 	features}
-	\label{BFS-opt}
+	\label{BFSimp}
 \end{figure}
 
-As mentioned in \autoref{sec:fairconj}, \BFSser{} puts answers in bags and 
-answers of the 
-same cost are in the same bag. The cost
-information is recorded subtly---the \texttt{car}s of a search space have cost 
-0 (i.e. they are all in the same bag), and every thunk indicates an increment 
-in cost. It is even more subtle that
-\texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
-respects the cost information. We make these facts more obvious by 
-changing the type of search space, modifying related function definitions, 
-and introducing a few more functions.
+% As mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
+% answers of the same cost are in the same bag. 
+% In the easy implementation, cost information is recorded subtly---the 
+% \texttt{car}s of a search space have cost 0 (i.e. they are all in the same 
+% bag),
+% and every thunk indicates an increment in cost. It is even more subtle that
+% \texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
+% respects the cost information. We make these facts more obvious by changing 
+% the type of search space, modifying related function definitions, and 
+% introducing a few more functions.
+
+We make the cost information more clear by changing the type of search space, 
+modifying related function definitions, and introducing a few more functions.
 
@@
 
-We list functions related to the pure subset in Fig.~\ref{BFS-opt} (the 
-others in Fig.~\ref{BFS-opt-cont}). We compare these functions with 
-\citeauthor{seres1999algebra}'s implementation in our proof. The first three 
-functions in Fig.~\ref{BFS-opt} are search space constructors. \texttt{none} 
-makes an empty search space; \texttt{unit} makes a space from one answer; and 
-\texttt{step} makes a space from a thunk. The remaining functions are as before.
+We list functions related to the pure subset in Fig.~\ref{BFSimp}. The first 
+three functions are search space constructors. \texttt{none} makes an empty 
+search space; \texttt{unit} makes a space from one answer; and \texttt{step} 
+makes a space from a thunk. The remaining functions are as before. We compare 
+these functions with \BFSser{} in our proof.
 
 Luckily, the change in \texttt{append$^\infty_{fair}$} also fixes the miserable 
-space 
-extravagance---the use of \texttt{append} helps us to reuse the first bag of 
-\texttt{t$^\infty$}.
+space extravagance---the use of \texttt{append} helps us to reuse the first bag 
+of \texttt{t$^\infty$}.
+
+\NOTE[LKC]{I do notice that in the below paragraph the leading sentence is not 
+at the beginning (but at the second position). Putting the current first 
+sentence at the beginning, however, looks more fun to me.}
 
 \citet{kiselyov2005backtracking} have demonstrated that a \emph{MonadPlus} 
-hides in 
-implementations of logic programming system. Our \BFSser{} implementation is 
-not an exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, 
-but takes arguments in reversed order; \texttt{none}, \texttt{unit}, and 
-\texttt{append$^\infty_{fair}$} correspond to \texttt{mzero}, \texttt{unit}, 
-and \texttt{mplus}, respectively.
+hides in implementations of logic programming system. \BFSimp{} is not an 
+exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, but takes 
+arguments in reversed order; \texttt{none}, \texttt{unit}, and 
+\texttt{append$^\infty_{fair}$} correspond to \texttt{mzero}, \texttt{unit}, and 
+\texttt{mplus}, respectively.
 
 \begin{figure}
-	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
+	\lstinputlisting{Figures/BFSimp-cont.rkt}	
 	\caption{new and changed functions in improved BFS that implement impure 
 		features}
-	\label{BFS-opt-cont}
+	\label{BFSimp-cont}
 \end{figure}
 
-Functions implementing impure features are in Fig.~\ref{BFS-opt-cont}. The 
+Functions implementing impure features are in Fig.~\ref{BFSimp-cont}. The 
 first function, \texttt{elim}, takes a space \texttt{s$^\infty$} and two 
-continuations \texttt{ks} and \texttt{kf}. When \texttt{s$^\infty$} contains 
-some 
-answers, it calls \texttt{ks} with the first answer and the rest of the space. 
-Otherwise, it calls \texttt{kf} with no argument. Here `s' means
-`succeed' and `f' means `fail'. This function is similar to an eliminator of 
+continuations \texttt{kf} and \texttt{ks}. When \texttt{s$^\infty$} contains 
+no answers, it calls \texttt{kf} with no argument. Otherwise, it calls 
+\texttt{ks} with the first answer and the rest of the space. Here  `f' means 
+`fail' and `s' means `succeed'. This function is similar to an eliminator of 
 search spaces, hence the name. The remaining functions are as before.
 
-\subsection{compare our implementation with the original one}
+\NOTE[LKC]{I swap \texttt{ks} and \texttt{kf} to mimic \texttt{ind-List}}
 
-In this section, we compare the pure subset of our implementation with the 
-original one. We focus on the pure subset because the original system is pure.
-\citeauthor{seres1999algebra} represent search spaces with streams of 
-lists of answers, where each list is a bag.
+\subsection{compare \BFSimp{} with \BFSser{}}
 
-To compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See supplements for the translated code). The translation is direct 
-due to the similarity in both logic programming systems and search space 
-representations. The translated code is longer and slower than our 
-implementation. Details about differences in efficiency are in the table below.
+\NOTE[LKC]{I have rewritten this subsection.}
 
-We use Coq to show that the two implementations are 
-semantically equivalent, (i.e., \texttt{(run n ? g)} 
-produces the same result (See supplements for the formal proof).
+In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
+focus on the pure subset because \BFSser{} is designed for a pure 
+relational programming system. We proof in Coq that these two search strategies 
+are are semantically equivalent, (i.e., \texttt{(run n ? g)} produces the same 
+result (See supplements for the formal proof). To compare efficiency, we 
+translate \BFSser{}'s Haskell code into Racket (See supplements for the 
+translated code). The translation is direct due to the similarity in two 
+relational programming systems. The translated code is longer than \BFSimp{}. 
+And it runs slower in all benchmarks. Details about differences in efficiency 
+are in \autoref{compare-efficiency}.
 
@@
 		benchmark & size & \DFSi{} & \DFSbi{} & \DFSf{} & 
-		our \BFSser{} & original \BFSser{}  
+		\BFSimp{} & \BFSser{}  
 		\\
@@
 
-Here we compare the efficiency of search strategies. A concise 
-description is in Table~\ref{compare-efficiency}. A hyphen means ``running out of 
-memory.'' The first two benchmarks are from 
+In this section, we compare the efficiency of search strategies. A concise 
+description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
+of memory.'' The first two benchmarks are from 
 TRS2. \reverso is from 
@@
 
-In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} 
-is just as 
-efficient in all benchmarks but \veryrecursiveo. Both implementations of BFS have obvious 
-overhead in many cases. Among the three variants of DFS, which all all have unfair \conj{}),
-\DFSf{} is most resistant to clause permutation, followed by 
-\DFSbi{} then 
-\DFSi{}. Among the two implementation of BFS, our improved \BFSser{} constantly performs as well 
-or 
-better. Interestingly, every strategy with fair \disj{} suffers in 
-\veryrecursiveo{} and \DFSf{} performs well elsewhere. 
-Therefore, this 
-benchmark might be a special case. Fair \conj{} imposes considerable overhead 
-constantly except in \appendo. The reason might be that strategies with 
-fair \conj{} tend to keep more intermediate answers in the memory.
-
-\NOTE[DPF]{appendo is not raised, though I tried.}
-\NOTE[LKC]{Which appendo is not raised? I couldn't find one.}
+In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} is just 
+as efficient in all benchmarks but \veryrecursiveo. Both implementations of BFS 
+have obvious overhead in many cases. Among the three variants of DFS, which all 
+all have unfair \conj{}), \DFSf{} is most resistant to clause permutation, 
+followed by \DFSbi{} then \DFSi{}. Among the two implementation of BFS, our 
+improved \BFSimp{} constantly performs as well or better. Interestingly, every 
+strategy with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs 
+well elsewhere. Therefore, this benchmark might be a special case. Fair \conj{} 
+imposes considerable overhead constantly except in \appendo. The reason might be 
+that strategies with fair \conj{} tend to keep more intermediate answers in the 
+memory.
 
@@
 
-%\citet{seres1999algebra} also describe a breadth-first search 
-%strategy. We prove \BFSser{} is semantically equivalent to \BFSopt. But,
-%The implementation of \BFSopt is shorter and performs better in comparison 
-%with a straightforward translation of their Haskell code.
-
 \section{conclusion}
@@
 (\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
-implementation of BFS. These strategies have different features 
+implementation of \BFS. These strategies have different features 
 in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
-\DFSf{} has fair \disj{} and unfair \conj{}. \BFSser{} has both fair
+\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
 \disj{} and fair \conj{}.
 
-Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are 
-competitive 
-alternatives to \DFSi{}, the current search strategy, and that 
-\BFSser{} is less practical than other breadth-first strategies.
-\NOTE[DPF]{I think what I have is okay, now.}
-\NOTE[LKC]{other search strategies}
+Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
+alternatives to \DFSi{}, the current search strategy, 
+and that \BFS{} is less practical.
+% and that \BFSser{} is less practical than other breadth-first strategies.
 
-We present another implementation of \BFSser. Our implementation is 
-semantically equivalent to the original one. But, ours is shorter and performs 
-better in comparison with a straightforward translation of their Haskell code.
-
-%We prove that \BFSopt{} is equivalent to \BFSser. 
-%Our optimized code is shorter and runs faster than a direct translation 
-%of their Haskell code.
+Our new implementation of \BFS{} is semantically equivalent to the original 
+one. But, ours is shorter and performs better in comparison with a 
+straightforward translation of their Haskell code.
 

### 2019-05-23 Paper/paper.tex
remove useless notes

@@
 
-\NOTE[LKC]{I change `1/4 in the answer' to `1/4 in the answer list'. }
-
 Given the following program, it is natural to expect lists of each letter to
@@
 \NOTE[DPF]{I think that should be said as directly as in your note.}
-\NOTE[LKC]{I state this fact at the beginning of this section.}
-\NOTE[LKC]{We never use run* in this paper because fairness is only 
+\NOTE[LKC]{I state this fact at the beginning of this section.
+
+``We never use run* in this paper because fairness is only 
 interesting when we have an unbounded number of answers. However, it is 
-perfectly fine to use run* with any search strategies.}
+perfectly fine to use run* with any search strategies.''}
 
@@
 
-\NOTE[LKC]{I have rewritten this subsection.}
-
 In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 

### 2019-05-23 Paper/paper.tex
Too many changes

@@
   		   {repeato}{{repeat$^o$}}{6}
+  		   {disj2}{{disj$_2$}}{4}
+  		   {conj2}{{conj$_2$}}{4}
   		   {g0}{{g$_0$}}{2}
@@
 
+\newcommand{\disjtwo}{\texttt{disj$_2$}}
+\newcommand{\conjtwo}{\texttt{conj$_2$}}
 \newcommand{\veryrecursiveo}{\texttt{very-recursive$^o$}}
@@
 \newcommand{\BFS}[0]{BFS}
-\newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
+\newcommand{\BFSser}[0]{BFS$_\textrm{}$}
 \newcommand{\BFSimp}[0]{BFS$_\textrm{imp}$}
@@
 and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
-demonstrated that miniKanren programs are useful in solving several problems.
-miniKanren.org contains the seeds of many more problems and their solutions.
+demonstrated that miniKanren programs are useful in solving several difficult
+problems. miniKanren.org contains the seeds of many difficult problems and 
+their solutions.
 
-\NOTE[DPF]{... Perhaps it should be part of the title that we have improved on 
-the the standard BFS implementation.}
-\NOTE[DPF]{When you rewrite the abstract and drop the abbreviations, remember 
-when you are rewriting the Introduction and introducing the abbreviations, that 
-you should explain the ser of BFSser using a reference.}
-\NOTE[LKC]{I have rewritten the abstract and explain the `ser' in the ending 
-paragraph of introduction, where we list contributions.}
+\NOTE[DPF]{[2,3] is the way to cite this, but I leave cleaning up this
+paragraph to you.  Mostly the point is to also include a reference to
+the two dimitris and to the first OCamren (OCanren), whatever. It is up to you
+in this paragraph.  You can refer to
+the two books like this ``Friedman et al[2,3] ... .'' This way the 
+paragraph will have only one ``Friedman''}
+
+\NOTE[DPF]{I have decided to agree with you that we should not use 
+BFSser, so I am going to remove all occurrences.  
+Also, we should say, ``Our implementation of BFS''
+and then say, shortened to ``Our BFS'' and then you can use it in the table,
+so one column should be Our BFS and the other should be BFS.}
+\NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
+that once, or very occasionally}
+
+\NOTE[DPF]{I think that subscripts i, bi, and f should
+match what is in the comments above code, so it should be italic, emph,
+or math, whichever was used before.}
+
+\NOTE[DPF]{Is the spelling of reverso truly written without the last e?
+Shouldn't it be reverseo with the appropriate raising of o.}
 
@@
 search strategy with fair \disj{} and fair \conj{}. We name the current 
-implementation by \citeauthor{seres1999algebra} as \BFSser{}, and our 
-new implementation as \BFSimp{}. We prove formally that they are semantically 
-equivalent. \BFSimp{}, however, runs faster in all benchmarks and is shorter, 
-thus being an \textbf{imp}rovement. 
+implementation by \citeauthor{seres1999algebra} and refer to ``our 
+BFS implementation as the improved one. We formally prove
+that the two BFS implementations are semantically 
+equivalent, however, our BFS implementation runs faster in all 
+benchmarks and is shorter.
 \end{itemize}
@@
 
-\NOTE[DPF]{I think that should be said as directly as in your note.}
-\NOTE[LKC]{I state this fact at the beginning of this section.
-
-``We never use run* in this paper because fairness is only 
+\NOTE[DPF]{Was this supposed to be a note?
+``We never use \texttt{run*} in this paper because fairness is only 
  interesting when we have an unbounded number of answers. However, it is 
@@
 
-\NOTE[DPF]{Next to the last line of the above paragraph the word same
-has too many meanings.  It could be have the same cost or it could be
-failing to distinguish two list that would be the same if we substituted
-a b for an a.  It needs to be clarified.  It might help to work out
-the actual numbers}
+\NOTE[DPF]{Would the answer be the same if the list had been this ((a) (b))
+or did you mean structurally the same?}
 \NOTE[LKC]{I have rewritten the relevant sentences.}
@@
 implementation of \disj. The 
-first function, \texttt{disj2}, implements binary disjunction. It applies the 
+first function, \disjtwo, implements binary disjunction. It applies the 
 two disjunctive goals to the input state \texttt{s} and composes the two 
@@
 definitions say \disj{} is right-associative. Fig.~\ref{DFSi-1} 
-shows the implementation of \conj. The first function, \texttt{conj2}, 
+shows the implementation of \conj. The first function, \conjtwo{}, 
 implements binary conjunction. 
@@
 
-\NOTE[DPF]{This came out fabulous. I think I spotted some missed opportunities
-later, which I will point out with additional notes.}
+\NOTE[DPF]{sure, go ahead and do it.}
 \NOTE[LKC]{I think we can simply remove \conde{} code and its accompany 
@@
 goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
-whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
+whose nodes are \disjtwo{}s, hence the name of this search strategy. 
 The new helper, \texttt{disj+}, takes two additional `arguments'. They 
@@
 implementation of \DFSf{} differs from \DFSi{}'s in 
-\texttt{disj2} (Fig.~\ref{fDFS}). The new \texttt{disj2} calls a new and 
+\disjtwo{} (Fig.~\ref{fDFS}). The new \disjtwo{} calls a new and 
 fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
@@
 
-\NOTE[LKC]{Applying the above changes won't result in \BFSser, but yet 
-another implementation of \BFS.}
+\NOTE[DPF]{I need clarification: Applying the above changes won't result in ``our \BFS,'' but yet a third implementation of \BFS?}
 
@@
 First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
-answers of the same cost are in the same bag. In this implementation, however, 
+answers of the same cost are in the same bag. In our implementation, however, 
 we manage cost information subtly---the \texttt{car}s of a search space have 
-cost 0 (i.e. they are all in the same bag), and every thunk indicates an 
+cost 0 (i.e., they are all in the same bag), and every thunk indicates an 
 increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
@@
 makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
-``length''s of input search spaces.
+``length''s of input spaces.
 
@@
 extravagance?}
+\NOTE[DPF]{probably}
 
-In the following subsections, we firstly describe \BFSimp{}, an improved \BFS{} 
-implementation which manages cost information in a more clear way and is less 
-extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}, the 
+In the following subsections, we first describe our improved \BFS{}
+implementation that manages cost information in a more clear and concise
+way and is less extravagant in memory usage. 
+Then we compare our BFS{} with \BFS{}, the 
 current implementation by \citeauthor{seres1999algebra}.
+
+\NOTE[DPF]{Let's use one more line and far less horizontal space
+by use 3 linefeeds.  They will still align nicely.}
 
@@
 	\lstinputlisting{Figures/BFSimp.rkt}	
-	\caption{new and changed functions in optimized BFS that implements pure 
+	\caption{New and changed functions in optimized BFS that implements pure 
 	features}
@@
 
+\NOTE[DPF]{I am not in love with the two calls to null?. I can think of at least
+two ways to fix it.  Pick one.}
+
 \begin{figure}
 	\lstinputlisting{Figures/BFSimp-cont.rkt}	
-	\caption{new and changed functions in improved BFS that implement impure 
+	\caption{New and changed functions in improved BFS that implement impure 
 		features}
@@
 \end{figure}
+
+\NOTE[DPF]{The use of the references to Fig 7 twice tells me that something
+has to change for the sake of clarity.}
 
@@
 
+\NOTE[DPF]{If we forget to use {} after \reverso, the o ends up too near
+the next word.  I fixed reverso on the second line of section 7, but there 
+may be others.}
+
 \subsection{compare \BFSimp{} with \BFSser{}}
 
-In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
-focus on the pure subset because \BFSser{} is designed for a pure 
-relational programming system. We proof in Coq that these two search strategies 
-are are semantically equivalent, (i.e., \texttt{(run n ? g)} produces the same 
-result (See supplements for the formal proof). To compare efficiency, we 
-translate \BFSser{}'s Haskell code into Racket (See supplements for the 
-translated code). The translation is direct due to the similarity in two 
-relational programming systems. The translated code is longer than \BFSimp{}. 
+In this subsection, we compare the pure subset of our BFS with \BFS{}. We 
+focus on the pure subset because \BFS{} is designed for a pure 
+relational programming system. We prove in Coq that these two search strategies 
+are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
+result in both our improved \BFS{} and BFS. (See supplements for the formal proof.) To compare efficiency, we 
+translate \BFS{}'s Haskell code into Racket (See supplements for the 
+translated code). The translation is direct due to the similarity of the two 
+relational programming systems. The translated code is longer than our \BFS{}. 
 And it runs slower in all benchmarks. Details about differences in efficiency 
@@
 of memory.'' The first two benchmarks are from 
-TRS2. \reverso is from 
+TRS2. \reverso{} is from 
 \citet{rozplokhas2018improving}. The next two benchmarks 
@@
 
-In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} is just 
-as efficient in all benchmarks but \veryrecursiveo. Both implementations of BFS 
-have obvious overhead in many cases. Among the three variants of DFS, which all 
-all have unfair \conj{}), \DFSf{} is most resistant to clause permutation, 
-followed by \DFSbi{} then \DFSi{}. Among the two implementation of BFS, our 
-improved \BFSimp{} constantly performs as well or better. Interestingly, every 
-strategy with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs 
-well elsewhere. Therefore, this benchmark might be a special case. Fair \conj{} 
-imposes considerable overhead constantly except in \appendo. The reason might be 
-that strategies with fair \conj{} tend to keep more intermediate answers in the 
-memory.
+\NOTE[DPF]{There is still some clumsiness using our improved DFS, since
+at some point, we may want to make this clearer, so have DFS not be fonted
+is a little weird.  I think both should always use ourDFS and 
+macro expand it to <our improved DFS>.  Then changes will be much easier.}
+
+In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
+is just as efficient in all benchmarks except those of \veryrecursiveo. Both
+implementations of BFS have obvious overhead in many cases. Among the
+three variants of DFS, which all have unfair \conj{}, \DFSf{} is most
+resistant to clause permutation, followed by \DFSbi{} then
+\DFSi{}. Among the two implementation of BFS, our improved \BFS{}
+constantly performs as well or better. Interestingly, every strategy
+with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs
+well elsewhere. Therefore, this benchmark might be a special
+case. Fair \conj{} imposes considerable overhead constantly except in
+\appendo. The reason might be that strategies with fair \conj{} tend
+to keep more intermediate answers in the memory.
 
@@
 with a straightforward translation of their Haskell code.
+
+\NOTE[DPF]{We might find the reference Ocanren in the two Dmitri's paper
+and say something here about it.}
 
@@
 Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
-alternatives to \DFSi{}, the current search strategy, 
+alternatives to \DFSi{}, the current search strategy miniKanren
 and that \BFS{} is less practical.
@@
 
-Our new implementation of \BFS{} is semantically equivalent to the original 
+Our improved \BFS{} is semantically equivalent to the original 
 one. But, ours is shorter and performs better in comparison with a 

### 2019-05-24 Paper/paper.tex
some fixes

@@
   		   {gr}{{g$_r$}}{2}
-  		   {DFSi }{{DFS$_\textrm{i}$}}{3}
-  		   {DFSbi}{{DFS$_\textrm{bi}$}}{3}
-  		   {DFSf }{{DFS$_\textrm{f}$}}{3}
+  		   {DFSi }{{DFS$_{i}$}}{3}
+  		   {DFSbi}{{DFS$_{bi}$}}{3}
+  		   {DFSf }{{DFS$_{f}$}}{3}
 }
@@
 
-\newcommand{\DFSi }[0]{DFS$_\textrm{i}$}
-\newcommand{\DFSf }[0]{DFS$_\textrm{f}$}
-\newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
+\newcommand{\DFSi }[0]{DFS$_{i}$}
+\newcommand{\DFSf }[0]{DFS$_{f}$}
+\newcommand{\DFSbi}[0]{DFS$_{bi}$}
 \newcommand{\BFS}[0]{BFS}
-\newcommand{\BFSser}[0]{BFS$_\textrm{}$}
-\newcommand{\BFSimp}[0]{BFS$_\textrm{imp}$}
+\newcommand{\BFSser}[0]{BFS}
+\newcommand{\BFSimp}[0]{Our BFS}
 
@@
 miniKanren is a family of relational programming languages.
-\citep{Friedman:2005:RS:1121583} \citet{friedman_reasoned_2018} introduce 
+\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
 miniKanren and its implementation in \emph{The Reasoned Schemer} 
@@
 
-\NOTE[DPF]{[2,3] is the way to cite this, but I leave cleaning up this
-paragraph to you.  Mostly the point is to also include a reference to
+\NOTE[DPF]{...  Mostly the point is to also include a reference to
 the two dimitris and to the first OCamren (OCanren), whatever. It is up to you
-in this paragraph.  You can refer to
-the two books like this ``Friedman et al[2,3] ... .'' This way the 
-paragraph will have only one ``Friedman''}
+in this paragraph.  ...}
+\NOTE[LKC]{I have fixed the cite to TRS and TRS2.}
+\NOTE[LKC]{What is the point of citing dmitris?}
+\NOTE[LKC]{Are we citing OCanren to show that miniKanren is widely used? If 
+yes, do we need to cite other implementations as well?}
 
@@
 that once, or very occasionally}
-
-\NOTE[DPF]{I think that subscripts i, bi, and f should
-match what is in the comments above code, so it should be italic, emph,
-or math, whichever was used before.}
-
 \NOTE[DPF]{Is the spelling of reverso truly written without the last e?
 Shouldn't it be reverseo with the appropriate raising of o.}
+\NOTE[LKC]{Yes, it is reverso (not reverseo) in Dmitris' paper}
 
@@
 
-\NOTE[LKC]{The following paragraph is extended to include an explanation on 
-\texttt{run*}}
-
-Now we elaborate fairness by running more queries about \repeato{}. We never use 
-\texttt{run*} in this paper because fairness is more interesting when we have 
-an unbounded number of answers. However, it is perfectly fine to use 
+Now we elaborate fairness by running more queries about \repeato{}. We never 
+use \texttt{run*} in this paper because fairness is more interesting when we 
+have an unbounded number of answers. However, it is perfectly fine to use 
 \texttt{run*} with any search strategies.
@@
 or did you mean structurally the same?}
-\NOTE[LKC]{I have rewritten the relevant sentences.}
+\NOTE[LKC]{I mean for all answer in the answer list, the answer's inner lists 
+are pairwise \texttt{equal?}. It is impossible to see a \texttt{((a) (b))} in 
+the answer list.}
 
@@
 definitions say \conj{} is also right-associative.
-% \begin{figure}
-% 	\lstinputlisting{Figures/conde.rkt}
-% 	\caption{implementation of \conde}
-% 	\label{conde}
-% \end{figure}
-% 
-% The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
-% strategies. It relates clauses disjunctively, and goals in the same 
-% clause conjunctively.
-
-\NOTE[DPF]{sure, go ahead and do it.}
-\NOTE[LKC]{I think we can simply remove \conde{} code and its accompany 
-description.}
 
@@
 two ways to fix it.  Pick one.}
+\NOTE[LKC]{fixed}
 
@@
 has to change for the sake of clarity.}
+\NOTE[LKC]{I guess you are talking about Table 1 becasue there is no Fig 7. I 
+have change the first reference.}
 
@@
 
-\NOTE[LKC]{I swap \texttt{ks} and \texttt{kf} to mimic \texttt{ind-List}}
-
 \NOTE[DPF]{If we forget to use {} after \reverso, the o ends up too near
@@
 may be others.}
+\NOTE[LKC]{I have checked all uses of similar macros by text search.}
 
@@
 And it runs slower in all benchmarks. Details about differences in efficiency 
-are in \autoref{compare-efficiency}.
+are in \autoref{sec:quan}.
+% \autoref{compare-efficiency}
+
+\NOTE[LKC]{I ref the next section instead of the table}
 
 \section{quantitative evaluation}
+\label{sec:quan}
 

### 2019-05-24 Paper/paper.tex
BFS

@@
   		   {g2}{{g$_2$}}{2}
+  		   {g3}{{g$_3$}}{2}
   		   {gl}{{g$_l$}}{2}
@@
 \newcommand{\BFSser}[0]{BFS}
-\newcommand{\BFSimp}[0]{Our BFS}
+\newcommand{\BFSuni}[0]{our BFS}
+\newcommand{\BFSimp}[0]{our improved BFS}
 
@@
 search, and the standard breadth-first search.
-The two non-standard depth-first searches are new. And we present a new, more 
-efficient and simpler implementation of the standard breadth-first search. Using 
+The two non-standard depth-first searches are new. And we present two new, more 
+efficient and shorter implementation of the standard breadth-first search. 
+Using 
 quantitative evaluation, we argue that the two new depth-first searches are 
 competitive alternatives to the standard one, 
-and that our breadth-first search implementation is more efficient than 
+and that our breadth-first search implementations are more efficient than 
 the current one.
+
+\NOTE[LKC]{``simpler'' -> ``shorter'' (more objective)}
+
+\NOTE[LKC]{We actually have two new BFS implementations, an easy one and an 
+improved one (BFSimp/BFSopt). Both of them runs faster than the current BFS. I 
+didn't name the easy one because I considered it just a stepstone to BFSimp. 
+But now I think giving names to both of them would be more clear.}
 
@@
 so one column should be Our BFS and the other should be BFS.}
+
 \NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
 that once, or very occasionally}
+
 \NOTE[DPF]{Is the spelling of reverso truly written without the last e?
 Shouldn't it be reverseo with the appropriate raising of o.}
-\NOTE[LKC]{Yes, it is reverso (not reverseo) in Dmitris' paper}
+\NOTE[LKC]{Yes, it is reverso instead of reverseo in Dmitris' paper.}
 
@@
 	\item implement in a new way the standard breath-first search (\BFS), a 
-search strategy with fair \disj{} and fair \conj{}. We name the current 
-implementation by \citeauthor{seres1999algebra} and refer to ``our 
-BFS implementation as the improved one. We formally prove
-that the two BFS implementations are semantically 
-equivalent, however, our BFS implementation runs faster in all 
-benchmarks and is shorter.
+search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
+BFS implementation'' (``BFS'' for short) as the implementation by 
+\citet{seres1999algebra} and refer to ``our BFS implementation'' (``our BFS'' 
+for short) as our new one. We formally prove that the two BFS implementations 
+are semantically equivalent, however, our BFS runs faster in all benchmarks and 
+is shorter.
 \end{itemize}
@@
 \NOTE[DPF]{Was this supposed to be a note?
-``We never use \texttt{run*} in this paper because fairness is only 
- interesting when we have an unbounded number of answers. However, it is 
- perfectly fine to use run* with any search strategies.''}
+``We never use \texttt{run*} in this paper because fairness is only interesting 
+when we have an unbounded number of answers. However, it is perfectly fine to 
+use run* with any search strategies.''}
+\NOTE[LKC]{I initially wrote it down as a note. I might get it wrong, but I 
+thought you suggested me to move it into the paper.}
 
@@
 
-\BFS{} has both fair \disj{} and fair \conj{}. An easy implementation is based 
-on \DFSf{} (not \DFSi{}): (1) replace \texttt{append$^\infty$} with 
-\texttt{append$^\infty_{fair}$} in \texttt{append-map$^\infty$}'s body (2) 
-rename \texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$}.
+\begin{figure}
+	\lstinputlisting{Figures/BFSuni.rkt}	
+	\caption{implementation of \BFSuni{} (based on \DFSf{})}
+	\label{BFSuni}
+\end{figure}
 
-% Our implementation is based 
-% on \DFSf{} (not \DFSi{}). To implement \BFS{} based on \DFSf{}, 
-% we need \texttt{append-map$^\infty_{fair}$} in addition to 
-% \texttt{append$^\infty_{fair}$}. 
-% The only difference between \texttt{append-map$^\infty$} and 
-% \texttt{append-map$^\infty_{fair}$} is that the latter calls 
-% \texttt{append$^\infty_{fair}$} instead of \texttt{append$^\infty$}.
+\BFS{} has both fair \disj{} and fair \conj{}. Our first implementation 
+(\autoref{BFSuni}) is based on \DFSf{} (not \DFSi{}). It is so similar to 
+\DFSf{} that we only need to apply two changes: (1) rename 
+\texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$} and (2) 
+replace \texttt{append$^\infty$} with \texttt{append$^\infty_{fair}$} in 
+\texttt{append-map$^\infty$}'s body.
 
-\NOTE[DPF]{I need clarification: Applying the above changes won't result in ``our \BFS,'' but yet a third implementation of \BFS?}
+\NOTE[DPF]{I need clarification: Applying the above changes won't result in 
+	``our \BFS,'' but yet a third implementation of \BFS?}
+\NOTE[LKC]{Improved.}
 
-% This implementation is improvable in two ways. First, as mentioned in 
-% \autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
-% cost are in the same bag. In this implementation, however, it is unclear where 
-% this information is recorded. Second, \texttt{append$^\infty_{fair}$} is 
-% extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
-% time, where $n$ and $m$ are the ``length''s of input search spaces.
+This implementation is improvable in two ways. First, as mentioned in 
+\autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
+cost are in the same bag. In the above implementation, however, 
+it is not very clear how we manage cost information --- the \texttt{car}s of a 
+search space have cost 0 (i.e., they are all in the same bag), and every thunk 
+indicates an increment in cost. It is even more subtle that 
+\texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
+respects the cost information. Second, \texttt{append$^\infty_{fair}$} is 
+extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
+time, where $n$ and $m$ are the ``length''s of input spaces. \DFSf{} also has 
+the space extravagance.
 
-This implementation is improvable in two ways. 
-First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
-answers of the same cost are in the same bag. In our implementation, however, 
-we manage cost information subtly---the \texttt{car}s of a search space have 
-cost 0 (i.e., they are all in the same bag), and every thunk indicates an 
-increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
-and the \texttt{append-map$^\infty_{fair}$} respects the cost information. 
-Second, \texttt{append$^\infty_{fair}$} is extravagant in memory usage. It 
-makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
-``length''s of input spaces.
+\NOTE[LKC]{I have pointed out ``\DFSf{} also has the space extravagance'' at 
+the end of the above paragraph.}
 
-\NOTE[LKC]{Should I point out that \DFSf{} also has the miserable space 
-extravagance?}
-\NOTE[DPF]{probably}
-
-In the following subsections, we first describe our improved \BFS{}
-implementation that manages cost information in a more clear and concise
-way and is less extravagant in memory usage. 
-Then we compare our BFS{} with \BFS{}, the 
-current implementation by \citeauthor{seres1999algebra}.
+In the following subsections, we first describe \BFSimp{} implementation that 
+manages cost information in a more clear and concise way and is less 
+extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}.
 
@@
 by use 3 linefeeds.  They will still align nicely.}
+\NOTE[LKC]{fixed}
 
@@
 	\lstinputlisting{Figures/BFSimp.rkt}	
-	\caption{New and changed functions in optimized BFS that implements pure 
+	\caption{New and changed functions in our BFS that implements pure 
 	features}
@@
 
-\NOTE[LKC]{I do notice that in the below paragraph the leading sentence is not 
-at the beginning (but at the second position). Putting the current first 
-sentence at the beginning, however, looks more fun to me.}
-
 \citet{kiselyov2005backtracking} have demonstrated that a \emph{MonadPlus} 
@@
 	\lstinputlisting{Figures/BFSimp-cont.rkt}	
-	\caption{New and changed functions in improved BFS that implement impure 
+	\caption{New and changed functions in our BFS that implement impure 
 		features}
@@
 
-In this subsection, we compare the pure subset of our BFS with \BFS{}. We 
-focus on the pure subset because \BFS{} is designed for a pure 
+In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
+focus on the pure subset because \BFSser{} is designed for a pure 
 relational programming system. We prove in Coq that these two search strategies 
 are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
-result in both our improved \BFS{} and BFS. (See supplements for the formal proof.) To compare efficiency, we 
+result in both our BFS and BFS. (See supplements for the formal proof.) To 
+compare efficiency, we 
 translate \BFS{}'s Haskell code into Racket (See supplements for the 
 translated code). The translation is direct due to the similarity of the two 
-relational programming systems. The translated code is longer than our \BFS{}. 
+relational programming systems. The translated code is longer than \BFSimp{}. 
 And it runs slower in all benchmarks. Details about differences in efficiency 
@@
 \begin{table}
-	\begin{tabular}{|c|c|c|c|c|c|c|}
+	% run in command line, with a memory limit of 500MB
+	\begin{tabular}{|c|c|c|c|c|c|c|c|}
 		\hline 
-		benchmark & size & \DFSi{} & \DFSbi{} & \DFSf{} & 
-		\BFSimp{} & \BFSser{}  
-		\\
+	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSuni & \BFSimp & \BFSser	\\
 		\hline
-		\veryrecursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
-		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
-		& 300000 & 2160 & 2836 &    - & 6137 &    - \\
+		\veryrecursiveo & 100000 & 166 & 103 & 412 &   417 &   451 &   1024 \\
+	    				& 200000 & 283 & 146 & 765 &   766 &   839 &   1875 \\
+						& 300000 & 429 & 346 &2085 &  2066 &  1809 &   4408 \\
 		\hline  
-		\appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
-		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
-		& 300 & 617 & 634 & 593 & 631 & 622 \\ 
+		\appendo        & 	 100 &  17 &  18 &  17 &    18 &    17 &     65 \\
+		         	  	& 	 200 & 145 & 137 & 137 &   137 &   142 &    121 \\
+          		      	&	 300 & 388 & 384 & 387 &   383 &   429 &    371 \\
+%   		& - & - & - & - & - & - \\
 		\hline 
-		\reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
-		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
-		& 30 & 446 & 442 & 485 & 123288 & 132159 \\ 
+		\reverso		& 	  10 &   3 &   4 &   3 &    18 &    18 &     36 \\
+						& 	  20 &  35 &  35 &  33 &  3119 &  3070 &   3695 \\
+						& 	  30 & 329 & 333 & 315 & 76243 & 75079 & 107531 \\
 		\hline
-		quine-1 & 1 &  71 &  44 & 69 & - & - \\ 
-		& 2 & 127 & 142 & 95 & - & - \\ 
-		& 3 & 114 & 114 & 93 & - & - \\ 
+		quine-1 		& 1 & 13 & 14 & 10 & - & - & - \\
+						& 2 & 30 & 34 & 25 & - & - & - \\
+						& 3 & 41 & 48 & 33 & - & - & - \\
 		\hline
-		quine-2 & 1 & 147 & 112 &  56 & - & - \\ 
-		& 2 & 161 & 123 & 101 & - & - \\ 
-		& 3 & 289 & 189 & 104 & - & - \\ 
+		quine-2 		& 1 & 22 & 21 & 12 & - & - & - \\
+						& 2 & 51 & 46 & 24 & - & - & - \\
+						& 3 & 72 & 76 & 32 & - & - & - \\
 		\hline
-		'(I love you)-1 &  99 & 56 & 15 & 22 &  74 & 165 \\ 
-		& 198 & 53 & 72 & 55 &  47 &  74 \\
-		& 297 & 72 & 90 & 44 & 181 & 365 \\ 
+%		quine-1 & 1 &  71 &  44 & 69 & ??? & - & - \\ 
+%		& 2 & 127 & 142 & 95 & ??? & - & - \\ 
+%		& 3 & 114 & 114 & 93 & ??? & - & - \\ 
+%		\hline
+%		quine-2 & 1 & 147 & 112 &  56 & ??? & - & - \\ 
+%		& 2 & 161 & 123 & 101 & ??? & - & - \\ 
+%		& 3 & 289 & 189 & 104 & ??? & - & - \\ 
+%		\hline 
+		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   40 &   96 \\
+						& 198 &  22 &  71 & - &  374 &  374 &  652 \\
+						& 297 &  24 & 292 & - & 1707 & 1668 & 3759 \\
 		\hline
-		'(I love you)-2 &  99 & 242 &  61 & 16 &  66 &  99 \\ 
-		& 198 & 445 & 110 & 60 &  42 &  64 \\
-		& 297 & 476 & 146 & 49 & 186 & 322 \\ 
+		'(I love you)-2 &  99 & 485 & 179 & - &   38 &   44 &   94 \\
+						& 198 & 808 & 638 & - &  366 &  414 &  630 \\
+						& 297 &1265 & 916 & - & 1674 & 1651 & 3691 \\ 
 		\hline 
+		% The data below is test with old benchmarks
+%'(I love you)-1 &  99 & 56 & 15 & 22 & ??? &  74 & 165 \\ 
+%& 198 & 53 & 72 & 55 & ??? &  47 &  74 \\
+%& 297 & 72 & 90 & 44 & ??? & 181 & 365 \\ 
+%\hline
+%'(I love you)-2 &  99 & 242 &  61 & 16 & ??? &  66 &  99 \\ 
+%& 198 & 445 & 110 & 60 & ??? &  42 &  64 \\
+%& 297 & 476 & 146 & 49 & ??? & 186 & 322 \\ 
+%\hline 
 	\end{tabular}
 	\caption{The results of a quantitative evaluation: running times of 
-	benchmarks 
-		in milliseconds}
+	benchmarks in milliseconds}
 	\label{compare-efficiency}
@@
 description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
-of memory.'' The first two benchmarks are from 
+of 500 MB memory.'' The first two benchmarks are from 
 TRS2. \reverso{} is from 
-\citet{rozplokhas2018improving}. The next two benchmarks 
-about quine are modified from a similar test case in \citet{byrd2017unified}. 
-The modifications are made 
-to circumvent the need for symbolic constraints (e.g. $\neq$, 
-\texttt{absent$^o$}). Our version generates de 
-Bruijnized expressions and prevents closures from being inside a list. The two 
-benchmarks differ in the \conde{} clause order of their relational 
+\citet{rozplokhas2018improving}. 
+The next two benchmarks about quine are modified from a similar test case in 
+\citet{byrd2017unified}. The modifications are made to circumvent the need for 
+symbolic constraints (e.g. $\neq$, \texttt{absent$^o$}).
+Our version generates de Bruijnized expressions and prevents closures from 
+being inside a list. 
+The sibling benchmarks differ in the \conde{} clause order of their relational 
 interpreters.
-The last two 
-benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
-you)}. This benchmark is from \citet{byrd2017unified}. Again, the 
-sibling benchmarks differ in the \conde{} clause order of their relational 
-interpreters. The first one 
-has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
-end, while the other has them at the beginning. We conjecture that \DFSi{} 
-would 
-perform badly in the second case because elimination rules complicate the 
-problem when synthesizing (i.e., our evaluation supports our conjecture.)
+The last two benchmarks are about synthesizing expressions that evaluate to 
+\texttt{'(I love you)}. 
+They are also modified from a similar test case in \citet{byrd2017unified} 
+because of the same reason. 
+Our version generates de Bruijnized expressions. 
+Again, the sibling benchmarks differ in the \conde{} clause order of their 
+relational interpreters. The first one has elimination rules (i.e. application, 
+\texttt{car}, and \texttt{cdr}) at the end, while the other has them at the 
+beginning. 
+We conjecture that \DFSi{} would perform badly in the second case because 
+elimination rules complicate the problem when synthesizing (i.e., our 
+evaluation supports our conjecture.)
+
+\NOTE[LKC]{I change the benchmark '(I love you) such that it doesn't prevent 
+closures from getting into pairs because I consider this restriction not 
+reasonable. As for quines, they are already very slow so I didn't make the 
+changes.}
 
@@
 macro expand it to <our improved DFS>.  Then changes will be much easier.}
+\NOTE[LKC]{I guess you are talking about ``our improved BFS''. I have added 
+relevant macros.}
+
+\NOTE[LKC]{I rewrote the following paragraph and the table to include the 
+additional BFS and update the '(I love you) benchmark.
+
+Also, all running time are re-measured by running in command-line. I used to 
+run benchmarks with DrRacket. Thus, the time measurements are smaller.}
 
 In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
-is just as efficient in all benchmarks except those of \veryrecursiveo. Both
-implementations of BFS have obvious overhead in many cases. Among the
-three variants of DFS, which all have unfair \conj{}, \DFSf{} is most
-resistant to clause permutation, followed by \DFSbi{} then
-\DFSi{}. Among the two implementation of BFS, our improved \BFS{}
-constantly performs as well or better. Interestingly, every strategy
-with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs
-well elsewhere. Therefore, this benchmark might be a special
-case. Fair \conj{} imposes considerable overhead constantly except in
-\appendo. The reason might be that strategies with fair \conj{} tend
-to keep more intermediate answers in the memory.
+is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
+implementations have obvious overhead in most cases. 
+Among the three variants of DFS, which all have unfair \conj{}, \DFSf{} is most 
+resistant to clause permutation in \texttt{quines}, followed by \DFSbi{} then 
+\DFSi{}. \DFSf{}, however, runs out of memory in \texttt{'(I love you)}s. In 
+contrast, \DFSbi{} still performs more stable than \DFSi{}. Thus, we consider 
+\DFSbi{} a competitive alternative to \DFSi{}, the current standard miniKanren 
+search strategy. 
+Among the three implementations of \BFS, our \BFS{}s constantly perform as well 
+or better. \BFSimp{} only out-performs \BFSuni{} significantly in 
+\veryrecursiveo{} 300000, while performing as well or worse elsewhere. The 
+reason might be that the size of bags are usually too small to be worried about.
+It is hard to conclude how \disj{} fairness affect performance based on these 
+statistics. Fair \conj{}, however, imposes considerable overhead constantly 
+except in \appendo. The reason might be that those strategies tend to keep more 
+intermediate answers in the memory.
 
@@
 Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
-alternatives to \DFSi{}, the current search strategy miniKanren
+alternatives to \DFSi{}, the current miniKanren search strategy,
 and that \BFS{} is less practical.

### 2019-05-24 Paper/paper.tex
cite Dmitris

@@
 
+\NOTE[LKC]{
+We actually have two new BFS implementations. One is modified from DFSf with 
+two simple steps. It has been described briefly at the beginning of the BFS 
+section but was not given a name. The other is the one described with two large 
+figures and was given the name ``our improved BFS''. Both of them runs faster 
+than the current BFS.
+
+I didn't name the first one because (1) it is so simple and (2) I considered 
+it merely a stepstone to our improved BFS. Now I decided to also give the first 
+BFS implementation a name. This is because I think having a nameless impl is 
+confusing.
+
+Currently, the nameless implementation is given the name ``our BFS''. And I 
+have changed the paper accordingly.
+
+BUT, I am thinking about going further --- removing ``our improved BFS'' from 
+this paper. The first reason is that our BFS is actually more efficient than 
+our improved BFS in most benchmarks (see Table 1), despite its theoretical 
+space extravagence. The second reason is that DFSi, DFSf, and our BFS look nice 
+when sitting together.}
+
 We describe fairness levels in disjunction and conjunction
@@
 \NOTE[LKC]{``simpler'' -> ``shorter'' (more objective)}
-
-\NOTE[LKC]{We actually have two new BFS implementations, an easy one and an 
-improved one (BFSimp/BFSopt). Both of them runs faster than the current BFS. I 
-didn't name the easy one because I considered it just a stepstone to BFSimp. 
-But now I think giving names to both of them would be more clear.}
 
@@
 miniKanren and its implementation in \emph{The Reasoned Schemer} 
-and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
+and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
+Scheme, miniKanren has been ported to many other languages (e.g. 
+OCanren\citep{kosarev2018typed}). \citet{byrd2017unified} have 
 demonstrated that miniKanren programs are useful in solving several difficult
@@
 in this paragraph.  ...}
-\NOTE[LKC]{I have fixed the cite to TRS and TRS2.}
-\NOTE[LKC]{What is the point of citing dmitris?}
-\NOTE[LKC]{Are we citing OCanren to show that miniKanren is widely used? If 
-yes, do we need to cite other implementations as well?}
+\NOTE[LKC]{I have fixed the references to TRS and TRS2.}
+\NOTE[LKC]{I have cited OCanren in this paragraph.}
 
@@
 so one column should be Our BFS and the other should be BFS.}
-
 \NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
@@
 a new search strategy with fair \disj{}.
-	\item implement in a new way the standard breath-first search (\BFS), a 
+	\item implement in two new ways the standard breath-first search (\BFS), a 
 search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
@@
 \citet{seres1999algebra} and refer to ``our BFS implementation'' (``our BFS'' 
-for short) as our new one. We formally prove that the two BFS implementations 
-are semantically equivalent, however, our BFS runs faster in all benchmarks and 
-is shorter.
+for short) and ``our improved BFS implementation'' (``our improved BFS`` for 
+short) as our new ones. We also refer to ``our \BFS{}s'' to both \BFSuni{} and 
+\BFSimp{}. We argue that our \BFS{}s are semantically equivalent and formally 
+prove that \BFSimp{} and \BFSser{} are semantically equivalent, however, our 
+\BFS{}s run faster in all benchmarks and are shorter.
 \end{itemize}
@@
 constraints to unification constraints.) Every answer corresponds to a 
-state. A space is a collection of states. And a \emph{goal} is a 
+state. A \emph{space} is a collection of states. And a \emph{goal} is a 
 function from a state to a space.
@@
 
-\NOTE[LKC]{I have pointed out ``\DFSf{} also has the space extravagance'' at 
-the end of the above paragraph.}
-
 In the following subsections, we first describe \BFSimp{} implementation that 
@@
 
-\NOTE[LKC]{I change the benchmark '(I love you) such that it doesn't prevent 
-closures from getting into pairs because I consider this restriction not 
-reasonable. As for quines, they are already very slow so I didn't make the 
-changes.}
+\NOTE[LKC]{I have changed the benchmarks about '(I love you), such that their 
+relational interpreters doesn't prevent closures from getting into pairs. I did 
+so because I consider this restriction doesn't make sense. Benchmarks about 
+quine are already very slow so I didn't apply similar changes.}
 
@@
 
-\NOTE[LKC]{I rewrote the following paragraph and the table to include the 
-additional BFS and update the '(I love you) benchmark.
-
-Also, all running time are re-measured by running in command-line. I used to 
-run benchmarks with DrRacket. Thus, the time measurements are smaller.}
+\NOTE[LKC]{I rewrote the following paragraph and the table to include our BFS 
+in additional to our improved BFS.}
+\NOTE[LKC]{I also re-measured all running time. I used to run benchmarks with 
+DrRacket, now I do it in command-line. Thus, the time measurements are smaller 
+and more stable.}
 
@@
 Among the three implementations of \BFS, our \BFS{}s constantly perform as well 
-or better. \BFSimp{} only out-performs \BFSuni{} significantly in 
-\veryrecursiveo{} 300000, while performing as well or worse elsewhere. The 
-reason might be that the size of bags are usually too small to be worried about.
+or better. Among our \BFS{}s, \BFSimp{} only performs better in 
+\veryrecursiveo{} 300000. The reason might be that the size of bags are usually 
+too small to be worried about. 
 It is hard to conclude how \disj{} fairness affect performance based on these 
-statistics. Fair \conj{}, however, imposes considerable overhead constantly 
-except in \appendo. The reason might be that those strategies tend to keep more 
+statistics. 
+Fair \conj{}, however, imposes considerable overhead constantly except in 
+\appendo. The reason might be that those strategies tend to keep more 
 intermediate answers in the memory.
@@
 
+\citet{rozplokhas2018improving} address the non-commutativity of conjunction, 
+while our work about \disj{} fairness addresses the non-commutativity of 
+disjunction.
+
 \NOTE[DPF]{We might find the reference Ocanren in the two Dmitri's paper
 and say something here about it.}
+\NOTE[LKC]{added}
 
@@
 We devise two new search strategies (i.e. balanced interleaving DFS 
-(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
-implementation of \BFS. These strategies have different features 
+(\DFSbi{}) and fair DFS (\DFSf{})) and devise two new 
+implementations of \BFS. These strategies have different features 
 in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
@@
 
-Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
-alternatives to \DFSi{}, the current miniKanren search strategy,
+Our quantitative evaluation shows that \DFSbi{} is a competitive 
+alternative to \DFSi{}, the current miniKanren search strategy,
 and that \BFS{} is less practical.

### 2019-05-24 Paper/paper.tex
TOO mant corrections, paper is looking good

@@
   basicstyle=\ttfamily,
-  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
+  morekeywords={run,conde,run*defrel,==,fresh,disj,conj,disj+},
   alsodigit={!\$\%&*+-./:<=>?@^_~},
@@
 \newcommand{\BFSimp}[0]{our improved BFS}
+\newcommand{\runstar}{run$^*$}
 
@@
 
-\NOTE[LKC]{
-We actually have two new BFS implementations. One is modified from DFSf with 
-two simple steps. It has been described briefly at the beginning of the BFS 
-section but was not given a name. The other is the one described with two large 
-figures and was given the name ``our improved BFS''. Both of them runs faster 
-than the current BFS.
+\NOTE[DPF]{Throughout the paper we have search spaces and search strategies.
+I can see leaving in the  ``search strategies'', but let's try to
+remove virtually all of the uses of ``search'' in front of spaces.}
 
-I didn't name the first one because (1) it is so simple and (2) I considered 
-it merely a stepstone to our improved BFS. Now I decided to also give the first 
-BFS implementation a name. This is because I think having a nameless impl is 
-confusing.
-
-Currently, the nameless implementation is given the name ``our BFS''. And I 
-have changed the paper accordingly.
-
-BUT, I am thinking about going further --- removing ``our improved BFS'' from 
+\NOTE[LKC]{BUT, I am thinking about going further --- removing ``our improved'' from 
 this paper. The first reason is that our BFS is actually more efficient than 
@@
 
+\NOTE[DPF]{Does this mean that the comment about append goes away.
+I really thought that was so clever.  I thought that the way you pointed
+out the trivial changes was very clear, so that did not bother me at
+all.}
+
 We describe fairness levels in disjunction and conjunction
 implementations.  Specifically, a disjunction implementation can be
-fair, almost-fair, or unfair. And a conjunction implementation can
-be fair or unfair.  We compare the fairness level of four search
+fair, almost-fair, or unfair. And a conjunction implementation can be
+fair or unfair.  We compare the fairness level of four search
 strategies: the standard miniKanren interleaving depth-first search,
 the balanced interleaving depth-first search, the fair depth-first
-search, and the standard breadth-first search.
-The two non-standard depth-first searches are new. And we present two new, more 
-efficient and shorter implementation of the standard breadth-first search. 
-Using 
-quantitative evaluation, we argue that the two new depth-first searches are 
-competitive alternatives to the standard one, 
-and that our breadth-first search implementations are more efficient than 
-the current one.
-
-\NOTE[LKC]{``simpler'' -> ``shorter'' (more objective)}
+search, and the standard breadth-first search.  The two non-standard
+depth-first searches are new. And we present two new, more efficient
+and shorter implementations of the standard breadth-first search.
+Using quantitative evaluation, we argue that the two new depth-first
+searches are competitive alternatives to the standard one, and that
+our breadth-first search implementations are more efficient than the
+current one.
 
@@
 
-\NOTE[DPF]{...  Mostly the point is to also include a reference to
-the two dimitris and to the first OCamren (OCanren), whatever. It is up to you
-in this paragraph.  ...}
-\NOTE[LKC]{I have fixed the references to TRS and TRS2.}
-\NOTE[LKC]{I have cited OCanren in this paragraph.}
-
-\NOTE[DPF]{I have decided to agree with you that we should not use 
-BFSser, so I am going to remove all occurrences.  
-Also, we should say, ``Our implementation of BFS''
-and then say, shortened to ``Our BFS'' and then you can use it in the table,
-so one column should be Our BFS and the other should be BFS.}
-\NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
-that once, or very occasionally}
-
-\NOTE[DPF]{Is the spelling of reverso truly written without the last e?
-Shouldn't it be reverseo with the appropriate raising of o.}
-\NOTE[LKC]{Yes, it is reverso instead of reverseo in Dmitris' paper.}
+\NOTE[DPF]{their BFS (or shortened to BFS). We need only say this once if we go with ``our'', which I don't like.
+I like ``the new'' or ``the improved'' and ``the current'' }
 
@@
 
-Next, consider the following disjunction of invoking \repeato{} with four 
+\noindent Next, consider the following disjunction of invoking \repeato{} with four 
 different letters.
@@
 
-\conde{} intuitively relates its clauses with logical \texttt{or}. And thus an 
+\noindent \conde{} intuitively relates its clauses with logical \texttt{or}. And thus an 
 unsuspicious beginner would expect each letter to contribute equally to the 
@@
 
-The \conde{} in TRS2, however, generates a less expected result.
+\noindent The \conde{} in TRS2, however, generates a less expected result.
 
@@
 \DFSi{} is not always the best choice. For instance, it might be less 
-desirable for little miniKanreners -- understanding implementation details and 
+desirable for novice miniKanrenuser---understanding implementation details and 
 fiddling with clause order is not their first priority. 
@@
 
+\NOTE[DPF]{The citetseres1999algebra must be not broken:
+            You can either rewrite the sentence or
+            use a tilde called a tie that means don't break the line.
+            Sometimes using tilde does not work out elegant enough,
+            so the first idea works best.}
+
 \section{search strategies and fairness}
@@
 Now we elaborate fairness by running more queries about \repeato{}. We never 
-use \texttt{run*} in this paper because fairness is more interesting when we 
-have an unbounded number of answers. However, it is perfectly fine to use 
-\texttt{run*} with any search strategies.
+use \runstar{} in this paper because fairness is more interesting when we 
+have an unbounded number of answers. It is perfectly fine, however, to use 
+\runstar{} with any search strategies.
 
@@
 
-Given the following program, it is natural to expect lists of each letter to
-constitute $1/4$ in the query result. \DFSi, the current search
-strategy, however, results in many more lists of \texttt{a}s than lists
-of other letters. And some letters  (e.g. \texttt{c} and \texttt{d}) are
-rarely seen. The situation would be exacerbated if the \conde{} would have
-contained more clauses.
+Given the following program, it is natural to expect lists of each
+letter to constitute $1/4$ in the query result. \DFSi, TRS2's search
+strategy, however, results in many more lists of \texttt{a}s than
+lists of other letters. And some letters (e.g. \texttt{c} and
+\texttt{d}) are rarely seen. The more clauses the worse the situation.
 
@@
 more general
-than the one in \citet{seres1999algebra}. Their definition is only
+than the one in \citet{seres1999algebra}, which is only
 for binary disjunction. We generalize it to a multi-arity one.
@@
 Given the following program, it is natural to expect lists of each letter to
-constitute $1/4$ in the answer list. Search strategies with unfair \conj{} 
-(e.g. 
-\DFSi, \DFSbi, \DFSf), however, results in many more lists of \texttt{a}s than 
-lists of other letters. And some letters are rarely seen. The situation would 
-be exacerbated if \conde{} were to contain more clauses.
+constitute $1/4$ in the answer list. Search strategies with unfair \conj{}:
+\DFSi, \DFSbi, and \DFSf, however, results in many more lists of \texttt{a}s than 
+lists of other letters. And some letters are rarely seen. Here again, as the
+number of clauses grows, the situation worsens.
+
 Although some strategies have a different level of fairness in \disj{}, they 
@@
 
-\NOTE[DPF]{Was this supposed to be a note?
-``We never use \texttt{run*} in this paper because fairness is only interesting 
-when we have an unbounded number of answers. However, it is perfectly fine to 
-use run* with any search strategies.''}
-\NOTE[LKC]{I initially wrote it down as a note. I might get it wrong, but I 
-thought you suggested me to move it into the paper.}
-
 \begin{center}
@@
 
-\NOTE[DPF]{Would the answer be the same if the list had been this ((a) (b))
-or did you mean structurally the same?}
+\NOTE[DPF]{Can you express exactly how all costs are determined?  I see that
+for this simple program, your notion of cost makes sense, but how does it
+generalize to all costs.}
 \NOTE[LKC]{I mean for all answer in the answer list, the answer's inner lists 
@@
 chapter 10 and the appendix, ``Connecting the wires'', 
-provides a comprehensive description of the 
+provide a comprehensive description of the 
 miniKanren 
@@
 states; \texttt{g}s (possibly with subscript) name goals; 
-variables ending with $^\infty$ name search spaces. Fig.~\ref{DFSi-0} shows the 
+variables ending with $^\infty$ name (search) spaces. Fig.~\ref{DFSi-0} shows the 
 implementation of \disj. The 
@@
 \texttt{t$^\infty$} are ended with a thunk, and that we have swapped them. In 
-this case, we construct a new thunk. The new thunk swaps two spaces back in the
-recursive call to \texttt{loop}. This is unnecessary for fairness. We do it to 
-produce answers in a more natural order.
-
-\NOTE[DPF]{When or where do you swap them back? This could be still clearer.}
-\NOTE[LKC]{Improved.}
+this case, we construct a new thunk. The new thunk swaps back the two spaces in the
+recursive call to \texttt{loop}. This is unnecessary for fairness---we do it to 
+produce answers in a more readable order.
 
@@
 
-This implementation is improvable in two ways. First, as mentioned in 
+\NOTE[DPF]{Why are the two texttt's macros, again?  Now, it hardly matters,
+but it is unfriendly to your other co-authors to have us reading long
+expressions when a newcommand would suffice.  I read the paper with a pen
+marking it up, then I read the paper on the .tex screen.  That's each time
+I read it.}
+
+\NOTE[DPF]{You know that ``bag'' is a technical terms.  It means that there
+is a structure where each element of the structure has an associated number, 
+which tells you have many occurrences of that element are in the list.
+For example, the list (a b a c a d c) could be represented like this:
+(a$^3$ b$^1$ c$^2$ d$^1$).  If that is not what you mean, you might change the name
+to bucket.}
+
+This implementation can be improved in two ways. First, as mentioned in 
 \autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
 cost are in the same bag. In the above implementation, however, 
-it is not very clear how we manage cost information --- the \texttt{car}s of a 
+it is not obvious how we manage cost information---the \texttt{car}s of a 
 search space have cost 0 (i.e., they are all in the same bag), and every thunk 
@@
 
-We make the cost information more clear by changing the type of search space, 
+\NOTE[DPF]{Font Space like in the code comments.}
+
+We make the cost information more clear by changing the Space type, 
 modifying related function definitions, and introducing a few more functions.
@@
 
-\NOTE[DPF]{I am not in love with the two calls to null?. I can think of at least
-two ways to fix it.  Pick one.}
-\NOTE[LKC]{fixed}
-
 \begin{figure}
@@
 
-\NOTE[DPF]{The use of the references to Fig 7 twice tells me that something
-has to change for the sake of clarity.}
-\NOTE[LKC]{I guess you are talking about Table 1 becasue there is no Fig 7. I 
-have change the first reference.}
+\NOTE[DPF]{ks --> sk and kf --> fk and you don't need to say f and s
+mean success continuation and failure continuation.}
 
@@
 search spaces, hence the name. The remaining functions are as before.
-
-\NOTE[DPF]{If we forget to use {} after \reverso, the o ends up too near
-the next word.  I fixed reverso on the second line of section 7, but there 
-may be others.}
-\NOTE[LKC]{I have checked all uses of similar macros by text search.}
 
@@
 % \autoref{compare-efficiency}
-
-\NOTE[LKC]{I ref the next section instead of the table}
 
@@
 
-\NOTE[DPF]{There is still some clumsiness using our improved DFS, since
-at some point, we may want to make this clearer, so have DFS not be fonted
-is a little weird.  I think both should always use ourDFS and 
-macro expand it to <our improved DFS>.  Then changes will be much easier.}
-\NOTE[LKC]{I guess you are talking about ``our improved BFS''. I have added 
-relevant macros.}
-
-\NOTE[LKC]{I rewrote the following paragraph and the table to include our BFS 
-in additional to our improved BFS.}
-\NOTE[LKC]{I also re-measured all running time. I used to run benchmarks with 
-DrRacket, now I do it in command-line. Thus, the time measurements are smaller 
-and more stable.}
+\NOTE[DPF]{We don't have disequality constraints, so no absento.  You might just
+say that.}
 
@@
 disjunction.
-
-\NOTE[DPF]{We might find the reference Ocanren in the two Dmitri's paper
-and say something here about it.}
-\NOTE[LKC]{added}
 

### 2019-05-25 Paper/paper.tex
corrections

@@
 \newcommand{\repeato}{\texttt{repeat$^o$}}
+\newcommand{\runstar}{\texttt{run$^*$}}
+\newcommand{\Space}{\texttt{Space}}
+\newcommand{\appendInf}{\texttt{append$^\infty$}}
+\newcommand{\appendInfFair}{\texttt{append$^\infty_{fair}$}}
+\newcommand{\appendMapInf}{\texttt{append-map$^\infty$}}
+\newcommand{\appendMapInfFair}{\texttt{append-map$^\infty_{fair}$}}
+\newcommand{\sInf}{\texttt{s$^\infty$}}
+\newcommand{\tInf}{\texttt{t$^\infty$}}
 
@@
 \newcommand{\BFSser}[0]{BFS}
-\newcommand{\BFSuni}[0]{our BFS}
-\newcommand{\BFSimp}[0]{our improved BFS}
-\newcommand{\runstar}{run$^*$}
+\newcommand{\BFSimp}[0]{the improved BFS}
 
@@
 
-\begin{abstract}
-
 \NOTE[DPF]{Throughout the paper we have search spaces and search strategies.
@@
 remove virtually all of the uses of ``search'' in front of spaces.}
+\NOTE[LKC]{Corrected.}
 
-\NOTE[LKC]{BUT, I am thinking about going further --- removing ``our improved'' from 
+\NOTE[LKC]{BUT, I am thinking about going further --- removing ``our improved'' 
+from 
 this paper. The first reason is that our BFS is actually more efficient than 
@@
 all.}
+\NOTE[LKC]{Yes, the comment about append will go away if we remove our improved 
+BFS. Then, let's don't remove it, i.e. have two new BFS implementations at the 
+same time.}
+\NOTE[LKC]{I think having two new BFSs is a bit confusing. So I brand the 
+new and easy/unimproved one as a ``stepping-stone'' and only mention it in BFS 
+section.}
+
+\begin{abstract}
 
@@
 search, and the standard breadth-first search.  The two non-standard
-depth-first searches are new. And we present two new, more efficient
-and shorter implementations of the standard breadth-first search.
-Using quantitative evaluation, we argue that the two new depth-first
-searches are competitive alternatives to the standard one, and that
-our breadth-first search implementations are more efficient than the
+depth-first searches are new. And we present a new, more efficient
+and shorter implementation of the standard breadth-first search.
+Using quantitative evaluation, we argue that a new depth-first searches is a
+competitive alternative to the standard one, and that our improved 
+breadth-first search implementation is more efficient than the
 current one.
@@
 
-\NOTE[DPF]{their BFS (or shortened to BFS). We need only say this once if we go with ``our'', which I don't like.
+\NOTE[DPF]{their BFS (or shortened to BFS). We need only say this once if we go 
+with ``our'', which I don't like.
 I like ``the new'' or ``the improved'' and ``the current'' }
+\NOTE[LKC]{Corrected. I pick ``the improved''.}
 
@@
 when a \conde{} contains many clauses: not every clause has an 
-equal chance of contributing to the result. As an example, consider the following 
+equal chance of contributing to the result. As an example, consider the 
+following 
 relation \repeato{} and its invocation.
@@
 
-\noindent Next, consider the following disjunction of invoking \repeato{} with four 
+\noindent Next, consider the following disjunction of invoking \repeato{} with 
+four 
 different letters.
@@
 
-\noindent \conde{} intuitively relates its clauses with logical \texttt{or}. And thus an 
+\noindent \conde{} intuitively relates its clauses with logical \texttt{or}. And 
+thus an 
 unsuspicious beginner would expect each letter to contribute equally to the 
@@
 \DFSi{} is not always the best choice. For instance, it might be less 
-desirable for novice miniKanrenuser---understanding implementation details and 
-fiddling with clause order is not their first priority. 
+desirable for novice miniKanren users---understanding implementation details 
+and fiddling with clause order is not their first priority. 
 There is another reason that miniKanren could use more search strategies than
@@
 a new search strategy with fair \disj{}.
-	\item implement in two new ways the standard breath-first search (\BFS), a 
-search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
-BFS implementation'' (``BFS'' for short) as the implementation by 
-\citet{seres1999algebra} and refer to ``our BFS implementation'' (``our BFS'' 
-for short) and ``our improved BFS implementation'' (``our improved BFS`` for 
-short) as our new ones. We also refer to ``our \BFS{}s'' to both \BFSuni{} and 
-\BFSimp{}. We argue that our \BFS{}s are semantically equivalent and formally 
-prove that \BFSimp{} and \BFSser{} are semantically equivalent, however, our 
-\BFS{}s run faster in all benchmarks and are shorter.
+	\item implement in a new way the standard breath-first search (\BFS) by 
+\citet{seres1999algebra}, a search strategy with fair \disj{} and fair \conj{}. 
+We refer to ``\BFSser{}'' as their implementation and ``the improved 
+BFS'' as our new one. We formally prove that the two implementations are 
+semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
+is shorter.
+%	\item implement in a new way the standard breath-first search (\BFS), a 
+%search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
+%BFS implementation'' (``BFS'' for short) as the one by 
+%\citet{seres1999algebra} 
+%and refer to ``our improved BFS implementation'' (``the improved BFS'' for 
+%short) as the new one. We formally prove that \BFSimp{} and \BFSser{} are 
+%semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
+%is shorter.
 \end{itemize}
@@
             so the first idea works best.}
+\NOTE[LKC]{I have rewritten the whole item.}
 
@@
 Before going further into fairness, we give a short review of the terms:
-\emph{state}, search \emph{space}, and \emph{goal}.
+\emph{state}, \emph{space}, and \emph{goal}.
 A \emph{state} is a collection of constraints. (Here, we restrict 
@@
 function from a state to a space.
-
-% Goals check their input states and outpust possibly extended states. A goal 
-% might fail for some inputs, in which case the output search space would be 
-% empty.
 
@@
 Given the following program, it is natural to expect lists of each
-letter to constitute $1/4$ in the query result. \DFSi, TRS2's search
+letter to constitute $1/4$ in the answer list. \DFSi, TRS2's search
 strategy, however, results in many more lists of \texttt{a}s than
@@
 Under the hood, the \conde{} here is allocating computational resources to 
-four trivially different search spaces. The unfair \disj{} in 
-\DFSi{} allocates many more resources to the first search space. On the 
-contrary, fair \disj{} would allocate resources evenly to each search space.
+four trivially different spaces. The unfair \disj{} in 
+\DFSi{} allocates many more resources to the first space. On the 
+contrary, fair \disj{} would allocate resources evenly to each space.
 
@@
 A \disj{} is fair if and only if it allocates computational resources evenly to 
-search spaces produced by goals in the same disjunction 
+spaces produced by goals in the same disjunction 
 (i.e., clauses in the same \conde).
@@
 A \disj{} is almost-fair if and only if it allocates computational resources
-so evenly to search spaces produced by goals in the same disjunction that 
+so evenly to spaces produced by goals in the same disjunction that 
 the maximal ratio of resources is bounded by a constant.
@@
 constitute $1/4$ in the answer list. Search strategies with unfair \conj{}:
-\DFSi, \DFSbi, and \DFSf, however, results in many more lists of \texttt{a}s than 
+\DFSi, \DFSbi, and \DFSf, however, results in many more lists of \texttt{a}s 
+than 
 lists of other letters. And some letters are rarely seen. Here again, as the
@@
 Under the hood, the \conde{} and the call to \repeato{} are connected by 
-\conj{}. The \conde{} goal outputs a search space including four trivially 
+\conj{}. The \conde{} goal outputs a space including four trivially 
 different states. 
 Applying the next conjunctive goal, \texttt{(repeato x q)}, produces four 
-trivially different search spaces.
+trivially different spaces.
 In the examples above, all search strategies allocate more computational 
-resources to the search space of \texttt{a}. On the contrary, fair \conj{} 
-would allocate resources evenly to each search space. For example,
+resources to the space of \texttt{a}. On the contrary, fair \conj{} 
+would allocate resources evenly to each space. For example,
 
@@
 Our solution requires a search strategy with \emph{fair} \conj{} to organize
-states in bags in search spaces, where each bag contains finite states, and 
-to allocate resources evenly among search spaces derived from states in the 
-same bag. It is up to a search strategy designer to decide by what criteria to 
-put states in the same bag, and how to allocate resources among search spaces 
-related to different bags.
+states in buckets in spaces, where each bucket contains finite states, 
+and 
+to allocate resources evenly among spaces derived from states in the 
+same bucket. It is up to a search strategy designer to decide by what criteria 
+to 
+put states in the same bucket, and how to allocate resources among spaces 
+related to different buckets.
 
-\BFS{} puts states of the same cost in the same bag, and allocates
-resources carefully among search spaces related to different bags such
+\BFS{} puts states of the same cost in the same bucket, and allocates
+resources carefully among spaces related to different buckets such
 that it produces answers in increasing order of cost. The \emph{cost}
 of an answer is its depth in the search tree (i.e., the number of
-calls to relations required to find them) \citep{seres1999algebra}. In
-the following example, every answer is a list of a list of symbols,
-where inner lists in the same outer list are identical. Here the cost of each 
-answer is equal
-to the length of its inner list plus the length of its outer list. For example,
-the cost of \texttt{((a) (a))} is $1 + 2 = 3$.
+calls to relational definitions required to find the answer) 
+\citep{seres1999algebra}. In the above examples, the cost of each answer is 
+equal to their lengths because we need to apply \repeato{} $n$ times to find an 
+answer of length $n$. In the following example, every answer is a list of a 
+list of symbols, where inner lists in the same outer list are identical. Here 
+the cost of each answer is equal to the length of its inner lists plus the 
+length of its outer list. For example, the cost of \texttt{((a) (a))} is $1 + 2 
+= 3$.
 
@@
 generalize to all costs.}
-\NOTE[LKC]{I mean for all answer in the answer list, the answer's inner lists 
-are pairwise \texttt{equal?}. It is impossible to see a \texttt{((a) (b))} in 
-the answer list.}
+\NOTE[LKC]{Corrected.}
 
@@
 A \conj{} is fair if and only if it allocates computational resources evenly to 
-search spaces produced from states in the same bag. A bag is a finite 
+spaces produced from states in the same bucket. A bucket is a finite 
 collection of states. And search strategies with fair \conj{} should represent 
-search spaces with possibly unbounded collections of bags. 
+spaces with possibly unbounded collections of buckets. 
 \end{defn}
@@
 chapter 10 and the appendix, ``Connecting the wires'', 
-provide a comprehensive description of the 
-miniKanren 
+provide a comprehensive description of the miniKanren 
 implementation but limited to unification constraints ($\equiv$).
 Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} show parts that are later compared 
-with other search 
-strategies. We follow some conventions to name variables: \texttt{s}s name 
-states; \texttt{g}s (possibly with subscript) name goals; 
-variables ending with $^\infty$ name (search) spaces. Fig.~\ref{DFSi-0} shows the 
+with other search strategies. We follow some conventions to name variables: 
+\texttt{s}s name states; \texttt{g}s (possibly with subscript) name goals; 
+variables ending with $^\infty$ name (search) spaces. Fig.~\ref{DFSi-0} shows 
+the 
 implementation of \disj. The 
@@
 two disjunctive goals to the input state \texttt{s} and composes the two 
-resulting search spaces with \texttt{append$^\infty$}. The following syntax 
+resulting spaces with \appendInf{}. The following syntax 
 definitions say \disj{} is right-associative. Fig.~\ref{DFSi-1} 
@@
 It applies the \emph{first} goal to the input state, then applies the second 
-goal to states in the resulting search space. The helper function 
-\texttt{append-map$^\infty$} applies its input goal to states 
-in its input search spaces and composes the resulting search spaces. It reuses 
-\texttt{append$^\infty$} for search space composition. The following syntax 
+goal to states in the resulting space. The helper function 
+\appendMapInf{} applies its input goal to states 
+in its input space and composes the resulting spaces. It reuses 
+\appendInf{} for space composition. The following syntax 
 definitions say \conj{} is also right-associative.
@@
 \conj{}. The implementation of \DFSbi{} differs from 
-\DFSi{}'s in the \disj{} macro. We list the new \disj{} with its 
-helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
-goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
+\DFSi{}'s in the \disj{} macro. When there are one or more disjunctive 
+goals, the new \disj{} builds a balanced binary tree whose leaves are the goals 
+and 
 whose nodes are \disjtwo{}s, hence the name of this search strategy. 
+In contrast, the \disj{} in \DFSi{} constructs the binary tree in a 
+particularly unbalanced form.
+We list the new \disj{} with its helper in Fig.~\ref{balanced-disj}.
 The new helper, \texttt{disj+}, takes two additional `arguments'. They 
@@
 goal remains. We handle these two new base cases in the second clause and the 
-third clause, respectively. In contrast, the \disj{} in \DFSi{} constructs the 
-binary tree in a particularly unbalanced form.
+third clause, respectively.
 
@@
 \disjtwo{} (Fig.~\ref{fDFS}). The new \disjtwo{} calls a new and 
-fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
+fair version of \appendInf{}. \appendInfFair{} 
 immediately 
@@
 \texttt{\#{}t}, which indicates that we haven't swapped
-\texttt{s$^\infty$} and \texttt{t$^\infty$}. The swapping 
+\sInf{} and \tInf{}. The swapping 
 happens at 
@@
 finite. The third clause, as we mentioned above, is just for swapping. When the 
-fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
-\texttt{t$^\infty$} are ended with a thunk, and that we have swapped them. In 
-this case, we construct a new thunk. The new thunk swaps back the two spaces in the
+fourth and last clause runs, we know that both \sInf{} and 
+\tInf{} are ended with a thunk, and that we have swapped them. In 
+this case, we construct a new thunk. The new thunk swaps back the two spaces in 
+the
 recursive call to \texttt{loop}. This is unnecessary for fairness---we do it to 
@@
 	\lstinputlisting{Figures/BFSuni.rkt}	
-	\caption{implementation of \BFSuni{} (based on \DFSf{})}
+	\caption{stepping-stone toward \BFSimp{} (based on \DFSf{})}
 	\label{BFSuni}
@@
 
-\BFS{} has both fair \disj{} and fair \conj{}. Our first implementation 
-(\autoref{BFSuni}) is based on \DFSf{} (not \DFSi{}). It is so similar to 
-\DFSf{} that we only need to apply two changes: (1) rename 
-\texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$} and (2) 
-replace \texttt{append$^\infty$} with \texttt{append$^\infty_{fair}$} in 
-\texttt{append-map$^\infty$}'s body.
+\BFS{} has both fair \disj{} and fair \conj{}. Our first BFS implementation 
+serves as a ``stepping-stone'' toward \BFSimp{}. It is so similar to \DFSf{} 
+(not \DFSi{}) that we only need to apply two changes: (1) rename 
+\appendMapInf{} 
+to \appendMapInfFair{} and (2) replace \appendInf{} with \appendInfFair{} in 
+\appendMapInfFair{}'s body.
 
@@
 	``our \BFS,'' but yet a third implementation of \BFS?}
-\NOTE[LKC]{Improved.}
+\NOTE[LKC]{If you still need clarification, please add a new note below. 
+Otherwise, you might delete these two notes.}
 
@@
 I read it.}
+\NOTE[LKC]{I am sorry about that. Thank you for telling me! I have added many 
+more macros and have removed many uses of texttt.}
 
@@
 For example, the list (a b a c a d c) could be represented like this:
-(a$^3$ b$^1$ c$^2$ d$^1$).  If that is not what you mean, you might change the name
-to bucket.}
+(a$^3$ b$^1$ c$^2$ d$^1$).  If that is not what you mean, you might change the 
+name to bucket.}
+\NOTE[LKC]{That is not what I mean. I have changed the name to bucket.}
 
 This implementation can be improved in two ways. First, as mentioned in 
-\autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
-cost are in the same bag. In the above implementation, however, 
+\autoref{sec:fairconj}, \BFS{} puts answers in buckets and answers of the same 
+cost are in the same bucket. In the above implementation, however, 
 it is not obvious how we manage cost information---the \texttt{car}s of a 
-search space have cost 0 (i.e., they are all in the same bag), and every thunk 
-indicates an increment in cost. It is even more subtle that 
-\texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
-respects the cost information. Second, \texttt{append$^\infty_{fair}$} is 
-extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
-time, where $n$ and $m$ are the ``length''s of input spaces. \DFSf{} also has 
-the space extravagance.
+space have cost 0 (i.e., they are all in the same bucket), and every 
+thunk indicates an increment in cost. It is even more subtle that 
+\appendInfFair{} and the \appendMapInfFair{} respects the cost information. 
+Second, \appendInfFair{} is extravagant in memory usage. It makes $O(n+m)$ new 
+\texttt{cons} cells every time, where $n$ and $m$ are the sizes of 
+the first buckets of two input spaces. \DFSf{} also has the space extravagance.
+
+\NOTE[LKC]{I rewrite the second last sentence in the above paragraph such that 
+it better corresponds to the comment about `append'.}
 
@@
 
-\NOTE[DPF]{Let's use one more line and far less horizontal space
-by use 3 linefeeds.  They will still align nicely.}
-\NOTE[LKC]{fixed}
-
 \subsection{improved BFS}
@@
 	\lstinputlisting{Figures/BFSimp.rkt}	
-	\caption{New and changed functions in our BFS that implements pure 
+	\caption{New and changed functions in \BFSimp{} that implements pure 
 	features}
@@
 
-% As mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
-% answers of the same cost are in the same bag. 
-% In the easy implementation, cost information is recorded subtly---the 
-% \texttt{car}s of a search space have cost 0 (i.e. they are all in the same 
-% bag),
-% and every thunk indicates an increment in cost. It is even more subtle that
-% \texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
-% respects the cost information. We make these facts more obvious by changing 
-% the type of search space, modifying related function definitions, and 
-% introducing a few more functions.
+\NOTE[DPF]{Font Space like in the code comments.}
+\NOTE[LKC]{corrected}
 
-\NOTE[DPF]{Font Space like in the code comments.}
-
-We make the cost information more clear by changing the Space type, 
+We make the cost information more clear by changing the \texttt{Space} type, 
 modifying related function definitions, and introducing a few more functions.
 
-The new type is a pair whose \texttt{car} is a list of answers (the bag), and 
-whose \texttt{cdr} is either \texttt{\#{}f} or a thunk returning a search 
-space. A falsy \texttt{cdr} means the search space is obviously finite.
+The new type of \texttt{Space} is a pair whose \texttt{car} is a list of 
+answers (the bucket), and whose \texttt{cdr} is either \texttt{\#{}f} or a 
+thunk returning a space. A falsy \texttt{cdr} means the space is obviously 
+finite.
 
 We list functions related to the pure subset in Fig.~\ref{BFSimp}. The first 
-three functions are search space constructors. \texttt{none} makes an empty 
-search space; \texttt{unit} makes a space from one answer; and \texttt{step} 
-makes a space from a thunk. The remaining functions are as before. We compare 
-these functions with \BFSser{} in our proof.
+three functions are space constructors. \texttt{none} makes an empty space; 
+\texttt{unit} makes a space from one answer; and \texttt{step} makes a space 
+from a thunk. The remaining functions are as before. We compare these functions 
+with \BFSser{} in our proof.
 
-Luckily, the change in \texttt{append$^\infty_{fair}$} also fixes the miserable 
-space extravagance---the use of \texttt{append} helps us to reuse the first bag 
-of \texttt{t$^\infty$}.
+Luckily, the change in \appendInfFair{} also fixes the miserable space 
+extravagance---the use of \texttt{append} helps us to reuse the first 
+bucket of \tInf{}.
 
 \citet{kiselyov2005backtracking} have demonstrated that a \emph{MonadPlus} 
-hides in implementations of logic programming system. \BFSimp{} is not an 
-exception: \texttt{append-map$^\infty_{fair}$} is like \texttt{bind}, but takes 
+hides in implementations of logic programming systems. \BFSimp{} is not an 
+exception: \appendMapInfFair{} is like \texttt{bind}, but takes 
 arguments in reversed order; \texttt{none}, \texttt{unit}, and 
-\texttt{append$^\infty_{fair}$} correspond to \texttt{mzero}, \texttt{unit}, and 
+\appendInfFair{} correspond to \texttt{mzero}, \texttt{unit}, and 
 \texttt{mplus}, respectively.
@@
 	\lstinputlisting{Figures/BFSimp-cont.rkt}	
-	\caption{New and changed functions in our BFS that implement impure 
+	\caption{New and changed functions in \BFSimp{} that implement impure 
 		features}
@@
 mean success continuation and failure continuation.}
+\NOTE[LKC]{corrected}
 
 Functions implementing impure features are in Fig.~\ref{BFSimp-cont}. The 
-first function, \texttt{elim}, takes a space \texttt{s$^\infty$} and two 
-continuations \texttt{kf} and \texttt{ks}. When \texttt{s$^\infty$} contains 
-no answers, it calls \texttt{kf} with no argument. Otherwise, it calls 
-\texttt{ks} with the first answer and the rest of the space. Here  `f' means 
-`fail' and `s' means `succeed'. This function is similar to an eliminator of 
-search spaces, hence the name. The remaining functions are as before.
+first function, \texttt{elim}, takes a space \sInf{} and two 
+continuations \texttt{fk} and \texttt{sk}. When \sInf{} contains 
+no answers, it calls \texttt{fk} with no argument. Otherwise, it calls 
+\texttt{sk} with the first answer and the rest of the space. This function is 
+similar to an eliminator of spaces, hence the name. The remaining 
+functions are as before.
 
@@
 are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
-result in both our BFS and BFS. (See supplements for the formal proof.) To 
-compare efficiency, we 
-translate \BFS{}'s Haskell code into Racket (See supplements for the 
-translated code). The translation is direct due to the similarity of the two 
-relational programming systems. The translated code is longer than \BFSimp{}. 
-And it runs slower in all benchmarks. Details about differences in efficiency 
-are in \autoref{sec:quan}.
-% \autoref{compare-efficiency}
+result in both \BFSimp{} and BFS. (See supplements for the formal proof.) To 
+compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See 
+supplements for the translated code). The translation is direct due to the 
+similarity of the two relational programming systems. The translated code is 
+longer than \BFSimp{}. And it runs slower in all benchmarks. Details about 
+differences in efficiency are in \autoref{sec:quan}.
 
@@
 	% run in command line, with a memory limit of 500MB
-	\begin{tabular}{|c|c|c|c|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|c|}
 		\hline 
-	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSuni & \BFSimp & \BFSser	\\
+	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSimp & \BFSser	\\
 		\hline
-		\veryrecursiveo & 100000 & 166 & 103 & 412 &   417 &   451 &   1024 \\
-	    				& 200000 & 283 & 146 & 765 &   766 &   839 &   1875 \\
-						& 300000 & 429 & 346 &2085 &  2066 &  1809 &   4408 \\
+		\veryrecursiveo & 100000 & 166 & 103 & 412 &   451 &   1024 \\
+	    				& 200000 & 283 & 146 & 765 &   839 &   1875 \\
+						& 300000 & 429 & 346 &2085 &  1809 &   4408 \\
 		\hline  
-		\appendo        & 	 100 &  17 &  18 &  17 &    18 &    17 &     65 \\
-		         	  	& 	 200 & 145 & 137 & 137 &   137 &   142 &    121 \\
-          		      	&	 300 & 388 & 384 & 387 &   383 &   429 &    371 \\
+		\appendo        & 	 100 &  17 &  18 &  17 &    17 &     65 \\
+		         	  	& 	 200 & 145 & 137 & 137 &   142 &    121 \\
+          		      	&	 300 & 388 & 384 & 387 &   429 &    371 \\
 %   		& - & - & - & - & - & - \\
 		\hline 
-		\reverso		& 	  10 &   3 &   4 &   3 &    18 &    18 &     36 \\
-						& 	  20 &  35 &  35 &  33 &  3119 &  3070 &   3695 \\
-						& 	  30 & 329 & 333 & 315 & 76243 & 75079 & 107531 \\
+		\reverso		& 	  10 &   3 &   4 &   3 &    18 &     36 \\
+						& 	  20 &  35 &  35 &  33 &  3070 &   3695 \\
+						& 	  30 & 329 & 333 & 315 & 75079 & 107531 \\
 		\hline
-		quine-1 		& 1 & 13 & 14 & 10 & - & - & - \\
-						& 2 & 30 & 34 & 25 & - & - & - \\
-						& 3 & 41 & 48 & 33 & - & - & - \\
+		quine-1 		& 1 & 13 & 14 & 10 & - & - \\
+						& 2 & 30 & 34 & 25 & - & - \\
+						& 3 & 41 & 48 & 33 & - & - \\
 		\hline
-		quine-2 		& 1 & 22 & 21 & 12 & - & - & - \\
-						& 2 & 51 & 46 & 24 & - & - & - \\
-						& 3 & 72 & 76 & 32 & - & - & - \\
+		quine-2 		& 1 & 22 & 21 & 12 & - & - \\
+						& 2 & 51 & 46 & 24 & - & - \\
+						& 3 & 72 & 76 & 32 & - & - \\
 		\hline
+		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   96 \\
+						& 198 &  22 &  71 & - &  374 &  652 \\
+						& 297 &  24 & 292 & - & 1668 & 3759 \\
+		\hline
+		'(I love you)-2 &  99 & 485 & 179 & - &   44 &   94 \\
+						& 198 & 808 & 638 & - &  414 &  630 \\
+						& 297 &1265 & 916 & - & 1651 & 3691 \\ 
+		\hline 
+		% The data below is test with old benchmarks
 %		quine-1 & 1 &  71 &  44 & 69 & ??? & - & - \\ 
@@
 %		\hline 
-		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   40 &   96 \\
-						& 198 &  22 &  71 & - &  374 &  374 &  652 \\
-						& 297 &  24 & 292 & - & 1707 & 1668 & 3759 \\
-		\hline
-		'(I love you)-2 &  99 & 485 & 179 & - &   38 &   44 &   94 \\
-						& 198 & 808 & 638 & - &  366 &  414 &  630 \\
-						& 297 &1265 & 916 & - & 1674 & 1651 & 3691 \\ 
-		\hline 
-		% The data below is test with old benchmarks
 %'(I love you)-1 &  99 & 56 & 15 & 22 & ??? &  74 & 165 \\ 
@@
 description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
-of 500 MB memory.'' The first two benchmarks are from 
+of 500 MB memory''. The first two benchmarks are from 
 TRS2. \reverso{} is from 
 \citet{rozplokhas2018improving}. 
-The next two benchmarks about quine are modified from a similar test case in 
-\citet{byrd2017unified}. The modifications are made to circumvent the need for 
-symbolic constraints (e.g. $\neq$, \texttt{absent$^o$}).
-Our version generates de Bruijnized expressions and prevents closures from 
-being inside a list. 
-The sibling benchmarks differ in the \conde{} clause order of their relational 
+The next two benchmarks about quine are based on a similar test case in 
+\citet{byrd2017unified}. We modify the relational interpreters because we don't 
+have disequality constraints (e.g. \texttt{absent$^o$}). The sibling 
+benchmarks differ in the \conde{} clause order of their relational 
 interpreters.
-The last two benchmarks are about synthesizing expressions that evaluate to 
-\texttt{'(I love you)}. 
-They are also modified from a similar test case in \citet{byrd2017unified} 
-because of the same reason. 
-Our version generates de Bruijnized expressions. 
-Again, the sibling benchmarks differ in the \conde{} clause order of their 
-relational interpreters. The first one has elimination rules (i.e. application, 
+The last two benchmarks are about synthesizing expressions that 
+evaluate to \texttt{'(I love you)}. 
+They are also based on a similar test case in \citet{byrd2017unified}. Again, 
+we modify the relational interpreters for the same reason. And the sibling 
+benchmarks differ in the \conde{} clause order of their relational 
+interpreters. The first one has elimination rules (i.e. application, 
 \texttt{car}, and \texttt{cdr}) at the end, while the other has them at the 
-beginning. 
-We conjecture that \DFSi{} would perform badly in the second case because 
-elimination rules complicate the problem when synthesizing (i.e., our 
+beginning. We conjecture that \DFSi{} would perform badly in the second case 
+because elimination rules complicate the problem when synthesizing (i.e., our 
 evaluation supports our conjecture.)
-
-\NOTE[LKC]{I have changed the benchmarks about '(I love you), such that their 
-relational interpreters doesn't prevent closures from getting into pairs. I did 
-so because I consider this restriction doesn't make sense. Benchmarks about 
-quine are already very slow so I didn't apply similar changes.}
 
@@
 say that.}
+\NOTE[LKC]{Corrected.}
 
@@
 search strategy. 
-Among the three implementations of \BFS, our \BFS{}s constantly perform as well 
-or better. Among our \BFS{}s, \BFSimp{} only performs better in 
-\veryrecursiveo{} 300000. The reason might be that the size of bags are usually 
-too small to be worried about. 
+Among the two implementations of \BFS, \BFSimp{} constantly perform as well 
+or better. 
 It is hard to conclude how \disj{} fairness affect performance based on these 
@@
 We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
-new definition of fair \conj{}. Our definition is orthogonal with completeness.
+new definition of fair \conj{}. Our definition of fair \conj{} is orthogonal 
+with completeness.
 
 We devise two new search strategies (i.e. balanced interleaving DFS 
-(\DFSbi{}) and fair DFS (\DFSf{})) and devise two new 
-implementations of \BFS. These strategies have different features 
+(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
+implementation of \BFS. These strategies have different features 
 in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
@@
 alternative to \DFSi{}, the current miniKanren search strategy,
-and that \BFS{} is less practical.
-% and that \BFSser{} is less practical than other breadth-first strategies.
+and that \BFSimp{} is more practical than \BFSser{}.
 
-Our improved \BFS{} is semantically equivalent to the original 
-one. But, ours is shorter and performs better in comparison with a 
-straightforward translation of their Haskell code.
+% \BFSimp{}
+We proof formally that \BFSimp{} is semantically equivalent to \BFSser{}. But, 
+\BFSimp{} is shorter and performs better in comparison with a straightforward 
+translation of their Haskell code.
 
-% We acknowledge that we are making large claims about efficiency given
-% that we have just a few benchmarks, but our intuition is based on
-% sound principles.
+We acknowledge that we are making large claims about efficiency given that we 
+have just a few benchmarks, but our intuition is based on sound principles. ...
 
@@
 Weixi.}
-\NOTE[LKC]{I will do it later.}
+\NOTE[LKC]{I have sent an email to Weixi on the clarification.}
 

### 2019-05-25 Paper/paper.tex
rescue paper.tex

@@
 
-\NOTE[DPF]{Throughout the paper we have search spaces and search strategies.
-I can see leaving in the  ``search strategies'', but let's try to
-remove virtually all of the uses of ``search'' in front of spaces.}
-\NOTE[LKC]{Corrected.}
-
-\NOTE[LKC]{BUT, I am thinking about going further --- removing ``our improved'' 
-from 
-this paper. The first reason is that our BFS is actually more efficient than 
-our improved BFS in most benchmarks (see Table 1), despite its theoretical 
-space extravagence. The second reason is that DFSi, DFSf, and our BFS look nice 
-when sitting together.}
-
-\NOTE[DPF]{Does this mean that the comment about append goes away.
-I really thought that was so clever.  I thought that the way you pointed
-out the trivial changes was very clear, so that did not bother me at
-all.}
-\NOTE[LKC]{Yes, the comment about append will go away if we remove our improved 
-BFS. Then, let's don't remove it, i.e. have two new BFS implementations at the 
-same time.}
-\NOTE[LKC]{I think having two new BFSs is a bit confusing. So I brand the 
-new and easy/unimproved one as a ``stepping-stone'' and only mention it in BFS 
-section.}
-
 \begin{abstract}
@@
 and shorter implementation of the standard breadth-first search.
-Using quantitative evaluation, we argue that a new depth-first searches is a
+Using quantitative evaluation, we argue that each depth-first search is a
 competitive alternative to the standard one, and that our improved 
@@
 
-\NOTE[DPF]{their BFS (or shortened to BFS). We need only say this once if we go 
-with ``our'', which I don't like.
-I like ``the new'' or ``the improved'' and ``the current'' }
-\NOTE[LKC]{Corrected. I pick ``the improved''.}
+\NOTE[DPF]{``current'' was for BFSser}
 
@@
 
-\NOTE[DPF]{The citetseres1999algebra must be not broken:
-            You can either rewrite the sentence or
-            use a tilde called a tie that means don't break the line.
-            Sometimes using tilde does not work out elegant enough,
-            so the first idea works best.}
-\NOTE[LKC]{I have rewritten the whole item.}
-
 \section{search strategies and fairness}
@@
 have an unbounded number of answers. It is perfectly fine, however, to use 
-\runstar{} with any search strategies.
+\runstar{} with any search strategy.
 
@@
 
-Under the hood, the \conde{} here is allocating computational resources to 
+Under the hood, the \conde{} here allocates computational resources to 
 four trivially different spaces. The unfair \disj{} in 
@@
 \DFSbi{} is fair only when the number of goals is a power of 2, 
-otherwise, it allocates some goals twice as many resources as the 
+otherwise, it allocates some goals with twice as many resources as the 
 others. In the above example, where the \conde{} has five clauses, \DFSbi{} 
@@
 = 3$.
-
-\NOTE[DPF]{Can you express exactly how all costs are determined?  I see that
-for this simple program, your notion of cost makes sense, but how does it
-generalize to all costs.}
-\NOTE[LKC]{Corrected.}
 
@@
 
-\NOTE[DPF]{I need clarification: Applying the above changes won't result in 
-	``our \BFS,'' but yet a third implementation of \BFS?}
-\NOTE[LKC]{If you still need clarification, please add a new note below. 
-Otherwise, you might delete these two notes.}
-
-\NOTE[DPF]{Why are the two texttt's macros, again?  Now, it hardly matters,
-but it is unfriendly to your other co-authors to have us reading long
-expressions when a newcommand would suffice.  I read the paper with a pen
-marking it up, then I read the paper on the .tex screen.  That's each time
-I read it.}
-\NOTE[LKC]{I am sorry about that. Thank you for telling me! I have added many 
-more macros and have removed many uses of texttt.}
-
-\NOTE[DPF]{You know that ``bag'' is a technical terms.  It means that there
-is a structure where each element of the structure has an associated number, 
-which tells you have many occurrences of that element are in the list.
-For example, the list (a b a c a d c) could be represented like this:
-(a$^3$ b$^1$ c$^2$ d$^1$).  If that is not what you mean, you might change the 
-name to bucket.}
-\NOTE[LKC]{That is not what I mean. I have changed the name to bucket.}
-
 This implementation can be improved in two ways. First, as mentioned in 
@@
 the first buckets of two input spaces. \DFSf{} also has the space extravagance.
-
-\NOTE[LKC]{I rewrite the second last sentence in the above paragraph such that 
-it better corresponds to the comment about `append'.}
 
@@
 
-\NOTE[DPF]{Font Space like in the code comments.}
-\NOTE[LKC]{corrected}
-
-We make the cost information more clear by changing the \texttt{Space} type, 
+We simplify the cost information by changing the \texttt{Space} type, 
 modifying related function definitions, and introducing a few more functions.
@@
 
-\NOTE[DPF]{ks --> sk and kf --> fk and you don't need to say f and s
-mean success continuation and failure continuation.}
-\NOTE[LKC]{corrected}
-
 Functions implementing impure features are in Fig.~\ref{BFSimp-cont}. The 
@@
 continuations \texttt{fk} and \texttt{sk}. When \sInf{} contains 
-no answers, it calls \texttt{fk} with no argument. Otherwise, it calls 
+no answers, it calls \texttt{fk}. Otherwise, it calls 
 \texttt{sk} with the first answer and the rest of the space. This function is 
@@
 are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
-result in both \BFSimp{} and BFS. (See supplements for the formal proof.) To 
+result in both BFS and \BFSimp{}. (See supplements for the formal proof.) To 
 compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See 
@@
 differences in efficiency are in \autoref{sec:quan}.
+
+\NOTE[DPF]{Make another macro or use a number when we want to drop ``the''
+from ``the improved BFS''.  In the table below, use that macro.}
 
@@
 
+\NOTE[DPF]{tilde problem 7 lines down.}
+
 In this section, we compare the efficiency of search strategies. A concise 
@@
 
-\NOTE[DPF]{We don't have disequality constraints, so no absento.  You might just
-say that.}
-\NOTE[LKC]{Corrected.}
-
 In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
@@
 \DFSi{}. \DFSf{}, however, runs out of memory in \texttt{'(I love you)}s. In 
-contrast, \DFSbi{} still performs more stable than \DFSi{}. Thus, we consider 
+contrast, \DFSbi{} is still more stable than \DFSi{}. Thus, we consider 
 \DFSbi{} a competitive alternative to \DFSi{}, the current standard miniKanren 
 search strategy. 
-Among the two implementations of \BFS, \BFSimp{} constantly perform as well 
+Among the two implementations of \BFS, \BFSimp{} constantly performs as well 
 or better. 
-It is hard to conclude how \disj{} fairness affect performance based on these 
+It is hard to conclude how \disj{} fairness affects performance based on these 
 statistics.
@@
 % \BFSimp{}
-We proof formally that \BFSimp{} is semantically equivalent to \BFSser{}. But, 
+We prove formally that \BFSimp{} is semantically equivalent to \BFSser{}. But, 
 \BFSimp{} is shorter and performs better in comparison with a straightforward 
 translation of their Haskell code.
+
+\NOTE[DPF]{Please leave ``prove'' and don't use ``proof''.}
 

### 2019-05-25 Paper/paper.tex
respond notes
responds to all notes

@@
 \newcommand{\BFSimp}[0]{the improved BFS}
+\newcommand{\BFSim}[0]{improved BFS}
 
@@
 \NOTE[DPF]{``current'' was for BFSser}
+\NOTE[LKC]{Do you mean I should not reserve ``current'' for BFSser, or I should 
+do so?}
 
@@
 is shorter.
-%	\item implement in a new way the standard breath-first search (\BFS), a 
-%search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
-%BFS implementation'' (``BFS'' for short) as the one by 
-%\citet{seres1999algebra} 
-%and refer to ``our improved BFS implementation'' (``the improved BFS'' for 
-%short) as the new one. We formally prove that \BFSimp{} and \BFSser{} are 
-%semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
-%is shorter.
 \end{itemize}
@@
 \texttt{unit} makes a space from one answer; and \texttt{step} makes a space 
-from a thunk. The remaining functions are as before. We compare these functions 
-with \BFSser{} in our proof.
+from a thunk. The remaining functions are as before. 
+%We compare these functions 
+%with \BFSser{} in our proof.
+
+\NOTE[LKC]{I delete the ending sentence of the above paragraph.}
 
@@
 from ``the improved BFS''.  In the table below, use that macro.}
+\NOTE[LKC]{I have defined another macro BFSim, which doesn't start with 
+``the''. Also, I have corrected the table below.}
 
@@
 		\hline 
-	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSimp & \BFSser	\\
+	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSim & \BFSser	\\
 		\hline
@@
 \NOTE[DPF]{tilde problem 7 lines down.}
+\NOTE[LKC]{Corrected.}
 
@@
 evaluate to \texttt{'(I love you)}. 
-They are also based on a similar test case in \citet{byrd2017unified}. Again, 
+They are also based on a similar test case in \mbox{\citet{byrd2017unified}}. 
+Again, 
 we modify the relational interpreters for the same reason. And the sibling 
@@
 \NOTE[DPF]{Please leave ``prove'' and don't use ``proof''.}
+\NOTE[LKC]{Do you mean we should not use the word ``proof'' everywhere in this 
+paper?}
 

### 2019-05-26 Paper/paper.tex
update

@@
 \newcommand{\BFS}[0]{BFS}
-\newcommand{\BFSser}[0]{BFS}
+\newcommand{\BFSser}[0]{the current BFS}
+\newcommand{\BFSse}[0]{current BFS}
 \newcommand{\BFSimp}[0]{the improved BFS}
@@
 \BFS{} has both fair \disj{} and fair \conj{}. Our first BFS implementation 
-serves as a ``stepping-stone'' toward \BFSimp{}. It is so similar to \DFSf{} 
+(Fig.~\ref{BFSuni})
+serves as a ``stepping-stone'' toward \BFSimp{}. It is so 
+similar to \DFSf{} 
 (not \DFSi{}) that we only need to apply two changes: (1) rename 
@@
 relational programming system. We prove in Coq that these two search strategies 
-are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
-result in both BFS and \BFSimp{}. (See supplements for the formal proof.) To 
+are are semantically equivalent, since the result of \texttt{(run n ? g)} is 
+the same either way. (See supplements for the formal proof.) To 
 compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See 
@@
 		\hline 
-	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSim & \BFSser	\\
+	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSim & \BFSse	\\
 		\hline

### 2019-05-26 Paper/paper.tex
Just a few loose ends

@@
 
-\NOTE[DPF]{``current'' was for BFSser}
-\NOTE[LKC]{Do you mean I should not reserve ``current'' for BFSser, or I should 
-do so?}
+\NOTE[DPF]{``current'' was for BFSser if we need it, which we probably won't
+since the re-emergence of BFSser.  So let's reserve the word just in case.}
 
@@
 
-The miniKanren in TRS2 implements interleaving DFS (\DFSi), the cause of this 
+The miniKanren in TRS2 implements \textbf{i}nterleaving DFS (\DFSi), the cause of this 
 unexpected result. With this search strategy, each \conde{} clause takes half 
@@
 lists of other letters. And some letters (e.g. \texttt{c} and
-\texttt{d}) are rarely seen. The more clauses the worse the situation.
+\texttt{d}) are rarely seen. The more clauses, the worse the situation.
 
@@
 \texttt{cons} cells every time, where $n$ and $m$ are the sizes of 
-the first buckets of two input spaces. \DFSf{} also has the space extravagance.
+the first buckets of two input spaces. \DFSf{} is also space extravagant.
 
@@
 %with \BFSser{} in our proof.
-
-\NOTE[LKC]{I delete the ending sentence of the above paragraph.}
 
@@
 relational programming system. We prove in Coq that these two search strategies 
-are are semantically equivalent, since the result of \texttt{(run n ? g)} is 
+are semantically equivalent, since the result of \texttt{(run n ? g)} is 
 the same either way. (See supplements for the formal proof.) To 
@@
 differences in efficiency are in \autoref{sec:quan}.
-
-\NOTE[DPF]{Make another macro or use a number when we want to drop ``the''
-from ``the improved BFS''.  In the table below, use that macro.}
-\NOTE[LKC]{I have defined another macro BFSim, which doesn't start with 
-``the''. Also, I have corrected the table below.}
 
@@
 
-\NOTE[DPF]{tilde problem 7 lines down.}
-\NOTE[LKC]{Corrected.}
-
 In this section, we compare the efficiency of search strategies. A concise 
@@
 contrast, \DFSbi{} is still more stable than \DFSi{}. Thus, we consider 
-\DFSbi{} a competitive alternative to \DFSi{}, the current standard miniKanren 
-search strategy. 
+\DFSbi{} a competitive alternative to \DFSi{}.
 Among the two implementations of \BFS, \BFSimp{} constantly performs as well 
@@
 
-\NOTE[DPF]{Please leave ``prove'' and don't use ``proof''.}
-\NOTE[LKC]{Do you mean we should not use the word ``proof'' everywhere in this 
-paper?}
+\NOTE[DPF]{Please leave ``prove'' (just here).}
 

### 2019-05-26 Paper/paper.tex
LKC responds to notes

@@
 since the re-emergence of BFSser.  So let's reserve the word just in case.}
+\NOTE[LKC]{What do you mean by ``re-emergence''?}
 
@@
 
-We devise two new search strategies (i.e. balanced interleaving DFS 
+We devise two new search strategies (i.e., balanced interleaving DFS 
 (\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
@@
 \NOTE[DPF]{Please leave ``prove'' (just here).}
+\NOTE[LKC]{OK. I won't touch it.}
 

### 2019-05-27 Paper/paper.tex
merge with dan-sw-19-paper

@@
   mathescape=true,
-  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
+  literate={-inf}{{$^\infty$}}{1}{/fair}{{$_{fair}$}}{3}
   		   {→}{{$\rightarrow$}}{1}
@@
 and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
-Scheme, miniKanren has been ported to many other languages (e.g. 
-OCanren\citep{kosarev2018typed}). \citet{byrd2017unified} have 
-demonstrated that miniKanren programs are useful in solving several difficult
-problems. miniKanren.org contains the seeds of many difficult problems and 
+Scheme, miniKanren has been implemented in many other languages, including
+multiple ones using the same language. (See miniKanren.org.) This has come
+about because of Hemann et al.'s work on microKanren. Also, miniKanren
+has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
+\citet{byrd2017unified} have 
+demonstrated that miniKanren problems that at first reading seem impossible
+are indeed possible by using a Scheme interpreter written in miniKanren, thereby
+having access to logic variables within Scheme.
+miniKanren.org contains the seeds of many interesting problems and 
 their solutions.
 
-\NOTE[DPF]{``current'' was for BFSser if we need it, which we probably won't
-since the re-emergence of BFSser.  So let's reserve the word just in case.}
-\NOTE[LKC]{What do you mean by ``re-emergence''?}
+\NOTE[DPF]{I thought we agreed to use BFSser throughout?  
+In that sense it had emerged a few days ago, and now it has
+re-emerged.  It is what we are going to use instead of ``current''.}
 
@@
 
-Balanced interleaving DFS (\DFSbi{}) has an almost-fair \disj{} and unfair 
+The strategy \textbf{b}alanced \textbf{i}nterleaving DFS (\DFSbi{}) has an 
+almost-fair \disj{} and unfair 
 \conj{}. The implementation of \DFSbi{} differs from 
@@
 calls 
-its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
+its helper, \texttt{loop}, with the first argument, \texttt{s?}, initialized to 
 \texttt{\#{}t}, which indicates that we haven't swapped
@@
 happens at 
-the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
+the third \texttt{cond} clause in \texttt{loop}, where \texttt{s?} is updated 
 accordingly. The first two \texttt{cond} clauses essentially copy the 
@@
 
-In this section, we compare the efficiency of search strategies. A concise 
+In this section, we compare the efficiency of the search strategies. A concise 
 description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
@@
 \citet{rozplokhas2018improving}. 
-The next two benchmarks about quine are based on a similar test case in 
+The next two benchmarks about generating quines are based on a similar test 
+case in 
 \citet{byrd2017unified}. We modify the relational interpreters because we don't 
@@
 
-\NOTE[DPF]{Please leave ``prove'' (just here).}
-\NOTE[LKC]{OK. I won't touch it.}
-
 We acknowledge that we are making large claims about efficiency given that we 

### 2019-05-27 Paper/paper.tex
cite DFSi uKanren
cite boskin

@@
 multiple ones using the same language. (See miniKanren.org.) This has come
-about because of Hemann et al.'s work on microKanren. Also, miniKanren
+about because of \citet{Hemann_2016}'s work on microKanren, a core of 
+miniKanren comprised of only 54 LOC. Also, miniKanren
 has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
@@
 re-emerged.  It is what we are going to use instead of ``current''.}
+\NOTE[LKC]{}
 
@@
 these two uses cannot be efficient at the same time. In fact, to make one use 
-efficient, the other one must be more sluggish.
+efficient, the other one must be more sluggish. \citet{boskin} propose and 
+implement a means to eliminate or re-order disjunctive clauses to accommodate 
+varying search needs such as these.
+
+\NOTE[LKC]{I have cited Boskin in the above paragraph.}
 

### 2019-05-27 Paper/dan-sw-19-paper.tex
restructure 1st para in intro

--- 2019-05-27 Paper/paper.tex
@@
   mathescape=true,
-  literate={-inf}{{$^\infty$}}{1}{/fair}{{$_{fair}$}}{3}
+  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
                    {→}{{$\rightarrow$}}{1}
@@
 \newcommand{\reverso}{\texttt{revers$^o$}}
-\newcommand{\repeato}{\texttt{repeat$^o$}}
+\alphax\newcommand{\repeato}{\texttt{repeat$^o$}}
 \newcommand{\runstar}{\texttt{run$^*$}}
@@
 
-The strategy \textbf{b}alanced \textbf{i}nterleaving DFS (\DFSbi{}) has an 
-almost-fair \disj{} and unfair 
+The strategy \textbf{b}alanced \textbf{i}nterleaving DFS (\DFSbi{}) has an almost-fair \disj{} and unfair 
 \conj{}. The implementation of \DFSbi{} differs from 
@@
 \citet{rozplokhas2018improving}. 
-The next two benchmarks about generating quines are based on a similar test 
-case in 
+The next two benchmarks about generating quines are based on a similar test case in 
 \citet{byrd2017unified}. We modify the relational interpreters because we don't 

### 2019-05-27 Paper/paper.tex
save on-going work

@@
 
+\NOTE[LKC]{I have restructured the following paragraph.}
+
 miniKanren is a family of relational programming languages.
@@
 miniKanren and its implementation in \emph{The Reasoned Schemer} 
-and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
-Scheme, miniKanren has been implemented in many other languages, including
-multiple ones using the same language. (See miniKanren.org.) This has come
-about because of \citet{Hemann_2016}'s work on microKanren, a core of 
-miniKanren comprised of only 54 LOC. Also, miniKanren
-has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
-\citet{byrd2017unified} have 
-demonstrated that miniKanren problems that at first reading seem impossible
-are indeed possible by using a Scheme interpreter written in miniKanren, thereby
-having access to logic variables within Scheme.
-miniKanren.org contains the seeds of many interesting problems and 
-their solutions.
+and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \citet{Hemann_2016} 
+describe microKanren, a minimal core of miniKanren comprised of only 54 LOC, 
+miniKanren has been implemented in many other languages, including
+multiple ones using the same language. (e.g. OCanren\citep{kosarev2018typed}). 
+\citet{byrd2017unified} have demonstrated that miniKanren problems that at 
+first reading seem impossible are indeed possible by using a Scheme interpreter 
+written in miniKanren, thereby having access to logic variables within Scheme.
+miniKanren.org contains links to many miniKanren implementations and the seeds 
+of many interesting problems and their solutions.
+
+%miniKanren is a family of relational programming languages.
+%\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
+%miniKanren and its implementation in \emph{The Reasoned Schemer} 
+%and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
+%Scheme, miniKanren has been implemented in many other languages, including
+%multiple ones using the same language. (See miniKanren.org.) This has come
+%about because of \citet{Hemann_2016}'s work on microKanren, a core of 
+%miniKanren comprised of only 54 LOC. Also, miniKanren
+%has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
+%\citet{byrd2017unified} have 
+%demonstrated that miniKanren problems that at first reading seem impossible
+%are indeed possible by using a Scheme interpreter written in miniKanren, 
+%thereby
+%having access to logic variables within Scheme.
+%miniKanren.org contains the seeds of many interesting problems and 
+%their solutions.
 
@@
 re-emerged.  It is what we are going to use instead of ``current''.}
-\NOTE[LKC]{}
+\NOTE[LKC]{I am confused. Do you mean we are going to use
+	``BFS'' for the search strategy,
+	``BFSser'' for Seres's BFS implementation, and
+	``the improved BFS'' for our BFS implementation
+?}
 
@@
 \noindent Next, consider the following disjunction of invoking \repeato{} with 
-four 
-different letters.
+four different letters.
 
@@
 
-\subsection{fair \texttt{disj}}
+\subsection{Fair \texttt{disj}}
 
@@
 
-\subsection{fair \texttt{conj}}
+\subsection{Fair \texttt{conj}}
 \label{sec:fairconj}
@@
 A more interesting situation is when the first conjunct produces an unbounded
-number of states. Consider the following example, a naive specification of 
+number of states. Consider the following example: a naive specification of 
 fair \conj{} 
@@
 fourth and last clause runs, we know that both \sInf{} and 
-\tInf{} are ended with a thunk, and that we have swapped them. In 
+\tInf{} end with thunks, and that we have swapped them. In 
 this case, we construct a new thunk. The new thunk swaps back the two spaces in 
@@
 produce answers in a more readable order.
+
+\NOTE[LKC]{Following Boskin's suggestion, ``are ended with a thunk'' -> ``end 
+with thunks''}
 
@@
 
-\subsection{improved BFS}
+\subsection{Improved BFS}
 
@@
 answers (the bucket), and whose \texttt{cdr} is either \texttt{\#{}f} or a 
-thunk returning a space. A falsy \texttt{cdr} means the space is obviously 
-finite.
+thunk returning a space. The \texttt{\#{}f} here means the space is obviously 
+finite, just like empty list in other implementations.
+
+\NOTE[LKC]{I have rewritten the sentence about \texttt{\#{}f}.}
 
@@
 
-\subsection{compare \BFSimp{} with \BFSser{}}
+\subsection{Compare \BFSimp{} with \BFSser{}}
 
@@
 
-In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
+\NOTE[LKC]{(following Boskin's suggestion) constantly -> consistently}
+
+In general, only \DFSi{} and \DFSbi{} consistently perform well. \DFSf{}
 is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
@@
 and that \BFSimp{} is more practical than \BFSser{}.
+We acknowledge that we are making large claims about efficiency given that we 
+have just a few benchmarks, but our benchmarks cover some practically 
+interesting cases (e.g. synthesizing expressions that evaluate to \texttt{'(I 
+love you)}.
+
+\NOTE[DPF]{Finish this paragraph with a clarification and you may
+place this anywhere in the conclusion. This may require some consultation with 
+Weixi.}
+\NOTE[LKC]{Correcting.}
 
@@
 translation of their Haskell code.
-
-We acknowledge that we are making large claims about efficiency given that we 
-have just a few benchmarks, but our intuition is based on sound principles. ...
-
-\NOTE[DPF]{Finish this paragraph with a clarification and you may
-place this anywhere in the conclusion. This may require some consultation with 
-Weixi.}
-\NOTE[LKC]{I have sent an email to Weixi on the clarification.}
 

### 2019-05-27 Paper/paper.tex
remove everything

@@
-\documentclass[format=acmlarge, review=true, authordraft=true]{acmart}
+\documentclass[format=acmlarge, review=false, authordraft=false]{acmart}
 
@@
 
-\NOTE[LKC]{submission deadline: Mon 27 May 2019}
-
 \begin{abstract}
@@
 
-\NOTE[LKC]{I have restructured the following paragraph.}
-
 miniKanren is a family of relational programming languages.
@@
 %their solutions.
-
-\NOTE[DPF]{I thought we agreed to use BFSser throughout?  
-In that sense it had emerged a few days ago, and now it has
-re-emerged.  It is what we are going to use instead of ``current''.}
-\NOTE[LKC]{I am confused. Do you mean we are going to use
-	``BFS'' for the search strategy,
-	``BFSser'' for Seres's BFS implementation, and
-	``the improved BFS'' for our BFS implementation
-?}
 
@@
 varying search needs such as these.
-
-\NOTE[LKC]{I have cited Boskin in the above paragraph.}
 
@@
 
-\NOTE[LKC]{Following Boskin's suggestion, ``are ended with a thunk'' -> ``end 
-with thunks''}
-
 \section{breadth-first search}
@@
 finite, just like empty list in other implementations.
-
-\NOTE[LKC]{I have rewritten the sentence about \texttt{\#{}f}.}
 
@@
 
-\NOTE[LKC]{(following Boskin's suggestion) constantly -> consistently}
-
 In general, only \DFSi{} and \DFSbi{} consistently perform well. \DFSf{}
@@
 We acknowledge that we are making large claims about efficiency given that we 
-have just a few benchmarks, but our benchmarks cover some practically 
-interesting cases (e.g. synthesizing expressions that evaluate to \texttt{'(I 
-love you)}.
-
-\NOTE[DPF]{Finish this paragraph with a clarification and you may
-place this anywhere in the conclusion. This may require some consultation with 
-Weixi.}
-\NOTE[LKC]{Correcting.}
+have just a few benchmarks, ...
 

### 2019-05-27 Paper/paper.tex
possibly final update

@@
   mathescape=true,
-  literate={-inf}{{$^\infty$}}{1}{/fair}{{$_{fair}$}}{3}
+  literate={append-inf/fair}{{append$^\infty_{fair}$}}{8}
+           {append-map-inf/fair}{{append-map$^\infty_{fair}$}}{11}
+           {-inf}{{$^\infty$}}{1}{/fair}{{$_{fair}$}}{3}
   		   {→}{{$\rightarrow$}}{1}
@@
 \newcommand{\BFS}[0]{BFS}
-\newcommand{\BFSser}[0]{the current BFS}
-\newcommand{\BFSse}[0]{current BFS}
-\newcommand{\BFSimp}[0]{the improved BFS}
-\newcommand{\BFSim}[0]{improved BFS}
+\newcommand{\BFSser}[0]{BFS$_{ser}$}
+\newcommand{\BFSimp}[0]{BFS$_{imp}$}
 
@@
 miniKanren and its implementation in \emph{The Reasoned Schemer} 
-and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \citet{Hemann_2016} 
+and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \mbox{\citet{Hemann_2016}}
 describe microKanren, a minimal core of miniKanren comprised of only 54 LOC, 
 miniKanren has been implemented in many other languages, including
-multiple ones using the same language. (e.g. OCanren\citep{kosarev2018typed}). 
+multiple ones using the same language (e.g. OCanren\citep{kosarev2018typed}). 
 \citet{byrd2017unified} have demonstrated that miniKanren problems that at 
@@
 \citet{seres1999algebra}, a search strategy with fair \disj{} and fair \conj{}. 
-We refer to ``\BFSser{}'' as their implementation and ``the improved 
-BFS'' as our new one. We formally prove that the two implementations are 
+We refer to \BFSser{} as their implementation and \BFSimp{} as our new 
+one. We formally prove that the two implementations are 
 semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
@@
 \texttt{s}s name states; \texttt{g}s (possibly with subscript) name goals; 
-variables ending with $^\infty$ name (search) spaces. Fig.~\ref{DFSi-0} shows 
+variables ending with $^\infty$ name spaces. Fig.~\ref{DFSi-0} shows 
 the 
@@
 
-In the following subsections, we first describe \BFSimp{} implementation that 
+%In the following subsections,
+In the following paragraphs,
+we first describe \BFSimp{} implementation that 
 manages cost information in a more clear and concise way and is less 
 extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}.
-
-\subsection{Improved BFS}
 
@@
 
+\begin{figure}
+	\lstinputlisting{Figures/BFSimp-cont.rkt}	
+	\caption{New and changed functions in \BFSimp{} that implement impure 
+		features}
+	\label{BFSimp-cont}
+\end{figure}
+
 We simplify the cost information by changing the \texttt{Space} type, 
 modifying related function definitions, and introducing a few more functions.
-
 The new type of \texttt{Space} is a pair whose \texttt{car} is a list of 
@@
 finite, just like empty list in other implementations.
-
 We list functions related to the pure subset in Fig.~\ref{BFSimp}. The first 
@@
 from a thunk. The remaining functions are as before. 
-%We compare these functions 
-%with \BFSser{} in our proof.
-
 Luckily, the change in \appendInfFair{} also fixes the miserable space 
@@
 bucket of \tInf{}. 
+Functions implementing impure features are in Fig.~\ref{BFSimp-cont}. The 
+first function, \texttt{elim}, takes a space \sInf{} and two 
+continuations \texttt{fk} and \texttt{sk}. When \sInf{} contains 
+no answers, it calls \texttt{fk}. Otherwise, it calls 
+\texttt{sk} with the first answer and the rest of the space. This function is 
+similar to an eliminator of spaces, hence the name. The remaining 
+functions are as before.
 
@@
 
-\begin{figure}
-	\lstinputlisting{Figures/BFSimp-cont.rkt}	
-	\caption{New and changed functions in \BFSimp{} that implement impure 
-		features}
-	\label{BFSimp-cont}
-\end{figure}
+%\subsection{Compare \BFSimp{} with \BFSser{}}
 
-Functions implementing impure features are in Fig.~\ref{BFSimp-cont}. The 
-first function, \texttt{elim}, takes a space \sInf{} and two 
-continuations \texttt{fk} and \texttt{sk}. When \sInf{} contains 
-no answers, it calls \texttt{fk}. Otherwise, it calls 
-\texttt{sk} with the first answer and the rest of the space. This function is 
-similar to an eliminator of spaces, hence the name. The remaining 
-functions are as before.
-
-\subsection{Compare \BFSimp{} with \BFSser{}}
-
-In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
+%In this subsection,
+Now we compare the pure subset of \BFSimp{} with \BFSser{}. We 
 focus on the pure subset because \BFSser{} is designed for a pure 
@@
 		\hline 
-	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSim & \BFSse	\\
+	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSimp{} & \BFSser{} \\
 		\hline
@@
 is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
-implementations have obvious overhead in most cases. 
+implementations have obvious overhead in most cases. The reason might be that 
+those strategies %tend to keep more intermediate answers in the memory.
+tend to remember more states at the same time. 
 Among the three variants of DFS, which all have unfair \conj{}, \DFSf{} is most 
@@
 or better.
-It is hard to conclude how \disj{} fairness affects performance based on these 
-statistics.
-Fair \conj{}, however, imposes considerable overhead constantly except in 
-\appendo. The reason might be that those strategies tend to keep more 
-intermediate answers in the memory.
 
@@
 
-\citet{yang2010adventures} points out that a disjunct complex would be `fair' 
-if it were a full and balanced tree.
-
+In this section, we describe related works. 
+\citet{yang2010adventures} points 
+out that a disjunct complex would be `fair' if it were a full and balanced tree.
 \citet{seres1999algebra} describe a breadth-first search 
@@
 with a straightforward translation of their Haskell code.
-
 \citet{rozplokhas2018improving} address the non-commutativity of conjunction, 
@@
 (\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
-implementation of \BFS. These strategies have different features 
+implementation of \BFS{} (\BFSimp{}). These strategies have different features 
 in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
@@
 and that \BFSimp{} is more practical than \BFSser{}.
-We acknowledge that we are making large claims about efficiency given that we 
-have just a few benchmarks, ...
 
-% \BFSimp{}
 We prove formally that \BFSimp{} is semantically equivalent to \BFSser{}. But, 
@@
 translation of their Haskell code.
+
+Although there are very few benchmarks, this is preliminary work where we are 
+making a point that certain levels of fairness come without cost in some cases, 
+and that each of the search strategies: \DFSi, \DFSbi, \DFSf, and 
+\BFS, can co-exist inside one's head. Constructing a miniKanren with all 
+levels of fairness is future work.
 

### 2019-05-28 Paper/paper.tex
a few more corrections

@@
 multiple ones using the same language (e.g. OCanren\citep{kosarev2018typed}). 
-\citet{byrd2017unified} have demonstrated that miniKanren problems that at 
-first reading seem impossible are indeed possible by using a Scheme interpreter 
-written in miniKanren, thereby having access to logic variables within Scheme.
-miniKanren.org contains links to many miniKanren implementations and the seeds 
-of many interesting problems and their solutions.
+% \citet{byrd2017unified} have demonstrated that miniKanren problems that at 
+% first reading seem impossible are indeed possible by using a Scheme interpreter 
+% written in miniKanren, thereby having access to logic variables within Scheme.
+As demonstrated in \citet{byrd2017unified}, miniKanren can be used to
+naturally express difficult computations, such as using an interpreter
+to perform example-based program synthesis, or using a proof checker
+as a theorem prover.
+% miniKanren.org contains links to many miniKanren implementations and the seeds 
+% of many unusual problems and their solutions in miniKanren.
+The papers, talks, and tutorials on \url{miniKanren.org} present many
+other unusual problems, and their solutions in miniKanren.
 

### 2019-05-28 Paper/paper.tex
colorless

@@
   basicstyle=\ttfamily,
+  keywordstyle=\bf\ttfamily\color{black},
+  commentstyle=\color{black},
   morekeywords={run,conde,run*defrel,==,fresh,disj,conj,disj+},
@@
   		   {==}{{$\equiv$}}{1}
-  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
+  		   {conde}{{\textcolor{black}{\textbf{cond$^e$}}}}{4}
            {appendo}{{append$^o$}}{6}

### 2019-06-18 Paper/paper.tex
revise

@@
 
-To summarize our contributions, we
+%To summarize our contributions, we
+%\begin{itemize}
+%	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
+%depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
+%	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
+%a new search strategy with fair \disj{}.
+%	\item implement in a new way the standard breath-first search (\BFS) by 
+%\citet{seres1999algebra}, a search strategy with fair \disj{} and fair 
+%\conj{}. 
+%We refer to \BFSser{} as their implementation and \BFSimp{} as our new 
+%one. We formally prove that the two implementations are 
+%semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
+%is shorter.
+%\end{itemize}
+
+Our research compares four search strategies with different features in fairness
+(\autoref{table-fairness}). To summarize our contributions, we
 \begin{itemize}
 	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
-depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
-	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
-a new search strategy with fair \disj{}.
+	depth-first search (\DFSbi{})
+	\item propose and implement \textbf{f}air depth-first search (\DFSf{})
 	\item implement in a new way the standard breath-first search (\BFS) by 
-\citet{seres1999algebra}, a search strategy with fair \disj{} and fair \conj{}. 
+	\citet{seres1999algebra}
 	We refer to \BFSser{} as their implementation and \BFSimp{} as our new 
 	one. We formally prove that the two implementations are 
-semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
+	semantically equivalent, however, \BFSimp{} runs faster in all benchmarks 
+	and 
 	is shorter.
@@
 
+\begin{table}[h]
+	\begin{tabular}{|c|c|c|}
+		\hline 
+		Search Strategies & disj & conj \\ 
+		\hline 
+		\DFSi & unfair & unfair \\ 
+		\hline 
+		\DFSbi & almost-fair & unfair \\ 
+		\hline 
+		\DFSf & fair & unfair \\ 
+		\hline 
+		\BFS & fair & fair \\ 
+		\hline 
+	\end{tabular} 
+	\caption{Fairness of all search strategies}
+	\label{table-fairness}
+\end{table}
+
 \section{search strategies and fairness}
 
-In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
+% In this section, we define fair \disj{}, almost-fair \disj{} and fair 
+%\conj{}. 
+In this section, we define fairness levels in disjunction and conjunction
+implementations. Specifically, a disjunction implementation can be
+fair, almost-fair, or unfair. And a conjunction implementation can be
+fair or unfair. Fairness, intuitively, measures how evenly a search strategy 
+allocates computational resource to ``sibling'' spaces.
+
 Before going further into fairness, we give a short review of the terms:
@@
 function from a state to a space.
+Every state in the output space includes the input state and possibly more 
+constraints.
 
@@
 Although some strategies have a different level of fairness in \disj{}, they 
-have the same behavior when there is no call to a relational definition in 
-\conde{} clauses (including this case).
+have similar behavior when there is no call to a relational definition 
+in \conde{} clauses, including this case. (The only potential difference is 
+that \DFSbi{} might reorder states.)
 
@@
 Our solution requires a search strategy with \emph{fair} \conj{} to organize
-states in buckets in spaces, where each bucket contains finite states, 
+states in buckets in spaces, where each bucket is a finite collection of states
+and every space contains possibly infinite buckets,
 and 
@@
 		\hline
-		quine-1 		& 1 & 13 & 14 & 10 & - & - \\
+	\texttt{quine-1}	& 1 & 13 & 14 & 10 & - & - \\
 						& 2 & 30 & 34 & 25 & - & - \\
@@
 		\hline
-		quine-2 		& 1 & 22 & 21 & 12 & - & - \\
+	\texttt{quine-2}	& 1 & 22 & 21 & 12 & - & - \\
 						& 2 & 51 & 46 & 24 & - & - \\
@@
 		\hline
-		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   96 \\
-						& 198 &  22 &  71 & - &  374 &  652 \\
-						& 297 &  24 & 292 & - & 1668 & 3759 \\
+%		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   96 \\
+%						& 198 &  22 &  71 & - &  374 &  652 \\
+%						& 297 &  24 & 292 & - & 1668 & 3759 \\
+%		\hline
+%		'(I love you)-2 &  99 & 485 & 179 & - &   44 &   94 \\
+%						& 198 & 808 & 638 & - &  414 &  630 \\
+%						& 297 &1265 & 916 & - & 1651 & 3691 \\ 
+%		\hline 
+\texttt{'(I love you)-1}&  999 &  78 &  70 &  59 & 254 & 605 \\
+						& 1998 & 152 & 154 & 109 & 315 & 635 \\
+						& 2997 & 430 & 440 & 266 & 317 & 643 \\
 		\hline
-		'(I love you)-2 &  99 & 485 & 179 & - &   44 &   94 \\
-						& 198 & 808 & 638 & - &  414 &  630 \\
-						& 297 &1265 & 916 & - & 1651 & 3691 \\ 
+\texttt{'(I love you)-2}&  999 & 631 & 173 &  61 & 253 & 605 \\
+						& 1998 &1233 & 511 & 111 & 308 & 659 \\
+						& 2997 &2145 & 682 & 269 & 307 & 642 \\ 
 		\hline 
@@
 
-In general, only \DFSi{} and \DFSbi{} consistently perform well. \DFSf{}
-is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
-implementations have obvious overhead in most cases. The reason might be that 
-those strategies %tend to keep more intermediate answers in the memory.
-tend to remember more states at the same time. 
-Among the three variants of DFS, which all have unfair \conj{}, \DFSf{} is most 
-resistant to clause permutation in \texttt{quines}, followed by \DFSbi{} then 
-\DFSi{}. \DFSf{}, however, runs out of memory in \texttt{'(I love you)}s. In 
-contrast, \DFSbi{} is still more stable than \DFSi{}. Thus, we consider 
-\DFSbi{} a competitive alternative to \DFSi{}.
-Among the two implementations of \BFS, \BFSimp{} constantly performs as well 
-or better.
+%In general, only \DFSi{} and \DFSbi{} consistently perform well. \DFSf{}
+%is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
+%implementations have obvious overhead in most cases. The reason might be that 
+%those strategies %tend to keep more intermediate answers in the memory.
+%tend to remember more states at the same time. 
+%Among the three variants of DFS, which all have unfair \conj{}, \DFSf{} is 
+%most 
+%resistant to clause permutation in \texttt{quines}, followed by \DFSbi{} then 
+%\DFSi{}. \DFSf{}, however, runs out of memory in \texttt{'(I love you)}s. In 
+%contrast, \DFSbi{} is still more stable than \DFSi{}. Thus, we consider 
+%\DFSbi{} a competitive alternative to \DFSi{}.
+%Among the two implementations of \BFS, \BFSimp{} constantly performs as well 
+%or better.
+
+In general, variants of DFS usually performs better than BFS. The reason might 
+be that \BFS{} tends to remember more states at the same time. Among the three 
+variants of DFS, which all have unfair \conj{}, \DFSf{} is most resistant to 
+clause permutation in \texttt{quine}s and \texttt{'(I love you)}s, followed by 
+\DFSbi{} then \DFSi{}. Thus, we consider \DFSbi{} and \DFSf{} competitive 
+alternatives to \DFSi{}. Among the two implementations of \BFS, \BFSimp{} 
+constantly performs as well or better.
 
@@
 \DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
-\disj{} and fair \conj{}.
+\disj{} and fair \conj{}. No search strategy in this paper combines unfair 
+\disj{} and fair \conj{}. This is because we haven't seen a case where this 
+kind of search strategies would be interesting.
 

### 2019-06-20 Paper/paper.tex
quasi-camera-ready with line number
updates from Dan

@@
-\documentclass[format=acmlarge, review=false, authordraft=false]{acmart}
+\documentclass[acmlarge, review=true]{acmart}
+%TODO 1. delete `, review=true' ; 2. delete this line .
+\usepackage[
+    type={CC},       
+    modifier={by-sa},
+    version={4.0},   
+]{doclicense}
+
+\settopmatter{printacmref=false}
+\fancyfoot{}
+
+\makeatletter
+\def\@formatdoi#1{}
+\def\@permissionCodeOne{miniKanren.org/workshop}
+\def\@copyrightpermission{\doclicenseThis} % your choice of text
+\def\@copyrightowner{Copyright held by the author(s).} % your choice
+\makeatother
+
+\copyrightyear{2019}
+\setcopyright{rightsretained}
+
+\acmMonth{8}
+\acmArticle{1}
 
@@
 \author{Kuang-Chen Lu}
-\affiliation{Indiana University}
+\affiliation{%
+  \institution{Indiana University}
+  \country{USA}}
+\email{kl13@iu.edu}
 \author{Weixi Ma}
-\affiliation{Indiana University}
+\affiliation{%
+  \institution{Indiana University}
+  \country{USA}}
+\email{mvc@iu.edu}
 \author{Daniel P. Friedman}
-\affiliation{Indiana University}
+\affiliation{%
+  \institution{Indiana University}
+  \country{USA}}
+\email{dfried@indiana.edu}
 
@@
 \maketitle
+%\thispagestyle{empty}
+%TODO uncomment the line above to be camera-ready
 
@@
 miniKanren and its implementation in \emph{The Reasoned Schemer} 
-and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \mbox{\citet{Hemann_2016}}
+and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \mbox{\citet{Hemann_2016}}
 describe microKanren, a minimal core of miniKanren comprised of only 54 LOC, 
@@
 	\item propose and implement \textbf{f}air depth-first search (\DFSf{})
-	\item implement in a new way the standard breath-first search (\BFS) by 
-	\citet{seres1999algebra}
-	We refer to \BFSser{} as their implementation and \BFSimp{} as our new 
+	\item implement in a new way the standard breath-first search. 
+	We refer to \BFSser{} as the original implementation by 
+	\citet{seres1999algebra} and \BFSimp{} as our new 
 	one. We formally prove that the two implementations are 
@@
 		\hline 
-		\BFS & fair & fair \\ 
+		\BFSimp, \BFSser & fair & fair \\ 
 		\hline 
@@
 Now we elaborate fairness by running more queries about \repeato{}. We never 
-use \runstar{} in this paper because fairness is more interesting when we 
-have an unbounded number of answers. It is perfectly fine, however, to use 
+use \runstar{} here because fairness is more interesting when we 
+ask a bounded number of answers. It is perfectly fine, however, to use 
 \runstar{} with any search strategy.
@@
 In this section, we review the implementation of interleaving depth-first 
-search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
+search (\DFSi). We focus on parts that are relevant to other strategies. TRS2,
 chapter 10 and the appendix, ``Connecting the wires'', 
@@
 
-\section{related works}
+\section{related research}
 
-In this section, we describe related works. 
+In this section, we describe related research. 
 \citet{yang2010adventures} points 
@@
 \DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
-\disj{} and fair \conj{}. No search strategy in this paper combines unfair 
+\disj{} and fair \conj{}. No search strategy here combines unfair 
 \disj{} and fair \conj{}. This is because we haven't seen a case where this 

### 2019-06-25 Paper/paper.tex
ack and BFS
more ack
camera-readify
use abbrev

@@
-\documentclass[acmlarge, review=true]{acmart}
-%TODO 1. delete `, review=true' ; 2. delete this line .
+\documentclass[acmlarge]{acmart}
 \usepackage[
@@
 
-% We describe fairness levels in disjunction and conjunction
-% implementations.  Specifically, a disjunction implementation can be
-% fair, almost-fair, or unfair. And a conjunction implementation can
-% be fair or unfair.  We compare the fairness level of four search
-% strategies: the standard miniKanren interleaving depth-first search (\DFSi),
-% the balanced interleaving depth-first search (\DFSbi), the fair depth-first
-% search (\DFSf), and the standard breadth-first search (\BFSser).
-% \DFSbi{} and \DFSf{} are new. And we present a new, more efficient
-% and simpler implementation of \BFSser. Using quantitative evaluation, 
-% we argue that
-% \DFSbi{} and \DFSf{} are competitive alternatives to \DFSi, 
-% and that our \BFSser{} implementation is more efficient than the current one.
-
-% The syntax of a programming language should reflect its semantics. When 
-%writing 
-% a \conde{} expression in miniKanren, a programmer would expect all clauses 
-% share the same chance of being explored, as these clauses are written in 
-% parallel. The existing search strategy, interleaving depth-first search 
-% (\DFSi{}), 
-% however, prioritizes its clauses by the order how they are written down. 
-% Similarly, when a \conde{} is followed by another goal conjunctively, a 
-% programmer would expect states in parallel share the same chance of being 
-% explored. Again, the answers by \DFSi{} is different from the 
-% expectation. We have devised three new search strategies that have different 
-% level of fairness in \disj{} and \conj{}.
-%
-
 \end{abstract}
@@
 \maketitle
-%\thispagestyle{empty}
-%TODO uncomment the line above to be camera-ready
+\thispagestyle{empty}
 
@@
 multiple ones using the same language (e.g. OCanren\citep{kosarev2018typed}). 
-% \citet{byrd2017unified} have demonstrated that miniKanren problems that at 
-% first reading seem impossible are indeed possible by using a Scheme interpreter 
-% written in miniKanren, thereby having access to logic variables within Scheme.
 As demonstrated in \citet{byrd2017unified}, miniKanren can be used to
@@
 as a theorem prover.
-% miniKanren.org contains links to many miniKanren implementations and the seeds 
-% of many unusual problems and their solutions in miniKanren.
 The papers, talks, and tutorials on \url{miniKanren.org} present many
 other unusual problems, and their solutions in miniKanren.
-
-%miniKanren is a family of relational programming languages.
-%\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
-%miniKanren and its implementation in \emph{The Reasoned Schemer} 
-%and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
-%Scheme, miniKanren has been implemented in many other languages, including
-%multiple ones using the same language. (See miniKanren.org.) This has come
-%about because of \citet{Hemann_2016}'s work on microKanren, a core of 
-%miniKanren comprised of only 54 LOC. Also, miniKanren
-%has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
-%\citet{byrd2017unified} have 
-%demonstrated that miniKanren problems that at first reading seem impossible
-%are indeed possible by using a Scheme interpreter written in miniKanren, 
-%thereby
-%having access to logic variables within Scheme.
-%miniKanren.org contains the seeds of many interesting problems and 
-%their solutions.
 
@@
 
-%In the example above, the letters \texttt{c} and \texttt{d} are 
-%allocated with less resources than \texttt{a}, and thus \texttt{c} and 
-%\texttt{d} barely contribute to the result.
-
 \DFSi{} is sometimes powerful for an expert. By carefully organizing the order 
@@
 efficiently.
-
-% A little miniKanrener, however, may beg to differ--understanding
-% implementation details and fiddling with clause order is not the first
-% priority of a beginner.
 
@@
 
-%To summarize our contributions, we
-%\begin{itemize}
-%	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
-%depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
-%	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
-%a new search strategy with fair \disj{}.
-%	\item implement in a new way the standard breath-first search (\BFS) by 
-%\citet{seres1999algebra}, a search strategy with fair \disj{} and fair 
-%\conj{}. 
-%We refer to \BFSser{} as their implementation and \BFSimp{} as our new 
-%one. We formally prove that the two implementations are 
-%semantically equivalent, however, \BFSimp{} runs faster in all benchmarks and 
-%is shorter.
-%\end{itemize}
-
 Our research compares four search strategies with different features in fairness
@@
 	\citet{seres1999algebra} and \BFSimp{} as our new 
-	one. We formally prove that the two implementations are 
+	one. When we use BFS without subscripts, we mean both \BFSser{} and 
+	\BFSimp{}.
+	We formally prove that the two implementations are 
 	semantically equivalent, however, \BFSimp{} runs faster in all benchmarks 
@@
 		\hline 
-		\BFSimp, \BFSser & fair & fair \\ 
+		\BFS & fair & fair \\ 
 		\hline 
@@
 use \runstar{} here because fairness is more interesting when we 
-ask a bounded number of answers. It is perfectly fine, however, to use 
+ask for a bounded number of answers. It is perfectly fine, however, to use 
 \runstar{} with any search strategy.
@@
 
-In this section, we review the implementation of interleaving depth-first 
-search (\DFSi). We focus on parts that are relevant to other strategies. TRS2,
+In this section, we review the implementation of \DFSi{}. We focus on parts 
+that are relevant to other strategies. TRS2,
 chapter 10 and the appendix, ``Connecting the wires'', 
@@
 
-The strategy \textbf{b}alanced \textbf{i}nterleaving DFS (\DFSbi{}) has an 
-almost-fair \disj{} and unfair 
-\conj{}. The implementation of \DFSbi{} differs from 
+\DFSbi{} has almost-fair \disj{} and unfair \conj{}. Its 
+implementation differs from 
 \DFSi{}'s in the \disj{} macro. When there are one or more disjunctive 
@@
 
-Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
-implementation of \DFSf{} differs from \DFSi{}'s in 
+\DFSf{} has fair \disj{} and unfair \conj{}. Its 
+implementation differs from \DFSi{}'s in 
 \disjtwo{} (Fig.~\ref{fDFS}). The new \disjtwo{} calls a new and 
@@
 \disj{} and fair \conj{}. No search strategy here combines unfair 
-\disj{} and fair \conj{}. This is because we haven't seen a case where this 
-kind of search strategies would be interesting.
+\disj{} and fair \conj{}. This is because we haven't seen a case where these 
+kinds of search strategies would be interesting.
 
@@
 
+We thank the program committee for their insightful observations. We also thank 
+our reviewers, both known and anonymous, for their corrections and suggestions.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-06-27 Paper/paper.tex
clean up repo
(formal) proof --> proofs

@@
 \end{itemize}
+
+Source code of implementations, examples, benchmarks, and formal proofs are 
+available at the 
+following URL:
+
+\begin{center}
+\url{https://github.com/LuKC1024/Towards-a-miniKanren-with-fair-search-strategies}
+\end{center}
 
@@
 
-%\subsection{Compare \BFSimp{} with \BFSser{}}
-
-%In this subsection,
 Now we compare the pure subset of \BFSimp{} with \BFSser{}. We 
@@
 are semantically equivalent, since the result of \texttt{(run n ? g)} is 
-the same either way. (See supplements for the formal proof.) To 
-compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See 
-supplements for the translated code). The translation is direct due to the 
+the same either way. (See the GitHub repository for the formal proofs.) To 
+compare efficiency, we translate \BFSser{}'s Haskell code into Racket. (See the 
+GitHub repository for the translated code.)
+The translation is direct due to the 
 similarity of the two relational programming systems. The translated code is 
@@
 out that a disjunct complex would be `fair' if it were a full and balanced tree.
-\citet{seres1999algebra} describe a breadth-first search 
-strategy. We present another implementation. Our implementation is semantically 
+\citet{seres1999algebra} describe BFS. We present another implementation. Our 
+implementation is semantically 
 equivalent to theirs. But, ours is shorter and performs better in comparison 
@@
 
-We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
-new definition of fair \conj{}. Our definition of fair \conj{} is orthogonal 
-with completeness.
+%We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
+%new definition of fair \conj{}. Our definition of fair \conj{} is orthogonal 
+%with completeness.
 
-We devise two new search strategies (i.e., balanced interleaving DFS 
-(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
-implementation of \BFS{} (\BFSimp{}). These strategies have different features 
-in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
+We analyze the definitions of fairness. Implementation of \disj{} can be fair, 
+almost-fair, or unfair, depending on how evenly it allocates computational 
+resources to spaces related to disjunctive goals. Implementation of \conj{}
+can be fair or unfair, depending on how evenly it allocates computational 
+resources to spaces related to states in the same bucket. Our definition of 
+fair \conj{}, unlike the one by \citet{seres1999algebra}, is orthogonal with 
+completeness.
+
+%We devise two new search strategies (i.e., balanced interleaving DFS 
+%(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
+%implementation of \BFS{} (\BFSimp{}). These strategies have different features 
+%in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
+%\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
+%\disj{} and fair \conj{}. No search strategy here combines unfair 
+%\disj{} and fair \conj{}. This is because we haven't seen a case where these 
+%kinds of search strategies would be interesting.
+
+We devise two new search strategies (i.e., \DFSbi{} and \DFSf{}) and devise a 
+new implementation of \BFS{}, \BFSimp{}. These strategies have different 
+features in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
 \DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
@@
 
-Our quantitative evaluation shows that \DFSbi{} is a competitive 
-alternative to \DFSi{}, the current miniKanren search strategy,
-and that \BFSimp{} is more practical than \BFSser{}.
+Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
+alternatives to \DFSi{}, the current miniKanren search strategy, and that 
+\BFSimp{} is more practical than \BFSser{}.
 
